### 2017-08-10 stp/paper_aaai/main.tex
begining of paper

\def\year{2018}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
\usepackage{aaai18}  %Required
\usepackage{times}  %Required
\usepackage{helvet}  %Required
\usepackage{courier}  %Required
\usepackage{url}  %Required
\usepackage{graphicx}  %Required
\frenchspacing  %Required
\setlength{\pdfpagewidth}{8.5in}  %Required
\setlength{\pdfpageheight}{11in}  %Required
\usepackage{spverbatim}
\usepackage{fancyvrb}

\usepackage{color}
\usepackage{xcolor}
\usepackage{amsmath,amsthm,stmaryrd}
\usepackage{algpseudocode}
\usepackage{algorithm}
\algrenewcommand\algorithmiccomment[2][\footnotesize]{{#1\hfill\(\triangleright\)
 #2}} %\normalsize
\usepackage{amssymb}
\usepackage{textcomp}

\usepackage{tikz}
\usetikzlibrary{shadows.blur}
\usetikzlibrary{shapes.symbols}
\usetikzlibrary{arrows,shapes,decorations.pathmorphing}
\usetikzlibrary{positioning}
\usetikzlibrary{decorations.text}
\usetikzlibrary{decorations.pathmorphing}
\tikzstyle{class}=[draw,ellipse,align=center,fill=green!25]
\tikzstyle{data}=[draw,rectangle,align=center,black!70]
\tikzstyle{hasaA} = [>=stealth',draw,dashed,-,black!70]
\tikzstyle{hasaC} = [>=stealth',draw,thick,-, black]
\tikzstyle{isa} = [>=latex,draw,double,black!90,double distance=1mm]

\newcommand{\authornote}[3]{
  {\fbox{\sc 
  #1}:$\blacktriangleright$\textcolor{#2}{\small{#3}}$\blacktriangleleft$}%
}
\newcommand{\pds}[1]{\authornote{PDS}{purple}{#1}}
\newcommand{\pjs}[1]{\authornote{PJS}{red}{#1}}
\newcommand{\gkg}[1]{\authornote{GKG}{brown}{#1}}
\newcommand{\ddg}[1]{\authornote{DDG}{blue}{#1}}
\newcommand{\npd}[1]{\authornote{NPD}{orange}{#1}}

\newcommand{\minizinc}{\textsc{MiniZinc}}
\newcommand{\chuffed}{\textsc{Chuffed}}
\newcommand{\relonto}{\textsc{Rel2Onto}}

\newcommand{\etal}{\textit{et al.}}

\newcommand{\code}[1]{\texttt{#1}}

%PDF Info Is Required:

%  \pdfinfo{
%/Title (2018 Formatting Instructions for Authors Using LaTeX)
%/Author (AAAI Press Staff)}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Using Machine Learning and Constraint Programming to Solve the 
Relational-To-Ontology Mapping Problem}
\author{}
\maketitle
\begin{abstract}
The problem of integrating heterogeneous data sources in an ontology is of high 
relevance in the database field. Several techniques exist to approach this 
problem. Nonetheless, side constraints on the data integration cannot be easily 
integrated with these tools and thus the results may be inconsistent. We 
present a new approach that combines Machine Learning and 
Constraint Programming techniques, by modelling the data integration problem as 
a Steiner Tree Problem in a weighted graph. We show that through this approach 
we can achieve better precision, recall and speed compared to state-of-the-art 
approaches. We provide a comprehensive set of experiments supporting our 
findings.
\end{abstract}

\section{Introduction}
The problem of integrating heterogeneous data sources is a long standing issue 
in the database research field and is of high relevance in many real-world 
domains.
A common approach to tackle this problem is to design a global model and to
construct source descriptions which specify mappings between the sources and
the global model \cite{doan2012principles}.

In our case, we would like this global model to account
not only for structural properties of the original data sources, but also to 
include the semantics which is usually implicitly present in the sources. In 
other words, we want to build a semantic model which describes the data sources 
in terms of concepts and relationships defined by an ontology. We can view this
semantic model as a graph with ontology classes as the nodes and ontology
properties as the links between the nodes \cite{Taheriyan2013}. Henceforth, we 
focus on a specific data integration problem: automatically mapping relational 
data sources onto a user provided ontology.

In this paper we use Machine Learning techniques (ML) to learn mapping rules 
from already mapped instances. To this end we formulate the 
Relational-To-Ontology Mapping Problem (\relonto{})
as a Minimum Cost Steiner Tree Problem (STP) with side constraints.
This problem is formulated for an \emph{integration graph} which includes the 
attributes from the new source as well as ontology classes and properties. We
apply machine learning techniques to assign costs to the links in the 
constructed integration graph.

The contributions of this work are:
\begin{itemize}
	\item \ddg{TODO}
\end{itemize}

Section bla  presents bla bla... \ddg{TODO}

\section{Previous Work}
\ddg{rewrite, add more}
One of the standard approaches to solve the relational-to-ontology (\relonto{})
mapping problem is to apply Knowledge Representation and Reasoning (KR)
techniques. The main idea of this approach is to exploit constraints specified 
within relational schemata and ontologies. Several mapping generation
tools based on this approach already exist, for example, BootOX, MIRROR,
COMA++ \cite{pinkel2016rodi}. The issue is though that constraints may be 
inconsistent or absent completely \ddg{Why?}. We suggest to use ML techniques 
to overcome this hurdle.

\cite{taheriyan2016learning} \ddg{Isn't this really similar??}

\section{Motivating Example}
\ddg{TODO}

\section{Problem Statement}
We follow the definitions proposed by Doal \etal{} \cite{doan2012principles}.

\begin{figure}[ht]
\centering
\begin{tikzpicture}
	\node[class] (pe) at (0,0)  {Person};
	\node[class] (co) at (0,-3) {Organisation};
	\node[class] (ev) at (3.5,1) {Event};
	\node[class] (pl) at (5,-1) {Place};
	\node[class] (ci) at (3,-3) {City};
	\node[class] (st) at (5,-3) {State};

	\path[hasaC,->] (pe) edge [bend left= -30] 
	node [midway, above, sloped] {worksFor} (co) ;
	\path[hasaC,->] (co) edge [bend left= -30] 
	node [midway, above, sloped] {ceo} (pe) ;

	\path[hasaC,->] (co) edge [] 
	node [midway, above, sloped] {location} (pl) ;

	\path[hasaC,->] (pe) edge [bend left = -20] 
	node [midway, above, sloped] {bornIn} (pl) ;
	\path[hasaC,->] (pe) edge [bend left = 0] 
	node [midway, above, sloped] {livesIn} (pl) ;

	\path[hasaC,->] (ev) edge [bend left = -20] 
	node [midway, above, sloped] {organizer} (pe) ;
	\path[hasaC,->] (ev) edge [bend left = 0] 
	node [midway, above, sloped] {location} (pl) ;

	\path[hasaC,->] (pl) edge [out=20,in=0,looseness=8] 
	node [midway, above, sloped] {nearby} (pl) ;
	\path[hasaC,->] (pl) edge [out=45,in=65,looseness=8] 
	node [midway, above, sloped] {partOf} (pl) ;

	\path[hasaC,->] (ci) edge  []
	node [midway, above, sloped] {state} (st) ;

	\path[isa,->] (ci) -- node [] {} (pl) ;
	\path[isa,->] (st) -- node [] {} (pl) ;

	\path[draw,hasaA,->] (pe) edge [bend left = 10] 
	node [midway, above, sloped] {name} (-0.5,2);
	\path[draw,hasaA,->] (pe) edge [bend left = 0] 
	node [midway, below, sloped] {birthDate} (0,2);

	\path[draw,hasaA,->] (co) edge [bend left = 0] 
	node [midway, below, sloped] {name} (-1,-5);
	\path[draw,hasaA,->] (co) edge [bend left = 0] 
	node [midway, above, sloped] {phone} (0,-5);
	\path[draw,hasaA,->] (co) edge [bend left = 0] 
	node [midway, above, sloped] {email} (1,-5);

	\path[draw,hasaA,->] (ev) edge [bend left = 0] 
	node [midway, below, sloped] {startDate} (2.5,3.2);
	\path[draw,hasaA,->] (ev) edge [bend left = 0] 
	node [midway, above, sloped] {endDate} (3.5,3.2);
	\path[draw,hasaA,->] (ev) edge [bend left = 0] 
	node [midway, below, sloped] {title} (4.5,3.2);

	\path[draw,hasaA,->] (pl) edge [bend left = 0] 
	node [midway, above, sloped] {name} (6.5,-1.8);
	\path[draw,hasaA,->] (pl) edge [bend left = 0] 
	node [midway, above, sloped] {postalCode} (6,-3);

\end{tikzpicture}
\caption{Example of ontology
(`\tikz{ \node[class] () at (0,0)  {};}' are Classes, `\tikz{ \path[hasaC,->] 
(0,1) -- (3ex,1);}' means ``has a Class property'', 
`\tikz{ \path[hasaA,->] (0,1) -- (3ex,1);}' means ``has a data property'' and 
`\tikz{ \path[isa,->] (0,1) -- (3ex,1);}' means ``is a'' ).
}
\label{FIG:onto}
\end{figure}

An ontology $\mathcal{O}$ is a specification of classes of objects and their 
data properties and relationships between them. An example of an ontology is 
given 
in Fig. \ref{FIG:onto}. A Class in an ontology can have \emph{data properties} 
or 
\emph{class properties}. For example an ``Organisation'' has a ``Person'' 
(which is a class with its own properties), and it has a ``name'' (which 
is a data property). Also, a Class can be a subclass of another Class. For 
example ``Cities'', ``Countries'' or ``States'' are all ``Places''. A subclass 
inherits all the properties of the parent class.

A \emph{semantic model} $m$ is a directed graph with two types of nodes: 
\emph{class nodes} and \emph{data nodes}. We denote them as $\mathcal{C}_m$ and 
$\mathcal{D}_m$ respectively. We define $\mathcal{N}_m = \mathcal{C}_m \cup 
\mathcal{D}_m$. $ \mathcal{C}_m$ corresponds to classes in the ontology 
$\mathcal{O}$. $\mathcal{D}_m$ corresponds to data 
properties in the ontology. The edges in the semantic model correspond to 
relationships in the ontology, as shown if Figures \ref{FIG:onto} and 
\ref{FIG:sem}.

\begin{figure}[ht]
\centering
\begin{tikzpicture}
\begin{scope}
	\node[class] (pe) at (0,0)  {\small Person};
	\node[class] (co) at (6,0) {\small Org.};
	\node[class] (ci) at (2.5,0) {\small City};
	\node[class] (st) at (4.5,0) {\small State};

	\node[data] (pen) at (-1,-1) {\scriptsize Person.name};
	\node[data] (peb) at (1,-1) {\scriptsize Person.birthDate};
	\node[data] (cin) at (3,-1) {\scriptsize City.name};
	\node[data] (stn) at (4.5,-1) {\scriptsize State.name};
	\node[data] (con) at (6,-1) {\scriptsize Org.name};

	\path[hasaC,->] (pe) edge [bend left= 20] 
	node [midway, above, sloped] {worksFor} (co) ;

	\path[hasaC,->] (pe) edge [bend left = 0] 
	node [midway, above, sloped] {bornIn} (ci) ;

	\path[hasaC,->] (ci) edge  []
	node [midway, above, sloped] {state} (st) ;

	\path[draw,hasaA,->] (pe) -- (pen);
	\path[draw,hasaA,->] (pe) -- (peb);

	\path[draw,hasaA,->] (co) -- (con);

	\path[draw,hasaA,->] (ci) -- (cin);

	\path[draw,hasaA,->] (st) -- (stn);
\end{scope}
\begin{scope}[yshift=-60]
	\node[class] (pl) at (-1,0)  {\small City};
	\node[class] (pe) at (3,0)  {\small Person};
	\node[class] (co) at (1,0) {\small Org.};
	\node[class] (ev) at (6,0) {\small Event};

	\node[data] (pen) at (2.5,-1) {\scriptsize Person.name};
	\node[data] (evs) at (4.2,-1) {\scriptsize Event.startDate};
	\node[data] (eve) at (6,-1) {\scriptsize Event endDate};
	\node[data] (con) at (1,-1) {\scriptsize Org.name};
	\node[data] (pln) at (-1,-1) {\scriptsize City.name};

	\path[hasaC,->] (co) edge [bend left= 0] 
	node [midway, above, sloped] {ceo} (pe) ;

	\path[hasaC,->] (ev) edge [bend left = 0] 
	node [midway, above, sloped] {organizer} (pe) ;

	\path[hasaC,->] (co) edge [bend left = -10] 
	node [midway, above, sloped] {location} (pl) ;

	\path[draw,hasaA,->] (pl) -- (pln);

	\path[draw,hasaA,->] (pe) -- (pen);

	\path[draw,hasaA,->] (co) -- (con);

	\path[draw,hasaA,->] (ev) -- (evs);
	\path[draw,hasaA,->] (ev) -- (eve);

\end{scope}
\end{tikzpicture}
\caption{Examples of two semantic models.}
\label{FIG:sem}
\end{figure}

A \emph{source} $s$ is a $n$-ary relation with a set of attributes 
$\mathcal{A}_s = 
(a_1,...,a_n)$.

An \emph{attribute mapping} function $\phi : \mathcal{A}_s \mapsto 
\mathcal{D}_m$ is a function which
maps the attributes of the source $s$ into the nodes of the semantic model $m$. 
It can be a partial mapping, meaning that only some of the attributes
are connected to the nodes of $m$.

A \emph{source description} is a triple $\delta = (s, m, \phi)$ where $s$ is a 
source, 
$m$ is a semantic
model, and $\phi$ is an attribute mapping.

Our problem can be stated now the following way. We have an ontology 
$\mathcal{O}$ and a set of source descriptions $S_T = \{(s_1, m_1, \phi_1),..., 
(s_l, m_l, \phi_l)\}$.
Given a new source $s^\star$, we want to build a semantic model $m^\star$ and 
an attribute mapping function $\phi^\star$ such that 
$\delta^\star = (s^\star,m^\star,\phi^\star)$ is an \emph{appropriate} source 
description. We
use the term appropriate since there might be many such triples which are
well-formed source descriptions, but only one or a few will capture the intended
meaning of the source. Our goal is to automatically build $\delta^\star$ such 
that it minimizes the \emph{graph edit distance} (GED) from the semantic model 
$m^\star$ to the semantic model $m^\dag$ that the user considers correct.

The GED is a measure of similarity between two graphs defined as follows for 
two graphs $g_1$ and $g_2$: $GED(g_1,g_2) = min_{(e_1 ,...,e_k)\in P} 
\sum_{i=1}^{k}c(e_i)$ where $P$ denotes the set of edit paths transforming 
$g_1$ into (a graph
isomorphic to) $g_2$ and $c(e) \geq 0$ is the cost of each graph edit operation 
$e$. Graph edit operations include among others node insertion, edge deletion, 
etc. \cite{gao2010survey}. In practice, we use some approximation measures of 
the graph edit distance. \ddg{which approx?}

\section{ML for Training on Source Descriptions \ddg{Better title than this 
please...}}

\subsection{Semantic Labeling}
The semantic types $\mathcal{L_O} = \{l_1, l_2, ..., l_p\}$ of an ontology 
correspond to all pairs $(c,d)$, where $c$ is a Class in $\mathcal{O}$, and $d$ 
is a data property of that class (including inherited properties). 
For example, from the ontology in Fig. \ref{FIG:onto}, we would get types such 
as 
(City,name) and (State,name).

The first step to model the semantics of a new source $s^\star$ is to recognize 
the semantic types present in the source. 
We call this step \emph{semantic labeling}, which involves giving a confidence 
value to a match occurring between an attribute from $s^\star$ and type $l \in 
\mathcal{L_O}$. \ddg{CHECK!}

We formulate the problem of semantic labeling as a multi-class classification
problem. The known source descriptions $S_T$ provide us the training sample. We
compute a feature vector for each source \ddg{Which features?} attribute and 
associate the known
semantic type with the corresponding feature vector. We train random forest
on this sample. Then we use the learnt model to classify attributes in the new
source.

In such way, we learn the mapping $\psi : \mathcal{A_s} \times \mathcal{L_O} 
\mapsto [0, 1]$,
where $\psi(a_i,l_j)$ indicates the confidence of the attribute $a_i$ to be 
mapped to the semantic type $l_j$.

\ddg{IMPORTANT: Do we keep all of them, or only the top $k$ with most 
confidence? If so, 
what is $k$?}

\subsection{Alignment Graph}

To provide an integrated view over the known sources descriptions $S_T$, we 
need to align their semantic models as well as all considered semantic 
types. This is achieved by constructing an \emph{alignment graph}.

The alignment graph is a directed weighted graph $\mathcal{G_O} = 
(\mathcal{V_O},\mathcal{E_O})$ built on top 
of the known semantic models and expanded using the semantic types 
$\mathcal{L_O}$ and the domain ontology $\mathcal{O}$. Similar to a semantic 
model, $\mathcal{G_O}$ contains both class and data nodes. The links correspond 
to properties in  $\mathcal{O}$ and are weighted \cite{taheriyan2016learning}.

The algorithm we used to construct $\mathcal{G_O}$ is the same as Taheriyan 
\etal{} and is described in detail in the cited paper 
\cite{taheriyan2016learning}.
Briefly, the algorithm has three parts:
\begin{enumerate}
\item Adding the known semantic models.
\item Adding the semantic types learned for the target source. \ddg{TODO: see 
Important note above}
\item Expanding the graph using the domain ontology $\mathcal{O}$.
\end{enumerate}

Note how the alignment graph contains data nodes that correspond to at least 
some of the semantic types. For instance, it could contain two nodes 
$City.name$ and $State.name$ rather than just one node $name$ connected to two 
nodes $City$ and $State$. We say these nodes are \emph{induced} into the 
alignment graph by the semantic types, we note them $\mathcal{D_{G_O}}$ and we 
call them \emph{data nodes} of the alignment graph.

The graph is weighted by a function $w_\mathcal{O} : \mathcal{E_O} \mapsto 
\mathbb{R}$ in 
such a way that links which are present in
the known semantic models have lower weights than those 
which are inferred from the ontology. As we will see int he next section, this 
makes links present in semantic models more attractive. \ddg{How exactly are 
they weighted?}

An example alignment graph is illustrated in Fig. \ddg{todo}. Black links 
correspond to the links which are supported by the known semantic models. Blue
links are inferred from the ontology $\mathcal{O}$ and can be assigned the 
maximum weight $w_max$ \ddg{where does this weight come from?} .

\subsection{Frequent Subgraph Pattern Mining}

\ddg{TODO}

\section{Steiner Tree Formulation}

The Steiner Tree Problem (STP) is defined the following way. Given a graph $G =
(V, E)$ and a subset of its nodes $T \subseteq V$ , called \emph{terminals}, a 
Steiner Tree $G_s = (V_s, E_s )$ is a tree such that $T \subseteq V_s \subseteq 
V$ and $E_s \subseteq E$. In other words, $G_s$ spans all the nodes in $T$ and 
may include additional nodes from $V$, in particular to ensure the 
connectedness of the constructed tree.

To formulate the \relonto{} schema mapping problem as a STP for a new source 
$s^\star$, we construct the 
\emph{integration graph} $\mathcal{I}_\mathcal{O}^{s^\star} = 
(\mathcal{V}_\mathcal{O}^{s^\star},\mathcal{E}_\mathcal{O}^{s^\star})$, with 
nodes $\mathcal{V}_\mathcal{O}^{s^\star} = \mathcal{V_O} \cup 
\mathcal{A}_{s^\star}$, 
edges $\mathcal{E}_\mathcal{O}^{s^\star}$.

The set of edges $\mathcal{E}_\mathcal{O}^{s^\star}$ is constructed by using 
all the edges in the alignment 
graph, and edges connecting each attributes of $s^\star$ to the nodes 
$\mathcal{D_{G_O}}$ of the 
alignment graph \emph{induced} by the semantic labels. We call this last set 
of edges $\mathcal{M}_\mathcal{O}^{s^\star}$ (for ``matches''). Thus, 
$\mathcal{E}_\mathcal{O}^{s^\star} = 
\mathcal{E_O} \cup \mathcal{M}_\mathcal{O}^{s^\star}$.

We associate a weighting function  $w_\mathcal{I} : E \mapsto \mathbb{R}^+$ to 
the integration graph. For an edge $e \in \mathcal{E_O}$, $w_\mathcal{I}(e) = 
w_\mathcal{O}(e)$. For an edge $e 
\in \mathcal{M}_\mathcal{O}^{s^\star}$ connecting attribute $a_i$ to the node 
$l_j$ induced by the semantic model, $w_\mathcal{I}(e) = - 
ln(\psi(a_i,l_i))$. \ddg{CHECK!}

An example of integration graph can be found in Fig. \ddg{TODO}.

Note that, although the alignment graph is directed, the semantic models are 
not necessarily rooted directed trees, therefore the directions of the edges is 
ignored for the STP model (and are all treated as undirected edges).

\section{Modeling as a Constraint Optimization Problem}

\subsection{Definitions}
A Constraint Satisfaction Problem (CSP) is a tuple $P = (\boldsymbol{v},D,C)$ 
where $\boldsymbol{v}$ is a 
set of \emph{variables}, $D$ is a set of unary constraints over 
$\boldsymbol{v}$ specifying 
the \emph{domain} of these variables, $C$ is a set of $n$-ary 
\emph{constraints} over variables $\boldsymbol{v}$.
A valuation $\theta(\boldsymbol{v})$ is a mapping from the set of variables to 
values in $D$. If there exist a valuation $\theta^\star$ such that all 
variables map 
to exactly one value, and all the constraints in $D\cup C$ are satisfied by the 
valuation, then $\theta^\star$ is a \emph{solution} to $P$.

A Constraint Optimization Problem (COP) is a CSP with an additional 
\emph{objective function} $o : \boldsymbol{v} \mapsto \mathbb{R}$ and a 
\emph{sign} which is either \verb|minimize| or \verb|maximize|.

A typical example of COP is the Traveling Salesman Problem, where we need to 
find a route that visits all cities in a region exactly one and is of minimal 
length.

\subsection{Constraint Programming}
Constraint Programming (CP) allows the user to model a CSP or COP and give it 
to a 
solver that will find a solution to the CSP, or will report unsatisfiability if 
no such valuation exists. In the case of COPs, the solver will try to optimize 
the objective function and prove optimality as well.

Briefly, the way a CP solver works is by assigning a value to each variable of 
$\boldsymbol{v}$ from $D$ in turn. At each iteration it will check whether any 
constraint in $C$ is violated, in which case it will backtrack to change it's 
last decision. The choice of the order of the variables to be assigned, and the 
choice of the value to be assigned to each variable is called the \emph{search 
strategy}.

Since only using a backtracking algorithm would have a prohibitive cost, CP 
uses a combination of search and \emph{propagation}. The latter is achieved by 
\emph{propagating} the last decision made via specialized algorithms called 
\emph{propagators}. A propagator is a function $p : (v, D_v) \mapsto D_v'$ that 
takes a subset of the variables of the problem $v \subseteq \boldsymbol{v}$ and 
the domain of those variables $D_v$ and returns a new domain for thus variables 
such that $D_v' \sqsubseteq D$. That is, a propagator removes values form the 
domains of variables (when possible). For a propagator to be correct, it must 
not remove a value of the domain of a variable if such value could participate 
in a solution given the decisions already made.

Global constraints are higher order constraints that enforce a complicated 
constraint over a set ov variables. Typical examples of this is enforcing that 
a set of variables take different values, or that they describe a path a in a 
graph. Although it is possible to express these constraints with a conjunction 
of simple constraints, it is often the case that specific algorithms for these 
constraints perform substantially better than a decomposition approach (e.g. 
\cite{regin1994filtering}). A wide 
list of these global constraints can be found in \cite{beldiceanu2012global}.

\subsubsection{Example} Consider the toy problem $P$ over variables $a$ and $b$ 
such that $a \in \{2,3,4\}$, $b \in \{1,2,3\}$. Let $C = \{a + 2b \leq 4, a 
\neq b\}$ the constraints to be satisfied. If the search step decides that $a = 
2$, then (i) $a \neq b \Rightarrow b \in \{1,3\}$ and (ii) $a + 2b \leq 4  
\Rightarrow b \in \{1\}$. Thus we automatically know that $b = 1$ without never 
trying any other of its original possible values.

\subsection{Modeling \relonto{} in CP}
In order to model this problem we used the \minizinc{} language, and the 
\chuffed{} solver because it has a global constraint implemented for Steiner 
Tree Problems \cite{deuna2016steiner}.

We need to build a subgraph $T^\star= (V^\star, E^\star)$ 
that is a subset of the integration graph 
$\mathcal{I}_\mathcal{O}^{s^\star}$ for the new source $s^\star$. The tree will 
be used to build the source description $\delta^\star = (s^\star, m^\star, 
\phi^\star)$. 
In particular, $(\mathcal{V_O} \cap V^\star,\mathcal{E_O} \cap E^\star)$ 
corresponds to the semantic model, and 
$(\mathcal{A}_{s^\star},\mathcal{M}_\mathcal{O}^{s^\star} \cap E^\star)$ 
corresponds to 
the attribute mapping function.

The solution $T^\star$ must satisfy the following constraints:
\begin{enumerate}
	\item $T^\star$ must be a tree (connected acyclic graph).
	\item $\forall a \in \mathcal{A}_{s^\star}, a\in V^\star$.
	\item $\forall a \in \mathcal{A}_{s^\star}, degree(a) = 1$.
	\item $\forall n \in \mathcal{D_{G_O}}, degree(a) \in 
	\{0,2\}$
	\item $\forall n \in \mathcal{D_{G_O}} \cap V^\star, 
	degree(a) = 2$
\end{enumerate}

Because attributes must be connected to exactly one node of the alignment 
graph, and that node will be in $\mathcal{D_{G_O}} \cap V^\star$ 
then the part of the problem between attribute nodes and the alignment graph is 
actually a matching problem. Each attribute must match exactly to one node of 
$\mathcal{D_{G_O}}$.

Because there are global constraints in CP specialized in matching 
\cite{regin1994filtering}, we split the problem into two parts: (i) the 
\verb|steiner_tree| global constraint will only deal with the part of the 
integration graph that corresponds to the alignment graph, and the 
\verb|alldifferent| global constraint will deal with he matching part of the 
problem.

We use the following variables to represent the tree $T^\star$: Boolean 
variables $c_n,\forall n \in 
\mathcal{V_O}$, $c_e, \forall e \in	\mathcal{E_O}$ and an array of variables 
$match$ indexed by the set of attributes of $s^\star$. The combination of these 
sets fo variables define the value of $T^\star$: $c_n = \mathit{true}$ means 
that $n \in V^\star$, $c_e = \mathit{true}$ means that $e \in E^\star$ and 
$match[a] = d$ (for $a \in \mathcal{A}_{s^\star}$ and $d \in 
\mathcal{D_{G_O}}$) means that the edge $(a,d) \in 
\mathcal{M}_\mathcal{O}^{s^\star}$ is part of $E^\star$.

\begin{flalign}
	& \text{Minimize~~} w_{STP} + w_{ADIFF}
	%\sum_{e \in \mathcal{E}_\mathcal{O}}c_e * 
	%w_\mathcal{I}(e) + \sum_{e \in \mathcal{M}_\mathcal{O}^{s^\star}} c_e * 
    %		w_\mathcal{I}(e)
	\label{EQ:obj}&&\\
	&\text{such that~~}  \nonumber&& \\
	& \textit{steiner\_tree}(\{c_n| n \in \mathcal{V_O}\},\{c_e| e \in 
	\mathcal{E_O}\},\mathcal{G_O},w_\mathcal{O},w_{STP})  \label{EQ:stp} &&\\
	&\forall d \in \mathcal{D_{G_O}}, degree(d) \leq 1 \label{EQ:deg1}&&\\
	&\forall d \in \mathcal{D_{G_O}}, c_d \Leftrightarrow degree(d) = 1 
	\label{EQ:deg2}&&\\
	&\forall a \in \mathcal{A}_{s^\star}, match[a] \in \{ d | (a,d)\in 
	\mathcal{M}_\mathcal{O}^{s^\star} \} \label{EQ:matchdom}&&\\
	& \textit{alldifferent}(match) \label{EQ:alld}&& \\
	& \forall a \in \mathcal{A}_{s^\star}, c_{match[a]} = \mathit{true} 
	\label{EQ:map}&&\\
	& w_{ADIFF} = \sum_{(a,d) \in \mathcal{M}_\mathcal{O}^{s^\star}} 
	w_\mathcal{I}(~(a,d)~) * \llbracket match[a] = d\rrbracket 
	\label{EQ:matchcost}
\end{flalign}

Eq. \ref{EQ:obj} is the objective function, we are trying to minimize the cost 
of $T^\star$. Eq. \ref{EQ:stp} enforces that the solution $T^\star$ is indeed a 
tree defined by the $c_n$ and $c_e$ variables, subgraph of the alignment graph 
and of total weight $w_{STP}$. Equations \ref{EQ:deg1} and \ref{EQ:deg2} ensure 
that if a data node of the alignment graph is selected, then at most one edge 
reaches it (from the side of the alignment graph) and otherwise it is 
disconnected. Eq. \ref{EQ:matchdom} ensures that the domain of each variable in 
the array $match$ corresponds to a subset of data nodes of the alignment graph 
for which there is an edge connecting to the attribute at hand. Eq. 
\ref{EQ:alld} ensure that each attribute is mapped to exactly one data node of 
the alignment graph. Equations \ref{EQ:matchdom} and \ref{EQ:alld} ensure that 
the matching part of the problem is a bijection. Eq. \ref{EQ:map} ensures that 
if a data node of the alignment graph has been mapped to some attribute, then 
that data node must be in the solution tree, and vice-versa. Eq. 
\ref{EQ:matchcost} computes the cost $w_{ADIFF}$ of the matches.

\section{Results}

\subsection{Experimental Setup}
\ddg{TODO}

\subsection{Experimental Results}
\ddg{TODO}

\section{Conclusions}
\ddg{TODO}

\bibliographystyle{aaai}
\bibliography{main}
\end{document}

### 2017-08-10 stp/paper_aaai/build.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+
+pdflatex main.tex
+bibtex main.aux
+pdflatex main.tex
+pdflatex main.tex
+ 

### 2017-08-10 stp/paper_aaai/main.tex
typo
fig

@@
 \tikzstyle{data}=[draw,rectangle,align=center,black!70]
-\tikzstyle{hasaA} = [>=stealth',draw,dashed,-,black!70]
+\tikzstyle{hasaA} = 
+[>=o,draw,densely dashed,-,black!70,decoration={snake,segment 
+length=10,amplitude=1.5,post length=4}]
 \tikzstyle{hasaC} = [>=stealth',draw,thick,-, black]
@@
 \newcommand{\ddg}[1]{\authornote{DDG}{blue}{#1}}
-\newcommand{\npd}[1]{\authornote{NPD}{orange}{#1}}
+\newcommand{\npr}[1]{\authornote{NPR}{orange}{#1}}
 
@@
 
-	\path[draw,hasaA,->] (pe) edge [bend left = 10] 
+	\path[draw,hasaA,->] (pe) edge [decorate,bend left = 10] 
 	node [midway, above, sloped] {name} (-0.5,2);
-	\path[draw,hasaA,->] (pe) edge [bend left = 0] 
+	\path[draw,hasaA,->] (pe) edge [decorate,bend left = 0] 
 	node [midway, below, sloped] {birthDate} (0,2);
 
-	\path[draw,hasaA,->] (co) edge [bend left = 0] 
+	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
 	node [midway, below, sloped] {name} (-1,-5);
-	\path[draw,hasaA,->] (co) edge [bend left = 0] 
+	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
 	node [midway, above, sloped] {phone} (0,-5);
-	\path[draw,hasaA,->] (co) edge [bend left = 0] 
+	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
 	node [midway, above, sloped] {email} (1,-5);
 
-	\path[draw,hasaA,->] (ev) edge [bend left = 0] 
+	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
 	node [midway, below, sloped] {startDate} (2.5,3.2);
-	\path[draw,hasaA,->] (ev) edge [bend left = 0] 
+	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
 	node [midway, above, sloped] {endDate} (3.5,3.2);
-	\path[draw,hasaA,->] (ev) edge [bend left = 0] 
+	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
 	node [midway, below, sloped] {title} (4.5,3.2);
 
-	\path[draw,hasaA,->] (pl) edge [bend left = 0] 
+	\path[draw,hasaA,->] (pl) edge [decorate,bend left = 0] 
 	node [midway, above, sloped] {name} (6.5,-1.8);
-	\path[draw,hasaA,->] (pl) edge [bend left = 0] 
+	\path[draw,hasaA,->] (pl) edge [decorate,bend left = 0] 
 	node [midway, above, sloped] {postalCode} (6,-3);
@@
 (0,1) -- (3ex,1);}' means ``has a Class property'', 
-`\tikz{ \path[hasaA,->] (0,1) -- (3ex,1);}' means ``has a data property'' and 
+`\tikz{ \path[hasaA] (0,1) edge[decorate] (3ex,1);}' means ``has a data 
+property'' and 
 `\tikz{ \path[isa,->] (0,1) -- (3ex,1);}' means ``is a'' ).

### 2017-08-11 stp/paper_aaai/main.tex
moved some paragraphs around, writtten pattern mining part

@@
 \tikzstyle{hasaA} = 
-[>=o,draw,densely dashed,-,black!70,decoration={snake,segment 
+[draw,densely dashed,-,black!70,decoration={snake,segment 
 length=10,amplitude=1.5,post length=4}]
@@
 %/Author (AAAI Press Staff)}
-\setcounter{secnumdepth}{0}  
+\setcounter{secnumdepth}{2}  
  \begin{document}
@@
 properties as the links between the nodes \cite{Taheriyan2013}. Henceforth, we 
-focus on a specific data integration problem: automatically mapping relational 
-data sources onto a user provided ontology.
+focus on a specific data integration problem: automatically mapping a new 
+relational data source onto a user provided ontology.
 
@@
 Relational-To-Ontology Mapping Problem (\relonto{})
-as a Minimum Cost Steiner Tree Problem (STP) with side constraints.
-This problem is formulated for an \emph{integration graph} which includes the 
-attributes from the new source as well as ontology classes and properties. We
-apply machine learning techniques to assign costs to the links in the 
-constructed integration graph.
+as a Minimum Cost Steiner Tree Problem (STP) with side constraints 
+\cite{deuna2016steiner}.
+
+Firstly, we build an \emph{integration graph} which includes the 
+attributes from the new source as well as ontology classes and properties. 
+Secondly, we apply machine learning techniques to 
+assign costs to its edges. 
+Lastly, we use Constraint Programming to 
+find a minimum cost Steiner Tree in the graph. The goal is to assign the costs 
+on the edges in such a way that the resulting Steiner Tree is a valid semantic 
+model for the new source.
 
@@
 (0,1) -- (3ex,1);}' means ``has a Class property'', 
-`\tikz{ \path[hasaA] (0,1) edge[decorate] (3ex,1);}' means ``has a data 
+`\tikz{ \path[hasaA,decoration={post length=0}] (0,0) edge[decorate] (3ex,0);}' 
+means ``has 
+a data 
 property'' and 
@@
 
-\section{ML for Training on Source Descriptions \ddg{Better title than this 
+\section{ML for Training on Source Descriptions \label{SEC:ML}\ddg{Better title 
+than this 
 please...}}
@@
 
-\ddg{TODO}
+As an extension to the problem, we consider using pattern mining techniques in 
+order to identify patterns in the training set of semantic model that repeat 
+themselves often. The hope is that with such information we can encourage the 
+semantic model $m^\star$ for the new source to use groups of edges that 
+appeared often together in training semantic models.
+
+In our context, we define a \emph{pattern} is a graph $P$ that is undirected 
+and simple (no multiple edges between two nodes, nor self-loops).
+
+Let $G = (V_G,E_G,\lambda_G)$ and $P = (V_P,E_P, \lambda_P)$ be two graphs 
+where $\lambda_P$ is a \emph{labeling function} that maps nodes/edges of $G$ 
+into a set of labels (e.g. natural numbers) $\mathbb{N}$ (similarly for 
+$\lambda_P$).
+An \emph{embedding} of $P$ into $G$ is an injective function $f : V_G \mapsto 
+V_P$ such that for all $x,y \in V_P$:
+\begin{enumerate}
+	\item $\{x,y\} \in E_P \implies \{f(x),f{y}\} \in E_G$.
+	\item $\lambda_P(x) = \lambda_G(f(x))$
+	\item $\lambda_P(\{x,y\}) = \lambda_G(\{f(x),f(y)\})$
+\end{enumerate} 
+That is, if an edge exists in $P$, it must also exist in $G$ (but not 
+vice-versa); and the labelling functions of both graphs must match after 
+applying the embedding function.
+
+Our goal is to take a set of graphs (the semantic models from the training set 
+$S_T$) and find patterns that appear often across that set of graphs. This is 
+known as the Frequent Subgraph Mining (FSM), which contains the subgraph 
+isomorphism, known to be NP-complete. 
+There exists a range of tools that can achieve this task using Transactional 
+Frequent Graph Pattern Mining
+\cite{petermann2017dimspan,yan2002gspan}. We chose to use DIMSpan 
+\cite{petermann2017dimspan}. \ddg{CHECK! How do they solve an NP-complete 
+problem??}
+
+This tool provides us with a list of patterns that are frequent, as well as 
+their support. The \emph{support} of a pattern is a measure of frequency. Thus 
+the higher the support, the more often the pattern appears. This typically 
+means that big patterns have low support.
 
@@
 
-The Steiner Tree Problem (STP) is defined the following way. Given a graph $G =
+Given a graph $G =
 (V, E)$ and a subset of its nodes $T \subseteq V$ , called \emph{terminals}, a 
@@
 may include additional nodes from $V$, in particular to ensure the 
-connectedness of the constructed tree.
+connectedness of the constructed tree. The Steiner Tree Problem 
+(STP) is stated as follows: given $G$ and a weight function $w_f : E 
+\longmapsto \mathbb{R}$, find the Steiner Tree that minimizes the sum of the 
+weights of the edges in $E_s$ given by $w_f$. This was proven to be NP-hard 
+by Karp \cite{Karp1972}.
 
@@
 Note that, although the alignment graph is directed, the semantic models are 
-not necessarily rooted directed trees, therefore the directions of the edges is 
-ignored for the STP model (and are all treated as undirected edges).
+not necessarily rooted directed trees (e.g. \ref{FIG:sem}), therefore the 
+directions of the edges is ignored for the STP model (and are all treated as 
+undirected edges).
+
+The goal is to build a subgraph $T^\star= (V^\star, E^\star)$ 
+of the integration graph 
+$\mathcal{I}_\mathcal{O}^{s^\star}$ for the new source $s^\star$. The solution 
+$T^\star$ will 
+be used to build the source description $\delta^\star = (s^\star, m^\star, 
+\phi^\star)$. 
+In particular, $(\mathcal{V_O} \cap V^\star,\mathcal{E_O} \cap E^\star)$ 
+corresponds to the semantic model, and 
+$(\mathcal{A}_{s^\star},\mathcal{M}_\mathcal{O}^{s^\star} \cap E^\star)$ 
+corresponds to 
+the attribute mapping function.
+
+The solution $T^\star$ must satisfy the following constraints:
+\begin{enumerate}
+	\item $T^\star$ must be a subgraph of $\mathcal{I}_\mathcal{O}^{s^\star}$.
+	\item $T^\star$ must be a tree (connected acyclic graph).
+	\item $\forall a \in \mathcal{A}_{s^\star}, a\in V^\star$.
+	\item $\forall a \in \mathcal{A}_{s^\star}, degree(a) = 1$.
+	\item $\forall n \in \mathcal{D_{G_O}}, degree(a) \in 
+	\{0,2\}$
+	\item $\forall n \in \mathcal{D_{G_O}} \cap V^\star, 
+	degree(a) = 2$
+\end{enumerate}
+
+It is therefore natural to model this a STP with side constraints, since the 2 
+first requirements imply that $T^\star$ is a Steiner Tree of the integration 
+graph. By designing the weighting function $w_\mathcal{I}$ through ML 
+techniques, as shown in Section \ref{SEC:ML}, 
+our hope is that the minimum weight Steiner Tree is a valid semantic model for 
+the new source.
 
@@
 Tree Problems \cite{deuna2016steiner}.
-
-We need to build a subgraph $T^\star= (V^\star, E^\star)$ 
-that is a subset of the integration graph 
-$\mathcal{I}_\mathcal{O}^{s^\star}$ for the new source $s^\star$. The tree will 
-be used to build the source description $\delta^\star = (s^\star, m^\star, 
-\phi^\star)$. 
-In particular, $(\mathcal{V_O} \cap V^\star,\mathcal{E_O} \cap E^\star)$ 
-corresponds to the semantic model, and 
-$(\mathcal{A}_{s^\star},\mathcal{M}_\mathcal{O}^{s^\star} \cap E^\star)$ 
-corresponds to 
-the attribute mapping function.
-
-The solution $T^\star$ must satisfy the following constraints:
-\begin{enumerate}
-	\item $T^\star$ must be a tree (connected acyclic graph).
-	\item $\forall a \in \mathcal{A}_{s^\star}, a\in V^\star$.
-	\item $\forall a \in \mathcal{A}_{s^\star}, degree(a) = 1$.
-	\item $\forall n \in \mathcal{D_{G_O}}, degree(a) \in 
-	\{0,2\}$
-	\item $\forall n \in \mathcal{D_{G_O}} \cap V^\star, 
-	degree(a) = 2$
-\end{enumerate}
 

### 2017-08-11 stp/paper_aaai/main.tex
patterns

@@
 
-\subsection{Frequent Subgraph Pattern Mining}
+\subsection{Frequent Subgraph Pattern Mining \label{SSEC:pattern-mining}}
 
@@
 
+\subsection{Using Patterns}
+
+As explained in Subsection \ref{SSEC:pattern-mining}, we also tried to use 
+frequently appearing patterns in order to incentivise the solution tree 
+$T^\star$ to contain subgraphs of the alignment graph that have been frequently 
+seen in the training set.
+
+To do this, we use the support of each of the obtained patters as a prize. If 
+the tree contains a pattern, then its weight is automatically reduced by a the 
+value of the support of that pattern. We will see in the next section how this 
+information is integrated in the model.
+
 \section{Modeling as a Constraint Optimization Problem}
@@
 
+Additionally, for a given set of patterns $\mathcal{P}$ with a support function 
+$w_\mathcal{P} : \mathcal{P} \mapsto \mathbb{R}$, we have a set of variables 
+$c_p, \forall p \in \mathcal{P}$ that tells us whether a pattern $p$ appears in 
+$T^\star$ or not.
+
 \begin{flalign}
-	& \text{Minimize~~} w_{STP} + w_{ADIFF}
+	& \text{Minimize~~} w_{STP} + w_{ADIFF} - w_{PAT}
 	%\sum_{e \in \mathcal{E}_\mathcal{O}}c_e * 
@@
 	\label{EQ:map}&&\\
-	& w_{ADIFF} = \sum_{(a,d) \in \mathcal{M}_\mathcal{O}^{s^\star}} 
+	& w_{\mathit{ADIFF}} = \sum_{(a,d) \in \mathcal{M}_\mathcal{O}^{s^\star}} 
 	w_\mathcal{I}(~(a,d)~) * \llbracket match[a] = d\rrbracket 
-	\label{EQ:matchcost}
+	\label{EQ:matchcost}  &&\\
+	& \forall p \in \mathcal{P}, \big(\forall e\in edges(p), c_e = 
+	\mathit{true} \big) \Leftrightarrow c_p \label{EQ:patt}&&\\
+	& w_{PAT} = \sum_{p\in\mathcal{P}} \mathit{support}[p] * c_p 
+	\label{EQ:pcost} 
 \end{flalign}
@@
 Eq. \ref{EQ:obj} is the objective function, we are trying to minimize the cost 
-of $T^\star$. Eq. \ref{EQ:stp} enforces that the solution $T^\star$ is indeed a 
-tree defined by the $c_n$ and $c_e$ variables, subgraph of the alignment graph 
+of $T^\star$ while collecting prizes for each pattern we use. Eq. \ref{EQ:stp} 
+enforces that the solution 
+$T^\star$ is indeed a tree defined by the $c_n$ and $c_e$ variables, subgraph 
+of the alignment graph 
 and of total weight $w_{STP}$. Equations \ref{EQ:deg1} and \ref{EQ:deg2} ensure 
@@
 \ref{EQ:matchcost} computes the cost $w_{ADIFF}$ of the matches.
+Eq. \ref{EQ:patt} indicated that a pattern is used if and only if all its edges 
+are selected in the tree. Eq. \ref{EQ:pcost} computes the prizes collected by 
+using patterns.
 

### 2017-08-11 stp/paper_aaai/main.tex
alignment graph

@@
 \usetikzlibrary{decorations.pathmorphing}
-\tikzstyle{class}=[draw,ellipse,align=center,fill=green!25]
+\usetikzlibrary{mindmap,backgrounds}
+\tikzstyle{class}=[ellipse,align=center,fill=green!25]
 \tikzstyle{data}=[draw,rectangle,align=center,black!70]
@@
 \tikzstyle{hasaC} = [>=stealth',draw,thick,-, black]
-\tikzstyle{isa} = [>=latex,draw,double,black!90,double distance=1mm]
+\tikzstyle{isa} = [>=o,draw,densely dotted,very thick,black!90]
 
@@
 property'' and 
-`\tikz{ \path[isa,->] (0,1) -- (3ex,1);}' means ``is a'' ).
+`\tikz{ \path[isa,->] (0,1) -- (3ex,1);}' means ``is a'' ). Based on 
+\cite{Taheriyan2013}.
 }
@@
 \begin{scope}
-	\node[class] (pe) at (0,0)  {\small Person};
+	\node[class] (pe) at (3,0)  {\small Person};
 	\node[class] (co) at (6,0) {\small Org.};
-	\node[class] (ci) at (2.5,0) {\small City};
-	\node[class] (st) at (4.5,0) {\small State};
+	\node[class] (ci) at (1,0) {\small City};
+	\node[class] (st) at (-1,0) {\small State};
 
-	\node[data] (pen) at (-1,-1) {\scriptsize Person.name};
-	\node[data] (peb) at (1,-1) {\scriptsize Person.birthDate};
-	\node[data] (cin) at (3,-1) {\scriptsize City.name};
-	\node[data] (stn) at (4.5,-1) {\scriptsize State.name};
+	\node[data] (pen) at (2.5,-1) {\scriptsize Person.name};
+	\node[data] (peb) at (4.3,-1) {\scriptsize Person.birthDate};
+	\node[data] (cin) at (1,-1) {\scriptsize City.name};
+	\node[data] (stn) at (-1,-1) {\scriptsize State.name};
 	\node[data] (con) at (6,-1) {\scriptsize Org.name};
 
-	\path[hasaC,->] (pe) edge [bend left= 20] 
+	\path[hasaC,->] (pe) edge [bend left= 0] 
 	node [midway, above, sloped] {worksFor} (co) ;
@@
 \end{tikzpicture}
-\caption{Examples of two semantic models.}
+\caption{Examples of two semantic models (`\tikz{ \node[class] () at (0,0)  
+{};}' are class nodes, and `\tikz{ \node[data] () at (0,0)  {};}' are data 
+nodes).}
 \label{FIG:sem}
@@
 associate the known
-semantic type with the corresponding feature vector. We train random forest
+semantic type with the corresponding feature vector. We train a random forest
 on this sample. Then we use the learnt model to classify attributes in the new
@@
 
-In such way, we learn the mapping $\psi : \mathcal{A_s} \times \mathcal{L_O} 
+In such way, we learn the mapping $\psi : \mathcal{A}_s \times \mathcal{L_O} 
 \mapsto [0, 1]$,
@@
 
-An example alignment graph is illustrated in Fig. \ddg{todo}. Black links 
+An example alignment graph is illustrated in Fig. \ref{FIG:ali}. Bigger 
+examples 
+can be found in \cite{Taheriyan2013}. Black links 
 correspond to the links which are supported by the known semantic models. Blue 
-links are inferred from the ontology $\mathcal{O}$ and can be assigned the 
+and orange links are inferred from the ontology $\mathcal{O}$ (the orange ones 
+correspond to the ones added to connect Classes od the ontology that never 
+appeared in the semantic models) and can be assigned the 
 maximum weight $w_max$ \ddg{where does this weight come from?} .
+
+\begin{figure}[ht]
+\centering
+\begin{tikzpicture}
+
+	\node[class] (pe1) at (3,0)  {\small Person};
+	\node[class] (co1) at (6,0) {\small Org.};
+	\node[class] (ci1) at (1,0) {\small City};
+	\node[class] (st1) at (-1,0) {\small State};
+
+	\node[data] (pen) at (2.5,1) {\scriptsize Person.name};
+	\node[data] (peb) at (4.3,1) {\scriptsize Person.birthDate};
+	\node[data] (cin) at (1,1) {\scriptsize City.name};
+	\node[data] (stn) at (-1,1) {\scriptsize State.name};
+	\node[data] (con) at (6,1) {\scriptsize Org.name};
+
+	\path[hasaC,->] (pe1) edge [bend left= 0] 
+	node [midway, above, sloped] {worksFor} (co1) ;
+
+	\path[hasaC,->] (pe1) edge [bend left = 0] 
+	node [midway, above, sloped] {bornIn} (ci1) ;
+
+	\path[hasaC,->] (ci1) edge  []
+	node [midway, above, sloped] {state} (st1) ;
+
+	\path[draw,hasaA,->] (pe1) -- (pen);
+	\path[draw,hasaA,->] (pe1) -- (peb);
+
+	\path[draw,hasaA,->] (co1) -- (con);
+
+	\path[draw,hasaA,->] (ci1) -- (cin);
+
+	\path[draw,hasaA,->] (st1) -- (stn);
+
+% % % CC2
+\def\ysh{-2.5};
+
+	\node[class] (pl2) at (-1,0+\ysh)  {\small City};
+	\node[class] (pe2) at (3,0+\ysh)  {\small Person};
+	\node[class] (co2) at (1,0+\ysh) {\small Org.};
+	\node[class] (ev2) at (6,0+\ysh) {\small Event};
+
+	\node[data] (pen) at (2.5,-1+\ysh) {\scriptsize Person.name};
+	\node[data] (evs) at (4.2,-1+\ysh) {\scriptsize Event.startDate};
+	\node[data] (eve) at (6,-1+\ysh) {\scriptsize Event endDate};
+	\node[data] (con) at (1,-1+\ysh) {\scriptsize Org.name};
+	\node[data] (pln) at (-1,-1+\ysh) {\scriptsize City.name};
+
+	\path[hasaC,->] (co2) edge [bend left= 0] 
+	node [midway, above, sloped] {ceo} (pe2) ;
+
+	\path[hasaC,->] (ev2) edge [bend left = 0] 
+	node [midway, above, sloped] {organizer} (pe2) ;
+
+	\path[hasaC,->] (co2) edge [bend left = -10] 
+	node [midway, above, sloped] {location} (pl2) ;
+
+	\path[draw,hasaA,->] (pl2) -- (pln);
+
+	\path[draw,hasaA,->] (pe2) -- (pen);
+
+	\path[draw,hasaA,->] (co2) -- (con);
+
+	\path[draw,hasaA,->] (ev2) -- (evs);
+	\path[draw,hasaA,->] (ev2) -- (eve);
+
+% % % Ontology
+
+	\path[draw,hasaC,->,blue!70] (co2)  edge [bend left = -5] (pe1);
+	\path[draw,hasaC,->,blue!70] (pe1)  edge [bend left = -5] (co2);
+
+	\path[draw,hasaC,->,blue!70] (co1)  edge [bend left = -5] (pe2);
+	\path[draw,hasaC,->,blue!70] (pe2)  edge [bend left = -5] (co1);
+
+	\path[draw,hasaC,->,blue!70] (pl2) -- (st1);
+
+	\path[draw,hasaC,->,blue!70] (ev2) -- (pe1);
+
+	\node[class,fill=orange!30!white] (PL) at (3,\ysh/2)  {\small Place};
+
+	\path[draw,hasaC,->,orange!30!white] (pe1) edge[bend left=10] (PL);
+	\path[draw,hasaC,->,orange!30!white] (pe1) edge[bend left=-10] (PL);
+
+	\path[draw,hasaC,->,orange!30!white] (pe2) edge[bend left=10] (PL);
+	\path[draw,hasaC,->,orange!30!white] (pe2) edge[bend left=-10] (PL);
+
+	\path[draw,hasaC,->,orange!30!white] (co1) edge[bend left=0] (PL);
+	\path[draw,hasaC,->,orange!30!white] (co2) edge[out=45,in=225] (PL);
+
+	\path[draw,hasaC,->,orange!30!white] (ev2) edge[out=90,in=0] (PL);
+
+	\path[draw,isa,->,orange!30!white] (ci1) edge[out=-45,in=120] (PL);
+	\path[draw,isa,->,orange!30!white] (pl2) edge[out=90,in=180] (PL);
+	\path[draw,isa,->,orange!30!white] (st1) edge[out=-45,in=150] (PL);
+
+\end{tikzpicture}
+\caption{Example of alignment graph.}
+\label{FIG:ali}
+\end{figure}
 
@@
 Let $G = (V_G,E_G,\lambda_G)$ and $P = (V_P,E_P, \lambda_P)$ be two graphs 
-where $\lambda_P$ is a \emph{labeling function} that maps nodes/edges of $G$ 
-into a set of labels (e.g. natural numbers) $\mathbb{N}$ (similarly for 
-$\lambda_P$).
+where $\lambda_G$ (resp. $\lambda_P$) is a \emph{labeling function} that maps 
+nodes/edges of $G$ (resp. $P$) into a set of labels (e.g. natural numbers).
 An \emph{embedding} of $P$ into $G$ is an injective function $f : V_G \mapsto 
@@
 (STP) is stated as follows: given $G$ and a weight function $w_f : E 
-\longmapsto \mathbb{R}$, find the Steiner Tree that minimizes the sum of the 
+\mapsto \mathbb{R}$, find the Steiner Tree that minimizes the sum of the 
 weights of the edges in $E_s$ given by $w_f$. This was proven to be NP-hard 
@@
 $s^\star$, we construct the 
-\emph{integration graph} $\mathcal{I}_\mathcal{O}^{s^\star} = 
+\emph{integration graph} $~\mathcal{I}_\mathcal{O}^{s^\star} = 
 (\mathcal{V}_\mathcal{O}^{s^\star},\mathcal{E}_\mathcal{O}^{s^\star})$, with 
@@
 all the edges in the alignment 
-graph, and edges connecting each attributes of $s^\star$ to the nodes 
-$\mathcal{D_{G_O}}$ of the 
-alignment graph \emph{induced} by the semantic labels. We call this last set 
+graph, and edges connecting each attributes of $s^\star$ to the nodes in the 
+alignment graph \emph{induced} by the semantic types (i.e. the set of nodes in 
+$\mathcal{D_{G_O}}$). We call this last set 
 of edges $\mathcal{M}_\mathcal{O}^{s^\star}$ (for ``matches''). Thus, 
@@
 Note that, although the alignment graph is directed, the semantic models are 
-not necessarily rooted directed trees (e.g. \ref{FIG:sem}), therefore the 
-directions of the edges is ignored for the STP model (and are all treated as 
+not necessarily rooted directed trees (e.g. Fig. \ref{FIG:sem}), therefore the 
+direction of the edges is ignored for the STP model (and are all treated as 
 undirected edges).
@@
 \begin{enumerate}
-	\item $T^\star$ must be a subgraph of $\mathcal{I}_\mathcal{O}^{s^\star}$.
-	\item $T^\star$ must be a tree (connected acyclic graph).
-	\item $\forall a \in \mathcal{A}_{s^\star}, a\in V^\star$.
-	\item $\forall a \in \mathcal{A}_{s^\star}, degree(a) = 1$.
+	\item $T^\star$ must be a subgraph of $\mathcal{I}_\mathcal{O}^{s^\star}$
+	\item $T^\star$ must be a tree (connected acyclic graph)
+	\item $\forall a \in \mathcal{A}_{s^\star}, a\in V^\star$
+	\item $\forall a \in \mathcal{A}_{s^\star}, degree(a) = 1$
 	\item $\forall n \in \mathcal{D_{G_O}}, degree(a) \in 
@@
 \subsection{Modeling \relonto{} in CP}
-In order to model this problem we used the \minizinc{} language, and the 
-\chuffed{} solver because it has a global constraint implemented for Steiner 
+In order to model this problem we used the \minizinc{} language 
+\cite{minizinc}, and the 
+\chuffed{} solver \cite{chu2011improving} because it has a global constraint 
+implemented for Steiner 
 Tree Problems \cite{deuna2016steiner}.
@@
 actually a matching problem. Each attribute must match exactly to one node of 
-$\mathcal{D_{G_O}}$.
+$\mathcal{D_{G_O}}$. Note that not all nodes in $\mathcal{D_{G_O}}$ must match 
+to an attribute, as not all of them are part of $T^\star$.
 
@@
 	& \textit{steiner\_tree}(\{c_n| n \in \mathcal{V_O}\},\{c_e| e \in 
-	\mathcal{E_O}\},\mathcal{G_O},w_\mathcal{O},w_{STP})  \label{EQ:stp} &&\\
+	\mathcal{E_O}\},\mathcal{G_O},w_\mathcal{O},w_\mathit{STP})  \label{EQ:stp} 
+	&&\\
 	&\forall d \in \mathcal{D_{G_O}}, degree(d) \leq 1 \label{EQ:deg1}&&\\

### 2017-08-11 stp/paper_aaai/main.tex
integration graph

@@
 \tikzstyle{data}=[draw,rectangle,align=center,black!70]
+\tikzstyle{att}=[rectangle,align=center,fill=brown!70!red]
 \tikzstyle{hasaA} = 
@@
 	\node[data] (evs) at (4.2,-1) {\scriptsize Event.startDate};
-	\node[data] (eve) at (6,-1) {\scriptsize Event endDate};
+	\node[data] (eve) at (6,-1) {\scriptsize Event.endDate};
 	\node[data] (con) at (1,-1) {\scriptsize Org.name};
@@
 and orange links are inferred from the ontology $\mathcal{O}$ (the orange ones 
-correspond to the ones added to connect Classes od the ontology that never 
+correspond to the ones added to connect Classes of the ontology that never 
 appeared in the semantic models) and can be assigned the 
@@
 
-	\node[class] (pe1) at (3,0)  {\small Person};
-	\node[class] (co1) at (6,0) {\small Org.};
-	\node[class] (ci1) at (1,0) {\small City};
+	\node[class] (pe1) at (3,0)  {\small Person1};
+	\node[class] (co1) at (6,0) {\small Org.1};
+	\node[class] (ci1) at (1,0) {\small City1};
 	\node[class] (st1) at (-1,0) {\small State};
 
-	\node[data] (pen) at (2.5,1) {\scriptsize Person.name};
-	\node[data] (peb) at (4.3,1) {\scriptsize Person.birthDate};
-	\node[data] (cin) at (1,1) {\scriptsize City.name};
+	\node[data] (pen) at (2.3,1) {\scriptsize Person1.name};
+	\node[data] (peb) at (4.2,1) {\scriptsize Person1.birthDate};
+	\node[data] (cin) at (0.7,1) {\scriptsize City1.name};
 	\node[data] (stn) at (-1,1) {\scriptsize State.name};
-	\node[data] (con) at (6,1) {\scriptsize Org.name};
+	\node[data] (con) at (6,1) {\scriptsize Org1.name};
 
@@
 
-	\node[class] (pl2) at (-1,0+\ysh)  {\small City};
-	\node[class] (pe2) at (3,0+\ysh)  {\small Person};
-	\node[class] (co2) at (1,0+\ysh) {\small Org.};
+	\node[class] (pl2) at (-1,0+\ysh)  {\small City2};
+	\node[class] (pe2) at (3,0+\ysh)  {\small Person2};
+	\node[class] (co2) at (1,0+\ysh) {\small Org.2};
 	\node[class] (ev2) at (6,0+\ysh) {\small Event};
 
-	\node[data] (pen) at (2.5,-1+\ysh) {\scriptsize Person.name};
+	\node[data] (pen) at (2.3,-1+\ysh) {\scriptsize Person2.name};
 	\node[data] (evs) at (4.2,-1+\ysh) {\scriptsize Event.startDate};
-	\node[data] (eve) at (6,-1+\ysh) {\scriptsize Event endDate};
-	\node[data] (con) at (1,-1+\ysh) {\scriptsize Org.name};
-	\node[data] (pln) at (-1,-1+\ysh) {\scriptsize City.name};
+	\node[data] (eve) at (6,-1+\ysh) {\scriptsize Event.endDate};
+	\node[data] (con) at (0.7,-1+\ysh) {\scriptsize Org2.name};
+	\node[data] (pln) at (-1,-1+\ysh) {\scriptsize City2.name};
 
@@
 \end{tikzpicture}
-\caption{Example of alignment graph.}
+\caption{Example of alignment graph (`\tikz{ \node[class] () at (0,0)  
+{};}' and `\tikz{ \node[class,fill=orange!30!white] () at (0,0)  
+{};}' are class nodes, and `\tikz{ \node[data] () at (0,0)  {};}' are data 
+nodes). We omit weights for clarity.}
 \label{FIG:ali}
@@
 
-An example of integration graph can be found in Fig. \ddg{TODO}.
+An example of integration graph can be found in Fig. \ref{FIG:inte}.
+
+\begin{figure}[ht]
+\centering
+\begin{tikzpicture}
+	\node[class, rectangle, rounded corners] (CLASS) at (0,0) { \small{Class 
+	Nodes of Alignment Graph}};
+
+	\node[data] (stn1) at (-3.9,-1) {\scriptsize S.n};
+	\node[data] (cin1) at (-3.1,-1) {\scriptsize C1.n};
+	\node[data] (pen1) at (-2.3,-1) {\scriptsize P1.n};
+	\node[data] (peb1) at (-1.5,-1) {\scriptsize P1.b};
+	\node[data] (con1) at (-0.7,-1) {\scriptsize O1.n};
+
+	\path[draw,hasaA] (CLASS) edge[out=180,in=90] (stn1);
+	\path[draw,hasaA] (CLASS) edge[out=190,in=90] (cin1);	
+	\path[draw,hasaA] (CLASS) edge[out=200,in=90] (pen1);
+	\path[draw,hasaA] (CLASS) edge[out=210,in=90] (peb1);	
+	\path[draw,hasaA] (CLASS) edge[out=220,in=90] (con1);
+
+% % % CC2
+\def\ysh{0};
+
+	\node[data] (cin2) at (0.7,-1+\ysh) {\scriptsize C2.n};
+	\node[data] (con2) at (1.5,-1+\ysh) {\scriptsize O2.n};
+	\node[data] (pen2) at (2.3,-1+\ysh) {\scriptsize P2.n};
+	\node[data] (evs2) at (3.1,-1+\ysh) {\scriptsize E.s};
+	\node[data] (eve2) at (3.9,-1+\ysh) {\scriptsize E.e};
+
+	\path[draw,hasaA] (CLASS) edge[out=320,in=90] (cin2);	
+	\path[draw,hasaA] (CLASS) edge[out=330,in=90] (con2);
+	\path[draw,hasaA] (CLASS) edge[out=340,in=90] (pen2);
+	\path[draw,hasaA] (CLASS) edge[out=350,in=90] (evs2);
+	\path[draw,hasaA] (CLASS) edge[out=360,in=90] (eve2);
+
+\node[rectangle, rounded corners,very thick,draw, dashed, 
+brown!40!red!40!white,minimum 
+height=18, minimum 
+width=220] 
+(source) at 
+(0,-3) 
+{};
+\node[brown!40!red!40!white] 
+(source) at 
+(-4.1,-3) 
+{$s^\star$:};
+	\node[att] (a1) at (-3,-3) {\small Surame};
+	\node[att] (a2) at (-1,-3) {\small Workplace};
+	\node[att] (a3) at (1,-3) {\small Date};
+	\node[att] (a4) at (3,-3) {\small Location};
+
+	\path[draw] (a1) -- (stn1);
+	\path[draw] (a1) -- (cin1);
+	\path[draw] (a1) -- (pen1);
+	\path[draw] (a1) -- (cin2);
+	\path[draw] (a1) -- (pen2);
+
+	\path[draw] (a2) -- (cin1);
+	\path[draw] (a2) -- (con1);
+	\path[draw] (a2) -- (con2);
+
+	\path[draw] (a3) -- (peb1);
+	\path[draw] (a3) -- (evs2);
+	\path[draw] (a3) -- (eve2);
+
+	\path[draw] (a4) -- (stn1);
+	\path[draw] (a4) -- (cin1);
+	\path[draw] (a4) -- (con1);
+	\path[draw] (a4) -- (cin2);
+	\path[draw] (a4) -- (con2);
+\end{tikzpicture}
+\caption{Example of integration graph. (`\tikz{ \node[att] () at (0,0)  
+{};}' are attribute nodes). We omit weights for clarity. Data node labels are 
+abbreviated but 
+correspond to the ones shown in Fig \ref{FIG:ali}.}
+\label{FIG:inte}
+\end{figure}
 

### 2017-08-11 stp/paper_aaai/main.tex
Checked. Ready for natalia to read and complete the missing parts

@@
 not only for structural properties of the original data sources, but also to 
-include the semantics which is usually implicitly present in the sources. In 
+include the semantics, which is usually implicitly present in the sources. In 
 other words, we want to build a semantic model which describes the data sources 
-in terms of concepts and relationships defined by an ontology. We can view this
-semantic model as a graph with ontology classes as the nodes and ontology
-properties as the links between the nodes \cite{Taheriyan2013}. Henceforth, we 
+in terms of concepts and relationships defined by an ontology 
+\cite{Taheriyan2013}. Henceforth, we 
 focus on a specific data integration problem: automatically mapping a new 
 relational data source onto a user provided ontology.
+
+\subsubsection{Example} Consider the situation where we have some simple 
+relational database tables with columns $\langle$\textit{Surname, 
+Workplace, Date, Location}$\rangle$, 
+$\langle$\textit{Company, Event, Begin, Until, Location}$\rangle$ and 
+$\langle$\textit{Name, D.O.B, Location}$\rangle$. We do not \textit{a priori} 
+know whether ``Date'' is the date of birth or the date a persons started 
+working in the first table; or whether the ``Location'' on the second table 
+refers to the location of the event, or the address of the company. 
+If we are given an ontology like the one in Fig. \ref{FIG:onto}, we would like 
+to automatically map the new data sources to classes of the 
+ontology.$\square$
 
@@
 assign costs to its edges. 
-Lastly, we use Constraint Programming to 
+Lastly, we use Constraint Programming (CP) to 
 find a minimum cost Steiner Tree in the graph. The goal is to assign the costs 
@@
 
-Section bla  presents bla bla... \ddg{TODO}
+Section \ref{SEC:pw} presents the previous work done to achieve this task. 
+Section \ref{SEC:problem} formally states the problem. 
+In Section \ref{SEC:ML} we present how we convert the information given into a 
+useful data representation. 
+Section \ref{SEC:STP} shows how we model the problem as a STP, 
+whereas Section \ref{SEC:CP} discusses how we implement the model in CP. 
+Section \ref{SEC:Res} shows our results.
 
-\section{Previous Work}
+\section{Previous Work \label{SEC:pw}}
 \ddg{rewrite, add more}
@@
 
-\section{Motivating Example}
-\ddg{TODO}
-
-\section{Problem Statement}
+\section{Problem Statement \label{SEC:problem}}
 We follow the definitions proposed by Doal \etal{} \cite{doan2012principles}.
@@
 
-An ontology $\mathcal{O}$ is a specification of classes of objects and their 
+An ontology $\mathcal{O}$ is a specification of classes of objects, their 
 data properties and relationships between them. An example of an ontology is 
@@
 is a data property). Also, a Class can be a subclass of another Class. For 
-example ``Cities'', ``Countries'' or ``States'' are all ``Places''. A subclass 
+example ``Cities'' and ``States'' are both ``Places''. A subclass 
 inherits all the properties of the parent class.
@@
 description. We
-use the term appropriate since there might be many such triples which are
+use the term ``appropriate'' since there might be many such triples which are
 well-formed source descriptions, but only one or a few will capture the intended
@@
 of the known semantic models and expanded using the semantic types 
-$\mathcal{L_O}$ and the domain ontology $\mathcal{O}$. Similar to a semantic 
+$\mathcal{L_O}$ and the ontology $\mathcal{O}$. Similar to a semantic 
 model, $\mathcal{G_O}$ contains both class and data nodes. The links correspond 
@@
 \mathbb{R}$ in 
-such a way that links which are present in
+such a way that edges which are present in
 the known semantic models have lower weights than those 
 which are inferred from the ontology. As we will see int he next section, this 
-makes links present in semantic models more attractive. \ddg{How exactly are 
+makes edges present in semantic models more attractive. \ddg{How exactly are 
 they weighted?}
@@
 
-\section{Steiner Tree Formulation}
+\section{Steiner Tree Formulation \label{SEC:STP}}
 
@@
 	\item $\forall a \in \mathcal{A}_{s^\star}, degree(a) = 1$
-	\item $\forall n \in \mathcal{D_{G_O}}, degree(a) \in 
-	\{0,2\}$
+	%\item $\forall n \in \mathcal{D_{G_O}}, degree(a) \in 
+	%\{0,2\}$
 	\item $\forall n \in \mathcal{D_{G_O}} \cap V^\star, 
@@
 
-To do this, we use the support of each of the obtained patters as a prize. If 
+To do this, we use the support of each of the obtained patterns as a prize. If 
 the tree contains a pattern, then its weight is automatically reduced by a the 
@@
 
-\section{Modeling as a Constraint Optimization Problem}
+\section{Modeling as a Constraint Optimization Problem \label{SEC:CP}}
 
@@
 solver that will find a solution to the CSP, or will report unsatisfiability if 
-no such valuation exists. In the case of COPs, the solver will try to optimize 
+no solution exists. In the case of COPs, the solver will try to optimize 
 the objective function and prove optimality as well.
@@
 takes a subset of the variables of the problem $v \subseteq \boldsymbol{v}$ and 
-the domain of those variables $D_v$ and returns a new domain for thus variables 
+the domain of those variables $D_v$ and returns a new domain for these 
+variables 
 such that $D_v' \sqsubseteq D$. That is, a propagator removes values form the 
@@
 
-Global constraints are higher order constraints that enforce a complicated 
-constraint over a set ov variables. Typical examples of this is enforcing that 
+\emph{Global constraints} are higher order constraints that enforce a 
+complicated 
+constraint over a set of variables. Typical examples of this is enforcing that 
 a set of variables take different values, or that they describe a path a in a 
@@
 such that $a \in \{2,3,4\}$, $b \in \{1,2,3\}$. Let $C = \{a + 2b \leq 4, a 
-\neq b\}$ the constraints to be satisfied. If the search step decides that $a = 
-2$, then (i) $a \neq b \Rightarrow b \in \{1,3\}$ and (ii) $a + 2b \leq 4  
+\neq b\}$ be the constraints. If the search step decides that $a = 
+2$, then $(i)$ $a \neq b \Rightarrow b \in \{1,3\}$ and $(ii)$ $a + 2b \leq 4  
 \Rightarrow b \in \{1\}$. Thus we automatically know that $b = 1$ without never 
-trying any other of its original possible values.
+trying any other of its original possible values. $\square$
 
@@
 Because there are global constraints in CP specialized in matching 
-\cite{regin1994filtering}, we split the problem into two parts: (i) the 
+\cite{regin1994filtering}, we split the problem into two parts: the 
 \verb|steiner_tree| global constraint will only deal with the part of the 
@@
 \mathcal{D_{G_O}}$) means that the edge $(a,d) \in 
-\mathcal{M}_\mathcal{O}^{s^\star}$ is part of $E^\star$.
+\mathcal{M}_\mathcal{O}^{s^\star}$ is part of $T^\star$.
 
 Additionally, for a given set of patterns $\mathcal{P}$ with a support function 
-$w_\mathcal{P} : \mathcal{P} \mapsto \mathbb{R}$, we have a set of variables 
+$w_\mathcal{P} : \mathcal{P} \mapsto \mathbb{R}$, we have a set of Boolean 
+variables 
 $c_p, \forall p \in \mathcal{P}$ that tells us whether a pattern $p$ appears in 
 $T^\star$ or not.
+The model is presented below.
 
@@
 	&\text{such that~~}  \nonumber&& \\
-	& \textit{steiner\_tree}(\{c_n| n \in \mathcal{V_O}\},\{c_e| e \in 
+	& \textit{steiner}(\{c_n| n \in \mathcal{V_O}\},\{c_e| e \in 
 	\mathcal{E_O}\},\mathcal{G_O},w_\mathcal{O},w_\mathit{STP})  \label{EQ:stp} 
@@
 	\mathit{true} \big) \Leftrightarrow c_p \label{EQ:patt}&&\\
-	& w_{PAT} = \sum_{p\in\mathcal{P}} \mathit{support}[p] * c_p 
+	& w_{PAT} = \sum_{p\in\mathcal{P}} w_\mathcal{P}(p)* c_p 
 	\label{EQ:pcost} 
@@
 
-Eq. \ref{EQ:obj} is the objective function, we are trying to minimize the cost 
+Eq. \ref{EQ:obj} is the objective function: we are minimizing the cost 
 of $T^\star$ while collecting prizes for each pattern we use. Eq. \ref{EQ:stp} 
@@
 the alignment graph. Equations \ref{EQ:matchdom} and \ref{EQ:alld} ensure that 
-the matching part of the problem is a bijection. Eq. \ref{EQ:map} ensures that 
+there is exactly one data node matched to an attribute, which has to be one of 
+the ones for which an edge existed. Eq. \ref{EQ:map} ensures that 
 if a data node of the alignment graph has been mapped to some attribute, then 
@@
 
-\section{Results}
+\section{Results \label{SEC:Res}}
 

### 2017-08-16 stp/paper_aaai/main.tex
Added stuff about unknown nodes

@@
 
+\subsection{Unmatched Attributes}
+It is common that the data sources to be integrated will have columns that 
+simply can't be matched to the ontology.
+This can happen when a column of a source table contains some information that 
+is uninteresting to the user, or because the ontology has not been properly 
+designed. 
+Examples of these situations can be found in domain specific data 
+\cite{Pham2016} or HTML 
+tables \cite{ritze2017matching}.
+
+For this reason, we add two artificial Class nodes to the integration graph:  
+\emph{unknown} and \emph{root}. 
+The latter will be connected to every other Class node in 
+$\mathcal{V}_\mathcal{O}^{s^\star}$, including \emph{unknown}.
+We also add a set $U = \{unk_1,...,unk_{|\mathcal{A}_{s^\star}|}\}$ of 
+$|\mathcal{A}_{s^\star}|$ data 
+nodes to the integration graph each connected to exactly one node in 
+$\mathcal{A}_{s^\star}$ and to the \emph{unknown} Class node.
+
+If an attribute $a$ is matched to $unk_a$, then $unk_a$ will be linked to Class 
+node \emph{unknown}. The rest of the attributes can then be matched normally 
+and build  a semantic model as usual. Then, to maintain connectedness of the 
+Steiner tree, the \emph{unknown} node and one of the selected Class nodes will 
+both be connected to the \emph{root} node. Note that if all attributes find a 
+match, then both the \emph{unknown} and \emph{root} won't be selected in the 
+Steiner tree and the normal behavior will take place.
+\ddg{Explain the weights of the edges introduced by the unknown nodes}
+
 \section{Modeling as a Constraint Optimization Problem \label{SEC:CP}}
@@
 	& w_{PAT} = \sum_{p\in\mathcal{P}} w_\mathcal{P}(p)* c_p 
-	\label{EQ:pcost} 
+	\label{EQ:pcost} &&\\
+	& c_{unknown} \Rightarrow \big( c_{root}  \land 
+	c_{(unknown,root)} \big) \label{EQ:unk}
 \end{flalign}
@@
 using patterns.
+Eq. \ref{EQ:unk} ensures that if the \emph{unknown} class node is used, then it 
+is connected to \emph{root}.
+Notice how there is no further requirement for unmatched attributes, as the 
+$unk_i$ data nodes behave like normal data nodes, and the connectedness 
+requirement will make sure that \emph{root} is connected to the rest of the 
+tree (i.e. the semantic model).
 
+Note how this CP model is easily adaptable to more classic settings where no 
+patterns are used (by dropping Eqs. \ref{EQ:patt} and \ref{EQ:pcost}), or where 
+the \emph{unknown} nodes are used (by dropping \ref{EQ:unk}).
 \section{Results \label{SEC:Res}}

### 2017-08-17 stp/paper_aaai/main.tex
Added stuff about unknown nodes
Related work for paper aaai, soccer experiments

@@
 \usepackage{textcomp}
+
+% natalia
+\usepackage{multirow}
 
@@
 %
-\title{Using Machine Learning and Constraint Programming to Solve the 
-Relational-To-Ontology Mapping Problem}
+\title{Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping }
 \author{}
@@
 In our case, we would like this global model to account
-not only for structural properties of the original data sources, but also to 
-include the semantics, which is usually implicitly present in the sources. In 
-other words, we want to build a semantic model which describes the data sources 
-in terms of concepts and relationships defined by an ontology 
-\cite{Taheriyan2013}. Henceforth, we 
-focus on a specific data integration problem: automatically mapping a new 
-relational data source onto a user provided ontology.
+not only for structural properties of the original data sources, but also to include the semantics, which is usually implicitly present in the sources.
+In other words, we want to build a semantic model which describes the data sources in terms of concepts and relationships defined by an ontology \cite{Taheriyan2013}.
+Henceforth, we focus on a specific data integration problem: automatically mapping a new relational data source onto a user provided ontology.
 
-\subsubsection{Example} Consider the situation where we have some simple 
-relational database tables with columns $\langle$\textit{Surname, 
-Workplace, Date, Location}$\rangle$, 
+\subsubsection{Example} Consider the situation where we have some simple relational database tables with columns $\langle$\textit{Surname, Workplace, Date, Location}$\rangle$, 
 $\langle$\textit{Company, Event, Begin, Until, Location}$\rangle$ and 
-$\langle$\textit{Name, D.O.B, Location}$\rangle$. We do not \textit{a priori} 
-know whether ``Date'' is the date of birth or the date a persons started 
-working in the first table; or whether the ``Location'' on the second table 
-refers to the location of the event, or the address of the company. 
-If we are given an ontology like the one in Fig. \ref{FIG:onto}, we would like 
-to automatically map the new data sources to classes of the 
+$\langle$\textit{Name, D.O.B, Location}$\rangle$.
+We do not \textit{a priori} know whether ``Date'' is the date of birth or the date a persons started working in the first table; or whether the ``Location'' on the second table refers to the location of the event, or the address of the company.
+If we are given an ontology like the one in Fig. \ref{FIG:onto}, we would like to automatically map the new data sources to classes of the 
 ontology.$\square$
 
-In this paper we use Machine Learning techniques (ML) to learn mapping rules 
-from already mapped instances. To this end we formulate the 
-Relational-To-Ontology Mapping Problem (\relonto{})
-as a Minimum Cost Steiner Tree Problem (STP) with side constraints 
-\cite{deuna2016steiner}.
+In this paper we use Machine Learning techniques (ML) to learn mapping rules from already mapped instances.
+To this end we formulate the Relational-To-Ontology Mapping Problem (\relonto{}) as a Minimum Cost Steiner Tree Problem (STP) with side constraints \cite{deuna2016steiner}.
 
@@
 Lastly, we use Constraint Programming (CP) to 
-find a minimum cost Steiner Tree in the graph. The goal is to assign the costs 
-on the edges in such a way that the resulting Steiner Tree is a valid semantic 
-model for the new source.
+find a minimum cost Steiner Tree in the graph.
+The goal is to assign the costs 
+on the edges in such a way that the resulting Steiner Tree is a valid semantic model for the new source.
 
@@
 Section \ref{SEC:Res} shows our results.
-
-\section{Previous Work \label{SEC:pw}}
-\ddg{rewrite, add more}
-One of the standard approaches to solve the relational-to-ontology (\relonto{})
-mapping problem is to apply Knowledge Representation and Reasoning (KR)
-techniques. The main idea of this approach is to exploit constraints specified 
-within relational schemata and ontologies. Several mapping generation
-tools based on this approach already exist, for example, BootOX, MIRROR,
-COMA++ \cite{pinkel2016rodi}. The issue is though that constraints may be 
-inconsistent or absent completely \ddg{Why?}. We suggest to use ML techniques 
-to overcome this hurdle.
-
-\cite{taheriyan2016learning} \ddg{Isn't this really similar??}
 
@@
 An ontology $\mathcal{O}$ is a specification of classes of objects, their 
-data properties and relationships between them. An example of an ontology is 
-given 
-in Fig. \ref{FIG:onto}. A Class in an ontology can have \emph{data properties} 
-or 
-\emph{class properties}. For example an ``Organisation'' has a ``Person'' 
+data properties and relationships between them.
+An example of an ontology is given in Fig. \ref{FIG:onto}. 
+A Class in an ontology can have \emph{data properties} or \emph{object properties}. 
+For example an ``Organisation'' has a ``Person'' 
 (which is a class with its own properties), and it has a ``name'' (which 
-is a data property). Also, a Class can be a subclass of another Class. For 
-example ``Cities'' and ``States'' are both ``Places''. A subclass 
-inherits all the properties of the parent class.
+is a data property). 
+Also, a Class can be a subclass of another Class. 
+For 
+example ``Cities'' and ``States'' are both ``Places''. 
+A subclass inherits all the properties of the parent class.
 
 A \emph{semantic model} $m$ is a directed graph with two types of nodes: 
-\emph{class nodes} and \emph{data nodes}. We denote them as $\mathcal{C}_m$ and 
-$\mathcal{D}_m$ respectively. We define $\mathcal{N}_m = \mathcal{C}_m \cup 
+\emph{class nodes} and \emph{data nodes}. 
+We denote them as $\mathcal{C}_m$ and $\mathcal{D}_m$ respectively.
+ We define $\mathcal{N}_m = \mathcal{C}_m \cup 
 \mathcal{D}_m$. $ \mathcal{C}_m$ corresponds to classes in the ontology 
 $\mathcal{O}$. $\mathcal{D}_m$ corresponds to data 
-properties in the ontology. The edges in the semantic model correspond to 
-relationships in the ontology, as shown if Figures \ref{FIG:onto} and 
-\ref{FIG:sem}.
+properties in the ontology. 
+The edges in the semantic model correspond to relationships in the ontology, as shown if Figures \ref{FIG:onto} and \ref{FIG:sem}.
 
@@
 well-formed source descriptions, but only one or a few will capture the intended
-meaning of the source. Our goal is to automatically build $\delta^\star$ such 
-that it minimizes the \emph{graph edit distance} (GED) from the semantic model 
-$m^\star$ to the semantic model $m^\dag$ that the user considers correct.
-
-The GED is a measure of similarity between two graphs defined as follows for 
-two graphs $g_1$ and $g_2$: $GED(g_1,g_2) = min_{(e_1 ,...,e_k)\in P} 
-\sum_{i=1}^{k}c(e_i)$ where $P$ denotes the set of edit paths transforming 
-$g_1$ into (a graph
-isomorphic to) $g_2$ and $c(e) \geq 0$ is the cost of each graph edit operation 
-$e$. Graph edit operations include among others node insertion, edge deletion, 
-etc. \cite{gao2010survey}. In practice, we use some approximation measures of 
-the graph edit distance. \ddg{which approx?}
+meaning of the source. 
+Our goal is to automatically build $\delta^\star$ such that it maximizes the \emph{precision} and \emph{recall} from the semantic model 
+$m^\star$ to the semantic model $m^\dag$ that the user considers correct. \npr{definitions for precision and recall}
 
@@
 
-The first step to model the semantics of a new source $s^\star$ is to recognize 
-the semantic types present in the source. 
-We call this step \emph{semantic labeling}, which involves giving a confidence 
-value to a match occurring between an attribute from $s^\star$ and type $l \in 
+The first step to model the semantics of a new source $s^\star$ is to recognize the semantic types present in the source. 
+We call this step \emph{semantic labeling}, which involves giving a confidence value to a match occurring between an attribute from $s^\star$ and type $l \in 
 \mathcal{L_O}$. \ddg{CHECK!}
@@
 We formulate the problem of semantic labeling as a multi-class classification
-problem. The known source descriptions $S_T$ provide us the training sample. We
-compute a feature vector for each source \ddg{Which features?} attribute and 
-associate the known
-semantic type with the corresponding feature vector. We train a random forest
-on this sample. Then we use the learnt model to classify attributes in the new
+problem.
+The known source descriptions $S_T$ provide us the training sample.
+We compute a feature vector for each source \ddg{Which features?} attribute and associate the known semantic type with the corresponding feature vector. We train a random forest on this sample. 
+Then we use the learnt model to classify attributes in the new
 source.
@@
 what is $k$?}
+\npr{We keep all, that is the crucial difference from Karma which does some voodoo heuristic filtering}
 
@@
 Note how the alignment graph contains data nodes that correspond to at least 
-some of the semantic types. For instance, it could contain two nodes 
-$City.name$ and $State.name$ rather than just one node $name$ connected to two 
+some of the semantic types. 
+For instance, it could contain two nodes $City.name$ and $State.name$ rather than just one node $name$ connected to two 
 nodes $City$ and $State$. We say these nodes are \emph{induced} into the 
@@
 the known semantic models have lower weights than those 
-which are inferred from the ontology. As we will see int he next section, this 
-makes edges present in semantic models more attractive. \ddg{How exactly are 
+which are inferred from the ontology.
+As we will see in the next section, this makes edges present in semantic models more attractive. \ddg{How exactly are 
 they weighted?}
 
-An example alignment graph is illustrated in Fig. \ref{FIG:ali}. Bigger 
-examples 
-can be found in \cite{Taheriyan2013}. Black links 
-correspond to the links which are supported by the known semantic models. Blue 
-and orange links are inferred from the ontology $\mathcal{O}$ (the orange ones 
-correspond to the ones added to connect Classes of the ontology that never 
-appeared in the semantic models) and can be assigned the 
+An example alignment graph is illustrated in Fig. \ref{FIG:ali}. 
+Bigger examples can be found in \cite{Taheriyan2013}. 
+Black links correspond to the links which are supported by the known semantic models. 
+Blue and orange links are inferred from the ontology $\mathcal{O}$ (the orange ones correspond to the ones added to connect Classes of the ontology that never appeared in the semantic models) and can be assigned the
 maximum weight $w_max$ \ddg{where does this weight come from?} .
@@
 
-\subsection{Frequent Subgraph Pattern Mining \label{SSEC:pattern-mining}}
+\subsection{Frequent Graph Pattern Mining \label{SSEC:pattern-mining}}
 
-As an extension to the problem, we consider using pattern mining techniques in 
-order to identify patterns in the training set of semantic model that repeat 
-themselves often. The hope is that with such information we can encourage the 
-semantic model $m^\star$ for the new source to use groups of edges that 
-appeared often together in training semantic models.
+As an extension to the problem, we consider using pattern mining techniques in order to identify patterns in the training set of semantic model that repeat themselves often. 
+The hope is that with such information we can encourage the semantic model $m^\star$ for the new source to use groups of edges that                                       appeared often together in training semantic models.
 
@@
 There exists a range of tools that can achieve this task using Transactional 
-Frequent Graph Pattern Mining
-\cite{petermann2017dimspan,yan2002gspan}. We chose to use DIMSpan 
-\cite{petermann2017dimspan}. \ddg{CHECK! How do they solve an NP-complete 
-problem??}
+Frequent Graph Pattern Mining\cite{petermann2017dimspan,yan2002gspan}. 
+We chose to use DIMSpan \cite{petermann2017dimspan}. 
+\ddg{CHECK! How do they solve an NP-complete problem??}
+\npr{Im not sure what to say here: there is just no guarantee how long it will take for the whole thing to run, except there is a threshold on how frequent they have to be; they use gSpan procedure to prune patterns and a variant of Ulmans algorithm for graph pattern matching}
 
 This tool provides us with a list of patterns that are frequent, as well as 
-their support. The \emph{support} of a pattern is a measure of frequency. Thus 
-the higher the support, the more often the pattern appears. This typically 
-means that big patterns have low support.
+their support. 
+The \emph{support} of a pattern is a measure of frequency. 
+Thus, the higher the support, the more often the pattern appears. This typically means that big patterns have low support.
 
@@
 Examples of these situations can be found in domain specific data 
-\cite{Pham2016} or HTML 
-tables \cite{ritze2017matching}.
+\cite{Pham:semantic} or HTML tables \cite{Ritze:matching}.
+In current systems, these columns are removed in a reprocess that requires extra time and effort as this is typically done manually in the real world.
 
@@
 Eq. \ref{EQ:patt} indicated that a pattern is used if and only if all its edges 
-are selected in the tree. Eq. \ref{EQ:pcost} computes the prizes collected by 
-using patterns.
+are selected in the tree. Eq. \ref{EQ:pcost} computes the prizes collected by using patterns.
 Eq. \ref{EQ:unk} ensures that if the \emph{unknown} class node is used, then it 
@@
 
+We run experiments on two domains: museum and soccer (see Fig.~\ref{tab:data} for statistics).
+
+\begin{table}[ht]\small
+  \centering
+  \caption{Description of data sources.}\label{tab:data}
+		\begin{tabular}{ccccc} 
+		\hline
+		\multirow{2}{*}{\textbf{Domain}} & \# data & \# semantic & \# & \# unknown\\
+		 & sources & labels & attributes & attributes\\
+		\hline
+		museum & 29 & 20 & 443 & 159  \\
+		soccer & 12 & 18 & 138 & 42 \\
+		\hline
+		\end{tabular} 
+\end{table}
+
+%\begin{table*}[ht]
+%  \centering
+%  \caption{Description of data sources.}\label{tab:data}
+%		\begin{tabular}{ccccccc} 
+%		\hline
+%		\multirow{2}{*}{\textbf{Domain}} & \# & \# semantic & \# & \# unknown & avg \# rows & avg \# attributes\\
+%		 & sources & labels & attributes & attributes & per source & per source\\
+%		\hline
+%		museum & 29 & 20 & 443 & 159 & 6978.89 & 15.27 \\
+%		soccer & 12 & 18 & 138 & 42 & 2120.16 & 11.5 \\
+%		\hline
+%		\end{tabular} 
+%\end{table*}
+
 \subsection{Experimental Results}
@@
 
-\section{Conclusions}
+\begin{table}[t]\small
+  \centering
+  \caption{Average performance of semantic labeling for leave one out strategy.}
+  	\label{tab:unknownloo}
+  	\begin{tabular}{c|cc|cc} 
+  		\hline
+  		\multirow{2}{*}{Model} & \multicolumn{2}{c|}{MRR scores} & \multicolumn{2}{c}{Train time ($s$)}\\
+  		 & museum & soccer & museum & soccer\\
+  		\hline
+  		DSL & 0.56 & 0.618 & 156.6 & 36.3\\
+ 		Serene & 0.866 & 0.827 & 100.6 & 6.8\\
+  		\hline
+		\end{tabular} 
+%\vspace*{-3mm}
+\end{table}
+
+\section{Related Work \label{SEC:pw}}
+\ddg{rewrite, add more}
+
+Relational data sources are still one of the most popular ways to store enterprise or Web data, however, the issue with relational schema is the lack of a well-defined semantic description.
+A common ontology provides a way to represent the meaning of a relational schema and can facilitate the integration of heterogeneous data sources within a domain.
+Indicating semantic correspondences manually might be appropriate if only few data sources need to be integrated, however, it becomes tedious with the growing number of heterogeneous schemata.
+Hence, automatic or semi-automatic approaches for relational-to-ontology schema mapping are being actively developed.
+
+The majority of approaches to solve the relational-to-ontology (\relonto{}) mapping problem are based on heuristic rules and alignment of constraints specified within relational schemata and ontologies.
+A very comprehensive overview and comparison of existing mapping generation tools based on this approach is given in~\cite{Pinkel:rodi} and~\cite{Spanos:semweb}.
+As examples, there are BootOX~\cite{Jimenez:Bootox}, MIRROR~\cite{Luciano:Mirror} and  ontop~\cite{Fagin:Clio}.
+Crudely speaking, these tools first apply a default direct mapping specified by the W3C.
+Further, the default ontology is enriched by using explicit and implicit schema constraints.
+Finally, ontology alignment techniques are applied to match the default ontology to the target ontology.
+The main advantage of these systems is the ability to run in a fully automatic setting.
+Our approach is complementary to the approaches from this group and at its current stage is semi-automatic.
+However, constraint programming offers a convenient framework to incorporate integrity constraints specified either within relational or ontological schema as additional constraints to govern the search for the solution.
+This opens an interesting direction for further research to develop an automatic system.
+
+A major issue with fully automatic systems is though that constraints may be inconsistent or absent completely, e.g., tables on the Web \ddg{Why?}.
+To overcome this issue, we can apply ML techniques.
+\cite{Limaye:Annotating} design a system to annotate web tables with entities for cell values, semantic labels for attributes and relationships for binary combinations of attributes.
+As in our approach, they decompose the process of mapping into two main stages: semantic labeling and finding relationships between matched semantic labels.
+\cite{Limaye:Annotating} enrich their data sources by using YAGO.
+\cite{Mulwad:Semantic} extend this approach by leveraging information from Wikitology Knowledge Base (KB).
+\cite{Venetis:Recovering} develop a scalable approach to recover the semantics of Web tables by incorporating data from the isA database KB.
+\cite{Ritze:matching}, on the other hand, use DBPedia as their KB.
+%extract additional data from knowledge bases to assign a semantic label to an attribute.
+Hence, these approaches are limited to domains well represented in those knowledge bases.
+Also, they are not able to find the relation between attributes in the table if there is no direct connection between the attributes.
+Our approach, on the other hand, allows a model to be trained on any data and can infer complex semantic paths which might exist between attributes.
+However, it might be further bootstrapped by leveraging external knowledge bases.
+This is especially beneficial at the start when the system does not have sufficient training data.
+
+As mentioned above, the approaches for mapping Web tables also perform semantic labeling.
+They design various similarity metrics for attribute names and attribute values.
+However, they disregard the attributes which are not matched to the ontology (the so-called \emph{unknown} class of attributes).
+It is clear that we cannot directly speak about similarity for unmatched attributes, since they are rather dissimilar from known semantic types.
+That is why we have developed a new approach for semantic labeling which can efficiently handle the \emph{unknown} class.
+We demonstrate its efficiency by comparing against the state-of-the-art approach DSL~\cite{Pham:semantic}.
+
+We build upon the work of~\cite{taheriyan2016learning} and use their ideas for the construction of the alignment graph.
+The only difference is that we introduce the \emph{unknown} and \emph{root} class nodes and as many \emph{unknown} data nodes as there are attributes in the modeled data source.
+These nodes serve to capture the unmatched attributes from the source.
+Though we have modified Karma to treat these additional nodes as well, our approach outperforms Karma since we have additional constraints for these nodes and use an exact algorithm to solve the STP.
+\cite{taheriyan2016learning} treat the matching and STP parts of \relonto{} independently and use heuristic algorithms for both.
+We, on the other hand, use exact algorithms for both parts and address them within a unified CP model.
+
+In their follow up work, \cite{Taheriyan:Leveraging} suggest to use graph patterns to boost the performance of their system.
+To perform semantic modeling in such scenario, \cite{Taheriyan:Leveraging} had to revise their algorithm by introducing additional heuristics.
+However, in our case we had to add pattern variables and to modify the objective function in the MiniZinc model.
+No changes to the solver were required.
+This makes our system very convenient and opens directions for validating various additional constraints.
+Though our approach beats the state-of-the-art system Karma in the conducted experiments, it is worth noting that the scalability of our approach is under question.
+The main argument why exact solution for STP is feasible in our setting is that we map data sources to a domain-specific ontology which is expected to be limited in its size.
+
+\ddg{Isn't this really similar??}
+\npr{It is very similar, I'm even using their code partially :)}
+
+\section{Conclusion}
 \ddg{TODO} 
+In this paper we have introduced a new approach to solve the problem of relational-to-ontology schema mapping.
+
+Future directions:
+incorporate Linked Open Data and other external knowledge bases to overcome cold start problem;
+incorporate schema and ontology constraints.
 
 \bibliographystyle{aaai}
+\npr{shorten citations}
 \bibliography{main}

### 2017-08-17 stp/alignment.py

@@ -22,7 +22,7 @@ except ImportError as e:
     sys.path.insert(0, '.')
     import serene
 from serene import Column, DataNode, ClassNode, ClassInstanceLink, ColumnLink, ObjectLink, DataLink,\
-    ALL_CN, DEFAULT_NS, UNKNOWN_CN
+    ALL_CN, DEFAULT_NS, UNKNOWN_CN, SSD
 
 
 def label(node):
@@ -343,12 +343,14 @@ def process_unknown(ssd, semantic_types):
 
     return mod_ssd
 
-def convert_ssd(ssd, integration_graph, file_name):
+
+def convert_ssd(ssd, integration_graph, file_name=None, clean_ssd=True):
     """
     Convert our ssd to nx object re-using ids from the integration graph whenever possible
     :param ssd: SSD instance
     :param integration_graph: nx MultiDigraph
-    :param file_name: name of the file to write the converted ssd
+    :param file_name: name of the file to write the converted ssd; default None
+    :param clean_ssd: boolean whether to remove extra "connect" links for the node "All"
     :return:
     """
     data_node_map = construct_data_node_map(integration_graph)
@@ -418,24 +420,26 @@ def convert_ssd(ssd, integration_graph, file_name):
             g.add_edge(ssd_node_map[source], ssd_node_map[target], attr_dict=link_data)
 
     # clean ssd: leave only 2 links for All
-    all_id = [n for (n, n_data) in g.nodes(data=True) if
-              n_data["type"] == "ClassNode" and n_data["label"] == ALL_CN]
-    unknown_id = [n for (n, n_data) in g.nodes(data=True) if
-              n_data["type"] == "ClassNode" and n_data["label"] == UNKNOWN_CN]
-    if len(all_id) and len(unknown_id):
-        all_id, unknown_id = all_id[0], unknown_id[0]
-        all_neigh = [(s, t, ld["weight"]) for (s, t, ld) in g.out_edges([all_id], data=True) if t != unknown_id]
-        min_weight = min(ld for (s, t, ld) in all_neigh)
-        keep = min(t for (s, t, ld) in all_neigh if ld == min_weight)
-        logging.info("Removing extra connect links: {}".format(len(all_neigh)-1))
-        for s, t, ld in all_neigh:
-            if t != keep:
-                g.remove_edge(s, t)
+    if clean_ssd:
+        all_id = [n for (n, n_data) in g.nodes(data=True) if
[…]

### 2017-08-17 stp/integration.py

@@ -11,9 +11,10 @@ import networkx as nx
 import yaml
 import os
 from collections import defaultdict
-from .minizinc import *
+from minizinc import *
 import subprocess
 import re
+import time
 import json
 from pygraphviz import AGraph
 from serene.elements.semantics.base import KARMA_DEFAULT_NS, DEFAULT_NS, ALL_CN, OBJ_PROP, UNKNOWN_CN, UNKNOWN_DN
@@ -23,7 +24,16 @@ class IntegrationGraph(object):
     """
     Integration graph to map a relational data source onto an ontology using a CP solver
     """
-    def __init__(self, octopus, dataset, match_threshold=0.0, simplify_graph=False, patterns=None):
+    UNKNOWN_SCORE = 5.0
+
+    def __init__(self, octopus, dataset, match_threshold=0.0,
+                 simplify_graph=False,
+                 patterns=None,
+                 pattern_sign=1.0,
+                 predicted_df=None,
+                 alignment_graph=None,
+                 alignment_node_map=None,
+                 alignment_link_map=None):
         """
         Octopus should be trained.
         :param octopus: Octopus object which is used to integrate the new data source
@@ -31,6 +41,12 @@ class IntegrationGraph(object):
         :param match_threshold: threshold on match links
         :param simplify_graph: Remove edges that are heavier than some path between its endpoints
         :param patterns: csv file with patterns, None if there will be no patterns
+        :param pattern_sign: positive float number which indicates significance of pattern weights
+                (they will be divided by this number)
+        :param predicted_df: pandas dataframe with predictions
+        :param alignment_graph: networkx multidigraph for the alignment graph
+        :param alignment_node_map: dictionary
+        :param alignment_link_map: dictionary
         :return:
         """
         logging.info("Initializing integration graph for the dataset {} using octopus {}".format(
@@ -41,22 +57,34 @@ class IntegrationGraph(object):
         self._match_threshold = match_threshold  # discard matches with confidence score < threshold
         self._simplify_graph = simplify_graph
         self._patterns = patterns
+        if pattern_sign <= 0:  # this number can be only positive
+            pattern_sign = 1.0
+        self._pattern_sign = pattern_sign
+        self._predicted_df = predicted_df
 
         # the integration graph contains the alignment graph at the beginning
-        self.graph, self._node_map, self._link_map = self._get_initial_alignment()
+        self.graph, self._node_map, self._link_map = self._get_initial_alignment(alignment_graph,
+                                                                                 alignment_node_map,
[…]

### 2017-08-17 stp/minizinc/utils.py

@@ -14,11 +14,13 @@ list2D2dznsetlist = lambda l: "["+_list2D2dznsetlist(l)+"];"
 
 #This needs to be done better
 def weight_conversion(v):
-    """If Chuffed is used to solve this STP, it does NOT support floats.
+    """
+    If Chuffed is used to solve this STP, it does NOT support floats.
     Therefore a conversion is made to get a higher precision by multiplying the 
     floats by 10000.
     Nonetheless, if some edge is way too heavy, this multiplication may overflow ints.
-    Therefore we do a pretty mediocre conversion...."""
+    Therefore we do a pretty mediocre conversion....
+    """
     fac = 10000 if v < 100 else 100
     return v*fac
 

### 2017-08-17 stp/museum_test.py

@@ -1,0 +1,274 @@
+# ===========
+#    SETUP
+# ===========
+try:
+    import serene
+except ImportError as e:
+    import sys
+    sys.path.insert(0, '.')
+    import serene
+
+import os
+import tarfile
+from importlib import reload
+import csv
+
+if "SERENE_PYTHON" not in os.environ:
+    os.environ["SERENE_PYTHON"] = "/home/natalia/PycharmProjects/serene-python-client"
+
+project_path = os.environ["SERENE_PYTHON"]
+
+from serene import SSD
+from serene.elements.semantics.base import KARMA_DEFAULT_NS, DEFAULT_NS, ALL_CN, OBJ_PROP, UNKNOWN_CN, UNKNOWN_DN
+
+try:
+    import integration as integ
+    import alignment as al
+except ImportError as e:
+    import sys
+    sys.path.insert(0, '.')
+    import integration as integ
+    import alignment as al
+
+import logging
+from logging.handlers import RotatingFileHandler
+
+# setting up the logging
+log_file = os.path.join(project_path, "stp", "resources", 'benchmark_stp.log')
+log_formatter = logging.Formatter('%(asctime)s %(levelname)s %(module)s: %(message)s',
+                                  '%Y-%m-%d %H:%M:%S')
+my_handler = RotatingFileHandler(log_file, mode='a', maxBytes=5 * 1024 * 1024,
+                                 backupCount=5, encoding=None, delay=0)
+my_handler.setFormatter(log_formatter)
+my_handler.setLevel(logging.DEBUG)
+# logging.basicConfig(filename=log_file,
+#                     level=logging.DEBUG, filemode='w+',
+#                     format='%(asctime)s %(levelname)s %(module)s: %(message)s', datefmt='%m/%d/%Y %I:%M:%S %p')
+
+log = logging.getLogger()
+log.setLevel(logging.DEBUG)
+log.addHandler(my_handler)
+# =======================
+#
+#  Start with a connection to the server...
+#
+# =======================
+sn = serene.Serene(
+    host='127.0.0.1',
+    port=8080,
+)
+print(sn)
+
+if "SERENE_BENCH" not in os.environ:
+    os.environ["SERENE_BENCH"] = os.path.join(project_path, "tests", "resources")
+
+benchmark_path = os.path.join(os.environ["SERENE_BENCH"], "museum_benchmark")
+print("benchmark_path: ", benchmark_path)
+
[…]

### 2017-08-17 stp/museum_test_unknown.py

@@ -1,0 +1,506 @@
+# ===========
+#    SETUP
+# ===========
+try:
+    import serene
+except ImportError as e:
+    import sys
+    sys.path.insert(0, '.')
+    import serene
+
+import os
+import tarfile
+from importlib import reload
+import csv
+
+if "SERENE_PYTHON" not in os.environ:
+    os.environ["SERENE_PYTHON"] = "/home/natalia/PycharmProjects/serene-python-client"
+
+project_path = os.environ["SERENE_PYTHON"]
+
+from serene import SSD
+from serene.elements.semantics.base import KARMA_DEFAULT_NS, DEFAULT_NS, ALL_CN, OBJ_PROP, UNKNOWN_CN, UNKNOWN_DN
+
+try:
+    import integration as integ
+    import alignment as al
+except ImportError as e:
+    import sys
+    sys.path.insert(0, '.')
+    import integration as integ
+    import alignment as al
+
+import logging
+from logging.handlers import RotatingFileHandler
+
+# setting up the logging
+log_file = os.path.join(project_path, "stp", "resources", 'benchmark_stp.log')
+log_formatter = logging.Formatter('%(asctime)s %(levelname)s %(module)s: %(message)s',
+                                  '%Y-%m-%d %H:%M:%S')
+my_handler = RotatingFileHandler(log_file, mode='a', maxBytes=5 * 1024 * 1024,
+                                 backupCount=5, encoding=None, delay=0)
+my_handler.setFormatter(log_formatter)
+my_handler.setLevel(logging.DEBUG)
+# logging.basicConfig(filename=log_file,
+#                     level=logging.DEBUG, filemode='w+',
+#                     format='%(asctime)s %(levelname)s %(module)s: %(message)s', datefmt='%m/%d/%Y %I:%M:%S %p')
+
+log = logging.getLogger()
+log.setLevel(logging.DEBUG)
+log.addHandler(my_handler)
+
+# =======================
+#
+#  Start with a connection to the server...
+#
+# =======================
+sn = serene.Serene(
+    host='127.0.0.1',
+    port=8080,
+)
+print(sn)
+
+if "SERENE_BENCH" not in os.environ:
+    os.environ["SERENE_BENCH"] = os.path.join(project_path, "tests", "resources")
+
+benchmark_path = os.path.join(os.environ["SERENE_BENCH"], "museum_benchmark")
+
+print("benchmark_path: ", benchmark_path)
+
[…]

### 2017-08-17 stp/soccer_test_unknown.py

@@ -1,0 +1,396 @@
+# ===========
+#    SETUP
+# ===========
+try:
+    import serene
+except ImportError as e:
+    import sys
+    sys.path.insert(0, '.')
+    import serene
+
+import os
+import tarfile
+from importlib import reload
+import csv
+
+if "SERENE_PYTHON" not in os.environ:
+    os.environ["SERENE_PYTHON"] = "/home/natalia/PycharmProjects/serene-python-client"
+
+project_path = os.environ["SERENE_PYTHON"]
+
+from serene import SSD
+from serene.elements.semantics.base import KARMA_DEFAULT_NS, DEFAULT_NS, ALL_CN, OBJ_PROP, UNKNOWN_CN, UNKNOWN_DN
+
+try:
+    import integration as integ
+    import alignment as al
+except ImportError as e:
+    import sys
+    sys.path.insert(0, '.')
+    import integration as integ
+    import alignment as al
+
+import logging
+from logging.handlers import RotatingFileHandler
+
+# setting up the logging
+log_file = os.path.join(project_path, "stp", "resources", 'benchmark_stp.log')
+log_formatter = logging.Formatter('%(asctime)s %(levelname)s %(module)s: %(message)s',
+                                  '%Y-%m-%d %H:%M:%S')
+my_handler = RotatingFileHandler(log_file, mode='a', maxBytes=5 * 1024 * 1024,
+                                 backupCount=5, encoding=None, delay=0)
+my_handler.setFormatter(log_formatter)
+my_handler.setLevel(logging.DEBUG)
+# logging.basicConfig(filename=log_file,
+#                     level=logging.DEBUG, filemode='w+',
+#                     format='%(asctime)s %(levelname)s %(module)s: %(message)s', datefmt='%m/%d/%Y %I:%M:%S %p')
+
+log = logging.getLogger()
+log.setLevel(logging.DEBUG)
+log.addHandler(my_handler)
+
+# =======================
+#
+#  Start with a connection to the server...
+#
+# =======================
+sn = serene.Serene(
+    host='127.0.0.1',
+    port=8080,
+)
+print(sn)
+
+if "SERENE_BENCH" not in os.environ:
+    os.environ["SERENE_BENCH"] = os.path.join(project_path, "tests", "resources")
+
+benchmark_path = os.path.join(os.environ["SERENE_BENCH"], "soccer")
+
+print("benchmark_path: ", benchmark_path)
+
[…]

### 2017-08-17 stp/stp_experiments.py

@@ -1,0 +1,277 @@
+# ===========
+#    SETUP
+# ===========
+try:
+    import serene
+except ImportError as e:
+    import sys
+    sys.path.insert(0, '.')
+    import serene
+
+import os
+import tarfile
+from importlib import reload
+import csv
+
+if "SERENE_PYTHON" not in os.environ:
+    os.environ["SERENE_PYTHON"] = "/home/natalia/PycharmProjects/serene-python-client"
+
+project_path = os.environ["SERENE_PYTHON"]
+
+from serene import SSD
+from serene.elements.semantics.base import KARMA_DEFAULT_NS, DEFAULT_NS, ALL_CN, OBJ_PROP, UNKNOWN_CN, UNKNOWN_DN
+
+try:
+    import integration as integ
+    import alignment as al
+except ImportError as e:
+    import sys
+    sys.path.insert(0, '.')
+    import integration as integ
+    import alignment as al
+
+import logging
+from logging.handlers import RotatingFileHandler
+
+# setting up the logging
+log_file = os.path.join(project_path, "stp", "resources", 'benchmark_stp.log')
+log_formatter = logging.Formatter('%(asctime)s %(levelname)s %(module)s: %(message)s',
+                                  '%Y-%m-%d %H:%M:%S')
+my_handler = RotatingFileHandler(log_file, mode='a', maxBytes=5 * 1024 * 1024,
+                                 backupCount=5, encoding=None, delay=0)
+my_handler.setFormatter(log_formatter)
+my_handler.setLevel(logging.DEBUG)
+# logging.basicConfig(filename=log_file,
+#                     level=logging.DEBUG, filemode='w+',
+#                     format='%(asctime)s %(levelname)s %(module)s: %(message)s', datefmt='%m/%d/%Y %I:%M:%S %p')
+
+log = logging.getLogger()
+log.setLevel(logging.DEBUG)
+log.addHandler(my_handler)
+# =======================
+#
+#  Start with a connection to the server...
+#
+# =======================
+sn = serene.Serene(
+    host='127.0.0.1',
+    port=8080,
+)
+print(sn)
+
+if "SERENE_BENCH" not in os.environ:
+    os.environ["SERENE_BENCH"] = os.path.join(project_path, "tests", "resources")
+
+benchmark_path = os.path.join(os.environ["SERENE_BENCH"], "museum_benchmark")
+print("benchmark_path: ", benchmark_path)
+
[…]

### 2017-08-17 stp/stp_experiments_unknown.py

@@ -1,0 +1,397 @@
+# ===========
+#    SETUP
+# ===========
+try:
+    import serene
+except ImportError as e:
+    import sys
+    sys.path.insert(0, '.')
+    import serene
+
+import os
+import tarfile
+from importlib import reload
+import csv
+
+if "SERENE_PYTHON" not in os.environ:
+    os.environ["SERENE_PYTHON"] = "/home/natalia/PycharmProjects/serene-python-client"
+
+project_path = os.environ["SERENE_PYTHON"]
+
+from serene import SSD
+from serene.elements.semantics.base import KARMA_DEFAULT_NS, DEFAULT_NS, ALL_CN, OBJ_PROP, UNKNOWN_CN, UNKNOWN_DN
+
+try:
+    import integration as integ
+    import alignment as al
+except ImportError as e:
+    import sys
+    sys.path.insert(0, '.')
+    import integration as integ
+    import alignment as al
+
+import logging
+from logging.handlers import RotatingFileHandler
+
+# setting up the logging
+log_file = os.path.join(project_path, "stp", "resources", 'benchmark_stp.log')
+log_formatter = logging.Formatter('%(asctime)s %(levelname)s %(module)s: %(message)s',
+                                  '%Y-%m-%d %H:%M:%S')
+my_handler = RotatingFileHandler(log_file, mode='a', maxBytes=5 * 1024 * 1024,
+                                 backupCount=5, encoding=None, delay=0)
+my_handler.setFormatter(log_formatter)
+my_handler.setLevel(logging.DEBUG)
+# logging.basicConfig(filename=log_file,
+#                     level=logging.DEBUG, filemode='w+',
+#                     format='%(asctime)s %(levelname)s %(module)s: %(message)s', datefmt='%m/%d/%Y %I:%M:%S %p')
+
+log = logging.getLogger()
+log.setLevel(logging.DEBUG)
+log.addHandler(my_handler)
+
+# =======================
+#
+#  Start with a connection to the server...
+#
+# =======================
+sn = serene.Serene(
+    host='127.0.0.1',
+    port=8080,
+)
+print(sn)
+
+if "SERENE_BENCH" not in os.environ:
+    os.environ["SERENE_BENCH"] = os.path.join(project_path, "tests", "resources")
+
+benchmark_path = os.path.join(os.environ["SERENE_BENCH"], "museum_benchmark")
+
+print("benchmark_path: ", benchmark_path)
+
[…]

### 2017-08-17 stp/unknown_benchmark.py

@@ -181,7 +181,7 @@ def create_octopus(ssd_range, sample):
     octo_local = sn.Octopus(
         ssds=[ssd_range[i] for i in sample],
         ontologies=ontologies,
-        name='octopus-unknown',
+        name='num_{}'.format(len(sample)),
         description='Testing example for places and companies',
         resampling_strategy="NoResampling",  # optional
         num_bags=80,  # optional
@@ -194,10 +194,10 @@ def create_octopus(ssd_range, sample):
             "mappingBranchingFactor": 50,
             "numCandidateMappings": 10,
             "topkSteinerTrees": 50,
-            "multipleSameProperty": False,
+            "multipleSameProperty": True,
             "confidenceWeight": 1.0,
             "coherenceWeight": 1.0,
-            "sizeWeight": 0.5,
+            "sizeWeight": 1.0,
             "numSemanticTypes": 10,
             "thingNode": False,
             "nodeClosure": True,
@@ -282,65 +282,135 @@ reload(al)
 reload(serene)
 
 
+def semantic_label_df(cur_ssd, col_name="pred_label"):
+    """
+    Get schema matcher part from ssd
+    :param cur_ssd: SSD
+    :param col_name: name to be given to the column which has the label
+    :return: pandas dataframe
+    """
+    ff = [(v.id, k.class_node.label + "---" + k.label) for (k, v) in cur_ssd.mappings.items()]
+    return pd.DataFrame(ff, columns=["column_id", col_name])
+
+
+import sklearn.metrics
+def compare_semantic_label(one_df, two_df):
+    """
+
+    :param one_df:
+    :param two_df:
+    :return:
+    """
+    merged = one_df.merge(two_df, on="column_id", how="outer")
+    y_true = merged["user_label"].as_matrix()
+    y_pred = merged["label"].as_matrix()
+    accuracy = sklearn.metrics.accuracy_score(y_true, y_pred)  # np.mean(y_pred == y_true)
+    fmeasure = sklearn.metrics.f1_score(y_true, y_pred, average='macro')
+    return {"accuracy": accuracy, "fmeasure": fmeasure}
+
+
 def do_chuffed(ch_octopus, ch_dataset, ch_column_names, ch_ssd, orig_ssd,
-               train_flag=False, chuffed_path=None, simplify=True, patterns=None):
+               train_flag=False, chuffed_path=None, simplify=True,
+               patterns=None, experiment="loo", soft_assumptions=False,
[…]

### 2017-08-17 tests/semantics/test_soccer_benchmark.py

@@ -1,0 +1,163 @@
+"""
+Copyright (C) 2017 Data61 CSIRO
+Licensed under http://www.apache.org/licenses/LICENSE-2.0 <see LICENSE file>
+
+Tests the soccer benchmark
+"""
+import os
+import logging
+import tarfile
+import csv
+
+from serene.elements import SSD
+from serene.endpoints import DataSetEndpoint, OntologyEndpoint, SSDEndpoint
+from ..utils import TestWithServer
+from serene.elements.semantics.base import KARMA_DEFAULT_NS
+
+# logging functions...
+_logger = logging.getLogger()
+_logger.setLevel(logging.DEBUG)
+
+
+class TestSoccer(TestWithServer):
+    """
+    Tests the JsonReader/JsonWriter for SSD
+    """
+
+    def __init__(self, method_name="runTest"):
+        super().__init__(method_name)
+        self._datasets = None
+        self._ontologies = None
+
+        self._benchmark_path = os.path.join(os.path.dirname(os.path.dirname(__file__)), "resources", "soccer")
+        self._soccer_owl_dir = os.path.join(self._benchmark_path, "owl")
+        self._soccer_data = os.path.join(self._benchmark_path, 'dataset')
+        self._soccer_ssd = os.path.join(self._benchmark_path, 'ssd')
+
+    def setUp(self):
+        self._datasets = DataSetEndpoint(self._session)
+        self._ontologies = OntologyEndpoint(self._session)
+        self._ssds = SSDEndpoint(self._session, self._datasets, self._ontologies)
+        self._clear_storage()
+
+        _logger.debug("SetUp complete")
+
+    def tearDown(self):
+        """
+        Be sure to remove all storage elements once a test is finished...
+        :return:
+        """
+        # self._clear_storage()
+        pass
+
+    def _add_owls(self):
+        # add ontologies
+        ontologies = []
+        for path in os.listdir(self._soccer_owl_dir):
+            f = os.path.join(self._soccer_owl_dir, path)
+            ontologies.append(self._ontologies.upload(f))
+        return ontologies
+
+    def _add_datasets(self, ontologies):
+
+
+        # add datasets with their ssds
+        for ds in os.listdir(self._soccer_data):
+            if ds.endswith(".gz"):
+                continue  # skip archive
+            ds_f = os.path.join(self._soccer_data, ds)
+            # ds_name = os.path.splitext(ds)[0]
+            ds_name = ds
+            ssd_f = os.path.join(self._soccer_ssd, ds_name + ".ssd")
+
[…]

### 2017-08-17 tests/test_integrationGraph.py

@@ -8,6 +8,7 @@ Test class for the IntegrationGraph which uses the chuffed solver
 import unittest2 as unittest
 import logging
 import os
+import tarfile
 
 from .utils import TestWithServer
 from serene.elements import SSD
@@ -25,7 +26,7 @@ class TestIntegrationGraph(TestWithServer):
         self._datasets = None
         self._ontologies = None
 
-        self._benchmark_path = os.path.join(os.path.dirname(os.path.dirname(__file__)), "resources", "museum_benchmark")
+        self._benchmark_path = os.path.join(os.path.dirname(os.path.dirname(__file__)), "tests","resources", "museum_benchmark")
         self._museum_owl_dir = os.path.join(self._benchmark_path, "owl")
         self._museum_data = os.path.join(self._benchmark_path, 'dataset')
         self._museum_ssd = os.path.join(self._benchmark_path, 'ssd')
@@ -80,6 +81,9 @@ class TestIntegrationGraph(TestWithServer):
 
     def _clear_storage(self):
         """Removes all server elements"""
+        for oc in self._serene.octopii.items:
+            self._serene.octopii.remove(oc)
+
         for ssd in self._ssds.items:
             self._ssds.remove(ssd)
 

### 2017-08-17 tests/utils.py

@@ -26,6 +26,7 @@ class SereneTestServer(object):
         self.host = None
         self.port = None
         self.SERENE_TEST_SERVER_PATH = 'SERENE_TEST_SERVER_PATH'
+        self.launch_server = True
 
     def setup(self):
         path = os.path.join(os.path.dirname(os.path.dirname(__file__)), "tests")
@@ -33,7 +34,7 @@ class SereneTestServer(object):
             config = yaml.load(stream)
 
         # Test if we need to launch a server here...
-        launch_server = config['launch-test-server']
+        self.launch_server = config['launch-test-server']
 
         # If launch-test-server is true, then this variable points to
         # the executable which will launch the server. If launch-test-server
@@ -51,7 +52,7 @@ class SereneTestServer(object):
         version = "v1.0"
 
         # if we need to, we start the server with a temporary storage directory
-        if launch_server:
+        if self.launch_server:
             self.server = subprocess.Popen(
                 [filename,
                  "--port", str(port),
@@ -93,7 +94,8 @@ class SereneTestServer(object):
         return False
 
     def tear_down(self):
-        self.server.kill()
+        if self.launch_server:
+            self.server.kill()
 
 
 class TestWithServer(unittest.TestCase):

### 2017-08-18 stp/paper_aaai/main.tex
reduced figure a bit. Taken Natalia's responses to my questions into account. Still one page of free space

@@
 	\node[class] (pe) at (0,0)  {Person};
-	\node[class] (co) at (0,-3) {Organisation};
-	\node[class] (ev) at (3.5,1) {Event};
+	\node[class] (co) at (0,-2.5) {Organisation};
+	\node[class] (ev) at (3,0.5) {Event};
 	\node[class] (pl) at (5,-1) {Place};
-	\node[class] (ci) at (3,-3) {City};
-	\node[class] (st) at (5,-3) {State};
+	\node[class] (ci) at (3,-2.5) {City};
+	\node[class] (st) at (5,-2.5) {State};
 
@@
 	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
-	node [midway, below, sloped] {name} (-1,-5);
+	node [midway, below, sloped] {name} (-1,-4);
 	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
-	node [midway, above, sloped] {phone} (0,-5);
+	node [midway, above, sloped] {phone} (0,-4);
 	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
-	node [midway, above, sloped] {email} (1,-5);
+	node [midway, above, sloped] {email} (1,-4);
 
 	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
-	node [midway, below, sloped] {startDate} (2.5,3.2);
+	node [midway, below, sloped] {startDate} (2.3,2.2);
 	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
-	node [midway, above, sloped] {endDate} (3.5,3.2);
+	node [midway, above, sloped] {endDate} (3.5,2.2);
 	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
-	node [midway, below, sloped] {title} (4.5,3.2);
+	node [midway, below, sloped] {title} (4.5,2);
 
@@
 
-\ddg{IMPORTANT: Do we keep all of them, or only the top $k$ with most 
-confidence? If so, 
-what is $k$?}
-\npr{We keep all, that is the crucial difference from Karma which does some voodoo heuristic filtering}
+Note that we keep all the matches, regardless of the confidence fo the match. 
+This is an important difference between our system and other approaches 
+\cite{taheriyan2016learning} that 
+remove some of the matches based on heuristics to then simplify the task of 
+finding the semantic model.
+
+%\ddg{IMPORTANT: Do we keep  all of them, or only the top $k$ with most 
+%confidence? If so, 
+%what is $k$?}
+%\npr{We keep all, that is the crucial difference from Karma which does some 
+%voodoo heuristic filtering}
 
@@
 \item Adding the known semantic models.
-\item Adding the semantic types learned for the target source. \ddg{TODO: see 
-Important note above}
+\item Adding the semantic types learned for the target source. \ddg{If we keep 
+all matches, isn't this just adding all the semantic types?}
 \item Expanding the graph using the domain ontology $\mathcal{O}$.
@@
 There exists a range of tools that can achieve this task using Transactional 
-Frequent Graph Pattern Mining\cite{petermann2017dimspan,yan2002gspan}. 
-We chose to use DIMSpan \cite{petermann2017dimspan}. 
-\ddg{CHECK! How do they solve an NP-complete problem??}
-\npr{Im not sure what to say here: there is just no guarantee how long it will take for the whole thing to run, except there is a threshold on how frequent they have to be; they use gSpan procedure to prune patterns and a variant of Ulmans algorithm for graph pattern matching}
+Frequent Graph Pattern Mining \cite{petermann2017dimspan,yan2002gspan}. 
+We chose to use DIMSpan \cite{petermann2017dimspan}, which uses gSpan as a 
+pruning procedure \cite{yan2002gspan}.
+%\ddg{CHECK! How do they solve an NP-complete problem??}
+%\npr{Im not sure what to say here: there is just no guarantee how long it will 
+%take for the whole thing to run, except there is a threshold on how frequent 
+%they have to be; they use gSpan procedure to prune patterns and a variant of 
+%Ulmans algorithm for graph pattern matching}
 
@@
 \caption{Example of integration graph. (`\tikz{ \node[att] () at (0,0)  
-{};}' are attribute nodes). We omit weights for clarity. Data node labels are 
+{};}' are attribute nodes). We omit weights and only show the most likely 
+matches for clarity. Data node labels are 
 abbreviated but 

### 2017-08-18 stp/paper_aaai/main.tex
Writing bits

--- 2017-08-17 stp/paper_aaai/main.tex
@@
 % natalia
+\usepackage{subcaption}
+\captionsetup{compatibility=false}
 \usepackage{multirow}
+\usepackage{pgfplots}
+\pgfplotsset{width=10cm,compat=1.9}
+\usepgfplotslibrary{colorbrewer}
 
@@
 \section{Introduction}
-The problem of integrating heterogeneous data sources is a long standing issue 
-in the database research field and is of high relevance in many real-world 
-domains.
+The problem of integrating heterogeneous data sources is a long standing issue in the database research field and is of high relevance in many real-world domains.
 A common approach to tackle this problem is to design a global model and to
@@
 
-In our case, we would like this global model to account
-not only for structural properties of the original data sources, but also to include the semantics, which is usually implicitly present in the sources.
+In our case, we would like this global model to account not only for structural properties of the original data sources, but also to include the semantics, which is usually implicitly present in the sources.
 In other words, we want to build a semantic model which describes the data sources in terms of concepts and relationships defined by an ontology \cite{Taheriyan2013}.
@@
 find a minimum cost Steiner Tree in the graph.
-The goal is to assign the costs 
-on the edges in such a way that the resulting Steiner Tree is a valid semantic model for the new source.
+The goal is to assign the costs on the edges in such a way that the resulting Steiner Tree is a valid semantic model for the new source.
 
@@
 data properties and relationships between them.
-An example of an ontology is given in Fig. \ref{FIG:onto}. 
+An example of an ontology is given in Fig.~\ref{FIG:onto}. 
 A Class in an ontology can have \emph{data properties} or \emph{object properties}. 
-For example an ``Organisation'' has a ``Person'' 
+For example, an ``Organisation'' has a ``Person'' 
 (which is a class with its own properties), and it has a ``name'' (which 
@@
 A subclass inherits all the properties of the parent class.
+\npr{rephrase, I think terminology is off}
 
@@
 properties in the ontology. 
-The edges in the semantic model correspond to relationships in the ontology, as shown if Figures \ref{FIG:onto} and \ref{FIG:sem}.
+The edges in the semantic model correspond to relationships in the ontology, as shown if Fig.~\ref{FIG:onto} and \ref{FIG:sem}.
 
@@
 A \emph{source} $s$ is a $n$-ary relation with a set of attributes 
-$\mathcal{A}_s = 
-(a_1,...,a_n)$.
+$\mathcal{A}_s = (a_1,...,a_n)$.
 
 An \emph{attribute mapping} function $\phi : \mathcal{A}_s \mapsto 
-\mathcal{D}_m$ is a function which
-maps the attributes of the source $s$ into the nodes of the semantic model $m$. 
+\mathcal{D}_m$ is a function which maps the attributes of the source $s$ into the nodes of the semantic model $m$. 
 It can be a partial mapping, meaning that only some of the attributes
@@
 
-A \emph{source description} is a triple $\delta = (s, m, \phi)$ where $s$ is a 
-source, 
-$m$ is a semantic
-model, and $\phi$ is an attribute mapping.
+A \emph{source description} is a triple $\delta = (s, m, \phi)$ where $s$ is a source, $m$ is a semantic model, and $\phi$ is an attribute mapping.
 
@@
 (s_l, m_l, \phi_l)\}$.
-Given a new source $s^\star$, we want to build a semantic model $m^\star$ and 
-an attribute mapping function $\phi^\star$ such that 
+Given a new source $s^\star$, we want to build a semantic model $m^\star$ and an attribute mapping function $\phi^\star$ such that 
 $\delta^\star = (s^\star,m^\star,\phi^\star)$ is an \emph{appropriate} source 
@@
 
+\npr{reformulate for typed directed multigraphs and example based on Fig3}
 In our context, we define a \emph{pattern} is a graph $P$ that is undirected 
@@
 \npr{Im not sure what to say here: there is just no guarantee how long it will take for the whole thing to run, except there is a threshold on how frequent they have to be; they use gSpan procedure to prune patterns and a variant of Ulmans algorithm for graph pattern matching}
+
+We obtain patterns of size upto 6 in under 4 minutes for the biggest instances in our evaluation framework.
+\npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe cite my work on how databases perform for graph pattern matching}
 
@@
 
-\subsection{Modeling \relonto{} in CP}
+\subsection{\relonto{} in Constraint Programming}
 In order to model this problem we used the \minizinc{} language 
@@
 
+We have run all our experiments on a Dell server with 252 GiB of memory, 2 CPUs with 4 cores each, 1 Titan GPU and 1 GeForce 1080 Ti GPU.
+\npr{check characteristics}
+
 \subsection{Experimental Results}
 \ddg{TODO}
+
+We have developed a new approach for semantic labeling which can efficiently handle the \emph{unknown} class.
+We demonstrate its efficiency by comparing against the state-of-the-art approach DSL~\cite{Pham:semantic}.
+\npr{Explain}
 
@@
 
+\begin{figure*}[ht]\small
+\pgfplotsset{
+    small,
+    %legend style={legend pos=north east}
+    legend style={
+        at={(0.01,0.01)},
+        anchor=south west,
+    },
+   }%
+\begin{minipage}[b]{.5\linewidth}
+\centering
+\begin{tikzpicture}[baseline]
+\begin{axis}[
+		    xlabel={\emph{numBags}},
+		    ylabel={Performance (MRR)},
+		    xmin=0, xmax=150,
+		    ymin=0.5, ymax=1,
+		    xtick={0,10,50,100,150},
+		    ytick={0.5,0.6,0.7,0.8,0.9,1},
+		    legend pos=south east,
+		    ymajorgrids=true,
+		    grid style=dashed
+		]
+
+		\addplot[
+		    color=blue,
+		    mark=square,
+		    ]
+		    coordinates {
+		    (10, 0.85154623154623166)(50, 0.85902097902097896)(100,0.87487956487956486)(150,0.8802331002331002)
+		    };
+		\addplot[
+		    color=red,
+		    mark=*,
+		    ]
+		    coordinates {
+		    (10,  0.73272601851632158)(50, 0.73596072887032105)(100,0.73736629035127532)(150,0.73512315058140676)
+		    };
+		\addplot[
+		    color=green,
+		    mark=x,
+		    ]
+		    coordinates {
+		    (10,  0.53396973928187841)(50, 0.56218126081141884)(100,0.55857468339226135)(150,0.55938671902457904)
+		    };
+		 \addplot[
+		    color=brown,
+		    mark=+,
+		    ]
+		    coordinates {
+		    (10,  0.81292733659634253)(50, 0.81182668838989458)(100, 0.80705336361770219)(150,0.80801980454223066)
+		    };
+		 \addplot[
+		    color=violet,
+		    mark=star,
+		    ]
+		    coordinates {
+		    (10,   0.87823326846764416)(50, 0.89727564102564272)(100,0.9136698717948738)(150,0.91708333333333425)
+		    };
+		%\legend{weather,weapons,soccer,museum,city}
+
+		\end{axis}
+\end{tikzpicture}
+\subcaption{fixing \emph{bagSize}=100}\label{fig:numbags}
+\end{minipage}%
+%
+\begin{minipage}[b]{.5\linewidth}
+\centering
+\begin{tikzpicture}[baseline]
+		\begin{axis}[
+		    xlabel={\emph{bagSize}},
+		    %ylabel={Performance (MRR)},
+		    xmin=0, xmax=100,
+		    ymin=0.5, ymax=1,
+		    xtick={0,10,30,50,100},
+		    ytick={0.5,0.6,0.7,0.8,0.9,1},
+		    legend pos=outer north east,
+		    ymajorgrids=true,
+		    grid style=dashed
+		]
+
+		\addplot[
+		    color=blue,
+		    mark=square,
+		    ]
+		    coordinates {
+		    (10, 0.88427350427350415)(30,  0.9027583527583527)(50,0.91336441336441332)(100,0.87871794871794873)
+		    };
+		\addplot[
+		    color=red,
+		    mark=*,
+		    ]
+		    coordinates {
+		    (10,  0.75910921069769555)(30, 0.76156533626682754)(50,0.75502218858295522)(100,0.75538165183154382)
+		    };
+		\addplot[
+		    color=green,
+		    mark=x,
+		    ]
+		    coordinates {
+		    (10,  0.56646107828012637)(30, 0.5693901714881866)(50,0.58629781920572777)(100,0.58408351395802571)
+		    };
+		 \addplot[
+		    color=brown,
+		    mark=+,
+		    ]
+		    coordinates {
+		    (10,  0.78552344907839267)(30, 0.78870711278952932)(50,0.78519302797324753)(100,0.77792094596490047)
+		    };
+		 \addplot[
+		    color=violet,
+		    mark=star,
+		    ]
+		    coordinates {
+		    (10,  0.80810421349483996)(30, 0.84745259081196467)(50,0.8751719894688631)(100,0.89739411630036825)
+		    };
+		\legend{weather,weapons,soccer,museum,city}
+
+		\end{axis}
+	\end{tikzpicture}
+\subcaption{fixing \emph{numBags}=50}\label{fig:bagsize}
+\end{minipage}
+\caption{Average precision and recall on museum domain.}\label{fig:bagging}
+\end{figure*}
+
 \section{Related Work \label{SEC:pw}}
 \ddg{rewrite, add more}
+\npr{Now the opposite: shrink please}
 
@@
 
+\npr{Should I mention complex matches like 1:n and n:1 and iMap?}
+
 \section{Conclusion}
@@
 \bibliographystyle{aaai}
-\npr{shorten citations}
+\npr{TODO: shorten citations like conference names and if there are more than 4 authors use et al}
 \bibliography{main}

### 2017-08-18 stp/stp_experiments_unknown.py

@@ -234,7 +234,7 @@ def do_experiment(octopus, orig_ds, orig_ssd, avail_labels, chosen_paths, chosen
 
     # karma approach
     print("---> trying karma")
-    res = al.do_karma(sn, octopus, orig_ds, cor_ssd, ssd, train_flag=False,
+    res = al.do_karma(sn, octopus, orig_ds, cor_ssd, ssd, train_flag=known_num,
                       accu=sm_accuracy, experiment=experiment_descr, pattern_time=pattern_time)
     benchmark_results += res
     csvfile.writerows(res)
@@ -245,7 +245,7 @@ def do_experiment(octopus, orig_ds, orig_ssd, avail_labels, chosen_paths, chosen
 # =======================
 import time
 chuffed_lookup_path = os.path.join(project_path, "stp", "minizinc")
-result_csv = os.path.join(project_path, "stp", "resources", "unknown_benchmark_museum_addpaths.csv")
+result_csv = os.path.join(project_path, "stp", "resources", "unknown_benchmark_museum_addpaths_loo.csv")
 with open(result_csv, "w+") as f:
     csvf = csv.writer(f)
     csvf.writerow(["experiment", "octopus", "dataset", "name", "ssd",
@@ -254,7 +254,8 @@ with open(result_csv, "w+") as f:
                    "karma_jaccard", "karma_precision", "karma_recall",
                    "known_num", "time", "chuffed_path", "simplify", "chuffed_time",
                    "soft_assumptions", "pattern_significance", "sm_accuracy", "sol_accuracy",
-                   "match_score", "cost", "objective", "cor_match_score", "cor_cost", "pattern_time"])  # header
+                   "match_score", "cost", "objective", "cor_match_score", "cor_cost", "pattern_time",
+                   "num_node", "num_edges"])  # header
 
     sample_range = list(range(len(new_ssds)))
     len_sample = len(sample_range)
@@ -272,7 +273,7 @@ with open(result_csv, "w+") as f:
         print("Currently selected ssd: ", cur_id)
         test_sample = [cur_id]
 
-        for num in range(1, len(sample_range)):
+        for num in [28]:#range(1, len(sample_range)):
             train_sample = sample_range[:max(cur_id + num + 1 - len_sample, 0)] + sample_range[
                                                                                   cur_id + 1: cur_id + 1 + num]
             print("     train sample size: ", num)
@@ -284,36 +285,36 @@ with open(result_csv, "w+") as f:
[…]

### 2017-08-18 stp/paper_aaai/main.tex

@@
 
-\ddg{IMPORTANT: Do we keep all of them, or only the top $k$ with most 
-confidence? If so, 
-what is $k$?}
-\npr{We keep all, that is the crucial difference from Karma which does some voodoo heuristic filtering}
+Note that we keep all the matches, regardless of the confidence fo the match.
+This is an important difference between our system and other approaches
+\cite{taheriyan2016learning} that
+remove some of the matches based on heuristics to then simplify the task of
+finding the semantic model.
+
+%\ddg{IMPORTANT: Do we keep  all of them, or only the top $k$ with most
+%confidence? If so,
+%what is $k$?}
+%\npr{We keep all, that is the crucial difference from Karma which does some
+%voodoo heuristic filtering}
 
@@
 \item Adding the known semantic models.
-\item Adding the semantic types learned for the target source. \ddg{TODO: see 
-Important note above}
+\item Adding the semantic types learned for the target source. \ddg{If we keep
+all matches, isn't this just adding all the semantic types?}
 \item Expanding the graph using the domain ontology $\mathcal{O}$.
@@
 There exists a range of tools that can achieve this task using Transactional 
-Frequent Graph Pattern Mining\cite{petermann2017dimspan,yan2002gspan}. 
-We chose to use DIMSpan \cite{petermann2017dimspan}. 
-\ddg{CHECK! How do they solve an NP-complete problem??}
-\npr{Im not sure what to say here: there is just no guarantee how long it will take for the whole thing to run, except there is a threshold on how frequent they have to be; they use gSpan procedure to prune patterns and a variant of Ulmans algorithm for graph pattern matching}
+Frequent Graph Pattern Mining \cite{petermann2017dimspan,yan2002gspan}.
+We chose to use DIMSpan \cite{petermann2017dimspan}, which uses gSpan as a
+pruning procedure \cite{yan2002gspan}.
+%\ddg{CHECK! How do they solve an NP-complete problem??}
+%\npr{Im not sure what to say here: there is just no guarantee how long it will take for the whole thing to run, except there is a threshold on how frequent they have to be; they use gSpan procedure to prune patterns and a variant of Ulmans algorithm for graph pattern matching}
 
@@
 \caption{Example of integration graph. (`\tikz{ \node[att] () at (0,0)  
-{};}' are attribute nodes). We omit weights for clarity. Data node labels are 
+{};}' are attribute nodes). We omit weights and only show the most likely
+matches for clarity. Data node labels are
 abbreviated but 

### 2017-08-19 stp/paper_aaai/main.tex
Experiments section partially

--- 2017-08-18 stp/paper_aaai/main.tex
@@
 $\delta^\star = (s^\star,m^\star,\phi^\star)$ is an \emph{appropriate} source 
-description. We
-use the term ``appropriate'' since there might be many such triples which are
-well-formed source descriptions, but only one or a few will capture the intended
-meaning of the source. 
-Our goal is to automatically build $\delta^\star$ such that it maximizes the \emph{precision} and \emph{recall} from the semantic model 
-$m^\star$ to the semantic model $m^\dag$ that the user considers correct. \npr{definitions for precision and recall}
+description. 
+We
+use the term ``appropriate'' since there might be many such triples which are well-formed source descriptions, but only one or a few will capture the intended meaning of the source. 
+Our goal is to automatically build $\delta^\star$ such that it maximizes the \emph{precision} and \emph{recall} between the semantic model 
+$m^\star$ and the semantic model $m^\dag$ that the user considers correct. \npr{definitions for precision and recall}
 
@@
 
-To provide an integrated view over the known sources descriptions $S_T$, we 
+To provide an integrated view over the known source descriptions $S_T$, we 
 need to align their semantic models as well as all considered semantic 
-types. This is achieved by constructing an \emph{alignment graph}.
+types. 
+This is achieved by constructing an \emph{alignment graph}.
 
@@
 of the known semantic models and expanded using the semantic types 
-$\mathcal{L_O}$ and the ontology $\mathcal{O}$. Similar to a semantic 
-model, $\mathcal{G_O}$ contains both class and data nodes. The links correspond 
+$\mathcal{L_O}$ and the ontology $\mathcal{O}$. 
+Similar to a semantic 
+model, $\mathcal{G_O}$ contains both class and data nodes.
+The links correspond 
 to properties in  $\mathcal{O}$ and are weighted \cite{taheriyan2016learning}.
 
-The algorithm we used to construct $\mathcal{G_O}$ is the same as Taheriyan 
-\etal{} and is described in detail in the cited paper 
-\cite{taheriyan2016learning}.
+The algorithm we used to construct $\mathcal{G_O}$ is the same as \cite{taheriyan2016learning} and is described in detail in their work.
 Briefly, the algorithm has three parts:
@@
 For instance, it could contain two nodes $City.name$ and $State.name$ rather than just one node $name$ connected to two 
-nodes $City$ and $State$. We say these nodes are \emph{induced} into the 
+nodes $City$ and $State$. 
+We say these nodes are \emph{induced} into the 
 alignment graph by the semantic types, we note them $\mathcal{D_{G_O}}$ and we 
@@
 
-An example alignment graph is illustrated in Fig. \ref{FIG:ali}. 
+An example alignment graph is illustrated in Fig.~\ref{FIG:ali}. 
 Bigger examples can be found in \cite{Taheriyan2013}. 
@@
 Our goal is to take a set of graphs (the semantic models from the training set 
-$S_T$) and find patterns that appear often across that set of graphs. This is 
-known as the Frequent Subgraph Mining (FSM), which contains the subgraph 
+$S_T$) and find patterns that appear often across that set of graphs. 
+This is 
+known as the Frequent Graph Pattern Mining, which contains the subgraph 
 isomorphism, known to be NP-complete. 
 There exists a range of tools that can achieve this task using Transactional 
-Frequent Graph Pattern Mining\cite{petermann2017dimspan,yan2002gspan}. 
+Frequent Graph Pattern Mining~\cite{yan2002gspan}. 
 We chose to use DIMSpan \cite{petermann2017dimspan}. 
@@
 We obtain patterns of size upto 6 in under 4 minutes for the biggest instances in our evaluation framework.
-\npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe cite my work on how databases perform for graph pattern matching}
+\npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe cite my work on how databases perform for graph pattern matching.
+Should it be better in related work?}
 
@@
 their support. 
-The \emph{support} of a pattern is a measure of frequency. 
+The \emph{support} of a pattern is an anti-monotonous measure of frequency. 
 Thus, the higher the support, the more often the pattern appears. This typically means that big patterns have low support.
@@
 If an attribute $a$ is matched to $unk_a$, then $unk_a$ will be linked to Class 
-node \emph{unknown}. The rest of the attributes can then be matched normally 
-and build  a semantic model as usual. Then, to maintain connectedness of the 
+node \emph{unknown}. 
+The rest of the attributes can then be matched normally 
+and build  a semantic model as usual. 
+Then, to maintain connectedness of the 
 Steiner tree, the \emph{unknown} node and one of the selected Class nodes will 
-both be connected to the \emph{root} node. Note that if all attributes find a 
+both be connected to the \emph{root} node. 
+Note that if all attributes find a 
 match, then both the \emph{unknown} and \emph{root} won't be selected in the 
@@
 A valuation $\theta(\boldsymbol{v})$ is a mapping from the set of variables to 
-values in $D$. If there exist a valuation $\theta^\star$ such that all 
+values in $D$. 
+If there exist a valuation $\theta^\star$ such that all 
 variables map 
@@
 
+% datasets for evaluation
 We run experiments on two domains: museum and soccer (see Fig.~\ref{tab:data} for statistics).
+The museum dataset~\cite{taheriyan2016learning} contains 29 sources which are mapped to the EDM domain ontology.
+The soccer dataset~\cite{Pham:semantic} is much smaller with only 12 data sources, and its domain ontology is an extension of the schema.org ontology.
 
@@
 
+% baseline for evaluation
+We choose \emph{Karma}~\cite{taheriyan2016learning} as our baseline.
+This system also phrases the \relonto{} problem as STP and decomposes it further into two parts.
+However, they use approximation algorithms both for the matching and for the STP parts.
+Additionally, they do not consider unmatched attributes in the sources.
+To ensure that Karma also handles such attributes, we change its semantic labeling model SemanticTyper~\cite{Ramnandan:Assigning} to ours and we add a special \emph{unknown} ontology which gives specification for \emph{root} and \emph{unknown} nodes of the alignment graph.
+The first modification also ensures the fairness of evaluation since both Karma and Serene will have the same matches for attributes.
+
+% performance metrics
+The performance of these systems is estimated in terms of \emph{precision} and \emph{recall}.
+Assuming $m^\star$ is the predicted semantic model and $m^\dag$ is the correct semantic model, then:
+$$precision = \frac{|rel(m^\star)\cap rel(m^\dag)|}{|rel(m^\star)|}$$
+$$recall = \frac{|rel(m^\star)\cap rel(m^\dag)|}{|rel(m^\dag)|}$$
+where $rel(m)$ is the set of triples $(u,e,v)$ with $e$ being an edge from the vertex $u$ to the vertex $v$ in the semantic model $m$.
+Since we want to estimate the accuracy of both the matching and STP parts,
+we also include triples for attributes and data nodes into the corresponding sets.
+Note that unmatched attributes as well as \emph{unknown} and \emph{root} nodes are not part of these sets.
+We perform also a modification to the ground truth semantic models:
+if the true semantic label of an attribute is not present in any of the previously mapped data sources,
+we substitute it with \emph{unknown} and map it to the \emph{Unknown} class node.
+In such way we validate how well the systems can detect earlier unseen cases.
+
+% semantic labeling models
+To illustrate that our semantic labeling model is better suited for the
+matching task, we compare it against the state-of-the-art model \emph{DSL}~\cite{Pham:semantic} which was shown to perform even better than SemanticTyper. 
+\npr{not sure whether I should explain how this model works}
+We use \emph{mean reciprocal rank} (MRR) to evaluate semantic labeling models.
+This measure is useful to estimate how highly the true semantic label is ranked among top $k$ suggestions.
+It is calculated the following way:
+$$MRR = \frac{1}{n}\sum_{i=1}^{n}{\frac{1}{rank_i}},$$
+where $rank_i$ is the rank of the correct semantic label for the attribute $a_i$ among the top $k$ predictions.
+
+% evaluation strategy
+We perform an evaluation strategy outlined by~\cite{taheriyan2016learning}.
+Let $M_j$ be the set of $j$ known semantic models.
+For each data source $s_i$ in the domain we perform experiments $t-1$ times,
+where $t$ is the total number of data sources in the domain and each experiment has a different number of known semantic models $M_1, M_2, \ldots, M_{t-1}$.
+The case with $M_{t-1}$ known semantic models corresponds to leave-one-out validation strategy. 
+For example, in the soccer domain for the source $s_1$ we run experiments 11 times using $M_1=\{m_2\}, M_2=\{m_2, m_3\}, \ldots, M_{11}=\{m_2, m_3, \ldots, m_{12}\}$
+We repeat the procedure for other data sources in the domain and then average the results.
+Such procedure ensures that each source is at least once in the training as well as testing datasets.
+
+% architecture
 We have run all our experiments on a Dell server with 252 GiB of memory, 2 CPUs with 4 cores each, 1 Titan GPU and 1 GeForce 1080 Ti GPU.
-\npr{check characteristics}
+\npr{check characteristics, AWS machine is bigger}
 
@@
 We demonstrate its efficiency by comparing against the state-of-the-art approach DSL~\cite{Pham:semantic}.
+Tab.~\ref{tab:semlab} provides evidence that our new semantic labeling model is better suited for the task when there are unmatched attributes in domains.
 \npr{Explain}
@@
   \centering
-  \caption{Average performance of semantic labeling for leave one out strategy.}
-  	\label{tab:unknownloo}
+  \caption{Average performance of semantic labeling models for leave one out strategy.}
+  	\label{tab:semlab}
   	\begin{tabular}{c|cc|cc} 
@@
 
+%%%
+% performance figures
+%%%
+We evaluate our new system \emph{serene} and its modification \emph{serene-pats}, which uses graph patterns, against the state-of-the-art system \emph{karma}.
+Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} show their performance on the museum and soccer domains.
+We report average precision, recall and run times for the systems with regard to variable number of semantic models in the training set.
+
+%%% museum domain
 \begin{figure*}[ht]\small
@@
    }%
-\begin{minipage}[b]{.5\linewidth}
+\begin{minipage}[b]{.34\linewidth}
 \centering
@@
 \begin{axis}[
-		    xlabel={\emph{numBags}},
-		    ylabel={Performance (MRR)},
-		    xmin=0, xmax=150,
-		    ymin=0.5, ymax=1,
-		    xtick={0,10,50,100,150},
+		    xlabel={\emph{known semantic models}},
+		    ylabel={Performance},
+		    xmin=1, xmax=28,
+		    ymin=0.2, ymax=0.9,
+		    xtick={1,5,10,15,20,25,28},
+		    ytick={0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
+		    legend pos=south east,
+		    ymajorgrids=true,
+		    grid style=dashed
+		]
+
+		\addplot[
+		    color=blue,
+		    mark=square,
+		    ]
+		    coordinates {
+		    (1,0.477688172043011)(2,0.543722761679028)(3,0.584279525763794)(4,0.560916442048518)(5,0.508442559100454)(6,0.451911027568922)(7,0.560410216718266)(8,0.627540834845735)(9,0.658907184769254)(10,0.494298245614035)(11,0.594547996272134)(12,0.572438909774436)(13,0.643132689678742)(14,0.544147521036133)(15,0.561388900346478)(16,0.620470013199142)(17,0.631330163644405)(18,0.644192377495463)(19,0.642924629016761)(20,0.656325397672681)(21,0.610482642157672)(22,0.628992740471869)(23,0.570074611816898)(24,0.679169187336157)(25,0.673558897243108)(26,0.667890182643746)(27,0.68742147145051)(28,0.709820528332325)
+		    };
+		\addplot[
+		    color=red,
+		    mark=*,
+		    ]
+		    coordinates {
+		    (1,0.570063795853269)(2,0.756845238095238)(3,0.621034680606911)(4,0.719615829557505)(5,0.663677414539484)(6,0.680661881977671)(7,0.702849371292569)(8,0.730720679999118)(9,0.715323491375385)(10,0.722695511010729)(11,0.722586065299008)(12,0.725508681952266)(13,0.728214414334958)(14,0.753560036454773)(15,0.778231825645619)(16,0.745982043507288)(17,0.715855206037534)(18,0.733838894506235)(19,0.728435738081271)(20,0.754932383250967)(21,0.76774421230943)(22,0.761660230839754)(23,0.750358005521049)(24,0.82098385331144)(25,0.823507591442374)(26,0.834847535505431)(27,0.84013108540293)(28,0.813133718212162)
+		    };
+		\addplot[
+		    color=green,
+		    mark=x,
+		    ]
+		    coordinates {
+		    (1,0.580144743457437)(2,0.699277168494516)(3,0.596982860940987)(4,0.683431847315197)(5,0.634133314342686)(6,0.630169810336433)(7,0.628025663269931)(8,0.642973856209151)(9,0.618457602339181)(10,0.616241290282443)(11,0.606940556177678)(12,0.605471976942706)(13,0.598988030767536)(14,0.608112237561116)(15,0.609841319882303)(16,0.578626150272492)(17,0.55776862026862)(18,0.57760989010989)(19,0.567994505494506)(20,0.492368742368742)(21,0.582722832722833)(22,0.574786324786325)(23,0.644688644688645)(24,0.658424908424909)(25,0.708791208791209)(26,0.716727716727717)(27,0.719373219373219)(28,0.708791208791209)
+		    };
+		%\legend{karma,serene,serene-pats}
+
+		\end{axis}
+\end{tikzpicture}
+\subcaption{precision}\label{fig:museumprec}
+\end{minipage}%
+%
+\begin{minipage}[b]{.33\linewidth}
+\centering
+\begin{tikzpicture}[baseline]
+		\begin{axis}[
+		    xlabel={\emph{known semantic models}},
+		    %ylabel={recall},
+		    xmin=1, xmax=28,
+		    ymin=0.2, ymax=0.9,
+		    xtick={1,5,10,15,20,25,28},
+		    ytick={0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
+		    ymajorgrids=true,
+		    grid style=dashed,
+		    legend style={at={(0.5,1.1)},anchor=south, legend columns=-1}
+		]
+
+		\addplot[
+		    color=blue,
+		    mark=square,
+		    ]
+		    coordinates {
+		    (1,0.209547221954433)(2,0.411561264822134)(3,0.457295783926219)(4,0.449720026350461)(5,0.414575098814229)(6,0.364575098814229)(7,0.452173913043478)(8,0.526317523056654)(9,0.588158761528327)(10,0.403491436100132)(11,0.506175889328063)(12,0.489690382081687)(13,0.584008563899868)(14,0.470553359683795)(15,0.48570487483531)(16,0.553513584117033)(17,0.553774817136886)(18,0.573236677115987)(19,0.567816091954023)(20,0.580551201671891)(21,0.557301462904911)(22,0.559979101358412)(23,0.477098571926158)(24,0.57088122605364)(25,0.56078021595263)(26,0.565134099616858)(27,0.585336119818878)(28,0.598310693138279)
+};
+		\addplot[
+		    color=red,
+		    mark=*,
+		    ]
+		    coordinates {
+		    (1,0.558240946045824)(2,0.733876811594203)(3,0.610770750988142)(4,0.707559288537549)(5,0.654891304347826)(6,0.670421607378129)(7,0.704710144927536)(8,0.729611330698287)(9,0.716913702239789)(10,0.728837285902504)(11,0.724769433465085)(12,0.724670619235837)(13,0.727783267457181)(14,0.76187417654809)(15,0.790283267457181)(16,0.751266980146291)(17,0.72991118077325)(18,0.761259143155695)(19,0.742058516196448)(20,0.759103970741902)(21,0.776149425287357)(22,0.758842737722048)(23,0.730668756530825)(24,0.800330895158482)(25,0.800330895158482)(26,0.808951584813654)(27,0.813305468477882)(28,0.790229885057471)
+};
+		\addplot[
+		    color=green,
+		    mark=x,
+		    ]
+		    coordinates {
+		    (1,0.571875702946753)(2,0.770701581027668)(3,0.637285902503294)(4,0.73596837944664)(5,0.677618577075099)(6,0.693148880105402)(7,0.725263504611331)(8,0.750164690382082)(9,0.739640974967062)(10,0.743988801054019)(11,0.742094861660079)(12,0.734420289855072)(13,0.742934782608696)(14,0.775131752305666)(15,0.795965085638999)(16,0.772361546499478)(17,0.752899686520376)(18,0.776671891327064)(19,0.765308254963427)(20,0.733838383838384)(21,0.783986415882968)(22,0.774255485893417)(23,0.751219087425984)(24,0.803030303030303)(25,0.828456983629397)(26,0.83707767328457)(27,0.841431556948798)(28,0.828456983629397)
+};
+		 %\legend{karma,serene,serene-pats}
+
+		\end{axis}
+	\end{tikzpicture}
+\subcaption{recall}\label{fig:museumrec}
+\end{minipage}%
+%
+\begin{minipage}[b]{.33\linewidth}
+\centering
+\begin{tikzpicture}[baseline]
+\begin{axis}[
+		    xlabel={\emph{known semantic models}},
+		    %ylabel={time(s)},
+		    xmin=1, xmax=28,
+		    ymin=0.0, ymax=8.5,
+		    xtick={1,5,10,15,20,25,28},
+		    ytick={0.0,1,2,3,4,5,6,7,8},
+		    ymajorgrids=true,
+		    grid style=dashed,
+		    %legend pos=outer north east,
+		    %legend style={at={(0.5,-0.1)},anchor=north, legend columns=-1}
+		]
+
+		\addplot[
+		    color=blue,
+		    mark=square,
+		    ]
+		    coordinates {
+		    (1,0.28413987159729)(2,0.598592698574067)(3,0.36263108253479)(4,0.400362551212311)(5,0.387216985225677)(6,0.392432987689972)(7,0.394440889358521)(8,0.430805265903473)(9,0.438177883625031)(10,0.441894292831421)(11,0.461780428886414)(12,0.469180881977081)(13,0.477133095264435)(14,0.498149693012238)(15,0.512342214584351)(16,0.600962460041046)(17,0.5725257396698)(18,0.907191514968871)(19,0.551609396934509)(20,0.585879027843475)(21,0.610454380512239)(22,0.575962841510773)(23,0.657813549041748)(24,0.671637773513794)(25,0.689822912216188)(26,0.724388360977171)(27,0.750569899876912)(28,0.771229823430379)
+};
+		\addplot[
+		    color=red,
+		    mark=*,
+		    ]
+		    coordinates {
+		    (1,0.0166666666666667)(2,0.995)(3,0.8725)(4,0.8325)(5,0.9175)(6,0.965)(7,0.89)(8,0.9675)(9,0.96)(10,1.1225)(11,1.1475)(12,1.36)(13,1.295)(14,1.3925)(15,1.375)(16,1.4975)(17,1.9575)(18,2.11)(19,1.9075)(20,1.9175)(21,1.865)(22,1.915)(23,2.49)(24,2.4)(25,2.49)(26,2.49)(27,2.68333333333333)(28,2.47666666666667)
+};
+		\addplot[
+		    color=green,
+		    mark=x,
+		    ]
+		    coordinates {
+		    (1,0.025)(2,1.0375)(3,0.93)(4,1)(5,0.9575)(6,0.9425)(7,0.9)(8,0.975)(9,1.06)(10,1.2025)(11,1.2975)(12,1.9425)(13,1.52)(14,2.2825)(15,1.6275)(16,3.5375)(17,2.255)(18,2.1625)(19,6.505)(20,1.44666666666667)(21,2.2825)(22,2.3475)(23,8.28666666666667)(24,1.895)(25,8.3)(26,3.75333333333333)(27,3.73)(28,3.75)
+};
+		 %\legend{karma,serene,serene-pats}
+
+		\end{axis}
+\end{tikzpicture}
+\subcaption{time (s)}\label{fig:museumtime}
+\end{minipage}%
+\caption{Average precision, recall and time on the museum domain for \relonto{} systems with variable training set size.}\label{fig:perfmuseum}
+\end{figure*}
+
+%%% soccer domain
+\begin{figure*}[ht]\small
+\pgfplotsset{
+    small,
+    %legend style={legend pos=north east}
+    legend style={
+        at={(0.01,0.01)},
+        anchor=south west,
+    },
+   }%
+\begin{minipage}[b]{.34\linewidth}
+\centering
+\begin{tikzpicture}[baseline]
+\begin{axis}[
+		    xlabel={\emph{known semantic models}},
+		    ylabel={Performance},
+		    xmin=1, xmax=11,
+		    ymin=0.5, ymax=0.9,
+		    xtick={1,2,4,6,8,10,11},
 		    ytick={0.5,0.6,0.7,0.8,0.9,1},
@@
 		    coordinates {
-		    (10, 0.85154623154623166)(50, 0.85902097902097896)(100,0.87487956487956486)(150,0.8802331002331002)
+		    (1,0.635191626901633)(2,0.549997502815009)(3,0.675720834727361)(4,0.719693253328935)(5,0.759169846724195)(6,0.760054331456753)(7,0.800812140122402)(8,0.812192030050689)(9,0.799552066440611)(10,0.821470975418344)(11,0.785878855002637)
 		    };
@@
 		    coordinates {
-		    (10,  0.73272601851632158)(50, 0.73596072887032105)(100,0.73736629035127532)(150,0.73512315058140676)
+		    (1,0.676934852587026)(2,0.61473599870339)(3,0.723937079602602)(4,0.786238815638129)(5,0.777035817669233)(6,0.781984613615049)(7,0.81368099248534)(8,0.817013725291758)(9,0.816270530687007)(10,0.846744827831784)(11,0.852649148301322)
 		    };
@@
 		    coordinates {
-		    (10,  0.53396973928187841)(50, 0.56218126081141884)(100,0.55857468339226135)(150,0.55938671902457904)
-		    };
-		 \addplot[
-		    color=brown,
-		    mark=+,
-		    ]
-		    coordinates {
-		    (10,  0.81292733659634253)(50, 0.81182668838989458)(100, 0.80705336361770219)(150,0.80801980454223066)
-		    };
-		 \addplot[
-		    color=violet,
-		    mark=star,
-		    ]
-		    coordinates {
-		    (10,   0.87823326846764416)(50, 0.89727564102564272)(100,0.9136698717948738)(150,0.91708333333333425)
-		    };
-		%\legend{weather,weapons,soccer,museum,city}
+		    (1,0.66759959719914)(2,0.629014687197419)(3,0.692208378950833)(4,0.744652988406557)(5,0.773486992410165)(6,0.756607637648352)(7,0.803820434917082)(8,0.793054493090329)(9,0.792256229657042)(10,0.822093203062231)(11,0.828181360184871)
+		    };
+		%\legend{karma,serene,serene-pats}
 
@@
 \end{tikzpicture}
-\subcaption{fixing \emph{bagSize}=100}\label{fig:numbags}
+\subcaption{precision}\label{fig:soccerprec}
 \end{minipage}%
 %
-\begin{minipage}[b]{.5\linewidth}
+\begin{minipage}[b]{.33\linewidth}
 \centering
@@
 		\begin{axis}[
-		    xlabel={\emph{bagSize}},
-		    %ylabel={Performance (MRR)},
-		    xmin=0, xmax=100,
-		    ymin=0.5, ymax=1,
-		    xtick={0,10,30,50,100},
-		    ytick={0.5,0.6,0.7,0.8,0.9,1},
-		    legend pos=outer north east,
+		    xlabel={\emph{known semantic models}},
+		    %ylabel={recall},
+		    xmin=1, xmax=11,
+		    ymin=0.3, ymax=0.9,
+		    xtick={1,2,4,6,8,10,11},
+		    ytick={0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
 		    ymajorgrids=true,
-		    grid style=dashed
+		    grid style=dashed,
+		    legend style={at={(0.5,1.1)},anchor=south, legend columns=-1}
 		]
@@
 		    coordinates {
-		    (10, 0.88427350427350415)(30,  0.9027583527583527)(50,0.91336441336441332)(100,0.87871794871794873)
+		    (1,0.444761527680188)(2,0.372447158105053)(3,0.545528381345078)(4,0.596008831526073)(5,0.6499887923799)(6,0.643884492868159)(7,0.685035675993026)(8,0.702870161195933)(9,0.654001538724769)(10,0.685153350715964)(11,0.662999993217779)
 		    };
@@
 		    coordinates {
-		    (10,  0.75910921069769555)(30, 0.76156533626682754)(50,0.75502218858295522)(100,0.75538165183154382)
+		    (1,0.690636806043505)(2,0.613080486764697)(3,0.72563707600459)(4,0.780625908674911)(5,0.776616927805676)(6,0.779496772132888)(7,0.813459305700685)(8,0.813245834960899)(9,0.810586300672508)(10,0.84298404022542)(11,0.849899398175261)
 		    };
@@
 		    coordinates {
-		    (10,  0.56646107828012637)(30, 0.5693901714881866)(50,0.58629781920572777)(100,0.58408351395802571)
+		    (1,0.689786194666577)(2,0.655399210040359)(3,0.719915653815835)(4,0.776231754935929)(5,0.802770096610387)(6,0.787355423564135)(7,0.838616573256072)(8,0.82175912881902)(9,0.821414409345444)(10,0.851497334083541)(11,0.85656084018153)
+		    };
+		 \legend{karma,serene,serene-pats}
+
+		\end{axis}
+	\end{tikzpicture}
+\subcaption{recall}\label{fig:soccerrec}
+\end{minipage}%
+%
+\begin{minipage}[b]{.33\linewidth}
+\centering
+\begin{tikzpicture}[baseline]
+\begin{axis}[
+		    xlabel={\emph{known semantic models}},
+		    %ylabel={time(s)},
+		    xmin=1, xmax=11,
+		    ymin=0.0, ymax=0.3,
+		    xtick={1,2,4,6,8,10,11},
+		    ytick={0.0,0.1,0.2},
+		    ymajorgrids=true,
+		    grid style=dashed,
+		    %legend pos=outer north east,
+		    %legend style={at={(0.5,-0.1)},anchor=north, legend columns=-1}
+		]
+
+		\addplot[
+		    color=blue,
+		    mark=square,
+		    ]
+		    coordinates {
+		    (1,0.107354099100286)(2,0.137003461519877)(3,0.163627962271372)(4,0.17774627606074)(5,0.179288367430369)(6,0.183507978916168)(7,0.189805428187052)(8,0.191188136736552)(9,0.196139633655548)(10,0.200133164723714)(11,0.218581974506378)
+		    };
+		\addplot[
+		    color=red,
+		    mark=*,
+		    ]
+		    coordinates {
+		    (1,0.0595748017051003)(2,0.0895205450057983)(3,0.0976518734296163)(4,0.103216880957286)(5,0.108438626130422)(6,0.115763804117839)(7,0.125697635014852)(8,0.118865826924642)(9,0.119359710216522)(10,0.123752357959747)(11,0.153613630930583)
+		    };
+		\addplot[
+		    color=green,
+		    mark=x,
+		    ]
+		    coordinates {
+		    (1,0.0687879033522172)(2,0.0874820310419256)(3,0.103948153495789)(4,0.104214943885803)(5,0.115242712974548)(6,0.126150580406189)(7,0.122052125063809)(8,0.128753701051076)(9,0.129606107076009)(10,0.13165650844574)(11,0.142413517634074)
+		    };
+		 %\legend{karma,serene,serene-pats}
+
+		\end{axis}
+\end{tikzpicture}
+\subcaption{time (s)}\label{fig:soccertime}
+\end{minipage}%
+\caption{Average precision, recall and time on the soccer domain for \relonto{} systems with variable training set size.}\label{fig:perfsoccer}
+\end{figure*}
+
+%%
+As mentioned previously, the chuffed solver outputs solutions as it finds them.
+In Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} we report the first found solutions.
+In Fig.~\ref{fig:perfsol} we show how the performance of \emph{serene} changes across sequentially found solutions.
+In all our experiments we use a timeout threshold of 15s for the chuffed solver.
+Additionally, we investigate how the performance is influenced if we introduce a weighting scheme on the patterns,
+i.e., costs of patterns are scaled by a factor. 
+%% sequentially found solutions and different weights for patterns
+\begin{figure*}[ht]\small
+\pgfplotsset{
+    small,
+    %legend style={legend pos=north east}
+    legend style={
+        at={(0.01,0.01)},
+        anchor=south west,
+    },
+   }%
+\begin{minipage}[b]{.34\linewidth}
+\centering
+\begin{tikzpicture}[baseline]
+\begin{axis}[
+		    xlabel={\emph{solution}},
+		    ylabel={Performance},
+		    xmin=0, xmax=20,
+		    ymin=0.7, ymax=1,
+		    xtick={0,5,10,15,20},
+		    ytick={0.7,0.8,0.9,1},
+		    legend pos=south east,
+		    ymajorgrids=true,
+		    grid style=dashed,
+		    legend style={at={(1.5,1.1)},anchor=south, legend columns=-1}
+		]
+
+		\addplot[
+		    color=blue,
+		    mark=square,
+		    ]
+		    coordinates {
+		    (0,0.813133718212162)(1,0.870689655172414)(2,0.869565217391304)(3,0.854700854700855)(4,0.847457627118644)(5,0.862068965517241)(6,0.862068965517241)(7,0.860869565217391)
+		    };
+		\addplot[
+		    color=red,
+		    mark=*,
+		    ]
+		    coordinates {
+		    (0,0.708791208791209)(1,0.720429778415431)(2,0.727852084972463)(3,0.734756097560976)(4,0.737969058591178)(5,0.723003960808839)(6,0.727905921593153)(7,0.740887177292826)(8,0.733003960808839)(9,0.746193299741805)(10,0.73554304773817)(11,0.74569890495285)(12,0.756325773784054)(13,0.745676961413577)(14,0.753615746683783)(15,0.7306060898002)(16,0.723882805154582)(17,0.720774744968293)(18,0.733079110976868)(19,0.731544715447155)(20,0.734034752112227)
+
+		    };
+		\addplot[
+		    color=green,
+		    mark=x,
+		    ]
+		    coordinates {
+		    (0,0.71031746031746)(1,0.722023912003826)(2,0.734193548387097)(3,0.740054370716392)(4,0.751788722391459)(5,0.752652119278914)(6,0.765286464150101)(7,0.766275317871063)(8,0.763956676916058)(9,0.779373522458629)(10,0.780497706328908)(11,0.786846912678115)(12,0.793409626193882)(13,0.801554001554001)(14,0.800878033205619)(15,0.861352657004831)(16,0.863636363636364)(17,0.863636363636364)(18,0.883720930232558)(19,0.8125)(20,0.795918367346939)
 		    };
@@
 		    coordinates {
-		    (10,  0.78552344907839267)(30, 0.78870711278952932)(50,0.78519302797324753)(100,0.77792094596490047)
+		    (0,0.71031746031746)(1,0.722023912003826)(2,0.734193548387097)(3,0.740054370716392)(4,0.751788722391459)(5,0.752652119278914)(6,0.758342019705656)(7,0.772281323877069)(8,0.774638933587619)(9,0.786846912678115)(10,0.786846912678115)(11,0.795363644516187)(12,0.804524886877828)(13,0.797201562617384)(14,0.812955643390426)(15,0.775568181818182)(16,0.863636363636364)(17,0.883720930232558)(18,0.883720930232558)(19,0.883720930232558)(20,0.904761904761905)
 };
@@
 		    coordinates {
-		    (10,  0.80810421349483996)(30, 0.84745259081196467)(50,0.8751719894688631)(100,0.89739411630036825)
-		    };
-		\legend{weather,weapons,soccer,museum,city}
+		    (0,0.716727716727717)(1,0.728559859716244)(2,0.740860215053763)(3,0.746857091804827)(4,0.757315933275812)(5,0.758342019705656)(6,0.765286464150101)(7,0.779373522458629)(8,0.787744083140503)(9,0.786846912678115)(10,0.789244481875285)(11,0.804524886877828)(12,0.811442006269593)(13,0.803401771336554)(14,0.785524847694936)(15,0.849173553719008)(16,0.852651515151516)(17,0.866230213015439)(18,0.876750700280112)(19,0.85593220338983)(20,0.863247863247863)
+};
+		\legend{serene,pats-1,pats-5,pats-10,pats-20}
 
@@
 \end{tikzpicture}
-\subcaption{fixing \emph{numBags}=50}\label{fig:bagsize}
-\end{minipage}
-\caption{Average precision and recall on museum domain.}\label{fig:bagging}
+\subcaption{precision}\label{fig:solprec}
+\end{minipage}%
+%
+\begin{minipage}[b]{.33\linewidth}
+\centering
+\begin{tikzpicture}[baseline]
+		\begin{axis}[
+		    xlabel={\emph{solution}},
+		    %ylabel={recall},
+		    xmin=0, xmax=20,
+		    ymin=0.7, ymax=1,
+		    xtick={0,5,10,15,20},
+		    ytick={0.7,0.8,0.9,1},
+		    ymajorgrids=true,
+		    grid style=dashed,
+		    %legend style={at={(0.5,1.1)},anchor=south, legend columns=-1}
+		]
+
+		\addplot[
+		    color=blue,
+		    mark=square,
+		    ]
+		    coordinates {
+		    (0,0.790229885057471)(1,0.870689655172414)(2,0.862068965517241)(3,0.862068965517241)(4,0.862068965517241)(5,0.862068965517241)(6,0.862068965517241)(7,0.853448275862069)
+		    };
+		\addplot[
+		    color=red,
+		    mark=*,
+		    ]
+		    coordinates {
+		    (0,0.828456983629397)(1,0.828456983629397)(2,0.828456983629397)(3,0.828456983629397)(4,0.828456983629397)(5,0.82088122605364)(6,0.82088122605364)(7,0.823754789272031)(8,0.82088122605364)(9,0.823754789272031)(10,0.841431556948798)(11,0.841431556948798)(12,0.841431556948798)(13,0.835684430512017)(14,0.838557993730407)(15,0.825583420411007)(16,0.810431905259492)(17,0.82088122605364)(18,0.82088122605364)(19,0.83098223615465)(20,0.833855799373041)
+};
+		\addplot[
+		    color=green,
+		    mark=x,
+		    ]
+		    coordinates {
+		    (0,0.83098223615465)(1,0.83098223615465)(2,0.83098223615465)(3,0.823406478578892)(4,0.828108672936259)(5,0.820532915360502)(6,0.828108672936259)(7,0.820532915360502)(8,0.820532915360502)(9,0.828108672936259)(10,0.820532915360502)(11,0.820532915360502)(12,0.818007662835249)(13,0.810431905259492)(14,0.800330895158482)(15,0.867163009404389)(16,0.863636363636364)(17,0.863636363636364)(18,0.863636363636364)(19,0.886363636363636)(20,0.886363636363636)
+};
+		 \addplot[
+		    color=brown,
+		    mark=+,
+		    ]
+		    coordinates {
+		    (0,0.83098223615465)(1,0.83098223615465)(2,0.83098223615465)(3,0.823406478578892)(4,0.828108672936259)(5,0.820532915360502)(6,0.820532915360502)(7,0.820532915360502)(8,0.820532915360502)(9,0.820532915360502)(10,0.820532915360502)(11,0.820532915360502)(12,0.820532915360502)(13,0.810431905259492)(14,0.810431905259492)(15,0.765151515151516)(16,0.863636363636364)(17,0.863636363636364)(18,0.863636363636364)(19,0.863636363636364)(20,0.863636363636364)
+};
+		 \addplot[
+		    color=violet,
+		    mark=star,
+		    ]
+		    coordinates {
+		    (0,0.838557993730407)(1,0.838557993730407)(2,0.838557993730407)(3,0.83098223615465)(4,0.828108672936259)(5,0.820532915360502)(6,0.828108672936259)(7,0.828108672936259)(8,0.828108672936259)(9,0.820532915360502)(10,0.820532915360502)(11,0.820532915360502)(12,0.818007662835249)(13,0.800330895158482)(14,0.790229885057471)(15,0.867163009404389)(16,0.867163009404389)(17,0.867163009404389)(18,0.867163009404389)(19,0.870689655172414)(20,0.870689655172414)
+};	
+	%\legend{serene,pats-1,pats-5,pats-10,pats-20}
+		\end{axis}
+	\end{tikzpicture}
+\subcaption{recall}\label{fig:solrec}
+\end{minipage}%
+%
+\begin{minipage}[b]{.33\linewidth}
+\centering
+\begin{tikzpicture}[baseline]
+\begin{axis}[
+		    xlabel={\emph{solution}},
+		    %ylabel={time(s)},
+		    xmin=0, xmax=20,
+		    ymin=0.0, ymax=21,
+		    xtick={0,5,10,15,20},
+		    ytick={0.0,3.0,6.0,9.0,12,15.0,18,21.0},
+		    ymajorgrids=true,
+		    grid style=dashed,
+		    %legend pos=outer north east,
+		    %legend style={at={(0.5,-0.1)},anchor=north, legend columns=-1}
+		]
+
+		\addplot[
+		    color=blue,
+		    mark=square,
+		    ]
+		    coordinates {
+		    (0,2.47666666666667)(1,7.15)(2,7.41)(3,8.83)(4,9.15)(5,9.32)(6,9.84)(7,10.04)
+};
+		\addplot[
+		    color=red,
+		    mark=*,
+		    ]
+		    coordinates {
+		    (0,3.75)(1,3.8)(2,3.84)(3,3.88666666666667)(4,3.93333333333333)(5,3.98)(6,4.03333333333333)(7,4.08)(8,4.13333333333333)(9,4.23)(10,4.29333333333333)(11,4.34)(12,4.38666666666667)(13,4.74)(14,4.83)(15,5.74333333333333)(16,5.96333333333333)(17,6.48666666666667)(18,6.53)(19,6.58333333333333)(20,6.63)
+};
+		\addplot[
+		    color=green,
+		    mark=x,
+		    ]
+		    coordinates {
+		    (0,3.74)(1,3.79)(2,3.83666666666667)(3,3.88666666666667)(4,3.93666666666667)(5,3.98666666666667)(6,4.03666666666667)(7,4.09333333333333)(8,4.17333333333333)(9,4.23)(10,4.31666666666667)(11,4.38)(12,4.54333333333333)(13,5)(14,6.17666666666667)(15,6.755)(16,1.61)(17,2.21)(18,2.35)(19,2.61)(20,3.11)
+};
+		\addplot[
+		    color=brown,
+		    mark=+,
+		    ]
+		    coordinates {
+		    (0,3.75)(1,3.8)(2,3.84666666666667)(3,3.89666666666667)(4,3.95)(5,3.99666666666667)(6,4.05)(7,4.10333333333333)(8,4.16666666666667)(9,4.23333333333333)(10,4.43)(11,4.53333333333333)(12,4.78)(13,5.15333333333333)(14,5.36333333333333)(15,3.365)(16,1.91)(17,1.95)(18,8.42)(19,8.62)(20,8.85)
+};
+		 \addplot[
+		    color=violet,
+		    mark=star,
+		    ]
+		    coordinates {
+		    (0,3.73666666666667)(1,3.78666666666667)(2,3.83666666666667)(3,3.88333333333333)(4,3.93666666666667)(5,3.98666666666667)(6,4.04333333333333)(7,4.09666666666667)(8,4.16)(9,4.22)(10,4.38333333333333)(11,4.49)(12,4.72333333333333)(13,4.99333333333333)(14,9.33333333333333)(15,10.715)(16,10.86)(17,10.915)(18,12.65)(19,20.35)(20,20.56)
+};	
+	%\legend{serene,pats-1,pats-5,pats-10,pats-20}
+		\end{axis}
+\end{tikzpicture}
+\subcaption{time (s)}\label{fig:soltime}
+\end{minipage}%
+\caption{Average precision, recall and time on the museum domain for leave-one-out strategy and different weighting scheme for patterns in serene.}\label{fig:perfsol}
 \end{figure*}
+
+% change in performance if we look at sequentially found solutions
+% only leave-one-out for museum domain with 15s timeout for chuffed
+\begin{figure}\small
+\begin{tikzpicture}\small
+\pgfplotsset{
+    scale only axis,
+    small,
+    xmin=0, xmax=9
+}
+
+\begin{axis}[
+  axis y line*=left,
+  ymin=0.5, ymax=1,
+  xlabel=solution number,
+  ylabel=performance,
+  legend pos=south east,
+]
+\addplot[smooth,mark=x,red]
+  coordinates{
+    (0,0.776507549540743)(1,0.71093042754513)(2,0.822783653218436)(3,0.845760233918129)(4,0.879310344827586)(5,0.88695652173913)(6,0.885964912280702)(7,0.870689655172414)(8,0.878260869565217)(9,0.87719298245614)
+
+}; \label{plot_one}
+\addlegendentry{precision}
+\addplot[smooth,mark=*,green]
+  coordinates{
+    (0,0.773180507486795)(1,0.677202255831871)(2,0.805899400726987)(3,0.838122605363985)(4,0.879310344827586)(5,0.879310344827586)(6,0.870689655172414)(7,0.870689655172414)(8,0.870689655172414)(9,0.862068965517241)
+}; \label{plot_two}
+\addlegendentry{recall}
+\end{axis}
+
+\begin{axis}[
+  axis y line*=right,
+  axis x line=none,
+  ymin=0, ymax=15,
+  legend pos=south east,
+  ylabel=time (s)
+]
+\addlegendimage{/pgfplots/refstyle=plot_one}\addlegendentry{precision}
+\addlegendimage{/pgfplots/refstyle=plot_two}\addlegendentry{recall}
+\addplot[smooth,mark=square,blue]
+  coordinates{
+    (0,0.894338290115883)(1,2.39426428574782)(2,6.89703391393025)(3,10.3563708686829)(4,9.87668780326843)(5,9.92719115257263)(6,10.4045292949677)(7,14.3818371582031)(8,14.4026180458069)(9,14.8023208427429)
+}; \addlegendentry{time}
+\end{axis}
+\end{tikzpicture}
+\caption{Performance of chuffed for museum leave-one-out}\label{fig:loo}
+\end{figure}
 
@@
 \ddg{rewrite, add more}
-\npr{Now the opposite: shrink please}
+\npr{Now the opposite problem}
 
@@
 
-A major issue with fully automatic systems is though that constraints may be inconsistent or absent completely, e.g., tables on the Web \ddg{Why?}.
+A major issue with fully automatic systems is though that constraints may be inconsistent or absent completely, e.g., data from Web services or tables on the Web \ddg{Why?}.
 To overcome this issue, we can apply ML techniques.

### 2017-08-19 stp/paper_aaai/main.tex
Experiments section partially

@@
 
-\npr{Should I mention complex matches like 1:n and n:1 and iMap?}
-
 \section{Conclusion}
@@
 incorporate Linked Open Data and other external knowledge bases to overcome cold start problem;
-incorporate schema and ontology constraints.
+incorporate schema and ontology constraints;
+complex matches like 1:n and n:1 and iMap.
 

### 2017-08-20 stp/paper_aaai/main.tex
Backing up everythin

@@
 \section{Problem Statement \label{SEC:problem}}
-We follow the definitions proposed by Doal \etal{} \cite{doan2012principles}.
 
@@
 
-An ontology $\mathcal{O}$ is a specification of classes of objects, their 
-data properties and relationships between them.
+In our work we consider that an ontology $\mathcal{O}$ has such basic elements as classes which represent a set of concepts, literal values, individuals which are members of classes and properties~\cite{Spanos:semweb}.
+Properties are classified into object properties, which relate two individuals, and datatype properties, which relate indivuduals to literal values.
 An example of an ontology is given in Fig.~\ref{FIG:onto}. 
-A Class in an ontology can have \emph{data properties} or \emph{object properties}. 
-For example, an ``Organisation'' has a ``Person'' 
-(which is a class with its own properties), and it has a ``name'' (which 
-is a data property). 
-Also, a Class can be a subclass of another Class. 
+Here, an individual of the class ``Organisation'' can be related to an individual of the class ``Person'' via object properties ``ceo'' or ``worksFor'', and it can have a data property ``name''. 
+We also consider a special ``subclass'' (or ``is-a'') type of object properties.
 For 
-example ``Cities'' and ``States'' are both ``Places''. 
+example, ``Cities'' and ``States'' are both ``Places''. 
 A subclass inherits all the properties of the parent class.
-\npr{rephrase, I think terminology is off}
+\npr{check}
 
@@
 properties in the ontology. 
-The edges in the semantic model correspond to relationships in the ontology, as shown if Fig.~\ref{FIG:onto} and \ref{FIG:sem}.
+The edges in the semantic model correspond to object properties in the ontology, as shown if Fig.~\ref{FIG:onto} and \ref{FIG:sem}.
+The semantic model may have several instances of the same ontology class or object property.
 
@@
 
-A \emph{source} $s$ is a $n$-ary relation with a set of attributes 
+In our setting we work with relational sources.
+Hence, a \emph{data source} $s$ is a $n$-ary relation with a set of attributes 
 $\mathcal{A}_s = (a_1,...,a_n)$.
+We want to map them to the target ontology $\mathcal{O}$.
+
+Following the traditional data integration framework~\cite{doan2012principles}, we decompose the problem into two parts: schema matching and schema mapping.
+Schema matching part, which we refer to as \emph{semantic labeling}, finds correspondences between attributes from data sources and data nodes of the target ontology.
+In the schema mapping part we want to generate the semantic models of data sources by identifying the connecting paths for the matched data nodes.
 
@@
 are connected to the nodes of $m$.
-
-A \emph{source description} is a triple $\delta = (s, m, \phi)$ where $s$ is a source, $m$ is a semantic model, and $\phi$ is an attribute mapping.
-
+The attribute mapping function addresses the first part of the problem (semantic labeling).
+
+We define a \emph{source description} as a triple $\delta = (s, m, \phi)$ where $s$ is a source, $m$ is a semantic model, and $\phi$ is an attribute mapping.
 Our problem can be stated now the following way. We have an ontology 
@@
 Given a new source $s^\star$, we want to build a semantic model $m^\star$ and an attribute mapping function $\phi^\star$ such that 
-$\delta^\star = (s^\star,m^\star,\phi^\star)$ is an \emph{appropriate} source 
-description. 
-We
-use the term ``appropriate'' since there might be many such triples which are well-formed source descriptions, but only one or a few will capture the intended meaning of the source. 
+$\delta^\star = (s^\star,m^\star,\phi^\star)$ is an \emph{appropriate} source description. 
+We use the term ``appropriate'' since there might be many such triples which are well-formed source descriptions, 
+but only one or a few will capture the intended meaning of the source. 
 Our goal is to automatically build $\delta^\star$ such that it maximizes the \emph{precision} and \emph{recall} between the semantic model 
@@
 The first step to model the semantics of a new source $s^\star$ is to recognize the semantic types present in the source. 
-We call this step \emph{semantic labeling}, which involves giving a confidence value to a match occurring between an attribute from $s^\star$ and type $l \in 
-\mathcal{L_O}$. \ddg{CHECK!}
+We call this step \emph{semantic labeling}, which assigns a confidence value to a match of an attribute from $s^\star$ to a type $l \in 
+\mathcal{L_O}$.
+%\ddg{CHECK!}
 

### 2017-08-20 serene/elements/octopus.py

@@ -251,13 +251,14 @@ class Octopus(object):
         logging.info("Training complete for {}.".format(self.id))
         return self._get_state().status == Status.COMPLETE
 
-    def get_patterns(self, path):
+    def get_patterns(self, path, serene_path=None):
         """
         Send the request to the API to perform pattern mining and pattern embeddings.
         Then a new csv is composed from the obtained files.
 
         Args:
             path: file name where to write the csv file with patterns
+            serene_path: location of storage with respect to python client
 
         Returns: string -- path of the csv file with patterns
 
@@ -271,7 +272,18 @@ class Octopus(object):
             raise Exception(msg)
 
         embeds_path = self._session.octopus_api.patterns(self.id)  # launch training
-        logging.info("Embeddings found for {}.".format(self.id))
+        logging.info("Embeddings found for {} and stored to {}.".format(self.id, embeds_path))
+        print("Embeddings path returned from api: ", embeds_path)
+
+        if serene_path:
+            print("Obtained path: ", serene_path)
+            part = embeds_path.split("/storage/")[1]
+            print("Part: ", part)
+            embeds_path = os.path.join(serene_path, part)
+            logging.info("Recomputed embeddings path {}.".format(embeds_path))
+            print("New Embeddings path: ", embeds_path)
+
+
 
         graph_j = os.path.join(embeds_path, "graphs.json")
         edges_j = os.path.join(embeds_path, "edges.json")

### 2017-08-20 stp/alignment.py

@@ -580,17 +580,17 @@ def create_octopus(server, ssd_range, sample, ontologies):
             "featureExtractorParams": [
                 {
                     "name": "prop-instances-per-class-in-knearestneighbours",
-                    "num-neighbours": 3
+                    "num-neighbours": 5
                 }
                 , {
                     "name": "min-editdistance-from-class-examples",
-                    "max-comparisons-per-class": 3
+                    "max-comparisons-per-class": 5
                 }, {
                     "name": "min-wordnet-jcn-distance-from-class-examples",
-                    "max-comparisons-per-class": 3
+                    "max-comparisons-per-class": 5
                 }, {
                     "name": "min-wordnet-lin-distance-from-class-examples",
-                    "max-comparisons-per-class": 3
+                    "max-comparisons-per-class": 5
                 }
             ]
         }
@@ -833,8 +833,9 @@ def do_chuffed(server, ch_octopus, ch_dataset, ch_column_names, ch_ssd, orig_ssd
         pattern_time = None
     try:
         integrat = integ.IntegrationGraph(octopus=ch_octopus, dataset=ch_dataset,
-                                          match_threshold=0.001, simplify_graph=simplify,
-                                          patterns=patterns, pattern_sign=pattern_sign)
+                                          simplify_graph=simplify,
+                                          patterns=patterns, pattern_sign=pattern_sign,
+                                          add_unknown=True)
         if chuffed_path:
             integrat._chuffed_path = chuffed_path  # change chuffed solver version
         solution = integrat.solve(ch_column_names,
@@ -866,6 +867,7 @@ def do_chuffed(server, ch_octopus, ch_dataset, ch_column_names, ch_ssd, orig_ssd
             match_score = json_sol["match_score"]
             cost = json_sol["cost"]
             objective = json_sol["objective"]
+            extended_time = json_sol["extended_time"]
 
             try:
                 comparison = server.ssds.compare(cp_ssd, ch_ssd, False, False)
@@ -889,14 +891,14 @@ def do_chuffed(server, ch_octopus, ch_dataset, ch_column_names, ch_ssd, orig_ssd
                      soft_assumptions, pattern_sign, accu, sol_accuracy,
                      match_score, cost, objective,
                      cor_match_score, cor_cost, pattern_time,
-                     integrat.graph.number_of_nodes(), integrat.graph.number_of_edges()]]
[…]

### 2017-08-20 stp/integration.py

@@ -11,7 +11,14 @@ import networkx as nx
 import yaml
 import os
 from collections import defaultdict
-from minizinc import *
+
+try:
+    from minizinc import *
+except ImportError as e:
+    import sys
+    sys.path.insert(0, '.')
+    from minizinc import *
+
 import subprocess
 import re
 import time
@@ -25,6 +32,7 @@ class IntegrationGraph(object):
     Integration graph to map a relational data source onto an ontology using a CP solver
     """
     UNKNOWN_SCORE = 5.0
+    DEFAULT_SCORE = 99.0
 
     def __init__(self, octopus, dataset, match_threshold=0.0,
                  simplify_graph=False,
@@ -33,7 +41,8 @@ class IntegrationGraph(object):
                  predicted_df=None,
                  alignment_graph=None,
                  alignment_node_map=None,
-                 alignment_link_map=None):
+                 alignment_link_map=None,
+                 add_unknown=False):
         """
         Octopus should be trained.
         :param octopus: Octopus object which is used to integrate the new data source
@@ -47,6 +56,7 @@ class IntegrationGraph(object):
         :param alignment_graph: networkx multidigraph for the alignment graph
         :param alignment_node_map: dictionary
         :param alignment_link_map: dictionary
+        :param add_unknown
         :return:
         """
         logging.info("Initializing integration graph for the dataset {} using octopus {}".format(
@@ -61,23 +71,28 @@ class IntegrationGraph(object):
             pattern_sign = 1.0
         self._pattern_sign = pattern_sign
         self._predicted_df = predicted_df
+        self._add_unknown = add_unknown
 
         # the integration graph contains the alignment graph at the beginning
         self.graph, self._node_map, self._link_map = self._get_initial_alignment(alignment_graph,
                                                                                  alignment_node_map,
-                                                                                 alignment_link_map)
+                                                                                 alignment_link_map,
+                                                                                 add_unknown)
         self._chuffed_path, self._mzn2fzn_exec, self._model_mzn, self._solns2out_exec, self._timeout = \
             self._read_config()
 
         self._graph_node_map = {}
 
-    def _get_initial_alignment(self, alignment_graph, alignment_node_map, alignment_link_map):
+    def _get_initial_alignment(self, alignment_graph,
+                               alignment_node_map, alignment_link_map,
[…]

### 2017-08-20 stp/soccer_experiments.py

@@ -56,14 +56,14 @@ log.addHandler(my_handler)
 # =======================
 sn = serene.Serene(
     host='127.0.0.1',
-    port=8080,
+    port=9090,
 )
 print(sn)
 
 if "SERENE_BENCH" not in os.environ:
     os.environ["SERENE_BENCH"] = os.path.join(project_path, "tests", "resources")
 
-benchmark_path = os.path.join(os.environ["SERENE_BENCH"], "museum_benchmark")
+benchmark_path = os.path.join(os.environ["SERENE_BENCH"], "soccer")
 
 print("benchmark_path: ", benchmark_path)
 
@@ -99,7 +99,7 @@ unknown_owl = os.path.join(project_path, "stp", "unknown", "unknown_class.ttl")
 print("Unknown ontology ", unknown_owl)
 ontologies.append(sn.ontologies.upload(unknown_owl))
 
-print("*********** Ontologies from museum benchmark")
+print("*********** Ontologies from soccer benchmark")
 for onto in ontologies:
     print(onto)
 print()
@@ -126,12 +126,13 @@ for ds in os.listdir(dataset_dir):
     if ds.endswith(".gz"):
         continue
     ds_f = os.path.join(dataset_dir, ds)
-    ds_name = os.path.splitext(ds)[0]
+    # ds_name = os.path.splitext(ds)[0]
+    ds_name = ds
     # associated semantic source description for this dataset
     ssd_f = os.path.join(ssd_dir, ds_name + ".ssd")
 
     print("Adding dataset: " + str(ds_f))
-    dataset = sn.datasets.upload(ds_f, description="museum_benchmark")
+    dataset = sn.datasets.upload(ds_f, description="soccer_benchmark")
     datasets.append(dataset)
 
     print("Adding ssd: " + str(ssd_f))
@@ -234,7 +235,7 @@ def do_experiment(octopus, orig_ds, orig_ssd, avail_labels, chosen_paths, chosen
 
     # karma approach
     print("---> trying karma")
-    res = al.do_karma(sn, octopus, orig_ds, cor_ssd, ssd, train_flag=known_num,
+    res = al.do_karma(sn, octopus, orig_ds, cor_ssd, ssd, train_flag=False,
                       accu=sm_accuracy, experiment=experiment_descr, pattern_time=pattern_time)
     benchmark_results += res
     csvfile.writerows(res)
[…]

### 2017-08-20 stp/soccer_test_unknown.py

@@ -245,8 +245,9 @@ def do_experiment(octopus, orig_ds, orig_ssd, avail_labels, chosen_paths, chosen
 #
 # =======================
 import time
+import yaml
 chuffed_lookup_path = os.path.join(project_path, "stp", "minizinc")
-result_csv = os.path.join(project_path, "stp", "resources", "results", "unknown_benchmark_soccer_addpaths.csv")
+result_csv = os.path.join(project_path, "stp", "resources", "results", "soccer_test.csv")
 with open(result_csv, "w+") as f:
     csvf = csv.writer(f)
     csvf.writerow(["experiment", "octopus", "dataset", "name", "ssd",
@@ -255,7 +256,8 @@ with open(result_csv, "w+") as f:
                    "karma_jaccard", "karma_precision", "karma_recall",
                    "known_num", "time", "chuffed_path", "simplify", "chuffed_time",
                    "soft_assumptions", "pattern_significance", "sm_accuracy", "sol_accuracy",
-                   "match_score", "cost", "objective", "cor_match_score", "cor_cost", "pattern_time"])  # header
+                   "match_score", "cost", "objective", "cor_match_score", "cor_cost",
+                   "pattern_time", "number_nodes", "number_links", "extended_time"])  # header
 
     sample_range = list(range(len(new_ssds)))
     len_sample = len(sample_range)
@@ -265,17 +267,17 @@ with open(result_csv, "w+") as f:
                           "karma_jaccard", "karma_precision", "karma_recall",
                           "train_flag", "time", "chuffed_path", "simplify", "chuffed_time",
                           "soft_assumptions", "pattern_significance", "sm_accuracy", "sol_accuracy",
-                          "match_score", "cost", "objective", "cor_match_score", "cor_cost", "pattern_time"]]
+                          "match_score", "cost", "objective", "cor_match_score", "cor_cost", "pattern_time",
+                          "extended_time"]]
 
     print("Starting benchmark")
 
-    for cur_id in sample_range:
+    for cur_id in [0]:#sample_range:
         print("Currently selected ssd: ", cur_id)
         test_sample = [cur_id]
 
-        for num in range(1, len(sample_range)):
-            train_sample = sample_range[:max(cur_id + num + 1 - len_sample, 0)] + sample_range[
-                                                                                  cur_id + 1: cur_id + 1 + num]
+        for num in [5]: #range(1, len(sample_range)):
[…]

### 2017-08-20 stp/stp_experiments_unknown.py

@@ -244,8 +244,9 @@ def do_experiment(octopus, orig_ds, orig_ssd, avail_labels, chosen_paths, chosen
 #
 # =======================
 import time
+import yaml
 chuffed_lookup_path = os.path.join(project_path, "stp", "minizinc")
-result_csv = os.path.join(project_path, "stp", "resources", "unknown_benchmark_museum_addpaths_loo.csv")
+result_csv = os.path.join(project_path, "stp", "resources", "results", "unknown_benchmark_museum_addpaths_2.csv")
 with open(result_csv, "w+") as f:
     csvf = csv.writer(f)
     csvf.writerow(["experiment", "octopus", "dataset", "name", "ssd",
@@ -255,7 +256,7 @@ with open(result_csv, "w+") as f:
                    "known_num", "time", "chuffed_path", "simplify", "chuffed_time",
                    "soft_assumptions", "pattern_significance", "sm_accuracy", "sol_accuracy",
                    "match_score", "cost", "objective", "cor_match_score", "cor_cost", "pattern_time",
-                   "num_node", "num_edges"])  # header
+                   "num_node", "num_edges", "extended_time"])  # header
 
     sample_range = list(range(len(new_ssds)))
     len_sample = len(sample_range)
@@ -273,7 +274,7 @@ with open(result_csv, "w+") as f:
         print("Currently selected ssd: ", cur_id)
         test_sample = [cur_id]
 
-        for num in [28]:#range(1, len(sample_range)):
+        for num in range(1, len(sample_range)):
             train_sample = sample_range[:max(cur_id + num + 1 - len_sample, 0)] + sample_range[
                                                                                   cur_id + 1: cur_id + 1 + num]
             print("     train sample size: ", num)
@@ -304,8 +305,12 @@ with open(result_csv, "w+") as f:
             pattern_time = None
             start_time = time.time()
             try:
-                octo_patterns = octo.get_patterns(octo_csv)
+                with open(os.path.join(project_path, "stp", 'config.yaml'), 'r') as stream:
+                    config = yaml.load(stream)
+                print("Serene-path: ", config["embeds-path"])
+                octo_patterns = octo.get_patterns(octo_csv, serene_path=str(config["embeds-path"]))
                 pattern_time = time.time() - start_time
+                print("Patterns obtained")
             except Exception as e:
                 print("failed to get patterns: {}".format(e))
                 logging.warning("failed to get patterns: {}".format(e))
@@ -348,18 +353,18 @@ with open(result_csv, "w+") as f:
[…]

### 2017-08-20 stp/paper_aaai/main.tex
Backing up everything, results section

@@
 In our case, we would like this global model to account not only for structural properties of the original data sources, but also to include the semantics, which is usually implicitly present in the sources.
-In other words, we want to build a semantic model which describes the data sources in terms of concepts and relationships defined by an ontology \cite{Taheriyan2013}.
+In other words, we want to build a semantic model which describes the data sources in terms of concepts and relationships defined by an ontology \cite{taheriyan2016learning}.
 Henceforth, we focus on a specific data integration problem: automatically mapping a new relational data source onto a user provided ontology.
@@
 
-In this paper we use Machine Learning techniques (ML) to learn mapping rules from already mapped instances.
+In this paper we use Machine Learning techniques (ML) to learn mapping rules from previously mapped instances.
 To this end we formulate the Relational-To-Ontology Mapping Problem (\relonto{}) as a Minimum Cost Steiner Tree Problem (STP) with side constraints \cite{deuna2016steiner}.
@@
 find a minimum cost Steiner Tree in the graph.
-The goal is to assign the costs on the edges in such a way that the resulting Steiner Tree is a valid semantic model for the new source.
-
-The contributions of this work are:
+The goal is to assign the costs on the edges in such a way that the resulting Steiner Tree is a valid and coherent semantic model for the new source.
+
+The contributions of this work are:\ddg{TODO}
 \begin{itemize}
-	\item \ddg{TODO}
+	\item A novel modeling framework for \relonto{} problem which seemlessly incorporates machine learning and constraint programming.
+	\item An efficient approach to handle attributes which cannot be matched to the ontology. \npr{semantic labeling model and root, unknown nodes in the alignment graph and additional constraints} 
 \end{itemize}
@@
 \mathcal{L_O}$.
+Typically semantic labeling techniques encounter several problems.
+Firstly, there can be naming conflicts~\cite{Pinkel:rodi}, including those cases where users represent the same data in different ways.
+Secondly, semantically different attributes might have syntactically similar content, for example, startDate versus endDate for the Event class.
+Thirdly, a considerable number of attributes which do not have any corresponding property in the ontology, either by accident or on purpose.
 %\ddg{CHECK!}
@@
 The known source descriptions $S_T$ provide us the training sample.
-We compute a feature vector for each source \ddg{Which features?} attribute and associate the known semantic type with the corresponding feature vector. We train a random forest on this sample. 
-Then we use the learnt model to classify attributes in the new
-source.
+We compute a feature vector for each attribute in a data source \ddg{Which features?} and associate the known semantic type with the corresponding feature vector.
+The feature vector includes characteristics of the attribute such as a number of whitespaces and other special characters, statistics of values in the column (e.g, mean/ max/ min string length and numeric statistics) and many more.
+One of the important features characterising information content of an attribute is Shannon's entropy of the attribute's concatenated rows.
+Shannon's entropy (or information entropy~\cite{Manning:Introduction}) of a string $X$ is defined as
+$H(X) = -\sum_{i}{p_i \log_{2}p_i},$ where $p_i$ is the probability of a character, whose index in character vocabulary is $i$, to appear in $X$, and the summation ranges over all
+characters in the vocabulary of all possible characters.
+To evaluate $p_i$ in Shannon's entropy, we evaluate normalized character frequency distribution \emph{chardist} of an attribute, as character counts in concatenated rows of the attribute, normalized by the total length of the concatenated rows.
+The vocabulary of all characters consists of 100 printable characters (including $\backslash$n).
+Finally, we add the 100-dimensional vector of $p_i$ to the attribute feature vector.
+We also compute a set of features based on similarity metrics inspired by state-of-the-art works~\cite{Pham:semantic} or~\cite{Ritze:matching}.
+Among others, we compute mean cosine similarity for character distributions of attribute values and string similarity metrics for attribute names.
+%To extract features from attribute names, we compute string similarity metrics: minimum edit distance, two WordNet based similarity measures such as JCN~\cite{Jiang:Semantic} and LIN ~\cite{Lin:Information}, and $k$-nearest neighbors using Needle-Wunsch distance~\cite{Needleman:General}.
+%The minimum edit distance between two strings $s_1$ and $s_2$ is the minimum number of edit operations, such as insertion, deletion, substitution, which are required to transform one string into another~\cite{Manning:Introduction}.
+%We compute the similarity between attribute name and all class instances in the training data.
+%The number of thus extracted features depends on the number of semantic labels in the training data.
+We train a random forest on the obtained sample.
 
@@
 
-The algorithm we used to construct $\mathcal{G_O}$ is the same as \cite{taheriyan2016learning} and is described in detail in their work.
+The algorithm for the construction of the alignment graph $\mathcal{G_O}$ follows the ideas of~\cite{taheriyan2016learning}.
 Briefly, the algorithm has three parts:
@@
 We say these nodes are \emph{induced} into the 
-alignment graph by the semantic types, we note them $\mathcal{D_{G_O}}$ and we 
-call them \emph{data nodes} of the alignment graph.
+alignment graph by the semantic types.
+We denote them as $\mathcal{D_{G_O}}$ and call them the \emph{data nodes} of the alignment graph.
 
@@
 
-As an extension to the problem, we consider using pattern mining techniques in order to identify patterns in the training set of semantic model that repeat themselves often. 
-The hope is that with such information we can encourage the semantic model $m^\star$ for the new source to use groups of edges that                                       appeared often together in training semantic models.
+Certain patterns of connections can be prevalent in the domain.
+For example, in Fig.~\ref{FIG:sem} both semantic models have class nodes ``City'', ``Organization'' and ``Person''.
+According to the ontology in Fig.~\ref{FIG:onto} there are multiple ways to connect these nodes.
+However, if we know that the ``Person'' works for the ``Organization'', then based on the known semantic models ``City'' is more likely to be the birth place of the ``Person'' rather than the location of the ``Organization''.
+To increase the coherence of the generated semantic models, we would like to discover such patterns of connections.
+
+%As an extension to the problem, we consider using pattern mining techniques in order to identify patterns in the training set of semantic model that repeat themselves often. 
+%The hope is that with such information we can encourage the semantic model $m^\star$ for the new source to use groups of edges that                                       appeared often together in training semantic models.
 
 \npr{reformulate for typed directed multigraphs and example based on Fig3}
-In our context, we define a \emph{pattern} is a graph $P$ that is undirected 
-and simple (no multiple edges between two nodes, nor self-loops).
-
-Let $G = (V_G,E_G,\lambda_G)$ and $P = (V_P,E_P, \lambda_P)$ be two graphs 
-where $\lambda_G$ (resp. $\lambda_P$) is a \emph{labeling function} that maps 
-nodes/edges of $G$ (resp. $P$) into a set of labels (e.g. natural numbers).
-An \emph{embedding} of $P$ into $G$ is an injective function $f : V_G \mapsto 
-V_P$ such that for all $x,y \in V_P$:
-\begin{enumerate}
-	\item $\{x,y\} \in E_P \implies \{f(x),f{y}\} \in E_G$.
-	\item $\lambda_P(x) = \lambda_G(f(x))$
-	\item $\lambda_P(\{x,y\}) = \lambda_G(\{f(x),f(y)\})$
-\end{enumerate} 
-That is, if an edge exists in $P$, it must also exist in $G$ (but not 
-vice-versa); and the labelling functions of both graphs must match after 
-applying the embedding function.
-
-Our goal is to take a set of graphs (the semantic models from the training set 
-$S_T$) and find patterns that appear often across that set of graphs. 
-This is 
-known as the Frequent Graph Pattern Mining, which contains the subgraph 
+In our context, patterns are typed directed graphs.
+We mine these patterns from the set of semantic models in the training set $S_T$.
+This is known as Transactional Frequent Graph Pattern Mining, which contains the subgraph 
 isomorphism, known to be NP-complete.
-There exists a range of tools that can achieve this task using Transactional 
-Frequent Graph Pattern Mining~\cite{yan2002gspan}. 
-We chose to use DIMSpan \cite{petermann2017dimspan}. 
-\ddg{CHECK! How do they solve an NP-complete problem??}
-\npr{Im not sure what to say here: there is just no guarantee how long it will take for the whole thing to run, except there is a threshold on how frequent they have to be; they use gSpan procedure to prune patterns and a variant of Ulmans algorithm for graph pattern matching}
-
+The frequency of a pattern is an anti-monotonous measure, meaning that bigger patterns will have lower supports than their subgraphs.
+We solve this pattern mining task with the tool DIMSpan \cite{petermann2017dimspan} which adapts gSpan~\cite{yan2002gspan} pruning techniques to the typed graphs and uses Apache Flink for scalability.
 We obtain patterns of size upto 6 in under 4 minutes for the biggest instances in our evaluation framework. 
-\npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe cite my work on how databases perform for graph pattern matching.
-Should it be better in related work?}
-
-This tool provides us with a list of patterns that are frequent, as well as 
-their support. 
-The \emph{support} of a pattern is an anti-monotonous measure of frequency. 
-Thus, the higher the support, the more often the pattern appears. This typically means that big patterns have low support.
+\npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe cite my work on how databases perform for graph pattern matching. Should it be better in related work?}
+
+%Let $G = (V_G,E_G,\lambda_G)$ and $P = (V_P,E_P, \lambda_P)$ be two graphs 
+%where $\lambda_G$ (resp. $\lambda_P$) is a \emph{labeling function} that maps 
+%nodes/edges of $G$ (resp. $P$) into a set of labels (e.g. natural numbers).
+%An \emph{embedding} of $P$ into $G$ is an injective function $f : V_G \mapsto 
+%V_P$ such that for all $x,y \in V_P$:
+%\begin{enumerate}
+%	\item $\{x,y\} \in E_P \implies \{f(x),f{y}\} \in E_G$.
+%	\item $\lambda_P(x) = \lambda_G(f(x))$
+%	\item $\lambda_P(\{x,y\}) = \lambda_G(\{f(x),f(y)\})$
+%\end{enumerate} 
+%That is, if an edge exists in $P$, it must also exist in $G$ (but not 
+%vice-versa); and the labelling functions of both graphs must match after 
+%applying the embedding function.
+
+%Our goal is to take a set of graphs (the semantic models from the training set 
+%$S_T$) and find patterns that appear often across that set of graphs. 
+%This is 
+%known as the Frequent Graph Pattern Mining, which contains the subgraph 
+%isomorphism, known to be NP-complete.  
+%We solve this task with the tool DIMSpan \cite{petermann2017dimspan} which adapts gSpan~\cite{yan2002gspan} pruning techniques to the typed graphs and uses Apache Flink for scalability. 
+%\ddg{CHECK! How do they solve an NP-complete problem??}
+%\npr{Im not sure what to say here: there is just no guarantee how long it will take for the whole thing to run, except there is a threshold on how frequent they have to be; they use gSpan procedure to prune patterns and a variant of Ulmans algorithm for graph pattern matching}
+% 
+%This tool provides us with a list of patterns that are frequent, as well as 
+%their support. 
+%The \emph{support} of a pattern is an anti-monotonous measure of frequency. 
+%Thus, the higher the support, the more often the pattern appears. 
+%This typically means that big patterns have low support.
 
@@
 This system also phrases the \relonto{} problem as STP and decomposes it further into two parts.
-However, they use approximation algorithms both for the matching and for the STP parts.
+However, they use heuristic algorithms both for the matching and for the STP parts.
+They solve the problems sequentially, i.e., once they produce a set of candidate mappings for attributes into the ontology, they fix this set and move onto the STP part.
 Additionally, they do not consider unmatched attributes in the sources.
@@
 \npr{check characteristics, AWS machine is bigger}
+In all our experiments we use a timeout threshold of 15s for the chuffed solver.
 
@@
 \ddg{TODO}
+
+To evaluate our new system \emph{serene}, we show that its semantic labeling model produces more accurate matches for attributes and the CP formulation leads to better semantic models in terms of precision and recall.
 
@@
 Tab.~\ref{tab:semlab} provides evidence that our new semantic labeling model is better suited for the task when there are unmatched attributes in domains.
-\npr{Explain}
+DSL uses heuristic measures to capture the similarity of attributes within the same class.
+It is clear that we cannot directly speak about similarity for unmatched attributes, since they are rather dissimilar from known semantic types.
+Our intution why our approach performs better is that we have encorporated features which are derived directly from attribute values and are not based on the notion of similarity.
+\npr{Good enough explanation?}
 
@@
 %%%
-We evaluate our new system \emph{serene} and its modification \emph{serene-pats}, which uses graph patterns, against the state-of-the-art system \emph{karma}.
-Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} show their performance on the museum and soccer domains.
-We report average precision, recall and run times for the systems with regard to variable number of semantic models in the training set.
-
 %%% museum domain
@@
 
-%%
-As mentioned previously, the chuffed solver outputs solutions as it finds them.
-In Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} we report the first found solutions.
-In Fig.~\ref{fig:perfsol} we show how the performance of \emph{serene} changes across sequentially found solutions.
-In all our experiments we use a timeout threshold of 15s for the chuffed solver.
-Additionally, we investigate how the performance is influenced if we introduce a weighting scheme on the patterns,
-i.e., costs of patterns are scaled by a factor. 
+% karma vs serene vs serene-pats
+We evaluate our new system \emph{serene} and its modification \emph{serene-pats}, which uses graph patterns, against the state-of-the-art system \emph{karma}.
+All three systems have access to the same set of matches produced by our semantic labeling model.
+Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} show their performance on the museum and soccer domains.
+We report average precision, recall and run times for the systems with regard to variable number of semantic models in the training set.
+For \emph{serene} and \emph{serene-pats} we report the first solutions found by the chuffed solver.
+We use default parameters for \emph{karma} which were shown to yield the best results~\cite{taheriyan2016learning}.
+As we can see, \emph{serene} produces on average the best semantic models in terms of precision while \emph{serene-pats} generates slightly better models in terms of recall.
+If we consider results separately per each instance and not on average, there are a few instances where \emph{karma} generates more precise models, however, our new approaches produce much better models in terms of recall in all considered instances.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %% sequentially found solutions and different weights for patterns
-\begin{figure*}[ht]\small
+\begin{figure*}[h]\small
 \pgfplotsset{
@@
 
+%% sequential solution
+As mentioned previously, the chuffed solver outputs solutions as it finds them.
+In Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} we report the first found solutions.
+In Fig.~\ref{fig:perfsol} we show how the performance of \emph{serene} changes across sequentially found solutions.
+The idea is that the chuffed solver finds better solutions in terms of cost function, however, as we can see from the results,
+that does not translate directly into more precise semantic models.
+Additionally, we investigate how the performance is influenced if we introduce a weighting scheme on the patterns,
+i.e., costs of patterns are scaled by a factor.
+In Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} we use a scaling factor 1 for pattern costs.
+Fig.~\ref{fig:perfsol} demonstrates that by using scaling factors 5, 10 or 20 for patterns from the museum domain we can generate semantic models which are almost 90\% in precision and recall.
+This is a 20\% improvement in presision compared to the first solution found by \emph{serene-pats} and a 10\% improvement both in precision and recall for the first solution from \emph{serene}.
+However, such improvement comes at a cost in run time.
+On average, we have observed that the chuffed solver yields very good results already with the first found solution.
+The sequential solutions are not always better, and hitting the optimal solution may take hours.
+
 % change in performance if we look at sequentially found solutions
 % only leave-one-out for museum domain with 15s timeout for chuffed
+\npr{not sure whether Fig.~\ref{fig:loo} is needed}
 \begin{figure}\small
@@
 \end{tikzpicture}
-\caption{Performance of chuffed for museum leave-one-out}\label{fig:loo}
+\caption{Performance of \emph{serene} for leave-one-out strategy on the museum domain.}\label{fig:loo}
 \end{figure}
+
+\npr{Maybe some words on how optimal solution found by chuffed relates to the ground truth?}
 
@@
 As mentioned above, the approaches for mapping Web tables also perform semantic labeling.
-They design various similarity metrics for attribute names and attribute values.
-However, they disregard the attributes which are not matched to the ontology (the so-called \emph{unknown} class of attributes).
+They design various similarity metrics for attribute names and values.
+However, they disregard the attributes which are not matched to the ontology (the so-called \emph{unknown} set of attributes) which are especially abundant on the Web~\cite{Ritze:matching}\cite{Pham:semantic}.
 It is clear that we cannot directly speak about similarity for unmatched attributes, since they are rather dissimilar from known semantic types.

### 2017-08-21 stp/paper_aaai/main.tex
Trying to shrink, rewrote section 5.1 and 5.2

@@
 \usepackage{tikz}
+\tikzset{every picture/.style={font issue=\small},
+         font issue/.style={execute at begin picture={#1\selectfont}}
+        }
 \usetikzlibrary{shadows.blur}
@@
 [draw,densely dashed,-,black!70,decoration={snake,segment 
-length=10,amplitude=1.5,post length=4}]
+length=10,amplitude=0.3,post length=4}]
 \tikzstyle{hasaC} = [>=stealth',draw,thick,-, black]
@@
 \newcommand{\code}[1]{\texttt{#1}}
+
+\newcommand{\ignore}[1]{}
 
@@
 	\node[class] (pe) at (0,0)  {Person};
-	\node[class] (co) at (0,-3) {Organisation};
-	\node[class] (ev) at (3.5,1) {Event};
+	\node[class] (co) at (0,-2) {Organisation};
+	\node[class] (ev) at (3,0.2) {Event};
 	\node[class] (pl) at (5,-1) {Place};
-	\node[class] (ci) at (3,-3) {City};
-	\node[class] (st) at (5,-3) {State};
+	\node[class] (ci) at (3,-2.5) {City};
+	\node[class] (st) at (5,-2.5) {State};
 
@@
 	\path[hasaC,->] (co) edge [] 
-	node [midway, above, sloped] {location} (pl) ;
+	node [near start, above, sloped] {location} (pl) ;
 
@@
 
-	\path[draw,hasaA,->] (pe) edge [decorate,bend left = 10] 
-	node [midway, above, sloped] {name} (-0.5,2);
-	\path[draw,hasaA,->] (pe) edge [decorate,bend left = 0] 
-	node [midway, below, sloped] {birthDate} (0,2);
+	\path[draw,hasaA,->] (pe) edge [decorate,out=140,in=0] 
+	node [midway, above, sloped] {name} (-0.9,0.5);
+	\path[draw,hasaA,->] (pe) edge [decorate,out=100,in=0] 
+	node [midway, above, sloped] {birthDate} (-0.9,1);
 
 	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
-	node [midway, below, sloped] {name} (-1,-5);
+	node [midway, below, sloped] {name} (-1,-3);
 	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
-	node [midway, above, sloped] {phone} (0,-5);
+	node [midway, above, sloped] {phone} (0,-3.2);
 	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
-	node [midway, above, sloped] {email} (1,-5);
-
+	node [midway, above, sloped] {email} (1.4,-3);
+
+	\path[draw,hasaA,->] (ev) edge [decorate,out=70,in=200] 
+	node [midway, above, sloped] {startDate} (3.8,1);
 	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
-	node [midway, below, sloped] {startDate} (2.5,3.2);
+	node [midway, above, sloped] {endDate} (4.5,0.8);
 	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
-	node [midway, above, sloped] {endDate} (3.5,3.2);
-	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
-	node [midway, below, sloped] {title} (4.5,3.2);
+	node [midway, above, sloped] {title} (5,0.2);
 
@@
 In our work we consider that an ontology $\mathcal{O}$ has such basic elements as classes which represent a set of concepts, literal values, individuals which are members of classes and properties~\cite{Spanos:semweb}.
-Properties are classified into object properties, which relate two individuals, and datatype properties, which relate indivuduals to literal values.
+Properties are classified into \emph{object properties}, which relate two 
+individuals, 
+and \emph{datatype properties}, which relate individuals to literal values.
 An example of an ontology is given in Fig.~\ref{FIG:onto}. 
@@
 A subclass inherits all the properties of the parent class.
-\npr{check}
 
@@
 
-	\node[data] (pen) at (2.5,-1) {\scriptsize Person.name};
-	\node[data] (peb) at (4.3,-1) {\scriptsize Person.birthDate};
-	\node[data] (cin) at (1,-1) {\scriptsize City.name};
-	\node[data] (stn) at (-1,-1) {\scriptsize State.name};
-	\node[data] (con) at (6,-1) {\scriptsize Org.name};
+	\node[data] (pen) at (2.5,-0.7) {\scriptsize Person.name};
+	\node[data] (peb) at (4.3,-0.7) {\scriptsize Person.birthDate};
+	\node[data] (cin) at (1,-0.7) {\scriptsize City.name};
+	\node[data] (stn) at (-1,-0.7) {\scriptsize State.name};
+	\node[data] (con) at (6,-0.7) {\scriptsize Org.name};
 
@@
 \end{scope}
-\begin{scope}[yshift=-60]
+\begin{scope}[yshift=-40]
 	\node[class] (pl) at (-1,0)  {\small City};
@@
 
-	\node[data] (pen) at (2.5,-1) {\scriptsize Person.name};
-	\node[data] (evs) at (4.2,-1) {\scriptsize Event.startDate};
-	\node[data] (eve) at (6,-1) {\scriptsize Event.endDate};
-	\node[data] (con) at (1,-1) {\scriptsize Org.name};
-	\node[data] (pln) at (-1,-1) {\scriptsize City.name};
+	\node[data] (pen) at (2.5,-0.7) {\scriptsize Person.name};
+	\node[data] (evs) at (4.2,-0.7) {\scriptsize Event.startDate};
+	\node[data] (eve) at (6,-0.7) {\scriptsize Event.endDate};
+	\node[data] (con) at (1,-0.7) {\scriptsize Org.name};
+	\node[data] (pln) at (-1,-0.7) {\scriptsize City.name};
 
@@
 
-	\path[hasaC,->] (co) edge [bend left = -10] 
+	\path[hasaC,->] (co) edge [bend left = 0] 
 	node [midway, above, sloped] {location} (pl) ;
@@
 Our goal is to automatically build $\delta^\star$ such that it maximizes the \emph{precision} and \emph{recall} between the semantic model 
-$m^\star$ and the semantic model $m^\dag$ that the user considers correct. \npr{definitions for precision and recall}
-
-\section{ML for Training on Source Descriptions \label{SEC:ML}\ddg{Better title 
-than this 
-please...}}
+$m^\star$ and the semantic model $m^\dag$ that the user considers correct. 
+%\npr{definitions for precision and recall}
+
+\section{ML for Training on Source Descriptions \label{SEC:ML}}
 
@@
 The known source descriptions $S_T$ provide us the training sample.
-We compute a feature vector for each attribute in a data source \ddg{Which features?} and associate the known semantic type with the corresponding feature vector.
+We compute a feature vector for each attribute in a data source and associate 
+the known semantic type with the corresponding feature vector.
 The feature vector includes characteristics of the attribute such as a number of whitespaces and other special characters, statistics of values in the column (e.g, mean/ max/ min string length and numeric statistics) and many more.
@@
 
-\ddg{IMPORTANT: Do we keep all of them, or only the top $k$ with most 
-confidence? If so, 
-what is $k$?}
-\npr{We keep all, that is the crucial difference from Karma which does some voodoo heuristic filtering}
+Note that we keep all the matches, regardless of the confidence fo the match. 
+This is an important difference between our system and other approaches 
+\cite{taheriyan2016learning} that 
+remove some of the matches based on heuristics to then simplify the task of 
+finding the semantic model. \ddg{CHECK}
+
+%\ddg{IMPORTANT: Do we keep  all of them, or only the top $k$ with most 
+%confidence? If so, 
+%what is $k$?}
+%\npr{We keep all, that is the crucial difference from Karma which does some 
+%voodoo heuristic filtering}
 
@@
 Briefly, the algorithm has three parts:
-\begin{enumerate}
-\item Adding the known semantic models.
-\item Adding the semantic types learned for the target source. \ddg{TODO: see 
-Important note above}
-\item Expanding the graph using the domain ontology $\mathcal{O}$.
-\end{enumerate}
+%\begin{enumerate}
+$(i)$ %\item 
+Adding the known semantic models
+$(ii)$ %\item 
+Adding the semantic types learned for the target source \ddg{If we keep 
+all matches, isn't this just adding all the semantic types?}
+%\item 
+$(iii)$ Expanding the graph using the domain ontology $\mathcal{O}$.
+%\end{enumerate}
 
@@
 Blue and orange links are inferred from the ontology $\mathcal{O}$ (the orange ones correspond to the ones added to connect Classes of the ontology that never appeared in the semantic models) and can be assigned the
-maximum weight $w_max$ \ddg{where does this weight come from?} .
+maximum weight $w_max$ \ddg{where does this weight come from?}
 
@@
 
-	\node[data] (pen) at (2.3,1) {\scriptsize Person1.name};
-	\node[data] (peb) at (4.2,1) {\scriptsize Person1.birthDate};
-	\node[data] (cin) at (0.7,1) {\scriptsize City1.name};
-	\node[data] (stn) at (-1,1) {\scriptsize State.name};
-	\node[data] (con) at (6,1) {\scriptsize Org1.name};
+	\node[data] (pen) at (2.3,0.7) {\scriptsize Person1.name};
+	\node[data] (peb) at (4.2,0.7) {\scriptsize Person1.birthDate};
+	\node[data] (cin) at (0.7,0.7) {\scriptsize City1.name};
+	\node[data] (stn) at (-1,0.7) {\scriptsize State.name};
+	\node[data] (con) at (6,0.7) {\scriptsize Org1.name};
 
@@
 % % % CC2
-\def\ysh{-2.5};
+\def\ysh{-2};
 
@@
 
-	\node[data] (pen) at (2.3,-1+\ysh) {\scriptsize Person2.name};
-	\node[data] (evs) at (4.2,-1+\ysh) {\scriptsize Event.startDate};
-	\node[data] (eve) at (6,-1+\ysh) {\scriptsize Event.endDate};
-	\node[data] (con) at (0.7,-1+\ysh) {\scriptsize Org2.name};
-	\node[data] (pln) at (-1,-1+\ysh) {\scriptsize City2.name};
+	\node[data] (pen) at (2.3,-0.7+\ysh) {\scriptsize Person2.name};
+	\node[data] (evs) at (4.2,-0.7+\ysh) {\scriptsize Event.startDate};
+	\node[data] (eve) at (6,-0.7+\ysh) {\scriptsize Event.endDate};
+	\node[data] (con) at (0.7,-0.7+\ysh) {\scriptsize Org2.name};
+	\node[data] (pln) at (-1,-0.7+\ysh) {\scriptsize City2.name};
 
@@
 
-	\path[draw,isa,->,orange!30!white] (ci1) edge[out=-45,in=120] (PL);
-	\path[draw,isa,->,orange!30!white] (pl2) edge[out=90,in=180] (PL);
-	\path[draw,isa,->,orange!30!white] (st1) edge[out=-45,in=150] (PL);
+	\path[draw,isa,->,orange!30!white] (ci1) edge[out=-25,in=130] (PL);
+	\path[draw,isa,->,orange!30!white] (pl2) edge[out=50,in=180] (PL);
+	\path[draw,isa,->,orange!30!white] (st1) edge[out=-45,in=160] (PL);
 
@@
 isomorphism, known to be NP-complete.
-The frequency of a pattern is an anti-monotonous measure, meaning that bigger patterns will have lower supports than their subgraphs.
+The frequency of a pattern is an anti-monotonous measure, meaning that bigger 
+patterns will have lower supports than their subgraphs. \ddg{Define support}
 We solve this pattern mining task with the tool DIMSpan \cite{petermann2017dimspan} which adapts gSpan~\cite{yan2002gspan} pruning techniques to the typed graphs and uses Apache Flink for scalability.
 We obtain patterns of size upto 6 in under 4 minutes for the biggest instances in our evaluation framework. 
-\npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe cite my work on how databases perform for graph pattern matching. Should it be better in related work?}
+\npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe 
+cite my work on how databases perform for graph pattern matching. Should it be 
+better in related work?}
 
@@
 Given a graph $G =
-(V, E)$ and a subset of its nodes $T \subseteq V$ , called \emph{terminals}, a 
+(V, E)$ and a subset of its nodes $T \subseteq V$, a 
 Steiner Tree $G_s = (V_s, E_s )$ is a tree such that $T \subseteq V_s \subseteq 
@@
 \emph{integration graph} $~\mathcal{I}_\mathcal{O}^{s^\star} = 
-(\mathcal{V}_\mathcal{O}^{s^\star},\mathcal{E}_\mathcal{O}^{s^\star})$, with 
-nodes $\mathcal{V}_\mathcal{O}^{s^\star} = \mathcal{V_O} \cup 
-\mathcal{A}_{s^\star}$, 
-edges $\mathcal{E}_\mathcal{O}^{s^\star}$.
+(\mathcal{V}_\mathcal{O}^{s^\star},\mathcal{E}_\mathcal{O}^{s^\star})$, where  
+$\mathcal{V}_\mathcal{O}^{s^\star} = \mathcal{V_O} \cup 
+\mathcal{A}_{s^\star}$.
 
@@
 
-	\node[data] (stn1) at (-3.9,-1) {\scriptsize S.n};
-	\node[data] (cin1) at (-3.1,-1) {\scriptsize C1.n};
-	\node[data] (pen1) at (-2.3,-1) {\scriptsize P1.n};
-	\node[data] (peb1) at (-1.5,-1) {\scriptsize P1.b};
-	\node[data] (con1) at (-0.7,-1) {\scriptsize O1.n};
+	\node[data] (stn1) at (-3.9,-0.9) {\scriptsize S.n};
+	\node[data] (cin1) at (-3.1,-0.9) {\scriptsize C1.n};
+	\node[data] (pen1) at (-2.3,-0.9) {\scriptsize P1.n};
+	\node[data] (peb1) at (-1.5,-0.9) {\scriptsize P1.b};
+	\node[data] (con1) at (-0.7,-0.9) {\scriptsize O1.n};
 
@@
 % % % CC2
-\def\ysh{0};
+\def\ysh{0.1};
 
@@
 (source) at 
-(0,-3) 
+(0,-2) 
 {};
@@
 (source) at 
-(-4.1,-3) 
+(-4.1,-2) 
 {$s^\star$:};
-	\node[att] (a1) at (-3,-3) {\small Surame};
-	\node[att] (a2) at (-1,-3) {\small Workplace};
-	\node[att] (a3) at (1,-3) {\small Date};
-	\node[att] (a4) at (3,-3) {\small Location};
+	\node[att] (a1) at (-3,-2) {\small Surame};
+	\node[att] (a2) at (-1,-2) {\small Workplace};
+	\node[att] (a3) at (1,-2) {\small Date};
+	\node[att] (a4) at (3,-2) {\small Location};
 
@@
 \caption{Example of integration graph. (`\tikz{ \node[att] () at (0,0)  
-{};}' are attribute nodes). We omit weights for clarity. Data node labels are 
-abbreviated but 
-correspond to the ones shown in Fig \ref{FIG:ali}.}
+{};}' are attribute nodes). We omit weights and only show the most likely 
+matches for clarity. Data node
+are the same as in Fig \ref{FIG:ali}.}
 \label{FIG:inte}
@@
 
-The goal is to build a subgraph $T^\star= (V^\star, E^\star)$ 
-of the integration graph 
+The goal is to build a subgraph $T^\star= (V^\star, E^\star)$ of
 $\mathcal{I}_\mathcal{O}^{s^\star}$ for the new source $s^\star$. The solution 
 $T^\star$ will 
-be used to build the source description $\delta^\star = (s^\star, m^\star, 
-\phi^\star)$. 
+be used to build the source description $\delta^\star$. 
 In particular, $(\mathcal{V_O} \cap V^\star,\mathcal{E_O} \cap E^\star)$ 
@@
 The solution $T^\star$ must satisfy the following constraints:
-\begin{enumerate}
-	\item $T^\star$ must be a subgraph of $\mathcal{I}_\mathcal{O}^{s^\star}$
-	\item $T^\star$ must be a tree (connected acyclic graph)
-	\item $\forall a \in \mathcal{A}_{s^\star}, a\in V^\star$
-	\item $\forall a \in \mathcal{A}_{s^\star}, degree(a) = 1$
+%\begin{enumerate}
+	$(i)$ %\item 
+	$T^\star$ must be a subgraph of $\mathcal{I}_\mathcal{O}^{s^\star}$,
+	$(ii)$ %\item 
+	$T^\star$ must be a tree (connected acyclic graph),
+	$(iii)$ %\item 
+	$\forall a \in \mathcal{A}_{s^\star}, a\in V^\star$,
+	$(iv)$ %\item 
+	$\forall a \in \mathcal{A}_{s^\star}, degree(a) = 1$,
 	%\item $\forall n \in \mathcal{D_{G_O}}, degree(a) \in 
 	%\{0,2\}$
-	\item $\forall n \in \mathcal{D_{G_O}} \cap V^\star, 
-	degree(a) = 2$
-\end{enumerate}
+	$(v)$ %\item 
+	$\forall n \in \mathcal{D_{G_O}} \cap V^\star, degree(a) = 2$
+%\end{enumerate}
 
@@
 \section{Modeling as a Constraint Optimization Problem \label{SEC:CP}}
-
 \subsection{Definitions}
-A Constraint Satisfaction Problem (CSP) is a tuple $P = (\boldsymbol{v},D,C)$ 
+A Constraint Optimization Problem (COP) is a tuple $P = (\boldsymbol{v},C,o)$ 
 where $\boldsymbol{v}$ is a 
-set of \emph{variables}, $D$ is a set of unary constraints over 
-$\boldsymbol{v}$ specifying 
-the \emph{domain} of these variables, $C$ is a set of $n$-ary 
-\emph{constraints} over variables $\boldsymbol{v}$.
-A valuation $\theta(\boldsymbol{v})$ is a mapping from the set of variables to 
-values in $D$. 
-If there exist a valuation $\theta^\star$ such that all 
-variables map 
-to exactly one value, and all the constraints in $D\cup C$ are satisfied by the 
-valuation, then $\theta^\star$ is a \emph{solution} to $P$.
-
-A Constraint Optimization Problem (COP) is a CSP with an additional 
-\emph{objective function} $o : \boldsymbol{v} \mapsto \mathbb{R}$ and a 
-\emph{sign} which is either \verb|minimize| or \verb|maximize|.
-
+set of \emph{variables}, $C$ is a set of $n$-ary 
+\emph{constraints} over variables $\boldsymbol{v}$ and $o$ is an 
+\emph{objective function} $o : \boldsymbol{v} \mapsto \mathbb{R}$ to be 
+(w.l.o.g.) minimized. 
+A valuation such that all variables in $\boldsymbol{v}$ map 
+to exactly one value, and all the constraints in $C$ are satisfied by the 
+valuation is a \emph{solution} to $P$. A solution $\theta$ is optimal if$\not 
+\exists \theta', \theta'(\boldsymbol{v}) < \theta(\boldsymbol{v})$.
+
+\ignore{
 A typical example of COP is the Traveling Salesman Problem, where we need to 
@@
 length.
-
-\subsection{Constraint Programming}
-Constraint Programming (CP) allows the user to model a CSP or COP and give it 
-to a 
-solver that will find a solution to the CSP, or will report unsatisfiability if 
-no solution exists. In the case of COPs, the solver will try to optimize 
-the objective function and prove optimality as well.
+}
+
+%\subsection{Constraint Programming}
+Constraint Programming (CP) allows the user to model a COP and give it 
+to a solver that will find solutions to the COP and while optimizing 
+the objective function (and prove optimality).
 
 Briefly, the way a CP solver works is by assigning a value to each variable of 
-$\boldsymbol{v}$ from $D$ in turn. At each iteration it will check whether any 
+$\boldsymbol{v}$ in turn. At each iteration it will check whether any 
 constraint in $C$ is violated, in which case it will backtrack to change it's 
-last decision. The choice of the order of the variables to be assigned, and the 
+last decision. \ignore{The choice of the order of the variables to be assigned, 
+and the 
 choice of the value to be assigned to each variable is called the \emph{search 
-strategy}.
+strategy}}.
 
@@
 \emph{propagating} the last decision made via specialized algorithms called 
-\emph{propagators}. A propagator is a function $p : (v, D_v) \mapsto D_v'$ that 
-takes a subset of the variables of the problem $v \subseteq \boldsymbol{v}$ and 
-the domain of those variables $D_v$ and returns a new domain for these 
-variables 
-such that $D_v' \sqsubseteq D$. That is, a propagator removes values form the 
-domains of variables (when possible). For a propagator to be correct, it must 
-not remove a value of the domain of a variable if such value could participate 
-in a solution given the decisions already made.
+\emph{propagators}. A propagator is a function that removes inconsistent values 
+form the domains of variables. That way, values that cannot appear in a 
+solution givent eh current set of decisions are never tried by the search.
 
 \emph{Global constraints} are higher order constraints that enforce a 
-complicated 
-constraint over a set of variables. Typical examples of this is enforcing that 
-a set of variables take different values, or that they describe a path a in a 
-graph. Although it is possible to express these constraints with a conjunction 
-of simple constraints, it is often the case that specific algorithms for these 
-constraints perform substantially better than a decomposition approach (e.g. 
-\cite{regin1994filtering}). A wide 
-list of these global constraints can be found in \cite{beldiceanu2012global}.
-
+complex 
+constraint over a set of variables. These are typically implemented with 
+propagators that use specific algorithms for these 
+constraints and perform substantially better than a decomposition approach
+\cite{regin1994filtering,beldiceanu2012global}.
+
+\ignore{
 \subsubsection{Example} Consider the toy problem $P$ over variables $a$ and $b$ 
@@
 trying any other of its original possible values. $\square$
+}
 
@@
 \cite{regin1994filtering}, we split the problem into two parts: the 
-\verb|steiner_tree| global constraint will only deal with the part of the 
+$\mathit{steiner}$ global constraint will only deal with the part of the 
 integration graph that corresponds to the alignment graph, and the 
-\verb|alldifferent| global constraint will deal with he matching part of the 
+$\mathit{alldifferent}$ global constraint will deal with he matching part of 
+the 
 problem.
@@
 $match$ indexed by the set of attributes of $s^\star$. The combination of these 
-sets fo variables define the value of $T^\star$: $c_n = \mathit{true}$ means 
+sets of variables define the value of $T^\star$: $c_n = \mathit{true}$ means 
 that $n \in V^\star$, $c_e = \mathit{true}$ means that $e \in E^\star$ and 
@@
 reaches it (from the side of the alignment graph) and otherwise it is 
-disconnected. Eq. \ref{EQ:matchdom} ensures that the domain of each variable in 
+disconnected. \ignore{Eq. \ref{EQ:matchdom} ensures that the domain of each 
+variable in 
 the array $match$ corresponds to a subset of data nodes of the alignment graph 
@@
 \ref{EQ:alld} ensure that each attribute is mapped to exactly one data node of 
-the alignment graph. Equations \ref{EQ:matchdom} and \ref{EQ:alld} ensure that 
+the alignment graph.} Equations \ref{EQ:matchdom} and \ref{EQ:alld} ensure that 
 there is exactly one data node matched to an attribute, which has to be one of 
@@
 
-Note how this CP model is easily adaptable to more classic settings where no 
+Note how this CP model is easy to adapt to more classic settings where no 
 patterns are used (by dropping Eqs. \ref{EQ:patt} and \ref{EQ:pcost}), or where 
@@
 \subsection{Experimental Setup}
-\ddg{TODO}
 
@@
 Assuming $m^\star$ is the predicted semantic model and $m^\dag$ is the correct semantic model, then:
-$$precision = \frac{|rel(m^\star)\cap rel(m^\dag)|}{|rel(m^\star)|}$$
-$$recall = \frac{|rel(m^\star)\cap rel(m^\dag)|}{|rel(m^\dag)|}$$
+$$\mathit{prec} = \frac{|\mathit{rel}(m^\star)\cap 
+\mathit{rel}(m^\dag)|}{|\mathit{rel}(m^\star)|}, 
+\mathit{recall} = \frac{|\mathit{rel}(m^\star)\cap 
+\mathit{rel}(m^\dag)|}{|\mathit{rel}(m^\dag)|}$$
 where $rel(m)$ is the set of triples $(u,e,v)$ with $e$ being an edge from the vertex $u$ to the vertex $v$ in the semantic model $m$.
-Since we want to estimate the accuracy of both the matching and STP parts,
-we also include triples for attributes and data nodes into the corresponding sets.
+\ignore{Since we want to estimate the accuracy of both the matching and STP 
+parts,
+we also include triples for attributes and data nodes into the corresponding 
+sets.}
 Note that unmatched attributes as well as \emph{unknown} and \emph{root} nodes are not part of these sets.
@@
 It is calculated the following way:
-$$MRR = \frac{1}{n}\sum_{i=1}^{n}{\frac{1}{rank_i}},$$
+$MRR = \frac{1}{n}\sum_{i=1}^{n}{\frac{1}{rank_i}},$
 where $rank_i$ is the rank of the correct semantic label for the attribute $a_i$ among the top $k$ predictions.
@@
 \subsection{Experimental Results}
-\ddg{TODO}
 
@@
 		%\legend{karma,serene,serene-pats}
-
 		\end{axis}
@@
 \section{Related Work \label{SEC:pw}}
-\ddg{rewrite, add more}
-\npr{Now the opposite problem}
 

### 2017-08-21 stp/paper_aaai/main.tex
Merged with the version Natalia sent via email, and shortened the paper a lot

@@
 \usetikzlibrary{mindmap,backgrounds}
-\tikzstyle{class}=[ellipse,align=center,fill=green!25]
+\tikzstyle{class}=[draw,green,ellipse,align=center,fill=green!25,text=black]
 \tikzstyle{data}=[draw,rectangle,align=center,black!70]
@@
 \newcommand{\relonto}{\textsc{Rel2Onto}}
+\newcommand{\karma}{\textsc{Karma}}
+\newcommand{\serene}{\textsc{Serene}}
+\newcommand{\serenepats}{\textsc{SerenePats}}
 
@@
 find a minimum cost Steiner Tree in the graph.
-The goal is to assign the costs on the edges in such a way that the resulting Steiner Tree is a valid and coherent semantic model for the new source.
+The goal is to assign the costs on the edges in such a way that the resulting 
+Steiner Tree is a valid and coherent semantic model for the new source. 
+We call our system \serene{}.
 
@@
 
-Section \ref{SEC:pw} presents the previous work done to achieve this task. 
 Section \ref{SEC:problem} formally states the problem. 
@@
 Section \ref{SEC:Res} shows our results. 
+Section \ref{SEC:pw} presents the previous work done to achieve this task.
 
@@
 We denote them as $\mathcal{C}_m$ and $\mathcal{D}_m$ respectively.
- We define $\mathcal{N}_m = \mathcal{C}_m \cup 
-\mathcal{D}_m$. $ \mathcal{C}_m$ corresponds to classes in the ontology 
-$\mathcal{O}$. $\mathcal{D}_m$ corresponds to data 
-properties in the ontology. 
-The edges in the semantic model correspond to object properties in the ontology, as shown if Fig.~\ref{FIG:onto} and \ref{FIG:sem}.
-The semantic model may have several instances of the same ontology class or object property.
+$ \mathcal{C}_m$ corresponds to classes in the ontology 
+whereas $\mathcal{D}_m$ corresponds to data 
+properties. 
+Edges in the semantic model correspond to properties in the ontology, as 
+shown in Fig.~\ref{FIG:onto} and \ref{FIG:sem}.
+The semantic model may have several instances of a same ontology class or 
+object property.
 
@@
 Typically semantic labeling techniques encounter several problems.
-Firstly, there can be naming conflicts~\cite{Pinkel:rodi}, including those cases where users represent the same data in different ways.
-Secondly, semantically different attributes might have syntactically similar content, for example, startDate versus endDate for the Event class.
+Firstly, there can be naming conflicts~\cite{Pinkel:rodi}, including those 
+cases where users represent the same data in different ways.
+Secondly, semantically different attributes might have syntactically similar 
+content, for example, startDate versus endDate for the Event class.
 Thirdly, a considerable number of attributes which do not have any corresponding property in the ontology, either by accident or on purpose.
@@
 the known semantic type with the corresponding feature vector.
-The feature vector includes characteristics of the attribute such as a number of whitespaces and other special characters, statistics of values in the column (e.g, mean/ max/ min string length and numeric statistics) and many more.
+The feature vector includes characteristics of the attribute such as a number 
+of whitespaces and other special characters, statistics of values in the column 
+(e.g, mean/max/min string length and numeric statistics) and more. A full 
+list can be found in appendix \ddg{Apendix!}
 One of the important features characterising information content of an attribute is Shannon's entropy of the attribute's concatenated rows.
@@
 remove some of the matches based on heuristics to then simplify the task of 
-finding the semantic model. \ddg{CHECK}
+finding the semantic model.
 
@@
 
-The algorithm for the construction of the alignment graph $\mathcal{G_O}$ follows the ideas of~\cite{taheriyan2016learning}.
+The algorithm we use for the construction of the alignment graph 
+$\mathcal{G_O}$ was given by~\cite{taheriyan2016learning}.
 Briefly, the algorithm has three parts:
@@
 $(ii)$ %\item 
-Adding the semantic types learned for the target source \ddg{If we keep 
-all matches, isn't this just adding all the semantic types?}
+Adding the semantic types learned for the target source
 %\item 
@@
 
-Note how the alignment graph contains data nodes that correspond to at least 
-some of the semantic types. 
+Note how the alignment graph contains data nodes that correspond to semantic 
+types. 
 For instance, it could contain two nodes $City.name$ and $State.name$ rather than just one node $name$ connected to two 
@@
 which are inferred from the ontology.
-As we will see in the next section, this makes edges present in semantic models more attractive. \ddg{How exactly are 
-they weighted?}
+As we will see in the next section, this makes edges present in semantic models 
+more attractive. 
+Details on the weighting function can be found in \cite{taheriyan2016learning}.
+%\ddg{How exactly are they weighted?}
 
 An example alignment graph is illustrated in Fig.~\ref{FIG:ali}. 
-Bigger examples can be found in \cite{Taheriyan2013}. 
+%Bigger examples can be found in \cite{Taheriyan2013}. 
 Black links correspond to the links which are supported by the known semantic models. 
-Blue and orange links are inferred from the ontology $\mathcal{O}$ (the orange ones correspond to the ones added to connect Classes of the ontology that never appeared in the semantic models) and can be assigned the
-maximum weight $w_max$ \ddg{where does this weight come from?}
+Blue and orange links are inferred from the ontology $\mathcal{O}$ (the orange 
+ones correspond to the ones added to connect Classes of the ontology that never 
+appeared in the semantic models).
+% and can be assigned the 
+%maximum weight $w_max$ \ddg{where does this weight come from?}
 
@@
 
-	\node[class,fill=orange!30!white] (PL) at (3,\ysh/2)  {\small Place};
+	\node[class,orange,fill=orange!30!white,text=black] (PL) at (3,\ysh/2)  
+	{\small 
+	Place};
 
@@
 \caption{Example of alignment graph (`\tikz{ \node[class] () at (0,0)  
-{};}' and `\tikz{ \node[class,fill=orange!30!white] () at (0,0)  
+{};}' `\tikz{ \node[class,orange,fill=orange!30!white,text=black] () at 
+(0,0)  
 {};}' are class nodes, and `\tikz{ \node[data] () at (0,0)  {};}' are data 
@@
 $l_j$ induced by the semantic model, $w_\mathcal{I}(e) = - 
-ln(\psi(a_i,l_i))$. \ddg{CHECK!}
+ln(\psi(a_i,l_i))$. %\ddg{CHECK!}
 
@@
 \cite{Pham:semantic} or HTML tables \cite{Ritze:matching}.
-In current systems, these columns are removed in a reprocess that requires extra time and effort as this is typically done manually in the real world.
+In current systems, these columns are removed in a process that requires 
+extra time and effort as this is typically done manually in the real world.
 
@@
 Then, to maintain connectedness of the 
-Steiner tree, the \emph{unknown} node and one of the selected Class nodes will 
+Steiner tree, the \emph{unknown} node and one of the other selected Class nodes 
+will 
 both be connected to the \emph{root} node. 
@@
 
-\section{Modeling as a Constraint Optimization Problem \label{SEC:CP}}
+\section{Modeling in Constraint Programming \label{SEC:CP}}
 \subsection{Definitions}
@@
 Constraint Programming (CP) allows the user to model a COP and give it 
-to a solver that will find solutions to the COP and while optimizing 
+to a solver that will find solutions while optimizing 
 the objective function (and prove optimality).
@@
 strategy}}.
-
 Since only using a backtracking algorithm would have a prohibitive cost, CP 
 uses a combination of search and \emph{propagation}. The latter is achieved by  
-\emph{propagating} the last decision made via specialized algorithms called 
-\emph{propagators}. A propagator is a function that removes inconsistent values 
+removing inconsistent values 
 form the domains of variables. That way, values that cannot appear in a 
-solution givent eh current set of decisions are never tried by the search.
-
+solution, given the current set of decisions, are never tried by the search. 
 \emph{Global constraints} are higher order constraints that enforce a 
@@
 constraint over a set of variables. These are typically implemented with 
-propagators that use specific algorithms for these 
-constraints and perform substantially better than a decomposition approach
+specialized algorithms for these 
+constraints and perform substantially better than a decomposition approaches
 \cite{regin1994filtering,beldiceanu2012global}.
@@
     %		w_\mathcal{I}(e)
-	\label{EQ:obj}&&\\
-	&\text{such that~~}  \nonumber&& \\
+	\label{EQ:obj}~~~\text{such that~~} && \\
 	& \textit{steiner}(\{c_n| n \in \mathcal{V_O}\},\{c_e| e \in 
@@
 the alignment graph.} Equations \ref{EQ:matchdom} and \ref{EQ:alld} ensure that 
-there is exactly one data node matched to an attribute, which has to be one of 
-the ones for which an edge existed. Eq. \ref{EQ:map} ensures that 
+there is exactly one data node matched to an attribute. Eq. \ref{EQ:map} 
+ensures that 
 if a data node of the alignment graph has been mapped to some attribute, then 
@@
 % baseline for evaluation
-We choose \emph{Karma}~\cite{taheriyan2016learning} as our baseline.
+We choose \karma{}~\cite{taheriyan2016learning} as our baseline.
 This system also phrases the \relonto{} problem as STP and decomposes it further into two parts.
@@
 Additionally, they do not consider unmatched attributes in the sources.
-To ensure that Karma also handles such attributes, we change its semantic labeling model SemanticTyper~\cite{Ramnandan:Assigning} to ours and we add a special \emph{unknown} ontology which gives specification for \emph{root} and \emph{unknown} nodes of the alignment graph.
-The first modification also ensures the fairness of evaluation since both Karma and Serene will have the same matches for attributes.
+To ensure that \karma{} also handles such attributes, we change its semantic 
+labeling model, SemanticTyper~\cite{Ramnandan:Assigning}, to ours and we add a 
+special \emph{unknown} ontology which gives specification for \emph{root} and 
+\emph{unknown} nodes of the alignment graph.
+The first modification also ensures the fairness of evaluation since both 
+\karma{} and \serene{} will have the same matches for attributes.
 
@@
 \npr{check characteristics, AWS machine is bigger}
-In all our experiments we use a timeout threshold of 15s for the chuffed solver.
+In all our experiments we use a timeout threshold of 15s for \chuffed{}.
 
@@
 
-To evaluate our new system \emph{serene}, we show that its semantic labeling model produces more accurate matches for attributes and the CP formulation leads to better semantic models in terms of precision and recall.
-
-We have developed a new approach for semantic labeling which can efficiently handle the \emph{unknown} class.
-We demonstrate its efficiency by comparing against the state-of-the-art approach DSL~\cite{Pham:semantic}.
+To evaluate our new system \serene{}, we show that its semantic labeling model 
+produces more accurate matches for attributes and that the CP formulation leads 
+to better semantic models in terms of precision and recall.
+
+\ignore{We have developed a new approach for semantic labeling which can 
+efficiently handle the \emph{unknown} class.}
+\ignore{We demonstrate its efficiency by comparing against the state-of-the-art 
+approach DSL~\cite{Pham:semantic}. } %Repeat from above
 Tab.~\ref{tab:semlab} provides evidence that our new semantic labeling model is better suited for the task when there are unmatched attributes in domains.
@@
 
-\begin{table}[t]\small
+\begin{table}[!ht]\small
   \centering
@@
   		\hline
-  		\multirow{2}{*}{Model} & \multicolumn{2}{c|}{MRR scores} & \multicolumn{2}{c}{Train time ($s$)}\\
+  		\multirow{2}{*}{Model} & \multicolumn{2}{c|}{MRR scores} & 
+  		\multicolumn{2}{c}{Train time ($s$)}\\
   		 & museum & soccer & museum & soccer\\
@@
 \end{table}
+
+\begin{figure}[!htb]
+\begin{minipage}[b]{.5\linewidth}
+\centering
+\hspace*{-15pt}
+\begin{tikzpicture}[baseline,scale=0.47]
+\begin{axis}[
+		    xlabel={\emph{known semantic models}},
+		    ylabel={},
+		    xmin=1, xmax=28,
+		    ymin=0.2, ymax=0.9,
+		    xtick={1,5,10,15,20,25,28},
+		    ytick={0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
+		    legend pos=south east,
+		    ymajorgrids=true,
+		    grid style=dashed,
+		    style = {font=\huge}
+		]
+
+		\addplot[
+		    color=blue,
+		    mark=square,
+		    ]
+		    coordinates {
+		    (1,0.517753313989873)(2,0.488688737671076)(3,0.51551313872799)(4,0.495118819099343)(5,0.527778910368045)(6,0.532176796157059)(7,0.566662366701066)(8,0.637110556563823)(9,0.685799234290614)(10,0.538089511412941)(11,0.621051710776405)(12,0.599367875333495)(13,0.670421793119162)(14,0.583598347357422)(15,0.623587223886899)(16,0.645277499838855)(17,0.653525664651826)(18,0.665572696108086)(19,0.670283086011174)(20,0.663804745401859)(21,0.633242908391853)(22,0.66099516031458)(23,0.644625119528521)(24,0.72069799334011)(25,0.737468671679198)(26,0.715572819263667)(27,0.727291592547725)(28,0.752558983666062)
+};
+		\addplot[
+		    color=red,
+		    mark=*,
+		    ]
+		    coordinates {
+		    (1,0.551714513556619)(2,0.682453503286837)(3,0.567702774084261)(4,0.646748619299324)(5,0.65492113250734)(6,0.701065228379203)(7,0.684439263401395)(8,0.700511175298951)(9,0.681034059961129)(10,0.685637253116215)(11,0.699316636125265)(12,0.697036509934383)(13,0.693463987436823)(14,0.704225209488367)(15,0.732978923190269)(16,0.724305489322319)(17,0.699459026247245)(18,0.716210056654951)(19,0.698987880687053)(20,0.733337516584389)(21,0.751908839952318)(22,0.75007040599401)(23,0.750592804644915)(24,0.814515445676703)(25,0.810987671748541)(26,0.817791638186375)(27,0.826003784931597)(28,0.809805364617137)
+};
+		\addplot[
+		    color=green,
+		    mark=x,
+		    ]
+		    coordinates {
+		    (1,0.598323207198336)(2,0.656420469232034)(3,0.551668227640311)(4,0.620327113896406)(5,0.623771074555817)(6,0.652894375155994)(7,0.625071981901494)(8,0.623287932111462)(9,0.601893257814311)(10,0.601192717220153)(11,0.602088073148115)(12,0.581718160067067)(13,0.570577347465439)(14,0.572274187082211)(15,0.581600752329829)(16,0.565774690293304)(17,0.5550594629542)(18,0.565097183518236)(19,0.524149694006153)(20,0.511449953555217)(21,0.576679655627024)(22,0.571388650336019)(23,0.546588180559473)(24,0.608169608169608)(25,0.608169608169608)(26,0.633066933066933)(27,0.634654234654234)(28,0.628305028305028)
+};
+
+		\end{axis}
+\end{tikzpicture}
+\subcaption{Precission (museum)}\label{fig:museumprec}
+\end{minipage}%
+\begin{minipage}[b]{.5\linewidth}
+\centering
+\begin{tikzpicture}[baseline,scale=0.47]
+		\begin{axis}[
+		    xlabel={\emph{known semantic models}},
+		    %ylabel={recall},
+		    xmin=1, xmax=28,
+		    ymin=0.2, ymax=0.9,
+		    xtick={1,5,10,15,20,25,28},
+		    ytick={0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
+		    ymajorgrids=true,
+		    grid style=dashed,
+		    		    style = {font=\huge},
+		    legend style={at={(0.5,1.1)},anchor=south, legend columns=-1}
+		]
+
+		\addplot[
+		    color=blue,
+		    mark=square,
+		    ]
+		    coordinates {
+		    (1,0.300191975130116)(2,0.387168789342702)(3,0.418780803201093)(4,0.414852632606256)(5,0.449767567691694)(6,0.454560596014134)(7,0.472473240503931)(8,0.552403403170667)(9,0.618322253509807)(10,0.45708434156857)(11,0.540246526073466)(12,0.523083348403042)(13,0.603209776078489)(14,0.509054454749254)(15,0.54874878365927)(16,0.577977828772285)(17,0.583053944903167)(18,0.591126557438254)(19,0.592414794781259)(20,0.591100946357877)(21,0.575601120513223)(22,0.587190134384184)(23,0.575949431206362)(24,0.655469912102772)(25,0.649409306042166)(26,0.64025693035835)(27,0.652378142479562)(28,0.666045239412379)
+};
+		\addplot[
+		    color=red,
+		    mark=*,
+		    ]
+		    coordinates {
+		    (1,0.517923133776792)(2,0.667141218952813)(3,0.56262382276875)(4,0.646790367442541)(5,0.651735815098987)(6,0.706388551614468)(7,0.698383379116542)(8,0.714984169630376)(9,0.700346244485205)(10,0.704664218197892)(11,0.717929077647748)(12,0.711690361988742)(13,0.707592621296799)(14,0.725417933239758)(15,0.760334088253952)(16,0.741766948274724)(17,0.726258869970838)(18,0.748428390280994)(19,0.723282293295816)(20,0.746991608671798)(21,0.769430045325921)(22,0.751719414109543)(23,0.756837646239269)(24,0.816669125330383)(25,0.816669125330383)(26,0.821841539123487)(27,0.824453869322024)(28,0.810608519269777)
+};
+		\addplot[
+		    color=green,
+		    mark=x,
+		    ]
+		    coordinates {
+		    (1,0.592810513524547)(2,0.704036744254136)(3,0.580300590445518)(4,0.665729761381935)(5,0.671789291034815)(6,0.721540066765983)(7,0.718258458411911)(8,0.728686409419572)(9,0.71549775963672)(10,0.719667189083217)(11,0.729479363111076)(12,0.713288181617252)(13,0.723866470903981)(14,0.739158277862456)(15,0.764121967041831)(16,0.755829992510182)(17,0.746486501253236)(18,0.758703555728573)(19,0.723655728717502)(20,0.729409784115667)(21,0.774654705722995)(22,0.768167419063295)(23,0.754561938768098)(24,0.828459715477971)(25,0.828459715477971)(26,0.838717192206036)(27,0.841329522404573)(28,0.833544778412933)
+};
+		 %\legend{karma,serene,serene-pats}
+
+		\end{axis}
+	\end{tikzpicture}
+\subcaption{Recall (museum)}\label{fig:museumrec}
+\end{minipage}%
+
+\begin{minipage}[b]{.5\linewidth}
+\centering
+\hspace*{-15pt}
+\begin{tikzpicture}[baseline,scale=0.47]
+\begin{axis}[
+		    xlabel={\emph{known semantic models}},
+		    ylabel={},
+		    xmin=1, xmax=11,
+		    ymin=0.5, ymax=0.9,
+		    xtick={1,2,4,6,8,10,11},
+		    ytick={0.5,0.6,0.7,0.8,0.9,1},
+		    legend pos=south east,
+		    ymajorgrids=true,
+		    grid style=dashed,
+		    		    		    style = {font=\huge},
+		]
+
+		\addplot[
+		    color=blue,
+		    mark=square,
+		    ]
+		    coordinates {
+		    (1,0.635191626901633)(2,0.549997502815009)(3,0.675720834727361)(4,0.719693253328935)(5,0.759169846724195)(6,0.760054331456753)(7,0.800812140122402)(8,0.812192030050689)(9,0.799552066440611)(10,0.821470975418344)(11,0.785878855002637)
+		    };
+		\addplot[
+		    color=red,
+		    mark=*,
+		    ]
+		    coordinates {
+		    (1,0.676934852587026)(2,0.61473599870339)(3,0.723937079602602)(4,0.786238815638129)(5,0.777035817669233)(6,0.781984613615049)(7,0.81368099248534)(8,0.817013725291758)(9,0.816270530687007)(10,0.846744827831784)(11,0.852649148301322)
+		    };
+		\addplot[
+		    color=green,
+		    mark=x,
+		    ]
+		    coordinates {
+		    (1,0.66759959719914)(2,0.629014687197419)(3,0.692208378950833)(4,0.744652988406557)(5,0.773486992410165)(6,0.756607637648352)(7,0.803820434917082)(8,0.793054493090329)(9,0.792256229657042)(10,0.822093203062231)(11,0.828181360184871)
+		    };
+		%\legend{karma,serene,serene-pats}
+
+		\end{axis}
+\end{tikzpicture}
+\subcaption{Precission (soccer)}\label{fig:soccerprec}
+\end{minipage}%
+\begin{minipage}[b]{0.5\linewidth}
+\centering
+\begin{tikzpicture}[baseline,scale=0.47]
+		\begin{axis}[
+		    xlabel={\emph{known semantic models}},
+		    %ylabel={recall},
+		    xmin=1, xmax=11,
+		    ymin=0.3, ymax=0.9,
+		    xtick={1,2,4,6,8,10,11},
+		    ytick={0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
+		    ymajorgrids=true,
+		    grid style=dashed, legend pos=south east,
+		    		    		    style = {font=\huge}
+		]
+
+		\addplot[
+		    color=blue,
+		    mark=square,
+		    ]
+		    coordinates {
+		    (1,0.444761527680188)(2,0.372447158105053)(3,0.545528381345078)(4,0.596008831526073)(5,0.6499887923799)(6,0.643884492868159)(7,0.685035675993026)(8,0.702870161195933)(9,0.654001538724769)(10,0.685153350715964)(11,0.662999993217779)
+		    };
+		\addplot[
+		    color=red,
+		    mark=*,
+		    ]
+		    coordinates {
+		    (1,0.690636806043505)(2,0.613080486764697)(3,0.72563707600459)(4,0.780625908674911)(5,0.776616927805676)(6,0.779496772132888)(7,0.813459305700685)(8,0.813245834960899)(9,0.810586300672508)(10,0.84298404022542)(11,0.849899398175261)
+		    };
+		\addplot[
+		    color=green,
+		    mark=x,
+		    ]
+		    coordinates {
+		    (1,0.689786194666577)(2,0.655399210040359)(3,0.719915653815835)(4,0.776231754935929)(5,0.802770096610387)(6,0.787355423564135)(7,0.838616573256072)(8,0.82175912881902)(9,0.821414409345444)(10,0.851497334083541)(11,0.85656084018153)
+		    };
+\legend{\karma{},\serene{},\serenepats{}}
+
+		\end{axis}
+	\end{tikzpicture}
+\subcaption{Recall (soccer)}\label{fig:soccerrec}
+\end{minipage}%
+\caption{Performance over the museum and soccer datasets\label{fig:perf}}
+\end{figure}
+
+% karma vs serene vs serene-pats
+We evaluate our new system \serene{} and its modification \serenepats{}, which 
+uses graph patterns, against the state-of-the-art system \karma{}.
+All three systems have access to the same set of matches produced by our semantic labeling model.
+Fig.~\ref{fig:perf} show their performance on the museum and soccer domains.
+We report average precision, recall and run times for the systems with regard to variable number of semantic models in the training set.
+For \serene{} and \serenepats{} we report the first solutions found by
+\chuffed{}.
+We use default parameters for \karma{} which were shown to yield the best 
+results~\cite{taheriyan2016learning}.
+As we can see, \serene{} produces on average the best semantic models in terms 
+of precision while \serenepats{} generates slightly better models in terms of 
+recall.
+If we consider results separately per each instance and not on average, there 
+are few instances where \karma{} generates more precise models, however, our 
+new approaches produce much better models in terms of recall in all considered 
+instances. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% sequentially found solutions and different weights for patterns
+\begin{figure*}[h]\small
+\pgfplotsset{
+    small,
+    %legend style={legend pos=north east}
+    legend style={
+        at={(0.01,0.01)},
+        anchor=south west,
+    },
+   }%
+\begin{minipage}[b]{.34\linewidth}
+\centering
+\begin{tikzpicture}[baseline]
+\begin{axis}[
+		    xlabel={\emph{solution}},
+		    ylabel={Performance},
+		    xmin=0, xmax=20,
+		    ymin=0.7, ymax=1,
+		    xtick={0,5,10,15,20},
+		    ytick={0.7,0.8,0.9,1},
+		    legend pos=south east,
+		    ymajorgrids=true,
+		    grid style=dashed,
+		    legend style={at={(1.5,1.1)},anchor=south, legend columns=-1}
+		]
+
+		\addplot[
+		    color=blue,
+		    mark=square,
+		    ]
+		    coordinates {
+		    (0,0.813133718212162)(1,0.870689655172414)(2,0.869565217391304)(3,0.854700854700855)(4,0.847457627118644)(5,0.862068965517241)(6,0.862068965517241)(7,0.860869565217391)
+		    };
+		\addplot[
+		    color=red,
+		    mark=*,
+		    ]
+		    coordinates {
+		    (0,0.708791208791209)(1,0.720429778415431)(2,0.727852084972463)(3,0.734756097560976)(4,0.737969058591178)(5,0.723003960808839)(6,0.727905921593153)(7,0.740887177292826)(8,0.733003960808839)(9,0.746193299741805)(10,0.73554304773817)(11,0.74569890495285)(12,0.756325773784054)(13,0.745676961413577)(14,0.753615746683783)(15,0.7306060898002)(16,0.723882805154582)(17,0.720774744968293)(18,0.733079110976868)(19,0.731544715447155)(20,0.734034752112227)
+
+		    };
+		\addplot[
+		    color=green,
+		    mark=x,
+		    ]
+		    coordinates {
+		    (0,0.71031746031746)(1,0.722023912003826)(2,0.734193548387097)(3,0.740054370716392)(4,0.751788722391459)(5,0.752652119278914)(6,0.765286464150101)(7,0.766275317871063)(8,0.763956676916058)(9,0.779373522458629)(10,0.780497706328908)(11,0.786846912678115)(12,0.793409626193882)(13,0.801554001554001)(14,0.800878033205619)(15,0.861352657004831)(16,0.863636363636364)(17,0.863636363636364)(18,0.883720930232558)(19,0.8125)(20,0.795918367346939)
+		    };
+		\addplot[
+		    color=brown,
+		    mark=+,
+		    ]
+		    coordinates {
+		    (0,0.71031746031746)(1,0.722023912003826)(2,0.734193548387097)(3,0.740054370716392)(4,0.751788722391459)(5,0.752652119278914)(6,0.758342019705656)(7,0.772281323877069)(8,0.774638933587619)(9,0.786846912678115)(10,0.786846912678115)(11,0.795363644516187)(12,0.804524886877828)(13,0.797201562617384)(14,0.812955643390426)(15,0.775568181818182)(16,0.863636363636364)(17,0.883720930232558)(18,0.883720930232558)(19,0.883720930232558)(20,0.904761904761905)
+};
+		 \addplot[
+		    color=violet,
+		    mark=star,
+		    ]
+		    coordinates {
+		    (0,0.716727716727717)(1,0.728559859716244)(2,0.740860215053763)(3,0.746857091804827)(4,0.757315933275812)(5,0.758342019705656)(6,0.765286464150101)(7,0.779373522458629)(8,0.787744083140503)(9,0.786846912678115)(10,0.789244481875285)(11,0.804524886877828)(12,0.811442006269593)(13,0.803401771336554)(14,0.785524847694936)(15,0.849173553719008)(16,0.852651515151516)(17,0.866230213015439)(18,0.876750700280112)(19,0.85593220338983)(20,0.863247863247863)
+};
+		\legend{serene,pats-1,pats-5,pats-10,pats-20}
+
+		\end{axis}
+\end{tikzpicture}
+\subcaption{precision}\label{fig:solprec}
+\end{minipage}%
+%
+\begin{minipage}[b]{.33\linewidth}
+\centering
+\begin{tikzpicture}[baseline]
+		\begin{axis}[
+		    xlabel={\emph{solution}},
+		    %ylabel={recall},
+		    xmin=0, xmax=20,
+		    ymin=0.7, ymax=1,
+		    xtick={0,5,10,15,20},
+		    ytick={0.7,0.8,0.9,1},
+		    ymajorgrids=true,
+		    grid style=dashed,
+		    %legend style={at={(0.5,1.1)},anchor=south, legend columns=-1}
+		]
+
+		\addplot[
+		    color=blue,
+		    mark=square,
+		    ]
+		    coordinates {
+		    (0,0.790229885057471)(1,0.870689655172414)(2,0.862068965517241)(3,0.862068965517241)(4,0.862068965517241)(5,0.862068965517241)(6,0.862068965517241)(7,0.853448275862069)
+		    };
+		\addplot[
+		    color=red,
+		    mark=*,
+		    ]
+		    coordinates {
+		    (0,0.828456983629397)(1,0.828456983629397)(2,0.828456983629397)(3,0.828456983629397)(4,0.828456983629397)(5,0.82088122605364)(6,0.82088122605364)(7,0.823754789272031)(8,0.82088122605364)(9,0.823754789272031)(10,0.841431556948798)(11,0.841431556948798)(12,0.841431556948798)(13,0.835684430512017)(14,0.838557993730407)(15,0.825583420411007)(16,0.810431905259492)(17,0.82088122605364)(18,0.82088122605364)(19,0.83098223615465)(20,0.833855799373041)
+};
+		\addplot[
+		    color=green,
+		    mark=x,
+		    ]
+		    coordinates {
+		    (0,0.83098223615465)(1,0.83098223615465)(2,0.83098223615465)(3,0.823406478578892)(4,0.828108672936259)(5,0.820532915360502)(6,0.828108672936259)(7,0.820532915360502)(8,0.820532915360502)(9,0.828108672936259)(10,0.820532915360502)(11,0.820532915360502)(12,0.818007662835249)(13,0.810431905259492)(14,0.800330895158482)(15,0.867163009404389)(16,0.863636363636364)(17,0.863636363636364)(18,0.863636363636364)(19,0.886363636363636)(20,0.886363636363636)
+};
+		 \addplot[
+		    color=brown,
+		    mark=+,
+		    ]
+		    coordinates {
+		    (0,0.83098223615465)(1,0.83098223615465)(2,0.83098223615465)(3,0.823406478578892)(4,0.828108672936259)(5,0.820532915360502)(6,0.820532915360502)(7,0.820532915360502)(8,0.820532915360502)(9,0.820532915360502)(10,0.820532915360502)(11,0.820532915360502)(12,0.820532915360502)(13,0.810431905259492)(14,0.810431905259492)(15,0.765151515151516)(16,0.863636363636364)(17,0.863636363636364)(18,0.863636363636364)(19,0.863636363636364)(20,0.863636363636364)
+};
+		 \addplot[
+		    color=violet,
+		    mark=star,
+		    ]
+		    coordinates {
+		    (0,0.838557993730407)(1,0.838557993730407)(2,0.838557993730407)(3,0.83098223615465)(4,0.828108672936259)(5,0.820532915360502)(6,0.828108672936259)(7,0.828108672936259)(8,0.828108672936259)(9,0.820532915360502)(10,0.820532915360502)(11,0.820532915360502)(12,0.818007662835249)(13,0.800330895158482)(14,0.790229885057471)(15,0.867163009404389)(16,0.867163009404389)(17,0.867163009404389)(18,0.867163009404389)(19,0.870689655172414)(20,0.870689655172414)
+};	
+	%\legend{serene,pats-1,pats-5,pats-10,pats-20}
+		\end{axis}
+	\end{tikzpicture}
+\subcaption{recall}\label{fig:solrec}
+\end{minipage}%
+%
+\begin{minipage}[b]{.33\linewidth}
+\centering
+\begin{tikzpicture}[baseline]
+\begin{axis}[
+		    xlabel={\emph{solution}},
+		    %ylabel={time(s)},
+		    xmin=0, xmax=20,
+		    ymin=0.0, ymax=21,
+		    xtick={0,5,10,15,20},
+		    ytick={0.0,3.0,6.0,9.0,12,15.0,18,21.0},
+		    ymajorgrids=true,
+		    grid style=dashed,
+		    %legend pos=outer north east,
+		    %legend style={at={(0.5,-0.1)},anchor=north, legend columns=-1}
+		]
+
+		\addplot[
+		    color=blue,
+		    mark=square,
+		    ]
+		    coordinates {
+		    (0,2.47666666666667)(1,7.15)(2,7.41)(3,8.83)(4,9.15)(5,9.32)(6,9.84)(7,10.04)
+};
+		\addplot[
+		    color=red,
+		    mark=*,
+		    ]
+		    coordinates {
+		    (0,3.75)(1,3.8)(2,3.84)(3,3.88666666666667)(4,3.93333333333333)(5,3.98)(6,4.03333333333333)(7,4.08)(8,4.13333333333333)(9,4.23)(10,4.29333333333333)(11,4.34)(12,4.38666666666667)(13,4.74)(14,4.83)(15,5.74333333333333)(16,5.96333333333333)(17,6.48666666666667)(18,6.53)(19,6.58333333333333)(20,6.63)
+};
+		\addplot[
+		    color=green,
+		    mark=x,
+		    ]
+		    coordinates {
+		    (0,3.74)(1,3.79)(2,3.83666666666667)(3,3.88666666666667)(4,3.93666666666667)(5,3.98666666666667)(6,4.03666666666667)(7,4.09333333333333)(8,4.17333333333333)(9,4.23)(10,4.31666666666667)(11,4.38)(12,4.54333333333333)(13,5)(14,6.17666666666667)(15,6.755)(16,1.61)(17,2.21)(18,2.35)(19,2.61)(20,3.11)
+};
+		\addplot[
+		    color=brown,
+		    mark=+,
+		    ]
+		    coordinates {
+		    (0,3.75)(1,3.8)(2,3.84666666666667)(3,3.89666666666667)(4,3.95)(5,3.99666666666667)(6,4.05)(7,4.10333333333333)(8,4.16666666666667)(9,4.23333333333333)(10,4.43)(11,4.53333333333333)(12,4.78)(13,5.15333333333333)(14,5.36333333333333)(15,3.365)(16,1.91)(17,1.95)(18,8.42)(19,8.62)(20,8.85)
+};
+		 \addplot[
+		    color=violet,
+		    mark=star,
+		    ]
+		    coordinates {
+		    (0,3.73666666666667)(1,3.78666666666667)(2,3.83666666666667)(3,3.88333333333333)(4,3.93666666666667)(5,3.98666666666667)(6,4.04333333333333)(7,4.09666666666667)(8,4.16)(9,4.22)(10,4.38333333333333)(11,4.49)(12,4.72333333333333)(13,4.99333333333333)(14,9.33333333333333)(15,10.715)(16,10.86)(17,10.915)(18,12.65)(19,20.35)(20,20.56)
+};	
+	%\legend{serene,pats-1,pats-5,pats-10,pats-20}
+		\end{axis}
+\end{tikzpicture}
+\subcaption{time (s)}\label{fig:soltime}
+\end{minipage}%
+\caption{Average precision, recall and time on the museum domain for leave-one-out strategy and different weighting scheme for patterns in serene.}\label{fig:perfsol}
+\end{figure*}
+
+%% sequential solution
+In Fig.~\ref{fig:perfsol} we show how the performance of \serene{} changes 
+across sequentially found solutions.
+\chuffed{} successively finds better solutions in terms of Eq. \ref{EQ:obj}, 
+however, as we can see from the results,
+that does not translate directly into more precise semantic models.
+Additionally, we investigate how the performance is influenced if we introduce a weighting scheme on the patterns,
+i.e., costs of patterns are scaled by a factor.
+In Fig.~\ref{fig:perf} we use a scaling factor 1 
+for pattern costs.
+Fig.~\ref{fig:perfsol} demonstrates that by using scaling factors 5, 10 or 20 
+for patterns costs from the museum domain we can generate semantic models which 
+are almost 90\% in precision and recall.
+This is a 20\% improvement in precision compared to the first solution found by 
+\serenepats{} and a 10\% improvement both in precision and recall for the 
+first solution from \serene{}.
+
+Yet such improvement comes at a cost in run time.
+On average, we have observed that \serene{} yields very good results already 
+with the first solution found.
+\serenepats{}, on the other hand, produces considerably better solutions with 
+scaled pattern costs and sequential solutions.
+However, the sequential solutions are not always better, and hitting the 
+optimal solution may take hours.
+
+We have also observed that \serenepats{} manages to find the ground truth on 
+many instances among its sequential solutions, but again it takes much more 
+time.
+
+% change in performance if we look at sequentially found solutions
+% only leave-one-out for museum domain with 15s timeout for chuffed
+\npr{not sure whether Fig.~\ref{fig:loo} is needed}
+\begin{figure}\small
+\begin{tikzpicture}\small
+\pgfplotsset{
+    scale only axis,
+    small,
+    xmin=0, xmax=9
+}
+
+\begin{axis}[
+  axis y line*=left,
+  ymin=0.5, ymax=1,
+  xlabel=solution number,
+  ylabel=performance,
+  legend pos=south east,
+]
+\addplot[smooth,mark=x,red]
+  coordinates{
+    (0,0.776507549540743)(1,0.71093042754513)(2,0.822783653218436)(3,0.845760233918129)(4,0.879310344827586)(5,0.88695652173913)(6,0.885964912280702)(7,0.870689655172414)(8,0.878260869565217)(9,0.87719298245614)
+
+}; \label{plot_one}
+\addlegendentry{precision}
+\addplot[smooth,mark=*,green]
+  coordinates{
+    (0,0.773180507486795)(1,0.677202255831871)(2,0.805899400726987)(3,0.838122605363985)(4,0.879310344827586)(5,0.879310344827586)(6,0.870689655172414)(7,0.870689655172414)(8,0.870689655172414)(9,0.862068965517241)
+}; \label{plot_two}
+\addlegendentry{recall}
+\end{axis}
+
+\begin{axis}[
+  axis y line*=right,
+  axis x line=none,
+  ymin=0, ymax=15,
+  legend pos=south east,
+  ylabel=time (s)
+]
+\addlegendimage{/pgfplots/refstyle=plot_one}\addlegendentry{precision}
+\addlegendimage{/pgfplots/refstyle=plot_two}\addlegendentry{recall}
+\addplot[smooth,mark=square,blue]
+  coordinates{
+    (0,0.894338290115883)(1,2.39426428574782)(2,6.89703391393025)(3,10.3563708686829)(4,9.87668780326843)(5,9.92719115257263)(6,10.4045292949677)(7,14.3818371582031)(8,14.4026180458069)(9,14.8023208427429)
+}; \addlegendentry{time}
+\end{axis}
+\end{tikzpicture}
+\caption{Performance of \emph{serene} for leave-one-out strategy on the museum domain.}\label{fig:loo}
+\end{figure}
+
+\npr{Maybe some words on how optimal solution found by chuffed relates to the ground truth?}
+
+\section{Related Work \label{SEC:pw}}
+
+Relational data sources are still one of the most popular ways to store enterprise or Web data, however, the issue with relational schema is the lack of a well-defined semantic description.
+A common ontology provides a way to represent the meaning of a relational schema and can facilitate the integration of heterogeneous data sources within a domain.
+Indicating semantic correspondences manually might be appropriate if only few data sources need to be integrated, however, it becomes tedious with the growing number of heterogeneous schemata.
+Hence, automatic or semi-automatic approaches for relational-to-ontology schema mapping are being actively developed.
+
+The majority of approaches to solve the \relonto{} mapping problem are based on 
+heuristic rules and alignment of constraints specified within relational 
+schemata and ontologies.
+A very comprehensive overview and comparison of existing mapping generation tools based on this approach is given in~\cite{Pinkel:rodi} and~\cite{Spanos:semweb}.
+As examples, there are BootOX~\cite{Jimenez:Bootox}, MIRROR~\cite{Luciano:Mirror} and  ontop~\cite{Fagin:Clio}.
+Crudely speaking, these tools first apply a default direct mapping specified by the W3C.
+Further, the default ontology is enriched by using explicit and implicit schema constraints.
+Finally, ontology alignment techniques are applied to match the default ontology to the target ontology.
+The main advantage of these systems is the ability to run in a fully automatic setting.
+Our approach is complementary to the approaches from this group and at its current stage is semi-automatic.
+However, constraint programming offers a convenient framework to incorporate integrity constraints specified either within relational or ontological schema as additional constraints to govern the search for the solution.
+This opens an interesting direction for further research to develop an automatic system.
+
+A major issue with fully automatic systems is though that constraints may be 
+inconsistent or absent completely, e.g., data from Web services or tables on 
+the Web.
+To overcome this issue, we can apply ML techniques.
+\cite{Limaye:Annotating} design a system to annotate web tables with entities for cell values, semantic labels for attributes and relationships for binary combinations of attributes.
+As in our approach, they decompose the process of mapping into two main stages: semantic labeling and finding relationships between matched semantic labels.
+\cite{Limaye:Annotating} enrich their data sources by using YAGO.
+\cite{Mulwad:Semantic} extend this approach by leveraging information from Wikitology Knowledge Base (KB).
+\cite{Venetis:Recovering} develop a scalable approach to recover the semantics of Web tables by incorporating data from the isA database KB.
+\cite{Ritze:matching}, on the other hand, use DBPedia as their KB.
+%extract additional data from knowledge bases to assign a semantic label to an attribute.
+Hence, these approaches are limited to domains well represented in those knowledge bases.
+Also, they are not able to find the relation between attributes in the table if there is no direct connection between the attributes.
+Our approach, on the other hand, allows a model to be trained on any data and can infer complex semantic paths which might exist between attributes.
+However, it might be further bootstrapped by leveraging external knowledge bases.
+This is especially beneficial at the start when the system does not have sufficient training data.
+
+As mentioned above, the approaches for mapping Web tables also perform semantic labeling.
+They design various similarity metrics for attribute names and values.
+However, they disregard the attributes which are not matched to the ontology (the so-called \emph{unknown} set of attributes) which are especially abundant on the Web~\cite{Ritze:matching}\cite{Pham:semantic}.
+It is clear that we cannot directly speak about similarity for unmatched attributes, since they are rather dissimilar from known semantic types.
+That is why we have developed a new approach for semantic labeling which can efficiently handle the \emph{unknown} class.
+We demonstrate its efficiency by comparing against the state-of-the-art approach DSL~\cite{Pham:semantic}.
+
+We build upon the work of~\cite{taheriyan2016learning} and use their ideas for the construction of the alignment graph.
+The only difference is that we introduce the \emph{unknown} and \emph{root} class nodes and as many \emph{unknown} data nodes as there are attributes in the modeled data source.
+These nodes serve to capture the unmatched attributes from the source.
+Though we have modified Karma to treat these additional nodes as well, our approach outperforms Karma since we have additional constraints for these nodes and use an exact algorithm to solve the STP.
+\cite{taheriyan2016learning} treat the matching and STP parts of \relonto{} independently and use heuristic algorithms for both.
+We, on the other hand, use exact algorithms for both parts and address them within a unified CP model.
+
+In their follow up work, \cite{Taheriyan:Leveraging} suggest to use graph 
+patterns to boost the performance of their system.
+To perform semantic modeling in such scenario, \cite{Taheriyan:Leveraging} had to revise their algorithm by introducing additional heuristics.
+However, in our case we only had to add pattern variables and to modify the 
+objective function in the \minizinc{} model.
+No changes to the solver were required.
+This makes our system very convenient and opens directions for validating various additional constraints.
+Though our approach beats the state-of-the-art in the conducted experiments, it 
+is worth noting that the scalability of our approach is under question.
+The main argument why exact solution for STP is feasible in our setting is that 
+we map data sources to a domain-specific ontology which is expected to be 
+limited in its size.
+
+\section{Conclusion}
+In this paper we have introduced a new approach \serene{} to solve the 
+problem of relational-to-ontology schema mapping \relonto{}.
+We have also built its extension \serenepats{} which additionally uses 
+frequent graph patterns.
+Our experiments on two domains demonstrate that 
+\serene{} generates on average more consistent semantic models in terms of 
+precision and recall compared to the state-of-the-art approach \karma{}.
+\serenepats{} produces, on average, better semantic models in terms of 
+recall, however, its overall performance is rather mixed if we consider the 
+first produced model.
+However, the solutions discovered by \serenepats{} afterwards tend to be 
+much better both in precision and recall.
+The disadvantage is though that it comes at a cost of run time.
+In the end, which approach to use for \relonto{} problem comes down to 
+trade-offs between precision, recall and time.
+
+%%%%%%%%future directions%%%%%%%%%%%%%
+% cold start problem and LOD
+One of the key limitations of our approach is the availability of training data 
+in the domain, which is often referred to as cold start problem.
+We consider leveraging the data from the Linked Open Cloud (LOD) which, on one 
+hand, leads to improved performance in the light of insufficient data and, on 
+the other hand, helps in publishing consistent Linked 
+Data~\cite{Taheriyan:Leveraging}. 
+As we have shown, the frequent graph pattern mining procedure 
+DIMSpan~\cite{petermann2017dimspan} which we use in our work is a highly 
+scalable approach compared to the technique based on SPARQL queries 
+from~\cite{Taheriyan:Leveraging}.
+
+%incorporate schema and ontology constraints
+Incorporating schema and ontology constraints may also help with the cold start 
+problem.
+Furthermore, it can provide means to improve disambiguation of properties.
+For example, it is hard for our system to differentiate between startDate and 
+endDate of the class Event.
+Having a constraint that startDate is before endDate might improve the mapping 
+in such situations.
+
+%complex matches
+Another interesting direction for further research is to recognize complex 
+matches.
+Our semantic labeling model in \serene{} as well as many others in the 
+literature~\cite{Pham:semantic,Ritze:matching} can learn only one-to-one 
+matches between attributes and properties in the ontology.
+\cite{Pinkel:rodi} show that such systems as BootOX can also handle efficiently 
+only one-to-one matches while their performance degrades considerably for $1:n$ 
+and $n:1$ matches.
+\karma{} \cite{taheriyan2016learning} offers its users to manually specify 
+transformations through Python scripts.
+\cite{Dhamankar:imap} offer a way to learn such transformations from the 
+historic data.
+This is one of the features which we want to incorporate into \emph{serene}.
+
+\bibliographystyle{aaai}
+\bibliography{main}
+
+\newpage
 
@@
 		    coordinates {
-		    (1,0.477688172043011)(2,0.543722761679028)(3,0.584279525763794)(4,0.560916442048518)(5,0.508442559100454)(6,0.451911027568922)(7,0.560410216718266)(8,0.627540834845735)(9,0.658907184769254)(10,0.494298245614035)(11,0.594547996272134)(12,0.572438909774436)(13,0.643132689678742)(14,0.544147521036133)(15,0.561388900346478)(16,0.620470013199142)(17,0.631330163644405)(18,0.644192377495463)(19,0.642924629016761)(20,0.656325397672681)(21,0.610482642157672)(22,0.628992740471869)(23,0.570074611816898)(24,0.679169187336157)(25,0.673558897243108)(26,0.667890182643746)(27,0.68742147145051)(28,0.709820528332325)
+		    (1,0.517753313989873)(2,0.488688737671076)(3,0.51551313872799)(4,0.495118819099343)(5,0.527778910368045)(6,0.532176796157059)(7,0.566662366701066)(8,0.637110556563823)(9,0.685799234290614)(10,0.538089511412941)(11,0.621051710776405)(12,0.599367875333495)(13,0.670421793119162)(14,0.583598347357422)(15,0.623587223886899)(16,0.645277499838855)(17,0.653525664651826)(18,0.665572696108086)(19,0.670283086011174)(20,0.663804745401859)(21,0.633242908391853)(22,0.66099516031458)(23,0.644625119528521)(24,0.72069799334011)(25,0.737468671679198)(26,0.715572819263667)(27,0.727291592547725)(28,0.752558983666062)
 };
@@
 		    coordinates {
-		    (1,0.570063795853269)(2,0.756845238095238)(3,0.621034680606911)(4,0.719615829557505)(5,0.663677414539484)(6,0.680661881977671)(7,0.702849371292569)(8,0.730720679999118)(9,0.715323491375385)(10,0.722695511010729)(11,0.722586065299008)(12,0.725508681952266)(13,0.728214414334958)(14,0.753560036454773)(15,0.778231825645619)(16,0.745982043507288)(17,0.715855206037534)(18,0.733838894506235)(19,0.728435738081271)(20,0.754932383250967)(21,0.76774421230943)(22,0.761660230839754)(23,0.750358005521049)(24,0.82098385331144)(25,0.823507591442374)(26,0.834847535505431)(27,0.84013108540293)(28,0.813133718212162)
+		    (1,0.551714513556619)(2,0.682453503286837)(3,0.567702774084261)(4,0.646748619299324)(5,0.65492113250734)(6,0.701065228379203)(7,0.684439263401395)(8,0.700511175298951)(9,0.681034059961129)(10,0.685637253116215)(11,0.699316636125265)(12,0.697036509934383)(13,0.693463987436823)(14,0.704225209488367)(15,0.732978923190269)(16,0.724305489322319)(17,0.699459026247245)(18,0.716210056654951)(19,0.698987880687053)(20,0.733337516584389)(21,0.751908839952318)(22,0.75007040599401)(23,0.750592804644915)(24,0.814515445676703)(25,0.810987671748541)(26,0.817791638186375)(27,0.826003784931597)(28,0.809805364617137)
 };
@@
 		    coordinates {
-		    (1,0.580144743457437)(2,0.699277168494516)(3,0.596982860940987)(4,0.683431847315197)(5,0.634133314342686)(6,0.630169810336433)(7,0.628025663269931)(8,0.642973856209151)(9,0.618457602339181)(10,0.616241290282443)(11,0.606940556177678)(12,0.605471976942706)(13,0.598988030767536)(14,0.608112237561116)(15,0.609841319882303)(16,0.578626150272492)(17,0.55776862026862)(18,0.57760989010989)(19,0.567994505494506)(20,0.492368742368742)(21,0.582722832722833)(22,0.574786324786325)(23,0.644688644688645)(24,0.658424908424909)(25,0.708791208791209)(26,0.716727716727717)(27,0.719373219373219)(28,0.708791208791209)
+		    (1,0.598323207198336)(2,0.656420469232034)(3,0.551668227640311)(4,0.620327113896406)(5,0.623771074555817)(6,0.652894375155994)(7,0.625071981901494)(8,0.623287932111462)(9,0.601893257814311)(10,0.601192717220153)(11,0.602088073148115)(12,0.581718160067067)(13,0.570577347465439)(14,0.572274187082211)(15,0.581600752329829)(16,0.565774690293304)(17,0.5550594629542)(18,0.565097183518236)(19,0.524149694006153)(20,0.511449953555217)(21,0.576679655627024)(22,0.571388650336019)(23,0.546588180559473)(24,0.608169608169608)(25,0.608169608169608)(26,0.633066933066933)(27,0.634654234654234)(28,0.628305028305028)
 };
 		%\legend{karma,serene,serene-pats}
+
 		\end{axis}
@@
 		    coordinates {
-		    (1,0.209547221954433)(2,0.411561264822134)(3,0.457295783926219)(4,0.449720026350461)(5,0.414575098814229)(6,0.364575098814229)(7,0.452173913043478)(8,0.526317523056654)(9,0.588158761528327)(10,0.403491436100132)(11,0.506175889328063)(12,0.489690382081687)(13,0.584008563899868)(14,0.470553359683795)(15,0.48570487483531)(16,0.553513584117033)(17,0.553774817136886)(18,0.573236677115987)(19,0.567816091954023)(20,0.580551201671891)(21,0.557301462904911)(22,0.559979101358412)(23,0.477098571926158)(24,0.57088122605364)(25,0.56078021595263)(26,0.565134099616858)(27,0.585336119818878)(28,0.598310693138279)
+		    (1,0.300191975130116)(2,0.387168789342702)(3,0.418780803201093)(4,0.414852632606256)(5,0.449767567691694)(6,0.454560596014134)(7,0.472473240503931)(8,0.552403403170667)(9,0.618322253509807)(10,0.45708434156857)(11,0.540246526073466)(12,0.523083348403042)(13,0.603209776078489)(14,0.509054454749254)(15,0.54874878365927)(16,0.577977828772285)(17,0.583053944903167)(18,0.591126557438254)(19,0.592414794781259)(20,0.591100946357877)(21,0.575601120513223)(22,0.587190134384184)(23,0.575949431206362)(24,0.655469912102772)(25,0.649409306042166)(26,0.64025693035835)(27,0.652378142479562)(28,0.666045239412379)
 };
@@
 		    coordinates {
-		    (1,0.558240946045824)(2,0.733876811594203)(3,0.610770750988142)(4,0.707559288537549)(5,0.654891304347826)(6,0.670421607378129)(7,0.704710144927536)(8,0.729611330698287)(9,0.716913702239789)(10,0.728837285902504)(11,0.724769433465085)(12,0.724670619235837)(13,0.727783267457181)(14,0.76187417654809)(15,0.790283267457181)(16,0.751266980146291)(17,0.72991118077325)(18,0.761259143155695)(19,0.742058516196448)(20,0.759103970741902)(21,0.776149425287357)(22,0.758842737722048)(23,0.730668756530825)(24,0.800330895158482)(25,0.800330895158482)(26,0.808951584813654)(27,0.813305468477882)(28,0.790229885057471)
+		    (1,0.517923133776792)(2,0.667141218952813)(3,0.56262382276875)(4,0.646790367442541)(5,0.651735815098987)(6,0.706388551614468)(7,0.698383379116542)(8,0.714984169630376)(9,0.700346244485205)(10,0.704664218197892)(11,0.717929077647748)(12,0.711690361988742)(13,0.707592621296799)(14,0.725417933239758)(15,0.760334088253952)(16,0.741766948274724)(17,0.726258869970838)(18,0.748428390280994)(19,0.723282293295816)(20,0.746991608671798)(21,0.769430045325921)(22,0.751719414109543)(23,0.756837646239269)(24,0.816669125330383)(25,0.816669125330383)(26,0.821841539123487)(27,0.824453869322024)(28,0.810608519269777)
 };
@@
 		    coordinates {
-		    (1,0.571875702946753)(2,0.770701581027668)(3,0.637285902503294)(4,0.73596837944664)(5,0.677618577075099)(6,0.693148880105402)(7,0.725263504611331)(8,0.750164690382082)(9,0.739640974967062)(10,0.743988801054019)(11,0.742094861660079)(12,0.734420289855072)(13,0.742934782608696)(14,0.775131752305666)(15,0.795965085638999)(16,0.772361546499478)(17,0.752899686520376)(18,0.776671891327064)(19,0.765308254963427)(20,0.733838383838384)(21,0.783986415882968)(22,0.774255485893417)(23,0.751219087425984)(24,0.803030303030303)(25,0.828456983629397)(26,0.83707767328457)(27,0.841431556948798)(28,0.828456983629397)
+		    (1,0.592810513524547)(2,0.704036744254136)(3,0.580300590445518)(4,0.665729761381935)(5,0.671789291034815)(6,0.721540066765983)(7,0.718258458411911)(8,0.728686409419572)(9,0.71549775963672)(10,0.719667189083217)(11,0.729479363111076)(12,0.713288181617252)(13,0.723866470903981)(14,0.739158277862456)(15,0.764121967041831)(16,0.755829992510182)(17,0.746486501253236)(18,0.758703555728573)(19,0.723655728717502)(20,0.729409784115667)(21,0.774654705722995)(22,0.768167419063295)(23,0.754561938768098)(24,0.828459715477971)(25,0.828459715477971)(26,0.838717192206036)(27,0.841329522404573)(28,0.833544778412933)
 };
@@
 		    coordinates {
-		    (1,0.28413987159729)(2,0.598592698574067)(3,0.36263108253479)(4,0.400362551212311)(5,0.387216985225677)(6,0.392432987689972)(7,0.394440889358521)(8,0.430805265903473)(9,0.438177883625031)(10,0.441894292831421)(11,0.461780428886414)(12,0.469180881977081)(13,0.477133095264435)(14,0.498149693012238)(15,0.512342214584351)(16,0.600962460041046)(17,0.5725257396698)(18,0.907191514968871)(19,0.551609396934509)(20,0.585879027843475)(21,0.610454380512239)(22,0.575962841510773)(23,0.657813549041748)(24,0.671637773513794)(25,0.689822912216188)(26,0.724388360977171)(27,0.750569899876912)(28,0.771229823430379)
+		    (1,0.268540382385254)(2,0.485812822977702)(3,0.346803307533264)(4,0.372188647588094)(5,0.367514610290527)(6,0.37602166334788)(7,0.376668055852254)(8,0.410835981369019)(9,0.422285079956055)(10,0.424292365709941)(11,0.439166347185771)(12,0.446258664131165)(13,0.46294093132019)(14,0.484450976053874)(15,0.489395022392273)(16,0.550653139750163)(17,0.543892900149027)(18,0.760240634282429)(19,0.529818336168925)(20,0.544886191685995)(21,0.576984961827597)(22,0.557323813438416)(23,0.563650608062744)(24,0.60092453956604)(25,0.626034975051881)(26,0.663434648513793)(27,0.692028045654297)(28,0.702148389816284)
 };
@@
 		    coordinates {
-		    (1,0.0166666666666667)(2,0.995)(3,0.8725)(4,0.8325)(5,0.9175)(6,0.965)(7,0.89)(8,0.9675)(9,0.96)(10,1.1225)(11,1.1475)(12,1.36)(13,1.295)(14,1.3925)(15,1.375)(16,1.4975)(17,1.9575)(18,2.11)(19,1.9075)(20,1.9175)(21,1.865)(22,1.915)(23,2.49)(24,2.4)(25,2.49)(26,2.49)(27,2.68333333333333)(28,2.47666666666667)
+		    (1,0.0175)(2,0.665)(3,0.585)(4,0.561666666666667)(5,0.62)(6,0.655)(7,0.605)(8,0.66)(9,0.655)(10,0.766666666666667)(11,0.783333333333333)(12,0.933333333333333)(13,0.901666666666667)(14,0.968333333333333)(15,0.956666666666667)(16,1.03333333333333)(17,1.34166666666667)(18,1.44666666666667)(19,1.30833333333333)(20,1.31333333333333)(21,1.27833333333333)(22,1.31333333333333)(23,1.28166666666667)(24,1.472)(25,1.526)(26,1.528)(27,1.642)(28,1.52)
 };
@@
 		    coordinates {
-		    (1,0.025)(2,1.0375)(3,0.93)(4,1)(5,0.9575)(6,0.9425)(7,0.9)(8,0.975)(9,1.06)(10,1.2025)(11,1.2975)(12,1.9425)(13,1.52)(14,2.2825)(15,1.6275)(16,3.5375)(17,2.255)(18,2.1625)(19,6.505)(20,1.44666666666667)(21,2.2825)(22,2.3475)(23,8.28666666666667)(24,1.895)(25,8.3)(26,3.75333333333333)(27,3.73)(28,3.75)
+		    (1,0.02)(2,0.696666666666667)(3,0.619166666666666)(4,0.67)(5,0.65)(6,0.64)(7,0.615833333333333)(8,0.674166666666667)(9,0.741666666666667)(10,0.8375)(11,0.9125)(12,1.62)(13,1.05)(14,1.94583333333333)(15,1.11916666666667)(16,2.85916666666667)(17,1.55583333333333)(18,1.53666666666667)(19,3.27)(20,1.399)(21,1.63833333333333)(22,1.66)(23,3.24181818181818)(24,3.64444444444444)(25,3.69777777777778)(26,2.343)(27,2.334)(28,2.373)
 };
@@
 \end{minipage}%
-\caption{Average precision, recall and time on the museum domain for \relonto{} systems with variable training set size.}\label{fig:perfmuseum}
+\caption{Average precision, recall and time on the museum domain for \relonto{} 
+systems with variable training set size.}\label{fig:perfmuseum}
 \end{figure*}
@@
 \end{tikzpicture}
-\subcaption{precision}\label{fig:soccerprec}
+\subcaption{precision}
 \end{minipage}%
@@
 	\end{tikzpicture}
-\subcaption{recall}\label{fig:soccerrec}
+\subcaption{recall}
 \end{minipage}%
@@
 \end{tikzpicture}
-\subcaption{time (s)}\label{fig:soccertime}
+\subcaption{time (s)}
 \end{minipage}%
-\caption{Average precision, recall and time on the soccer domain for \relonto{} systems with variable training set size.}\label{fig:perfsoccer}
+\caption{Average precision, recall and time on the soccer domain for \relonto{} 
+systems with variable training set size.}
 \end{figure*}
 
-% karma vs serene vs serene-pats
-We evaluate our new system \emph{serene} and its modification \emph{serene-pats}, which uses graph patterns, against the state-of-the-art system \emph{karma}.
-All three systems have access to the same set of matches produced by our semantic labeling model.
-Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} show their performance on the museum and soccer domains.
-We report average precision, recall and run times for the systems with regard to variable number of semantic models in the training set.
-For \emph{serene} and \emph{serene-pats} we report the first solutions found by the chuffed solver.
-We use default parameters for \emph{karma} which were shown to yield the best results~\cite{taheriyan2016learning}.
-As we can see, \emph{serene} produces on average the best semantic models in terms of precision while \emph{serene-pats} generates slightly better models in terms of recall.
-If we consider results separately per each instance and not on average, there are a few instances where \emph{karma} generates more precise models, however, our new approaches produce much better models in terms of recall in all considered instances.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% sequentially found solutions and different weights for patterns
-\begin{figure*}[h]\small
-\pgfplotsset{
-    small,
-    %legend style={legend pos=north east}
-    legend style={
-        at={(0.01,0.01)},
-        anchor=south west,
-    },
-   }%
-\begin{minipage}[b]{.34\linewidth}
-\centering
-\begin{tikzpicture}[baseline]
-\begin{axis}[
-		    xlabel={\emph{solution}},
-		    ylabel={Performance},
-		    xmin=0, xmax=20,
-		    ymin=0.7, ymax=1,
-		    xtick={0,5,10,15,20},
-		    ytick={0.7,0.8,0.9,1},
-		    legend pos=south east,
-		    ymajorgrids=true,
-		    grid style=dashed,
-		    legend style={at={(1.5,1.1)},anchor=south, legend columns=-1}
-		]
-
-		\addplot[
-		    color=blue,
-		    mark=square,
-		    ]
-		    coordinates {
-		    (0,0.813133718212162)(1,0.870689655172414)(2,0.869565217391304)(3,0.854700854700855)(4,0.847457627118644)(5,0.862068965517241)(6,0.862068965517241)(7,0.860869565217391)
-		    };
-		\addplot[
-		    color=red,
-		    mark=*,
-		    ]
-		    coordinates {
-		    (0,0.708791208791209)(1,0.720429778415431)(2,0.727852084972463)(3,0.734756097560976)(4,0.737969058591178)(5,0.723003960808839)(6,0.727905921593153)(7,0.740887177292826)(8,0.733003960808839)(9,0.746193299741805)(10,0.73554304773817)(11,0.74569890495285)(12,0.756325773784054)(13,0.745676961413577)(14,0.753615746683783)(15,0.7306060898002)(16,0.723882805154582)(17,0.720774744968293)(18,0.733079110976868)(19,0.731544715447155)(20,0.734034752112227)
-
-		    };
-		\addplot[
-		    color=green,
-		    mark=x,
-		    ]
-		    coordinates {
-		    (0,0.71031746031746)(1,0.722023912003826)(2,0.734193548387097)(3,0.740054370716392)(4,0.751788722391459)(5,0.752652119278914)(6,0.765286464150101)(7,0.766275317871063)(8,0.763956676916058)(9,0.779373522458629)(10,0.780497706328908)(11,0.786846912678115)(12,0.793409626193882)(13,0.801554001554001)(14,0.800878033205619)(15,0.861352657004831)(16,0.863636363636364)(17,0.863636363636364)(18,0.883720930232558)(19,0.8125)(20,0.795918367346939)
-		    };
-		\addplot[
-		    color=brown,
-		    mark=+,
-		    ]
-		    coordinates {
-		    (0,0.71031746031746)(1,0.722023912003826)(2,0.734193548387097)(3,0.740054370716392)(4,0.751788722391459)(5,0.752652119278914)(6,0.758342019705656)(7,0.772281323877069)(8,0.774638933587619)(9,0.786846912678115)(10,0.786846912678115)(11,0.795363644516187)(12,0.804524886877828)(13,0.797201562617384)(14,0.812955643390426)(15,0.775568181818182)(16,0.863636363636364)(17,0.883720930232558)(18,0.883720930232558)(19,0.883720930232558)(20,0.904761904761905)
-};
-		 \addplot[
-		    color=violet,
-		    mark=star,
-		    ]
-		    coordinates {
-		    (0,0.716727716727717)(1,0.728559859716244)(2,0.740860215053763)(3,0.746857091804827)(4,0.757315933275812)(5,0.758342019705656)(6,0.765286464150101)(7,0.779373522458629)(8,0.787744083140503)(9,0.786846912678115)(10,0.789244481875285)(11,0.804524886877828)(12,0.811442006269593)(13,0.803401771336554)(14,0.785524847694936)(15,0.849173553719008)(16,0.852651515151516)(17,0.866230213015439)(18,0.876750700280112)(19,0.85593220338983)(20,0.863247863247863)
-};
-		\legend{serene,pats-1,pats-5,pats-10,pats-20}
-
-		\end{axis}
-\end{tikzpicture}
-\subcaption{precision}\label{fig:solprec}
-\end{minipage}%
-%
-\begin{minipage}[b]{.33\linewidth}
-\centering
-\begin{tikzpicture}[baseline]
-		\begin{axis}[
-		    xlabel={\emph{solution}},
-		    %ylabel={recall},
-		    xmin=0, xmax=20,
-		    ymin=0.7, ymax=1,
-		    xtick={0,5,10,15,20},
-		    ytick={0.7,0.8,0.9,1},
-		    ymajorgrids=true,
-		    grid style=dashed,
-		    %legend style={at={(0.5,1.1)},anchor=south, legend columns=-1}
-		]
-
-		\addplot[
-		    color=blue,
-		    mark=square,
-		    ]
-		    coordinates {
-		    (0,0.790229885057471)(1,0.870689655172414)(2,0.862068965517241)(3,0.862068965517241)(4,0.862068965517241)(5,0.862068965517241)(6,0.862068965517241)(7,0.853448275862069)
-		    };
-		\addplot[
-		    color=red,
-		    mark=*,
-		    ]
-		    coordinates {
-		    (0,0.828456983629397)(1,0.828456983629397)(2,0.828456983629397)(3,0.828456983629397)(4,0.828456983629397)(5,0.82088122605364)(6,0.82088122605364)(7,0.823754789272031)(8,0.82088122605364)(9,0.823754789272031)(10,0.841431556948798)(11,0.841431556948798)(12,0.841431556948798)(13,0.835684430512017)(14,0.838557993730407)(15,0.825583420411007)(16,0.810431905259492)(17,0.82088122605364)(18,0.82088122605364)(19,0.83098223615465)(20,0.833855799373041)
-};
-		\addplot[
-		    color=green,
-		    mark=x,
-		    ]
-		    coordinates {
-		    (0,0.83098223615465)(1,0.83098223615465)(2,0.83098223615465)(3,0.823406478578892)(4,0.828108672936259)(5,0.820532915360502)(6,0.828108672936259)(7,0.820532915360502)(8,0.820532915360502)(9,0.828108672936259)(10,0.820532915360502)(11,0.820532915360502)(12,0.818007662835249)(13,0.810431905259492)(14,0.800330895158482)(15,0.867163009404389)(16,0.863636363636364)(17,0.863636363636364)(18,0.863636363636364)(19,0.886363636363636)(20,0.886363636363636)
-};
-		 \addplot[
-		    color=brown,
-		    mark=+,
-		    ]
-		    coordinates {
-		    (0,0.83098223615465)(1,0.83098223615465)(2,0.83098223615465)(3,0.823406478578892)(4,0.828108672936259)(5,0.820532915360502)(6,0.820532915360502)(7,0.820532915360502)(8,0.820532915360502)(9,0.820532915360502)(10,0.820532915360502)(11,0.820532915360502)(12,0.820532915360502)(13,0.810431905259492)(14,0.810431905259492)(15,0.765151515151516)(16,0.863636363636364)(17,0.863636363636364)(18,0.863636363636364)(19,0.863636363636364)(20,0.863636363636364)
-};
-		 \addplot[
-		    color=violet,
-		    mark=star,
-		    ]
-		    coordinates {
-		    (0,0.838557993730407)(1,0.838557993730407)(2,0.838557993730407)(3,0.83098223615465)(4,0.828108672936259)(5,0.820532915360502)(6,0.828108672936259)(7,0.828108672936259)(8,0.828108672936259)(9,0.820532915360502)(10,0.820532915360502)(11,0.820532915360502)(12,0.818007662835249)(13,0.800330895158482)(14,0.790229885057471)(15,0.867163009404389)(16,0.867163009404389)(17,0.867163009404389)(18,0.867163009404389)(19,0.870689655172414)(20,0.870689655172414)
-};	
-	%\legend{serene,pats-1,pats-5,pats-10,pats-20}
-		\end{axis}
-	\end{tikzpicture}
-\subcaption{recall}\label{fig:solrec}
-\end{minipage}%
-%
-\begin{minipage}[b]{.33\linewidth}
-\centering
-\begin{tikzpicture}[baseline]
-\begin{axis}[
-		    xlabel={\emph{solution}},
-		    %ylabel={time(s)},
-		    xmin=0, xmax=20,
-		    ymin=0.0, ymax=21,
-		    xtick={0,5,10,15,20},
-		    ytick={0.0,3.0,6.0,9.0,12,15.0,18,21.0},
-		    ymajorgrids=true,
-		    grid style=dashed,
-		    %legend pos=outer north east,
-		    %legend style={at={(0.5,-0.1)},anchor=north, legend columns=-1}
-		]
-
-		\addplot[
-		    color=blue,
-		    mark=square,
-		    ]
-		    coordinates {
-		    (0,2.47666666666667)(1,7.15)(2,7.41)(3,8.83)(4,9.15)(5,9.32)(6,9.84)(7,10.04)
-};
-		\addplot[
-		    color=red,
-		    mark=*,
-		    ]
-		    coordinates {
-		    (0,3.75)(1,3.8)(2,3.84)(3,3.88666666666667)(4,3.93333333333333)(5,3.98)(6,4.03333333333333)(7,4.08)(8,4.13333333333333)(9,4.23)(10,4.29333333333333)(11,4.34)(12,4.38666666666667)(13,4.74)(14,4.83)(15,5.74333333333333)(16,5.96333333333333)(17,6.48666666666667)(18,6.53)(19,6.58333333333333)(20,6.63)
-};
-		\addplot[
-		    color=green,
-		    mark=x,
-		    ]
-		    coordinates {
-		    (0,3.74)(1,3.79)(2,3.83666666666667)(3,3.88666666666667)(4,3.93666666666667)(5,3.98666666666667)(6,4.03666666666667)(7,4.09333333333333)(8,4.17333333333333)(9,4.23)(10,4.31666666666667)(11,4.38)(12,4.54333333333333)(13,5)(14,6.17666666666667)(15,6.755)(16,1.61)(17,2.21)(18,2.35)(19,2.61)(20,3.11)
-};
-		\addplot[
-		    color=brown,
-		    mark=+,
-		    ]
-		    coordinates {
-		    (0,3.75)(1,3.8)(2,3.84666666666667)(3,3.89666666666667)(4,3.95)(5,3.99666666666667)(6,4.05)(7,4.10333333333333)(8,4.16666666666667)(9,4.23333333333333)(10,4.43)(11,4.53333333333333)(12,4.78)(13,5.15333333333333)(14,5.36333333333333)(15,3.365)(16,1.91)(17,1.95)(18,8.42)(19,8.62)(20,8.85)
-};
-		 \addplot[
-		    color=violet,
-		    mark=star,
-		    ]
-		    coordinates {
-		    (0,3.73666666666667)(1,3.78666666666667)(2,3.83666666666667)(3,3.88333333333333)(4,3.93666666666667)(5,3.98666666666667)(6,4.04333333333333)(7,4.09666666666667)(8,4.16)(9,4.22)(10,4.38333333333333)(11,4.49)(12,4.72333333333333)(13,4.99333333333333)(14,9.33333333333333)(15,10.715)(16,10.86)(17,10.915)(18,12.65)(19,20.35)(20,20.56)
-};	
-	%\legend{serene,pats-1,pats-5,pats-10,pats-20}
-		\end{axis}
-\end{tikzpicture}
-\subcaption{time (s)}\label{fig:soltime}
-\end{minipage}%
-\caption{Average precision, recall and time on the museum domain for leave-one-out strategy and different weighting scheme for patterns in serene.}\label{fig:perfsol}
-\end{figure*}
-
-%% sequential solution
-As mentioned previously, the chuffed solver outputs solutions as it finds them.
-In Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} we report the first found solutions.
-In Fig.~\ref{fig:perfsol} we show how the performance of \emph{serene} changes across sequentially found solutions.
-The idea is that the chuffed solver finds better solutions in terms of cost function, however, as we can see from the results,
-that does not translate directly into more precise semantic models.
-Additionally, we investigate how the performance is influenced if we introduce a weighting scheme on the patterns,
-i.e., costs of patterns are scaled by a factor.
-In Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} we use a scaling factor 1 for pattern costs.
-Fig.~\ref{fig:perfsol} demonstrates that by using scaling factors 5, 10 or 20 for patterns from the museum domain we can generate semantic models which are almost 90\% in precision and recall.
-This is a 20\% improvement in presision compared to the first solution found by \emph{serene-pats} and a 10\% improvement both in precision and recall for the first solution from \emph{serene}.
-However, such improvement comes at a cost in run time.
-On average, we have observed that the chuffed solver yields very good results already with the first found solution.
-The sequential solutions are not always better, and hitting the optimal solution may take hours.
-
-% change in performance if we look at sequentially found solutions
-% only leave-one-out for museum domain with 15s timeout for chuffed
-\npr{not sure whether Fig.~\ref{fig:loo} is needed}
-\begin{figure}\small
-\begin{tikzpicture}\small
-\pgfplotsset{
-    scale only axis,
-    small,
-    xmin=0, xmax=9
-}
-
-\begin{axis}[
-  axis y line*=left,
-  ymin=0.5, ymax=1,
-  xlabel=solution number,
-  ylabel=performance,
-  legend pos=south east,
-]
-\addplot[smooth,mark=x,red]
-  coordinates{
-    (0,0.776507549540743)(1,0.71093042754513)(2,0.822783653218436)(3,0.845760233918129)(4,0.879310344827586)(5,0.88695652173913)(6,0.885964912280702)(7,0.870689655172414)(8,0.878260869565217)(9,0.87719298245614)
-
-}; \label{plot_one}
-\addlegendentry{precision}
-\addplot[smooth,mark=*,green]
-  coordinates{
-    (0,0.773180507486795)(1,0.677202255831871)(2,0.805899400726987)(3,0.838122605363985)(4,0.879310344827586)(5,0.879310344827586)(6,0.870689655172414)(7,0.870689655172414)(8,0.870689655172414)(9,0.862068965517241)
-}; \label{plot_two}
-\addlegendentry{recall}
-\end{axis}
-
-\begin{axis}[
-  axis y line*=right,
-  axis x line=none,
-  ymin=0, ymax=15,
-  legend pos=south east,
-  ylabel=time (s)
-]
-\addlegendimage{/pgfplots/refstyle=plot_one}\addlegendentry{precision}
-\addlegendimage{/pgfplots/refstyle=plot_two}\addlegendentry{recall}
-\addplot[smooth,mark=square,blue]
-  coordinates{
-    (0,0.894338290115883)(1,2.39426428574782)(2,6.89703391393025)(3,10.3563708686829)(4,9.87668780326843)(5,9.92719115257263)(6,10.4045292949677)(7,14.3818371582031)(8,14.4026180458069)(9,14.8023208427429)
-}; \addlegendentry{time}
-\end{axis}
-\end{tikzpicture}
-\caption{Performance of \emph{serene} for leave-one-out strategy on the museum domain.}\label{fig:loo}
-\end{figure}
-
-\npr{Maybe some words on how optimal solution found by chuffed relates to the ground truth?}
-
-\section{Related Work \label{SEC:pw}}
-
-Relational data sources are still one of the most popular ways to store enterprise or Web data, however, the issue with relational schema is the lack of a well-defined semantic description.
-A common ontology provides a way to represent the meaning of a relational schema and can facilitate the integration of heterogeneous data sources within a domain.
-Indicating semantic correspondences manually might be appropriate if only few data sources need to be integrated, however, it becomes tedious with the growing number of heterogeneous schemata.
-Hence, automatic or semi-automatic approaches for relational-to-ontology schema mapping are being actively developed.
-
-The majority of approaches to solve the relational-to-ontology (\relonto{}) mapping problem are based on heuristic rules and alignment of constraints specified within relational schemata and ontologies.
-A very comprehensive overview and comparison of existing mapping generation tools based on this approach is given in~\cite{Pinkel:rodi} and~\cite{Spanos:semweb}.
-As examples, there are BootOX~\cite{Jimenez:Bootox}, MIRROR~\cite{Luciano:Mirror} and  ontop~\cite{Fagin:Clio}.
-Crudely speaking, these tools first apply a default direct mapping specified by the W3C.
-Further, the default ontology is enriched by using explicit and implicit schema constraints.
-Finally, ontology alignment techniques are applied to match the default ontology to the target ontology.
-The main advantage of these systems is the ability to run in a fully automatic setting.
-Our approach is complementary to the approaches from this group and at its current stage is semi-automatic.
-However, constraint programming offers a convenient framework to incorporate integrity constraints specified either within relational or ontological schema as additional constraints to govern the search for the solution.
-This opens an interesting direction for further research to develop an automatic system.
-
-A major issue with fully automatic systems is though that constraints may be inconsistent or absent completely, e.g., data from Web services or tables on the Web \ddg{Why?}.
-To overcome this issue, we can apply ML techniques.
-\cite{Limaye:Annotating} design a system to annotate web tables with entities for cell values, semantic labels for attributes and relationships for binary combinations of attributes.
-As in our approach, they decompose the process of mapping into two main stages: semantic labeling and finding relationships between matched semantic labels.
-\cite{Limaye:Annotating} enrich their data sources by using YAGO.
-\cite{Mulwad:Semantic} extend this approach by leveraging information from Wikitology Knowledge Base (KB).
-\cite{Venetis:Recovering} develop a scalable approach to recover the semantics of Web tables by incorporating data from the isA database KB.
-\cite{Ritze:matching}, on the other hand, use DBPedia as their KB.
-%extract additional data from knowledge bases to assign a semantic label to an attribute.
-Hence, these approaches are limited to domains well represented in those knowledge bases.
-Also, they are not able to find the relation between attributes in the table if there is no direct connection between the attributes.
-Our approach, on the other hand, allows a model to be trained on any data and can infer complex semantic paths which might exist between attributes.
-However, it might be further bootstrapped by leveraging external knowledge bases.
-This is especially beneficial at the start when the system does not have sufficient training data.
-
-As mentioned above, the approaches for mapping Web tables also perform semantic labeling.
-They design various similarity metrics for attribute names and values.
-However, they disregard the attributes which are not matched to the ontology (the so-called \emph{unknown} set of attributes) which are especially abundant on the Web~\cite{Ritze:matching}\cite{Pham:semantic}.
-It is clear that we cannot directly speak about similarity for unmatched attributes, since they are rather dissimilar from known semantic types.
-That is why we have developed a new approach for semantic labeling which can efficiently handle the \emph{unknown} class.
-We demonstrate its efficiency by comparing against the state-of-the-art approach DSL~\cite{Pham:semantic}.
-
-We build upon the work of~\cite{taheriyan2016learning} and use their ideas for the construction of the alignment graph.
-The only difference is that we introduce the \emph{unknown} and \emph{root} class nodes and as many \emph{unknown} data nodes as there are attributes in the modeled data source.
-These nodes serve to capture the unmatched attributes from the source.
-Though we have modified Karma to treat these additional nodes as well, our approach outperforms Karma since we have additional constraints for these nodes and use an exact algorithm to solve the STP.
-\cite{taheriyan2016learning} treat the matching and STP parts of \relonto{} independently and use heuristic algorithms for both.
-We, on the other hand, use exact algorithms for both parts and address them within a unified CP model.
-
-In their follow up work, \cite{Taheriyan:Leveraging} suggest to use graph patterns to boost the performance of their system.
-To perform semantic modeling in such scenario, \cite{Taheriyan:Leveraging} had to revise their algorithm by introducing additional heuristics.
-However, in our case we had to add pattern variables and to modify the objective function in the MiniZinc model.
-No changes to the solver were required.
-This makes our system very convenient and opens directions for validating various additional constraints.
-Though our approach beats the state-of-the-art system Karma in the conducted experiments, it is worth noting that the scalability of our approach is under question.
-The main argument why exact solution for STP is feasible in our setting is that we map data sources to a domain-specific ontology which is expected to be limited in its size.
-
-\ddg{Isn't this really similar??}
-\npr{It is very similar, I'm even using their code partially :)}
-
-\section{Conclusion}
-\ddg{TODO} 
-In this paper we have introduced a new approach to solve the problem of relational-to-ontology schema mapping.
-
-Future directions:
-incorporate Linked Open Data and other external knowledge bases to overcome cold start problem;
-incorporate schema and ontology constraints;
-complex matches like 1:n and n:1 and iMap.
-
-\bibliographystyle{aaai}
-\npr{TODO: shorten citations like conference names and if there are more than 4 authors use et al}
-\bibliography{main}
 \end{document}

### 2017-08-21 stp/paper_aaai/main.tex
Conclusion section

--- 2017-08-20 stp/paper_aaai/main.tex
@@
 		    coordinates {
-		    (1,0.580144743457437)(2,0.699277168494516)(3,0.596982860940987)(4,0.683431847315197)(5,0.634133314342686)(6,0.630169810336433)(7,0.628025663269931)(8,0.642973856209151)(9,0.618457602339181)(10,0.616241290282443)(11,0.606940556177678)(12,0.605471976942706)(13,0.598988030767536)(14,0.608112237561116)(15,0.609841319882303)(16,0.578626150272492)(17,0.55776862026862)(18,0.57760989010989)(19,0.567994505494506)(20,0.492368742368742)(21,0.582722832722833)(22,0.574786324786325)(23,0.644688644688645)(24,0.658424908424909)(25,0.708791208791209)(26,0.716727716727717)(27,0.719373219373219)(28,0.708791208791209)
+		    (1,0.598323207198336)(2,0.656420469232034)(3,0.551668227640311)(4,0.620327113896406)(5,0.623771074555817)(6,0.652894375155994)(7,0.625071981901494)(8,0.623287932111462)(9,0.601893257814311)(10,0.601192717220153)(11,0.602088073148115)(12,0.581718160067067)(13,0.570577347465439)(14,0.572274187082211)(15,0.581600752329829)(16,0.565774690293304)(17,0.5550594629542)(18,0.565097183518236)(19,0.524149694006153)(20,0.511449953555217)(21,0.576679655627024)(22,0.571388650336019)(23,0.546588180559473)(24,0.608169608169608)(25,0.608169608169608)(26,0.633066933066933)(27,0.634654234654234)(28,0.628305028305028)
 };
@@
 		\end{axis}
-\end{tikzpicture}
+\end{tikzpicture}com
 \subcaption{time (s)}\label{fig:soltime}
@@
 In Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} we report the first found solutions.
-In Fig.~\ref{fig:perfsol} we show how the performance of \emph{serene} changes across sequentially found solutions.
+In Fig.~\ref{fig:perfsol} we show how the performance of \emph{serene} changes across sequentially found solutions for the museum domain.
 The idea is that the chuffed solver finds better solutions in terms of cost function, however, as we can see from the results,
@@
 In Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} we use a scaling factor 1 for pattern costs.
-Fig.~\ref{fig:perfsol} demonstrates that by using scaling factors 5, 10 or 20 for patterns from the museum domain we can generate semantic models which are almost 90\% in precision and recall.
+Fig.~\ref{fig:perfsol} demonstrates that by using scaling factors 5, 10 or 20 for pattern costs from the museum domain we can generate semantic models which are almost 90\% in precision and recall.
 This is a 20\% improvement in presision compared to the first solution found by \emph{serene-pats} and a 10\% improvement both in precision and recall for the first solution from \emph{serene}.
-However, such improvement comes at a cost in run time.
-On average, we have observed that the chuffed solver yields very good results already with the first found solution.
-The sequential solutions are not always better, and hitting the optimal solution may take hours.
+Yet such improvement comes at a cost in run time.
+On average, we have observed that \emph{serene} yields very good results already with the first solution found found by the chuffed solver.
+\emph{Serene-pats}, on the other hand, produces considerably better solutions with scaled pattern costs and sequential solutions.
+However, the sequential solutions are not always better, and hitting the optimal solution may take hours.
+
+We have also observed that \emph{serene-pats} manages to find the ground truth on many instances among its sequential solutions, but again it takes much more time.
+In the end, which approach to use for \relonto{} problem comes down to trade-offs between precision, recall and time.
 
@@
 
-\ddg{Isn't this really similar??}
-\npr{It is very similar, I'm even using their code partially :)}
+%\ddg{Isn't this really similar??}
+%\npr{It is very similar, I'm even using their code partially :)}
 
@@
 \ddg{TODO} 
-In this paper we have introduced a new approach to solve the problem of relational-to-ontology schema mapping.
-
-Future directions:
-incorporate Linked Open Data and other external knowledge bases to overcome cold start problem;
-incorporate schema and ontology constraints;
-complex matches like 1:n and n:1 and iMap.
+In this paper we have introduced a new approach \emph{serene} to solve the problem of relational-to-ontology schema mapping \relonto{}.
+We have also built its extension \emph{serene-pats} which uses additionally frequent graph patterns.
+Our experiments on two domains \emph{museum} and \emph{soccer} demonstrate that \emph{serene} generates on average more consistent semantic models in terms of precision and recall compared to the state-of-the-art system \emph{karma}.
+The modified version \emph{serene-pats} produces, on average, better semantic models in terms of recall, however, its overall performance is rather mixed if we consider the first produced model.
+However, the solutions discovered by \emph{serene-pats} afterwards tend to be much better both in precision and recall.
+The disadvantage is though that it comes at a cost of run time.
+In the end, which approach to use for \relonto{} problem comes down to trade-offs between precision, recall and time.
+
+%%%%%%%%future directions%%%%%%%%%%%%%
+% cold start problem and LOD
+One of the key limitations of our approach is the availability of training data in the domain, which is often referred to as cold start problem.
+We consider leveraging the data from the Linked Open Cloud (LOD) which, on one hand, leads to improved performance in the light of insufficient data and, on the other hand, helps in publishin consistent Linked Data~\cite{Taheriyan:Leveraging}.
+As we have shown, the frequent graph pattern mining procedure DIMSpan~\cite{petermann2017dimspan} which we use in our work is a highly scalable approach compared to the technique based on SPARQL queries from~\cite{Taheriyan:Leveraging}.
+
+%incorporate schema and ontology constraints
+Incorporating schema and ontology constraints may also help with the cold start problem.
+Furthermore, it can provide means to improve disambiguation of properties.
+For example, it is hard for our system to differentiate between startDate and endDate of the class Event.
+Having a constraint that startDate is before endDate might improve the mapping in such situations.
+
+%complex matches
+Another interesting direction for further research is to recognise complex matches.
+Our semantic labeling model \emph{serene} as well as many others in the literature~\cite{Pham:semantic}\cite{Ritze:matching} can learn only one-to-one matches between attributes and properties in the ontology.
+\cite{Pinkel:rodi} show that such systems as BootOX can also handle efficiently only one-to-one matches while their performance degrades considerably for $1:n$ and $n:1$ matches.
+\emph{Karma}~\cite{taheriyan2016learning} offers its users to manually specify tranformations through Python scripts.
+\cite{Dhamankar:imap} offer a way to learn such transformations from the historic data.
+This is one of the features which we want to incorporate into \emph{serene}.
 

### 2017-08-21 stp/paper_aaai/main.tex
merged

--- 2017-08-21 stp/paper_aaai/main.tex
@@
 shown in Fig.~\ref{FIG:onto} and \ref{FIG:sem}.
-The semantic model may have several instances of a same ontology class or 
+The semantic model may have several instances of the same ontology class or
 object property.
@@
 
-\section{ML for Training on Source Descriptions \label{SEC:ML}}
+\section{ML for Training on Source Descriptions}\label{SEC:ML}
+%\ddg{Better title than this please...}}
 
@@
 of whitespaces and other special characters, statistics of values in the column
-(e.g, mean/max/min string length and numeric statistics) and more. A full 
-list can be found in appendix \ddg{Apendix!}
+(e.g, mean/max/min string length and numeric statistics) and more.
+A full list can be found in appendix \ddg{Apendix!}
 One of the important features characterising information content of an attribute is Shannon's entropy of the attribute's concatenated rows.
@@
 \cite{Pham:semantic} or HTML tables \cite{Ritze:matching}.
-In current systems, these columns are removed in a process that requires 
-extra time and effort as this is typically done manually in the real world.
+In current systems, these columns are removed in a pre-processing step that requires
+extra time and effort on the user side.
 
@@
 };
+		%\legend{karma,serene,serene-pats}
 
@@
 historic data.
-This is one of the features which we want to incorporate into \emph{serene}.
+This is one of the features which we want to incorporate into \serene{}.
 

### 2017-08-23 stp/paper_aaai/main.tex
rearranging
Two more tables
Taken Peter's comments into account, and most thuings that we discussed in person. Not far from the page limit anymore

--- 2017-08-21 stp/paper_aaai/main.tex
@@
 \section{Introduction}
-The problem of integrating heterogeneous data sources is a long standing issue in the database research field and is of high relevance in many real-world domains.
+The problem of integrating heterogeneous data sources is a long standing issue 
+in the database research field and is of high relevance in many real-world 
+domains (see e.g. 
+\cite{Rahm:2001:SAA:767149.767154,Dhamankar:imap,Taheriyan2013}).
 A common approach to tackle this problem is to design a global model and to
@@
 $\langle$\textit{Name, D.O.B, Location}$\rangle$.
-We do not \textit{a priori} know whether ``Date'' is the date of birth or the date a persons started working in the first table; or whether the ``Location'' on the second table refers to the location of the event, or the address of the company.
+We do not \textit{a priori} know whether ``Date'' in the first table is the 
+date of birth or the date a persons started working; or whether the 
+``Location'' on the second table refers to the location of the event, or the 
+address of the company. 
 If we are given an ontology like the one in Fig. \ref{FIG:onto}, we would like to automatically map the new data sources to classes of the 
-ontology.$\square$
+ontology.\hfill$\square$
 
@@
 Steiner Tree is a valid and coherent semantic model for the new source. 
-We call our system \serene{}.
-
-The contributions of this work are:\ddg{TODO}
+The contributions of this work are:
 \begin{itemize}
-	\item A novel modeling framework for \relonto{} problem which seemlessly incorporates machine learning and constraint programming.
-	\item An efficient approach to handle attributes which cannot be matched to the ontology. \npr{semantic labeling model and root, unknown nodes in the alignment graph and additional constraints} 
+	\item A novel modeling framework for the \relonto{} problem which 
+	seamlessly incorporates machine learning and constraint programming.
+	\item An efficient approach to handle attributes which cannot be matched to 
+	the ontology, through a new semantic labeling model and a new STP 
+	model with additional nodes.
+	\item A flexible and extensible approach to the problem, which is easy to 
+	reuse and adapt to specific situations.
 \end{itemize}
@@
 Section \ref{SEC:STP} shows how we model the problem as a STP, 
-whereas Section \ref{SEC:CP} discusses how we implement the model in CP. 
+whereas Section \ref{SEC:CP} presents our implementation in CP. 
 Section \ref{SEC:Res} shows our results. 
-Section \ref{SEC:pw} presents the previous work done to achieve this task.
+Section \ref{SEC:pw} compares with the previous work done to achieve this task.
 
@@
 
-In our work we consider that an ontology $\mathcal{O}$ has such basic elements as classes which represent a set of concepts, literal values, individuals which are members of classes and properties~\cite{Spanos:semweb}.
+In our work we consider that an ontology $\mathcal{O}$ includes basic elements 
+as classes which represent a set of concepts, literal values, individuals which 
+are members of classes and properties~\cite{Spanos:semweb}.
 Properties are classified into \emph{object properties}, which relate two 
@@
 shown in Fig.~\ref{FIG:onto} and \ref{FIG:sem}.
-The semantic model may have several instances of a same ontology class or 
+The semantic model may have several instances of the same ontology class or 
 object property.
@@
 Following the traditional data integration framework~\cite{doan2012principles}, we decompose the problem into two parts: schema matching and schema mapping.
-Schema matching part, which we refer to as \emph{semantic labeling}, finds correspondences between attributes from data sources and data nodes of the target ontology.
+Schema matching, which we refer to as \emph{semantic labeling}, finds 
+correspondences between attributes from data sources and data nodes of the 
+target ontology.
 In the schema mapping part we want to generate the semantic models of data sources by identifying the connecting paths for the matched data nodes.
@@
 We define a \emph{source description} as a triple $\delta = (s, m, \phi)$ where $s$ is a source, $m$ is a semantic model, and $\phi$ is an attribute mapping.
-Our problem can be stated now the following way. We have an ontology 
+Our problem can hence be stated as follows. We have an ontology 
 $\mathcal{O}$ and a set of source descriptions $S_T = \{(s_1, m_1, \phi_1),..., 
@@
 content, for example, startDate versus endDate for the Event class.
-Thirdly, a considerable number of attributes which do not have any corresponding property in the ontology, either by accident or on purpose.
+Thirdly, there may be considerable number of attributes which do not have any 
+corresponding property in the ontology, either by accident or deliberately.
 %\ddg{CHECK!}
@@
 
-In such way, we learn the mapping $\psi : \mathcal{A}_s \times \mathcal{L_O} 
+In this way, we learn the mapping $\psi : \mathcal{A}_s \times \mathcal{L_O} 
 \mapsto [0, 1]$,
-where $\psi(a_i,l_j)$ indicates the confidence of the attribute $a_i$ to be 
+where $\psi(a_i,l_j)$ indicates the confidence that the attribute $a_i$ is 
 mapped to the semantic type $l_j$.
 
-Note that we keep all the matches, regardless of the confidence fo the match. 
+Note that we keep all the matches, regardless of the confidence of the match. 
 This is an important difference between our system and other approaches 
 \cite{taheriyan2016learning} that 
-remove some of the matches based on heuristics to then simplify the task of 
+remove some of the matches based on heuristics in order to simplify the task of 
 finding the semantic model.
@@
 We mine these patterns from the set of semantic models in the training set $S_T$.
-This is known as Transactional Frequent Graph Pattern Mining, which contains the subgraph 
-isomorphism, known to be NP-complete.
+This is known as Transactional Frequent Graph Pattern Mining, which generalizes 
+the subgraph isomorphism problem, known to be NP-complete.
 The frequency of a pattern is an anti-monotonous measure, meaning that bigger 
@@
 We solve this pattern mining task with the tool DIMSpan \cite{petermann2017dimspan} which adapts gSpan~\cite{yan2002gspan} pruning techniques to the typed graphs and uses Apache Flink for scalability.
-We obtain patterns of size upto 6 in under 4 minutes for the biggest instances in our evaluation framework. 
+We obtain patterns of size up to 6 in under 4 minutes for the biggest instances 
+in our evaluation framework. 
 \npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe 
@@
 (V, E)$ and a subset of its nodes $T \subseteq V$, a 
-Steiner Tree $G_s = (V_s, E_s )$ is a tree such that $T \subseteq V_s \subseteq 
+Steiner Tree $G_s = (V_s, E_s )$ is a tree (connected acyclic graph) such that 
+$T \subseteq V_s \subseteq 
 V$ and $E_s \subseteq E$. In other words, $G_s$ spans all the nodes in $T$ and 
@@
 all the edges in the alignment 
-graph, and edges connecting each attributes of $s^\star$ to the nodes in the 
+graph, and edges connecting each attribute of $s^\star$ to the nodes in the 
 alignment graph \emph{induced} by the semantic types (i.e. the set of nodes in 
@@
 $l_j$ induced by the semantic model, $w_\mathcal{I}(e) = - 
-ln(\psi(a_i,l_i))$. %\ddg{CHECK!}
+ln(\psi(a_i,l_j))$. %\ddg{CHECK!}
 
@@
 {$s^\star$:};
-	\node[att] (a1) at (-3,-2) {\small Surame};
+	\node[att] (a1) at (-3,-2) {\small Surname};
 	\node[att] (a2) at (-1,-2) {\small Workplace};
@@
 	$(ii)$ %\item 
-	$T^\star$ must be a tree (connected acyclic graph),
+	$T^\star$ must be a tree,
 	$(iii)$ %\item 
@@
 	$(v)$ %\item 
-	$\forall n \in \mathcal{D_{G_O}} \cap V^\star, degree(a) = 2$
+	$\forall n \in \mathcal{D_{G_O}} \cap V^\star, degree(a) = 2$.
 %\end{enumerate}
 
-It is therefore natural to model this a STP with side constraints, since the 2 
-first requirements imply that $T^\star$ is a Steiner Tree of the integration 
-graph. By designing the weighting function $w_\mathcal{I}$ through ML 
-techniques, as shown in Section \ref{SEC:ML}, 
-our hope is that the minimum weight Steiner Tree is a valid semantic model for 
-the new source.
+It is therefore natural to model this a STP with side constraints, since the 
+two first requirements imply that $T^\star$ is a Steiner Tree of the 
+integration graph. By designing the weighting function $w_\mathcal{I}$ through 
+ML techniques, as shown in Section \ref{SEC:ML}, 
+our expectation is that the minimum weight Steiner Tree is a valid semantic 
+model for the new source.
 
@@
 It is common that the data sources to be integrated will have columns that 
-simply can't be matched to the ontology.
+simply cannot be matched to the ontology.
 This can happen when a column of a source table contains some information that 
@@
 Note that if all attributes find a 
-match, then both the \emph{unknown} and \emph{root} won't be selected in the 
-Steiner tree and the normal behavior will take place.
+match, then both the \emph{unknown} and \emph{root} nodes won't be selected in 
+the Steiner tree and the normal behavior will take place.
 \ddg{Explain the weights of the edges introduced by the unknown nodes}
@@
 \subsection{Definitions}
+
 A Constraint Optimization Problem (COP) is a tuple $P = (\boldsymbol{v},C,o)$ 
@@
 
-\ignore{
-A typical example of COP is the Traveling Salesman Problem, where we need to 
-find a route that visits all cities in a region exactly one and is of minimal 
-length.
-}
-
-%\subsection{Constraint Programming}
 Constraint Programming (CP) allows the user to model a COP and give it 
@@
 $\boldsymbol{v}$ in turn. At each iteration it will check whether any 
-constraint in $C$ is violated, in which case it will backtrack to change it's 
+constraint in $C$ is violated, in which case it will backtrack to change its 
 last decision. \ignore{The choice of the order of the variables to be assigned, 
@@
 choice of the value to be assigned to each variable is called the \emph{search 
-strategy}}.
+strategy}.}
 Since only using a backtracking algorithm would have a prohibitive cost, CP 
@@
 removing inconsistent values 
-form the domains of variables. That way, values that cannot appear in a 
+from the domains of variables. That way, values that cannot appear in a 
 solution, given the current set of decisions, are never tried by the search. 
@@
 
-\ignore{
-\subsubsection{Example} Consider the toy problem $P$ over variables $a$ and $b$ 
-such that $a \in \{2,3,4\}$, $b \in \{1,2,3\}$. Let $C = \{a + 2b \leq 4, a 
-\neq b\}$ be the constraints. If the search step decides that $a = 
-2$, then $(i)$ $a \neq b \Rightarrow b \in \{1,3\}$ and $(ii)$ $a + 2b \leq 4  
-\Rightarrow b \in \{1\}$. Thus we automatically know that $b = 1$ without never 
-trying any other of its original possible values. $\square$
-}
-
 \subsection{\relonto{} in Constraint Programming}
@@
 integration graph that corresponds to the alignment graph, and the 
-$\mathit{alldifferent}$ global constraint will deal with he matching part of 
-the 
-problem.
+$\mathit{alldifferent}$ global constraint will deal with the matching part of 
+the problem.
 
@@
 \ref{EQ:matchcost} computes the cost $w_{ADIFF}$ of the matches.
-Eq. \ref{EQ:patt} indicated that a pattern is used if and only if all its edges 
+Eq. \ref{EQ:patt} indicates that a pattern is used if and only if all its edges 
 are selected in the tree. Eq. \ref{EQ:pcost} computes the prizes collected by using patterns.
@@
 Note how this CP model is easy to adapt to more classic settings where no 
-patterns are used (by dropping Eqs. \ref{EQ:patt} and \ref{EQ:pcost}), or where 
-the \emph{unknown} nodes are used (by dropping \ref{EQ:unk}).
+patterns are used (by dropping Eqs. \ref{EQ:patt} and \ref{EQ:pcost}), or 
+without \emph{unknown} nodes (by dropping Eq. \ref{EQ:unk}).
 \section{Results \label{SEC:Res}}
@@
 % datasets for evaluation
+For the rest of the paper, we call our system \serene{} when it is not using 
+patterns in the CP model, and \serenepats{} when it uses them.
+
 We run experiments on two domains: museum and soccer (see Fig.~\ref{tab:data} for statistics).
@@
 This system also phrases the \relonto{} problem as STP and decomposes it further into two parts.
-However, they use heuristic algorithms both for the matching and for the STP parts.
-They solve the problems sequentially, i.e., once they produce a set of candidate mappings for attributes into the ontology, they fix this set and move onto the STP part.
-Additionally, they do not consider unmatched attributes in the sources.
+However, it uses heuristic algorithms both for the matching and for the STP 
+parts.
+It solve the problems sequentially, i.e., once it produces a set of candidate 
+mappings for attributes into the ontology, it fixes this set and move onto the 
+STP part.
+Additionally, it does not consider unmatched attributes in the sources.
 To ensure that \karma{} also handles such attributes, we change its semantic 
@@
 Note that unmatched attributes as well as \emph{unknown} and \emph{root} nodes are not part of these sets.
-We perform also a modification to the ground truth semantic models:
-if the true semantic label of an attribute is not present in any of the previously mapped data sources,
-we substitute it with \emph{unknown} and map it to the \emph{Unknown} class node.
+We also perform a modification to the ground truth semantic models:
+if the true semantic label of an attribute $a$ is not present in any of the 
+previously mapped data sources, we substitute it with $unk_a$ and map it to the 
+\emph{unknown} class node.
 In such way we validate how well the systems can detect earlier unseen cases.
@@
 % architecture
-We have run all our experiments on a Dell server with 252 GiB of memory, 2 CPUs with 4 cores each, 1 Titan GPU and 1 GeForce 1080 Ti GPU.
+We have run all our experiments on a Dell server with 252 GB of memory, 2 CPUs 
+with 4 cores each.
 \npr{check characteristics, AWS machine is bigger}
-In all our experiments we use a timeout threshold of 15s for \chuffed{}.
+In all our experiments we use a timeout threshold of 15s for \chuffed{}, which 
+runs on a single core (thus easy to deploy on any user's machine).
 
@@
 It is clear that we cannot directly speak about similarity for unmatched attributes, since they are rather dissimilar from known semantic types.
-Our intution why our approach performs better is that we have encorporated features which are derived directly from attribute values and are not based on the notion of similarity.
+Our intuition as to why our approach performs better is that we have 
+incorporated features which are derived directly from attribute values and are 
+not based on the notion of similarity.
 \npr{Good enough explanation?}
@@
   		\hline
-  		DSL & 0.56 & 0.618 & 156.6 & 36.3\\
- 		Serene & 0.866 & 0.827 & 100.6 & 6.8\\
+  		DSL & 0.560 & 0.618 & 156.6 & 36.3\\
+ 		\textsc{Serene(Pats)} & 0.866 & 0.827 & 100.6 & 6.80\\
   		\hline
@@
 \end{tikzpicture}
-\subcaption{Precission (museum)}\label{fig:museumprec}
+\subcaption{Precision (museum)}\label{fig:museumprec}
 \end{minipage}%
@@
 \end{tikzpicture}
-\subcaption{Precission (soccer)}\label{fig:soccerprec}
+\subcaption{Precision (soccer)}\label{fig:soccerprec}
 \end{minipage}%
@@
 \end{minipage}%
-\caption{Performance over the museum and soccer datasets\label{fig:perf}}
+\caption{Performance over the museum and soccer datasets. Average size of 
+integration graph: 88 nodes and 1129 nodes.\label{fig:perf}}
 \end{figure}
@@
 Fig.~\ref{fig:perf} show their performance on the museum and soccer domains.
-We report average precision, recall and run times for the systems with regard to variable number of semantic models in the training set.
+We report average precision and recall for the systems with regard to variable 
+number of semantic models in the training set.
 For \serene{} and \serenepats{} we report the first solutions found by
-\chuffed{}.
+\chuffed{}. All three systems find solutions in less than a second in average.
 We use default parameters for \karma{} which were shown to yield the best 
@@
 
+%% sequential solution
+In Fig.~\ref{fig:loo} we show how the performance of \serene{} changes 
+across sequentially found solutions.
+\chuffed{} successively finds better solutions in terms of Eq. \ref{EQ:obj}, 
+however,
+that does not translate directly into more precise semantic models.
+On average, we have observed that \serene{} yields very good results already 
+with the first solution found, and plateaus after the third solution.
+
+Additionally, we investigate how the performance is influenced by introducing 
+a weighting scheme on the patterns, i.e., costs of patterns are scaled by a 
+factor.
+In Fig.~\ref{fig:perf} we use a scaling factor 1 
+for pattern costs.
+When trying scaling factors 5, 10 or 20 for patterns costs from the museum 
+domain we can generate semantic models which 
+are almost 90\% in precision and recall.
+This is a 20\% improvement in precision compared to the first solution found 
+with a scaling factor of 1, and a 10\% improvement both in precision and recall 
+for the first solution from \serene{}.
+Contrarily to \serene{}, \serenepats{} with scaled factors produced better 
+solutions in terms of precision over time.
+However, the sequential solutions are not always better, and hitting the 
+optimal solution may take hours.
+
+We have also observed that \serenepats{} manages to find the ground truth on 
+many instances among its sequential solutions, but again it takes much more 
+time.
+
+% change in performance if we look at sequentially found solutions
+% only leave-one-out for museum domain with 15s timeout for chuffed
+
+\begin{figure}[!ht]
+\centering
+\begin{tikzpicture}[scale=0.4]
+\pgfplotsset{
+    scale only axis,
+    xmin=0, xmax=9
+}
+
+\begin{axis}[
+  axis y line*=left,
+  ymin=0.5, ymax=1,
+  xlabel=Solution Number,
+  ylabel=performance,
+  		    		    style = {font=\huge}
+]
+\addplot[smooth,mark=x,red]
+  coordinates{
+    (0,0.776507549540743)(1,0.71093042754513)(2,0.822783653218436)(3,0.845760233918129)(4,0.879310344827586)(5,0.88695652173913)(6,0.885964912280702)(7,0.870689655172414)(8,0.878260869565217)(9,0.87719298245614)
+
+}; \label{plot_one}
+\addplot[smooth,mark=*,green]
+  coordinates{
+    (0,0.773180507486795)(1,0.677202255831871)(2,0.805899400726987)(3,0.838122605363985)(4,0.879310344827586)(5,0.879310344827586)(6,0.870689655172414)(7,0.870689655172414)(8,0.870689655172414)(9,0.862068965517241)
+}; \label{plot_two}
+\end{axis}
+
+\begin{axis}[
+  axis y line*=right,
+  axis x line=none,
+  ymin=0, ymax=15,
+  legend pos=south east,
+  ylabel=time (s),
+  		    		    style = {font=\huge}
+]
+\addlegendimage{/pgfplots/refstyle=plot_one}\addlegendentry{precision}
+\addlegendimage{/pgfplots/refstyle=plot_two}\addlegendentry{recall}
+\addplot[smooth,mark=square,blue]
+  coordinates{
+    (0,0.894338290115883)(1,2.39426428574782)(2,6.89703391393025)(3,10.3563708686829)(4,9.87668780326843)(5,9.92719115257263)(6,10.4045292949677)(7,14.3818371582031)(8,14.4026180458069)(9,14.8023208427429)
+}; \addlegendentry{time}
+\end{axis}
+\end{tikzpicture}
+\caption{Performance of \serene{} for leave-one-out strategy on the museum 
+domain.}\label{fig:loo}
+\end{figure}
+
+\npr{Maybe some words on how optimal solution found by chuffed relates to the ground truth?}
+
+\section{Related Work \label{SEC:pw}}
+
+Relational data sources are still one of the most popular ways to store enterprise or Web data, however, the issue with relational schema is the lack of a well-defined semantic description.
+A common ontology provides a way of representing the meaning of a relational 
+schema and can facilitate the integration of heterogeneous data sources within 
+a domain.
+Indicating semantic correspondences manually might be appropriate if only few data sources need to be integrated, however, it becomes tedious with the growing number of heterogeneous schemata.
+Hence, automatic or semi-automatic approaches for relational-to-ontology schema mapping are being actively developed.
+
+The majority of approaches to solve the \relonto{} mapping problem are based on 
+heuristic rules and alignment of constraints specified within relational 
+schemata and ontologies.
+A very comprehensive overview and comparison of existing mapping generation tools based on this approach is given in~\cite{Pinkel:rodi} and~\cite{Spanos:semweb}.
+As examples, there are BootOX~\cite{Jimenez:Bootox}, MIRROR~\cite{Luciano:Mirror} and  ontop~\cite{Fagin:Clio}.
+Crudely speaking, these tools first apply a default direct mapping specified by the W3C.
+Further, the default ontology is enriched by using explicit and implicit schema constraints.
+Finally, ontology alignment techniques are applied to match the default ontology to the target ontology.
+The main advantage of these systems is the ability to run in a fully automatic setting.
+Our approach is complementary to the approaches from this group and at its current stage is semi-automatic.
+However, constraint programming offers a convenient framework to incorporate integrity constraints specified either within relational or ontological schema as additional constraints to govern the search for the solution.
+This opens an interesting direction for further research to develop an automatic system.
+
+A major issue with fully automatic systems is that constraints may be 
+inconsistent or absent completely, e.g., data from Web services or tables on 
+the Web.
+To overcome this issue, we can apply ML techniques.
+\cite{Limaye:Annotating} design a system to annotate web tables with entities for cell values, semantic labels for attributes and relationships for binary combinations of attributes.
+As in our approach, they decompose the process of mapping into two main stages: semantic labeling and finding relationships between matched semantic labels.
+\cite{Limaye:Annotating} enrich their data sources by using YAGO.
+\cite{Mulwad:Semantic} extend this approach by leveraging information from Wikitology Knowledge Base (KB).
+\cite{Venetis:Recovering} develop a scalable approach to recover the semantics of Web tables by incorporating data from the isA database KB.
+\cite{Ritze:matching}, on the other hand, use DBPedia as their KB.
+%extract additional data from knowledge bases to assign a semantic label to an attribute.
+Hence, these approaches are limited to domains well represented in those knowledge bases.
+Also, they are not able to find the relation between attributes in the table if there is no direct connection between the attributes.
+Our approach, on the other hand, allows a model to be trained on any data and can infer complex semantic paths which might exist between attributes.
+However, it might be further bootstrapped by leveraging external knowledge bases.
+This is especially beneficial at the start when the system does not have sufficient training data.
+
+As mentioned above, the approaches for mapping Web tables also perform semantic labeling.
+They design various similarity metrics for attribute names and values.
+However, they disregard the attributes which are not matched to the ontology 
+(the so-called \emph{unknown} set of attributes) which are especially abundant 
+on the Web~\cite{Ritze:matching,Pham:semantic}.
+It is clear that we cannot directly speak about similarity for unmatched attributes, since they are rather dissimilar from known semantic types.
+That is why we have developed a new approach for semantic labeling which can efficiently handle the \emph{unknown} class.
+We demonstrate its efficiency by comparing against the state-of-the-art approach DSL~\cite{Pham:semantic}.
+
+We build upon the work of~\cite{taheriyan2016learning} and use their ideas for the construction of the alignment graph.
+The only difference is that we introduce the \emph{unknown} and \emph{root} class nodes and as many \emph{unknown} data nodes as there are attributes in the modeled data source.
+These nodes serve to capture the unmatched attributes from the source.
+Though we have modified \karma{} to treat these additional nodes as well, our 
+approach outperforms \karma{} since we have additional constraints for these 
+nodes and use an exact algorithm to solve the STP.
+\cite{taheriyan2016learning} treat the matching and STP parts of \relonto{} independently and use heuristic algorithms for both.
+We, on the other hand, use exact algorithms for both parts and address them within a unified CP model.
+
+In their follow up work, \cite{Taheriyan:Leveraging} suggest using graph 
+patterns to boost the performance of their system.
+To perform semantic modeling in such scenario, \cite{Taheriyan:Leveraging} had to revise their algorithm by introducing additional heuristics.
+However, in our case we only had to add pattern variables and to modify the 
+objective function in the \minizinc{} model.
+No changes to the solver were required.
+This makes our system very convenient and opens directions for validating various additional constraints.
+\ignore{Though our approach beats the state-of-the-art in the conducted 
+experiments, it 
+is worth noting that the scalability of our approach is under question.
+The main argument why exact solution for STP is feasible in our setting is that 
+we map data sources to a domain-specific ontology which is expected to be 
+limited in its size.}
+
+\section{Conclusion}
+In this paper we have introduced a new approach, \serene{} (and its extension 
+that uses frequent graph patterns, \serenepats{}) to solve the problem of 
+relational-to-ontology schema mapping.
+Our experiments demonstrate that 
+\serene{} generates on average more consistent semantic models in terms of 
+precision and recall compared to the state-of-the-art approach \karma{}.
+\serenepats{} produces, on average, better semantic models in terms of 
+recall, and it's precision can be enhanced by adding a scaling factor for 
+pattern costs.
+
+Furthermore, our approach is extremely flexible and easy to extend with 
+specific side constraints thanks to the use of CP rather than a specific 
+heuristic algorithm.
+\ignore{
+However, the solutions discovered by \serenepats{} later tend to be 
+much better both in precision and recall.
+The disadvantage is though that it comes at a cost of run time.
+In the end, which approach to use for the \relonto{} problem comes down to 
+trade-offs between precision, recall and time.
+}
+
+\ignore{
+%%%%%%%%future directions%%%%%%%%%%%%%
+% cold start problem and LOD
+One of the key limitations of our approach is the availability of training data 
+in the domain, which is often referred to as cold start problem.
+We consider leveraging the data from the Linked Open Cloud (LOD) which, on one 
+hand, leads to improved performance in the light of insufficient data and, on 
+the other hand, helps in publishing consistent Linked 
+Data~\cite{Taheriyan:Leveraging}. 
+As we have shown, the frequent graph pattern mining procedure 
+DIMSpan~\cite{petermann2017dimspan} which we use in our work is a highly 
+scalable approach compared to the technique based on SPARQL queries 
+from~\cite{Taheriyan:Leveraging}.
+
+%incorporate schema and ontology constraints
+Incorporating schema and ontology constraints may also help with the cold start 
+problem.
+Furthermore, it can provide means to improve disambiguation of properties.
+For example, it is hard for our system to differentiate between startDate and 
+endDate of the class Event.
+Having a constraint that startDate is before endDate might improve the mapping 
+in such situations.
+
+%complex matches
+Another interesting direction for further research is to recognize complex 
+matches.
+Our semantic labeling model in \serene{} as well as many others in the 
+literature~\cite{Pham:semantic,Ritze:matching} can learn only one-to-one 
+matches between attributes and properties in the ontology.
+\cite{Pinkel:rodi} show that such systems as BootOX can also handle efficiently 
+only one-to-one matches while their performance degrades considerably for $1:n$ 
+and $n:1$ matches.
+\karma{} \cite{taheriyan2016learning} offers its users to manually specify 
+transformations through Python scripts.
+\cite{Dhamankar:imap} offer a way to learn such transformations from the 
+historic data.
+This is one of the features which we want to incorporate into \serene{}.
+}
+\bibliographystyle{aaai}
+\bibliography{main}
+
+\ignore{
 %% sequentially found solutions and different weights for patterns
@@
 
-%% sequential solution
-In Fig.~\ref{fig:perfsol} we show how the performance of \serene{} changes 
-across sequentially found solutions.
-\chuffed{} successively finds better solutions in terms of Eq. \ref{EQ:obj}, 
-however, as we can see from the results,
-that does not translate directly into more precise semantic models.
-Additionally, we investigate how the performance is influenced if we introduce a weighting scheme on the patterns,
-i.e., costs of patterns are scaled by a factor.
-In Fig.~\ref{fig:perf} we use a scaling factor 1 
-for pattern costs.
-Fig.~\ref{fig:perfsol} demonstrates that by using scaling factors 5, 10 or 20 
-for patterns costs from the museum domain we can generate semantic models which 
-are almost 90\% in precision and recall.
-This is a 20\% improvement in precision compared to the first solution found by 
-\serenepats{} and a 10\% improvement both in precision and recall for the 
-first solution from \serene{}.
-
-Yet such improvement comes at a cost in run time.
-On average, we have observed that \serene{} yields very good results already 
-with the first solution found.
-\serenepats{}, on the other hand, produces considerably better solutions with 
-scaled pattern costs and sequential solutions.
-However, the sequential solutions are not always better, and hitting the 
-optimal solution may take hours.
-
-We have also observed that \serenepats{} manages to find the ground truth on 
-many instances among its sequential solutions, but again it takes much more 
-time.
-
-% change in performance if we look at sequentially found solutions
-% only leave-one-out for museum domain with 15s timeout for chuffed
-\npr{not sure whether Fig.~\ref{fig:loo} is needed}
-\begin{figure}\small
-\begin{tikzpicture}\small
-\pgfplotsset{
-    scale only axis,
-    small,
-    xmin=0, xmax=9
 }
 
-\begin{axis}[
-  axis y line*=left,
-  ymin=0.5, ymax=1,
-  xlabel=solution number,
-  ylabel=performance,
-  legend pos=south east,
-]
-\addplot[smooth,mark=x,red]
-  coordinates{
-    (0,0.776507549540743)(1,0.71093042754513)(2,0.822783653218436)(3,0.845760233918129)(4,0.879310344827586)(5,0.88695652173913)(6,0.885964912280702)(7,0.870689655172414)(8,0.878260869565217)(9,0.87719298245614)
-
-}; \label{plot_one}
-\addlegendentry{precision}
-\addplot[smooth,mark=*,green]
-  coordinates{
-    (0,0.773180507486795)(1,0.677202255831871)(2,0.805899400726987)(3,0.838122605363985)(4,0.879310344827586)(5,0.879310344827586)(6,0.870689655172414)(7,0.870689655172414)(8,0.870689655172414)(9,0.862068965517241)
-}; \label{plot_two}
-\addlegendentry{recall}
-\end{axis}
-
-\begin{axis}[
-  axis y line*=right,
-  axis x line=none,
-  ymin=0, ymax=15,
-  legend pos=south east,
-  ylabel=time (s)
-]
-\addlegendimage{/pgfplots/refstyle=plot_one}\addlegendentry{precision}
-\addlegendimage{/pgfplots/refstyle=plot_two}\addlegendentry{recall}
-\addplot[smooth,mark=square,blue]
-  coordinates{
-    (0,0.894338290115883)(1,2.39426428574782)(2,6.89703391393025)(3,10.3563708686829)(4,9.87668780326843)(5,9.92719115257263)(6,10.4045292949677)(7,14.3818371582031)(8,14.4026180458069)(9,14.8023208427429)
-}; \addlegendentry{time}
-\end{axis}
-\end{tikzpicture}
-\caption{Performance of \emph{serene} for leave-one-out strategy on the museum domain.}\label{fig:loo}
-\end{figure}
-
-\npr{Maybe some words on how optimal solution found by chuffed relates to the ground truth?}
-
-\section{Related Work \label{SEC:pw}}
-
-Relational data sources are still one of the most popular ways to store enterprise or Web data, however, the issue with relational schema is the lack of a well-defined semantic description.
-A common ontology provides a way to represent the meaning of a relational schema and can facilitate the integration of heterogeneous data sources within a domain.
-Indicating semantic correspondences manually might be appropriate if only few data sources need to be integrated, however, it becomes tedious with the growing number of heterogeneous schemata.
-Hence, automatic or semi-automatic approaches for relational-to-ontology schema mapping are being actively developed.
-
-The majority of approaches to solve the \relonto{} mapping problem are based on 
-heuristic rules and alignment of constraints specified within relational 
-schemata and ontologies.
-A very comprehensive overview and comparison of existing mapping generation tools based on this approach is given in~\cite{Pinkel:rodi} and~\cite{Spanos:semweb}.
-As examples, there are BootOX~\cite{Jimenez:Bootox}, MIRROR~\cite{Luciano:Mirror} and  ontop~\cite{Fagin:Clio}.
-Crudely speaking, these tools first apply a default direct mapping specified by the W3C.
-Further, the default ontology is enriched by using explicit and implicit schema constraints.
-Finally, ontology alignment techniques are applied to match the default ontology to the target ontology.
-The main advantage of these systems is the ability to run in a fully automatic setting.
-Our approach is complementary to the approaches from this group and at its current stage is semi-automatic.
-However, constraint programming offers a convenient framework to incorporate integrity constraints specified either within relational or ontological schema as additional constraints to govern the search for the solution.
-This opens an interesting direction for further research to develop an automatic system.
-
-A major issue with fully automatic systems is though that constraints may be 
-inconsistent or absent completely, e.g., data from Web services or tables on 
-the Web.
-To overcome this issue, we can apply ML techniques.
-\cite{Limaye:Annotating} design a system to annotate web tables with entities for cell values, semantic labels for attributes and relationships for binary combinations of attributes.
-As in our approach, they decompose the process of mapping into two main stages: semantic labeling and finding relationships between matched semantic labels.
-\cite{Limaye:Annotating} enrich their data sources by using YAGO.
-\cite{Mulwad:Semantic} extend this approach by leveraging information from Wikitology Knowledge Base (KB).
-\cite{Venetis:Recovering} develop a scalable approach to recover the semantics of Web tables by incorporating data from the isA database KB.
-\cite{Ritze:matching}, on the other hand, use DBPedia as their KB.
-%extract additional data from knowledge bases to assign a semantic label to an attribute.
-Hence, these approaches are limited to domains well represented in those knowledge bases.
-Also, they are not able to find the relation between attributes in the table if there is no direct connection between the attributes.
-Our approach, on the other hand, allows a model to be trained on any data and can infer complex semantic paths which might exist between attributes.
-However, it might be further bootstrapped by leveraging external knowledge bases.
-This is especially beneficial at the start when the system does not have sufficient training data.
-
-As mentioned above, the approaches for mapping Web tables also perform semantic labeling.
-They design various similarity metrics for attribute names and values.
-However, they disregard the attributes which are not matched to the ontology (the so-called \emph{unknown} set of attributes) which are especially abundant on the Web~\cite{Ritze:matching}\cite{Pham:semantic}.
-It is clear that we cannot directly speak about similarity for unmatched attributes, since they are rather dissimilar from known semantic types.
-That is why we have developed a new approach for semantic labeling which can efficiently handle the \emph{unknown} class.
-We demonstrate its efficiency by comparing against the state-of-the-art approach DSL~\cite{Pham:semantic}.
-
-We build upon the work of~\cite{taheriyan2016learning} and use their ideas for the construction of the alignment graph.
-The only difference is that we introduce the \emph{unknown} and \emph{root} class nodes and as many \emph{unknown} data nodes as there are attributes in the modeled data source.
-These nodes serve to capture the unmatched attributes from the source.
-Though we have modified Karma to treat these additional nodes as well, our approach outperforms Karma since we have additional constraints for these nodes and use an exact algorithm to solve the STP.
-\cite{taheriyan2016learning} treat the matching and STP parts of \relonto{} independently and use heuristic algorithms for both.
-We, on the other hand, use exact algorithms for both parts and address them within a unified CP model.
-
-In their follow up work, \cite{Taheriyan:Leveraging} suggest to use graph 
-patterns to boost the performance of their system.
-To perform semantic modeling in such scenario, \cite{Taheriyan:Leveraging} had to revise their algorithm by introducing additional heuristics.
-However, in our case we only had to add pattern variables and to modify the 
-objective function in the \minizinc{} model.
-No changes to the solver were required.
-This makes our system very convenient and opens directions for validating various additional constraints.
-Though our approach beats the state-of-the-art in the conducted experiments, it 
-is worth noting that the scalability of our approach is under question.
-The main argument why exact solution for STP is feasible in our setting is that 
-we map data sources to a domain-specific ontology which is expected to be 
-limited in its size.
-
-\section{Conclusion}
-In this paper we have introduced a new approach \serene{} to solve the 
-problem of relational-to-ontology schema mapping \relonto{}.
-We have also built its extension \serenepats{} which additionally uses 
-frequent graph patterns.
-Our experiments on two domains demonstrate that 
-\serene{} generates on average more consistent semantic models in terms of 
-precision and recall compared to the state-of-the-art approach \karma{}.
-\serenepats{} produces, on average, better semantic models in terms of 
-recall, however, its overall performance is rather mixed if we consider the 
-first produced model.
-However, the solutions discovered by \serenepats{} afterwards tend to be 
-much better both in precision and recall.
-The disadvantage is though that it comes at a cost of run time.
-In the end, which approach to use for \relonto{} problem comes down to 
-trade-offs between precision, recall and time.
-
-%%%%%%%%future directions%%%%%%%%%%%%%
-% cold start problem and LOD
-One of the key limitations of our approach is the availability of training data 
-in the domain, which is often referred to as cold start problem.
-We consider leveraging the data from the Linked Open Cloud (LOD) which, on one 
-hand, leads to improved performance in the light of insufficient data and, on 
-the other hand, helps in publishing consistent Linked 
-Data~\cite{Taheriyan:Leveraging}. 
-As we have shown, the frequent graph pattern mining procedure 
-DIMSpan~\cite{petermann2017dimspan} which we use in our work is a highly 
-scalable approach compared to the technique based on SPARQL queries 
-from~\cite{Taheriyan:Leveraging}.
-
-%incorporate schema and ontology constraints
-Incorporating schema and ontology constraints may also help with the cold start 
-problem.
-Furthermore, it can provide means to improve disambiguation of properties.
-For example, it is hard for our system to differentiate between startDate and 
-endDate of the class Event.
-Having a constraint that startDate is before endDate might improve the mapping 
-in such situations.
-
-%complex matches
-Another interesting direction for further research is to recognize complex 
-matches.
-Our semantic labeling model in \serene{} as well as many others in the 
-literature~\cite{Pham:semantic,Ritze:matching} can learn only one-to-one 
-matches between attributes and properties in the ontology.
-\cite{Pinkel:rodi} show that such systems as BootOX can also handle efficiently 
-only one-to-one matches while their performance degrades considerably for $1:n$ 
-and $n:1$ matches.
-\karma{} \cite{taheriyan2016learning} offers its users to manually specify 
-transformations through Python scripts.
-\cite{Dhamankar:imap} offer a way to learn such transformations from the 
-historic data.
-This is one of the features which we want to incorporate into \emph{serene}.
-
-\bibliographystyle{aaai}
-\bibliography{main}
-
-\newpage
-
-%%%
-% performance figures
-%%%
-%%% museum domain
-\begin{figure*}[ht]\small
-\pgfplotsset{
-    small,
-    %legend style={legend pos=north east}
-    legend style={
-        at={(0.01,0.01)},
-        anchor=south west,
-    },
-   }%
-\begin{minipage}[b]{.34\linewidth}
+\ignore{
+
+\begin{table}[ht]\small
   \centering
-\begin{tikzpicture}[baseline]
-\begin{axis}[
-		    xlabel={\emph{known semantic models}},
-		    ylabel={Performance},
-		    xmin=1, xmax=28,
-		    ymin=0.2, ymax=0.9,
-		    xtick={1,5,10,15,20,25,28},
-		    ytick={0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
-		    legend pos=south east,
-		    ymajorgrids=true,
-		    grid style=dashed
-		]
-
-		\addplot[
-		    color=blue,
-		    mark=square,
-		    ]
-		    coordinates {
-		    (1,0.517753313989873)(2,0.488688737671076)(3,0.51551313872799)(4,0.495118819099343)(5,0.527778910368045)(6,0.532176796157059)(7,0.566662366701066)(8,0.637110556563823)(9,0.685799234290614)(10,0.538089511412941)(11,0.621051710776405)(12,0.599367875333495)(13,0.670421793119162)(14,0.583598347357422)(15,0.623587223886899)(16,0.645277499838855)(17,0.653525664651826)(18,0.665572696108086)(19,0.670283086011174)(20,0.663804745401859)(21,0.633242908391853)(22,0.66099516031458)(23,0.644625119528521)(24,0.72069799334011)(25,0.737468671679198)(26,0.715572819263667)(27,0.727291592547725)(28,0.752558983666062)
-};
-		\addplot[
-		    color=red,
-		    mark=*,
-		    ]
-		    coordinates {
-		    (1,0.551714513556619)(2,0.682453503286837)(3,0.567702774084261)(4,0.646748619299324)(5,0.65492113250734)(6,0.701065228379203)(7,0.684439263401395)(8,0.700511175298951)(9,0.681034059961129)(10,0.685637253116215)(11,0.699316636125265)(12,0.697036509934383)(13,0.693463987436823)(14,0.704225209488367)(15,0.732978923190269)(16,0.724305489322319)(17,0.699459026247245)(18,0.716210056654951)(19,0.698987880687053)(20,0.733337516584389)(21,0.751908839952318)(22,0.75007040599401)(23,0.750592804644915)(24,0.814515445676703)(25,0.810987671748541)(26,0.817791638186375)(27,0.826003784931597)(28,0.809805364617137)
-};
-		\addplot[
-		    color=green,
-		    mark=x,
-		    ]
-		    coordinates {
-		    (1,0.598323207198336)(2,0.656420469232034)(3,0.551668227640311)(4,0.620327113896406)(5,0.623771074555817)(6,0.652894375155994)(7,0.625071981901494)(8,0.623287932111462)(9,0.601893257814311)(10,0.601192717220153)(11,0.602088073148115)(12,0.581718160067067)(13,0.570577347465439)(14,0.572274187082211)(15,0.581600752329829)(16,0.565774690293304)(17,0.5550594629542)(18,0.565097183518236)(19,0.524149694006153)(20,0.511449953555217)(21,0.576679655627024)(22,0.571388650336019)(23,0.546588180559473)(24,0.608169608169608)(25,0.608169608169608)(26,0.633066933066933)(27,0.634654234654234)(28,0.628305028305028)
-};
-		%\legend{karma,serene,serene-pats}
-
-		\end{axis}
-\end{tikzpicture}
-\subcaption{precision}\label{fig:museumprec}
-\end{minipage}%
-%
-\begin{minipage}[b]{.33\linewidth}
+  \caption{Run times (s) for all instances on the museum domain}\label{tab:time}
+		\begin{tabular}{cccc}
+		\hline
+		System & Mean & Min & Max\\
+		\hline
+		karma & 0.48 & 0.19 & 2.3  \\
+		serene & 0.53 & 0.01 & 8 \\
+		serene-pats & 0.97 & 0.01 & 20.3 \\
+		\hline
+		\end{tabular} 
+\end{table}
+\begin{table}[ht]\small
   \centering
-\begin{tikzpicture}[baseline]
-		\begin{axis}[
-		    xlabel={\emph{known semantic models}},
-		    %ylabel={recall},
-		    xmin=1, xmax=28,
-		    ymin=0.2, ymax=0.9,
-		    xtick={1,5,10,15,20,25,28},
-		    ytick={0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
-		    ymajorgrids=true,
-		    grid style=dashed,
-		    legend style={at={(0.5,1.1)},anchor=south, legend columns=-1}
-		]
-
-		\addplot[
-		    color=blue,
-		    mark=square,
-		    ]
-		    coordinates {
-		    (1,0.300191975130116)(2,0.387168789342702)(3,0.418780803201093)(4,0.414852632606256)(5,0.449767567691694)(6,0.454560596014134)(7,0.472473240503931)(8,0.552403403170667)(9,0.618322253509807)(10,0.45708434156857)(11,0.540246526073466)(12,0.523083348403042)(13,0.603209776078489)(14,0.509054454749254)(15,0.54874878365927)(16,0.577977828772285)(17,0.583053944903167)(18,0.591126557438254)(19,0.592414794781259)(20,0.591100946357877)(21,0.575601120513223)(22,0.587190134384184)(23,0.575949431206362)(24,0.655469912102772)(25,0.649409306042166)(26,0.64025693035835)(27,0.652378142479562)(28,0.666045239412379)
-};
-		\addplot[
-		    color=red,
-		    mark=*,
-		    ]
-		    coordinates {
-		    (1,0.517923133776792)(2,0.667141218952813)(3,0.56262382276875)(4,0.646790367442541)(5,0.651735815098987)(6,0.706388551614468)(7,0.698383379116542)(8,0.714984169630376)(9,0.700346244485205)(10,0.704664218197892)(11,0.717929077647748)(12,0.711690361988742)(13,0.707592621296799)(14,0.725417933239758)(15,0.760334088253952)(16,0.741766948274724)(17,0.726258869970838)(18,0.748428390280994)(19,0.723282293295816)(20,0.746991608671798)(21,0.769430045325921)(22,0.751719414109543)(23,0.756837646239269)(24,0.816669125330383)(25,0.816669125330383)(26,0.821841539123487)(27,0.824453869322024)(28,0.810608519269777)
-};
-		\addplot[
-		    color=green,
-		    mark=x,
-		    ]
-		    coordinates {
-		    (1,0.592810513524547)(2,0.704036744254136)(3,0.580300590445518)(4,0.665729761381935)(5,0.671789291034815)(6,0.721540066765983)(7,0.718258458411911)(8,0.728686409419572)(9,0.71549775963672)(10,0.719667189083217)(11,0.729479363111076)(12,0.713288181617252)(13,0.723866470903981)(14,0.739158277862456)(15,0.764121967041831)(16,0.755829992510182)(17,0.746486501253236)(18,0.758703555728573)(19,0.723655728717502)(20,0.729409784115667)(21,0.774654705722995)(22,0.768167419063295)(23,0.754561938768098)(24,0.828459715477971)(25,0.828459715477971)(26,0.838717192206036)(27,0.841329522404573)(28,0.833544778412933)
-};
-		 %\legend{karma,serene,serene-pats}
-
-		\end{axis}
-	\end{tikzpicture}
-\subcaption{recall}\label{fig:museumrec}
-\end{minipage}%
-%
-\begin{minipage}[b]{.33\linewidth}
-\centering
-\begin{tikzpicture}[baseline]
-\begin{axis}[
-		    xlabel={\emph{known semantic models}},
-		    %ylabel={time(s)},
-		    xmin=1, xmax=28,
-		    ymin=0.0, ymax=8.5,
-		    xtick={1,5,10,15,20,25,28},
-		    ytick={0.0,1,2,3,4,5,6,7,8},
-		    ymajorgrids=true,
-		    grid style=dashed,
-		    %legend pos=outer north east,
-		    %legend style={at={(0.5,-0.1)},anchor=north, legend columns=-1}
-		]
-
-		\addplot[
-		    color=blue,
-		    mark=square,
-		    ]
-		    coordinates {
-		    (1,0.268540382385254)(2,0.485812822977702)(3,0.346803307533264)(4,0.372188647588094)(5,0.367514610290527)(6,0.37602166334788)(7,0.376668055852254)(8,0.410835981369019)(9,0.422285079956055)(10,0.424292365709941)(11,0.439166347185771)(12,0.446258664131165)(13,0.46294093132019)(14,0.484450976053874)(15,0.489395022392273)(16,0.550653139750163)(17,0.543892900149027)(18,0.760240634282429)(19,0.529818336168925)(20,0.544886191685995)(21,0.576984961827597)(22,0.557323813438416)(23,0.563650608062744)(24,0.60092453956604)(25,0.626034975051881)(26,0.663434648513793)(27,0.692028045654297)(28,0.702148389816284)
-};
-		\addplot[
-		    color=red,
-		    mark=*,
-		    ]
-		    coordinates {
-		    (1,0.0175)(2,0.665)(3,0.585)(4,0.561666666666667)(5,0.62)(6,0.655)(7,0.605)(8,0.66)(9,0.655)(10,0.766666666666667)(11,0.783333333333333)(12,0.933333333333333)(13,0.901666666666667)(14,0.968333333333333)(15,0.956666666666667)(16,1.03333333333333)(17,1.34166666666667)(18,1.44666666666667)(19,1.30833333333333)(20,1.31333333333333)(21,1.27833333333333)(22,1.31333333333333)(23,1.28166666666667)(24,1.472)(25,1.526)(26,1.528)(27,1.642)(28,1.52)
-};
-		\addplot[
-		    color=green,
-		    mark=x,
-		    ]
-		    coordinates {
-		    (1,0.02)(2,0.696666666666667)(3,0.619166666666666)(4,0.67)(5,0.65)(6,0.64)(7,0.615833333333333)(8,0.674166666666667)(9,0.741666666666667)(10,0.8375)(11,0.9125)(12,1.62)(13,1.05)(14,1.94583333333333)(15,1.11916666666667)(16,2.85916666666667)(17,1.55583333333333)(18,1.53666666666667)(19,3.27)(20,1.399)(21,1.63833333333333)(22,1.66)(23,3.24181818181818)(24,3.64444444444444)(25,3.69777777777778)(26,2.343)(27,2.334)(28,2.373)
-};
-		 %\legend{karma,serene,serene-pats}
-
-		\end{axis}
-\end{tikzpicture}
-\subcaption{time (s)}\label{fig:museumtime}
-\end{minipage}%
-\caption{Average precision, recall and time on the museum domain for \relonto{} 
-systems with variable training set size.}\label{fig:perfmuseum}
-\end{figure*}
-
-%%% soccer domain
-\begin{figure*}[ht]\small
-\pgfplotsset{
-    small,
-    %legend style={legend pos=north east}
-    legend style={
-        at={(0.01,0.01)},
-        anchor=south west,
-    },
-   }%
-\begin{minipage}[b]{.34\linewidth}
-\centering
-\begin{tikzpicture}[baseline]
-\begin{axis}[
-		    xlabel={\emph{known semantic models}},
-		    ylabel={Performance},
-		    xmin=1, xmax=11,
-		    ymin=0.5, ymax=0.9,
-		    xtick={1,2,4,6,8,10,11},
-		    ytick={0.5,0.6,0.7,0.8,0.9,1},
-		    legend pos=south east,
-		    ymajorgrids=true,
-		    grid style=dashed
-		]
-
-		\addplot[
-		    color=blue,
-		    mark=square,
-		    ]
-		    coordinates {
-		    (1,0.635191626901633)(2,0.549997502815009)(3,0.675720834727361)(4,0.719693253328935)(5,0.759169846724195)(6,0.760054331456753)(7,0.800812140122402)(8,0.812192030050689)(9,0.799552066440611)(10,0.821470975418344)(11,0.785878855002637)
-		    };
-		\addplot[
-		    color=red,
-		    mark=*,
-		    ]
-		    coordinates {
-		    (1,0.676934852587026)(2,0.61473599870339)(3,0.723937079602602)(4,0.786238815638129)(5,0.777035817669233)(6,0.781984613615049)(7,0.81368099248534)(8,0.817013725291758)(9,0.816270530687007)(10,0.846744827831784)(11,0.852649148301322)
-		    };
-		\addplot[
-		    color=green,
-		    mark=x,
-		    ]
-		    coordinates {
-		    (1,0.66759959719914)(2,0.629014687197419)(3,0.692208378950833)(4,0.744652988406557)(5,0.773486992410165)(6,0.756607637648352)(7,0.803820434917082)(8,0.793054493090329)(9,0.792256229657042)(10,0.822093203062231)(11,0.828181360184871)
-		    };
-		%\legend{karma,serene,serene-pats}
-
-		\end{axis}
-\end{tikzpicture}
-\subcaption{precision}
-\end{minipage}%
-%
-\begin{minipage}[b]{.33\linewidth}
-\centering
-\begin{tikzpicture}[baseline]
-		\begin{axis}[
-		    xlabel={\emph{known semantic models}},
-		    %ylabel={recall},
-		    xmin=1, xmax=11,
-		    ymin=0.3, ymax=0.9,
-		    xtick={1,2,4,6,8,10,11},
-		    ytick={0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
-		    ymajorgrids=true,
-		    grid style=dashed,
-		    legend style={at={(0.5,1.1)},anchor=south, legend columns=-1}
-		]
-
-		\addplot[
-		    color=blue,
-		    mark=square,
-		    ]
-		    coordinates {
-		    (1,0.444761527680188)(2,0.372447158105053)(3,0.545528381345078)(4,0.596008831526073)(5,0.6499887923799)(6,0.643884492868159)(7,0.685035675993026)(8,0.702870161195933)(9,0.654001538724769)(10,0.685153350715964)(11,0.662999993217779)
-		    };
-		\addplot[
-		    color=red,
-		    mark=*,
-		    ]
-		    coordinates {
-		    (1,0.690636806043505)(2,0.613080486764697)(3,0.72563707600459)(4,0.780625908674911)(5,0.776616927805676)(6,0.779496772132888)(7,0.813459305700685)(8,0.813245834960899)(9,0.810586300672508)(10,0.84298404022542)(11,0.849899398175261)
-		    };
-		\addplot[
-		    color=green,
-		    mark=x,
-		    ]
-		    coordinates {
-		    (1,0.689786194666577)(2,0.655399210040359)(3,0.719915653815835)(4,0.776231754935929)(5,0.802770096610387)(6,0.787355423564135)(7,0.838616573256072)(8,0.82175912881902)(9,0.821414409345444)(10,0.851497334083541)(11,0.85656084018153)
-		    };
-		 \legend{karma,serene,serene-pats}
-
-		\end{axis}
-	\end{tikzpicture}
-\subcaption{recall}
-\end{minipage}%
-%
-\begin{minipage}[b]{.33\linewidth}
-\centering
-\begin{tikzpicture}[baseline]
-\begin{axis}[
-		    xlabel={\emph{known semantic models}},
-		    %ylabel={time(s)},
-		    xmin=1, xmax=11,
-		    ymin=0.0, ymax=0.3,
-		    xtick={1,2,4,6,8,10,11},
-		    ytick={0.0,0.1,0.2},
-		    ymajorgrids=true,
-		    grid style=dashed,
-		    %legend pos=outer north east,
-		    %legend style={at={(0.5,-0.1)},anchor=north, legend columns=-1}
-		]
-
-		\addplot[
-		    color=blue,
-		    mark=square,
-		    ]
-		    coordinates {
-		    (1,0.107354099100286)(2,0.137003461519877)(3,0.163627962271372)(4,0.17774627606074)(5,0.179288367430369)(6,0.183507978916168)(7,0.189805428187052)(8,0.191188136736552)(9,0.196139633655548)(10,0.200133164723714)(11,0.218581974506378)
-		    };
-		\addplot[
-		    color=red,
-		    mark=*,
-		    ]
-		    coordinates {
-		    (1,0.0595748017051003)(2,0.0895205450057983)(3,0.0976518734296163)(4,0.103216880957286)(5,0.108438626130422)(6,0.115763804117839)(7,0.125697635014852)(8,0.118865826924642)(9,0.119359710216522)(10,0.123752357959747)(11,0.153613630930583)
-		    };
-		\addplot[
-		    color=green,
-		    mark=x,
-		    ]
-		    coordinates {
-		    (1,0.0687879033522172)(2,0.0874820310419256)(3,0.103948153495789)(4,0.104214943885803)(5,0.115242712974548)(6,0.126150580406189)(7,0.122052125063809)(8,0.128753701051076)(9,0.129606107076009)(10,0.13165650844574)(11,0.142413517634074)
-		    };
-		 %\legend{karma,serene,serene-pats}
-
-		\end{axis}
-\end{tikzpicture}
-\subcaption{time (s)}
-\end{minipage}%
-\caption{Average precision, recall and time on the soccer domain for \relonto{} 
-systems with variable training set size.}
-\end{figure*}
+  \caption{Sizes of integration graphs on the museum domain}\label{tab:size}
+		\begin{tabular}{cccc}
+		\hline
+		 & Mean & Min & Max\\
+		\hline
+		number of nodes & 87.8 & 29 & 168  \\
+		number of edges & 1129.4 & 88 & 5629 \\
+		\hline
+		\end{tabular} 
+\end{table}
+}
 

### 2017-08-24 stp/paper_aaai/main.tex
one last comment
added citeasnoun command to remove parenthesis of citations

@@
 \newcommand{\ignore}[1]{}
+
+\newcommand{\citeasnoun}[1]{\citeauthor{#1}~\shortcite{#1}}
 
@@
 (`\tikz{ \node[class] () at (0,0)  {};}' are Classes, `\tikz{ \path[hasaC,->] 
-(0,1) -- (3ex,1);}' means ``has a Class property'', 
+(0,1) -- (3ex,1);}' means ``has an object property'', 
 `\tikz{ \path[hasaA,decoration={post length=0}] (0,0) edge[decorate] (3ex,0);}' 
-means ``has 
-a data 
-property'' and 
-`\tikz{ \path[isa,->] (0,1) -- (3ex,1);}' means ``is a'' ). Based on 
-\cite{Taheriyan2013}.
+means ``has a data property'' and 
+`\tikz{ \path[isa,->] (0,1) -- (3ex,1);}' means ``is a'' ). Example by
+\citeasnoun{Taheriyan2013}.
 }
@@
 remove some of the matches based on heuristics in order to simplify the task of 
-finding the semantic model.
+finding the semantic model. \ddg{is this last paragraph true?}
 
@@
 schemata and ontologies.
-A very comprehensive overview and comparison of existing mapping generation tools based on this approach is given in~\cite{Pinkel:rodi} and~\cite{Spanos:semweb}.
+A very comprehensive overview and comparison of existing mapping generation 
+tools based on this approach is given by~\citeasnoun{Pinkel:rodi}
+and~\citeasnoun{Spanos:semweb}.
 As examples, there are BootOX~\cite{Jimenez:Bootox}, MIRROR~\cite{Luciano:Mirror} and  ontop~\cite{Fagin:Clio}.
@@
 To overcome this issue, we can apply ML techniques.
-\cite{Limaye:Annotating} design a system to annotate web tables with entities for cell values, semantic labels for attributes and relationships for binary combinations of attributes.
+\citeasnoun{Limaye:Annotating} design a system to annotate web tables with 
+entities for cell values, semantic labels for attributes and relationships for 
+binary combinations of attributes.
 As in our approach, they decompose the process of mapping into two main stages: semantic labeling and finding relationships between matched semantic labels.
-\cite{Limaye:Annotating} enrich their data sources by using YAGO.
-\cite{Mulwad:Semantic} extend this approach by leveraging information from Wikitology Knowledge Base (KB).
-\cite{Venetis:Recovering} develop a scalable approach to recover the semantics of Web tables by incorporating data from the isA database KB.
-\cite{Ritze:matching}, on the other hand, use DBPedia as their KB.
+\citeasnoun{Limaye:Annotating} enrich their data sources by using YAGO.
+\citeasnoun{Mulwad:Semantic} extend this approach by leveraging information 
+from Wikitology Knowledge Base (KB).
+\citeasnoun{Venetis:Recovering} develop a scalable approach to recover the 
+semantics of Web tables by incorporating data from the isA database KB.
+\citeasnoun{Ritze:matching}, on the other hand, use DBPedia as their KB.
 %extract additional data from knowledge bases to assign a semantic label to an attribute.
@@
 
-We build upon the work of~\cite{taheriyan2016learning} and use their ideas for the construction of the alignment graph.
+We build upon the work of \citeasnoun{taheriyan2016learning} and use their 
+ideas for the construction of the alignment graph.
 The only difference is that we introduce the \emph{unknown} and \emph{root} class nodes and as many \emph{unknown} data nodes as there are attributes in the modeled data source.

### 2017-08-29 stp/paper_aaai/main.tex
Change result charts, add missing ref, reply comments

@@
 present a new approach that combines Machine Learning and 
-Constraint Programming techniques, by modelling the data integration problem as 
+Constraint Programming techniques, by modeling the data integration problem as 
 a Steiner Tree Problem in a weighted graph. We show that through this approach 
@@
 shown in Fig.~\ref{FIG:onto} and \ref{FIG:sem}.
-The semantic model may have several instances of the same ontology class or 
-object property.
+The semantic model may have several instances of the same ontology class, that is why class nodes are enumerated.
 
@@
 \begin{scope}
-	\node[class] (pe) at (3,0)  {\small Person};
-	\node[class] (co) at (6,0) {\small Org.};
-	\node[class] (ci) at (1,0) {\small City};
-	\node[class] (st) at (-1,0) {\small State};
-
-	\node[data] (pen) at (2.5,-0.7) {\scriptsize Person.name};
-	\node[data] (peb) at (4.3,-0.7) {\scriptsize Person.birthDate};
-	\node[data] (cin) at (1,-0.7) {\scriptsize City.name};
-	\node[data] (stn) at (-1,-0.7) {\scriptsize State.name};
-	\node[data] (con) at (6,-0.7) {\scriptsize Org.name};
+	\node[class] (pe) at (3,0)  {\small Person1};
+	\node[class] (co) at (6,0) {\small Org.1};
+	\node[class] (ci) at (1,0) {\small City1};
+	\node[class] (st) at (-1,0) {\small State1};
+
+	\node[data] (pen) at (2.5,-0.7) {\scriptsize Person1.name};
+	\node[data] (peb) at (4.3,-0.7) {\scriptsize Person1.birthDate};
+	\node[data] (cin) at (1,-0.7) {\scriptsize City1.name};
+	\node[data] (stn) at (-1,-0.7) {\scriptsize State1.name};
+	\node[data] (con) at (6,-0.7) {\scriptsize Org1.name};
 
@@
 \begin{scope}[yshift=-40]
-	\node[class] (pl) at (-1,0)  {\small City};
-	\node[class] (pe) at (3,0)  {\small Person};
-	\node[class] (co) at (1,0) {\small Org.};
-	\node[class] (ev) at (6,0) {\small Event};
-
-	\node[data] (pen) at (2.5,-0.7) {\scriptsize Person.name};
-	\node[data] (evs) at (4.2,-0.7) {\scriptsize Event.startDate};
-	\node[data] (eve) at (6,-0.7) {\scriptsize Event.endDate};
-	\node[data] (con) at (1,-0.7) {\scriptsize Org.name};
-	\node[data] (pln) at (-1,-0.7) {\scriptsize City.name};
+	\node[class] (pl) at (-1,0)  {\small City2};
+	\node[class] (pe) at (3,0)  {\small Person2};
+	\node[class] (co) at (1,0) {\small Org.2};
+	\node[class] (ev) at (6,0) {\small Event1};
+
+	\node[data] (pen) at (2.5,-0.7) {\scriptsize Person2.name};
+	\node[data] (evs) at (4.2,-0.7) {\scriptsize Event1.startDate};
+	\node[data] (eve) at (6,-0.7) {\scriptsize Event1.endDate};
+	\node[data] (con) at (1,-0.7) {\scriptsize Org2.name};
+	\node[data] (pln) at (-1,-0.7) {\scriptsize City2.name};
 
@@
 the known semantic type with the corresponding feature vector.
-The feature vector includes characteristics of the attribute such as a number 
-of whitespaces and other special characters, statistics of values in the column 
-(e.g, mean/max/min string length and numeric statistics) and more. A full 
-list can be found in appendix \ddg{Apendix!}
+The feature vector, among others, includes characteristics
+such as a number 
+of whitespaces and other special characters, statistics of 
+values in the column 
+(e.g, mean/max/min string length and numeric statistics), etc. 
+A full list can be found in appendix \ddg{Apendix!}
+\npr{If I remove entropy descr, we are perfectly within page limit}
+%\ignore{
 One of the important features characterising information content of an attribute is Shannon's entropy of the attribute's concatenated rows.
@@
 Finally, we add the 100-dimensional vector of $p_i$ to the attribute feature vector.
+%}
 We also compute a set of features based on similarity metrics inspired by state-of-the-art works~\cite{Pham:semantic} or~\cite{Ritze:matching}.
@@
 remove some of the matches based on heuristics in order to simplify the task of 
-finding the semantic model. \ddg{is this last paragraph true?}
+finding the semantic model. 
+%\ddg{is this last paragraph true?} \npr{yes}
 
@@
 	\node[class] (ci1) at (1,0) {\small City1};
-	\node[class] (st1) at (-1,0) {\small State};
+	\node[class] (st1) at (-1,0) {\small State1};
 
@@
 	\node[data] (cin) at (0.7,0.7) {\scriptsize City1.name};
-	\node[data] (stn) at (-1,0.7) {\scriptsize State.name};
+	\node[data] (stn) at (-1,0.7) {\scriptsize State1.name};
 	\node[data] (con) at (6,0.7) {\scriptsize Org1.name};
@@
 	\node[class] (co2) at (1,0+\ysh) {\small Org.2};
-	\node[class] (ev2) at (6,0+\ysh) {\small Event};
+	\node[class] (ev2) at (6,0+\ysh) {\small Event1};
 
 	\node[data] (pen) at (2.3,-0.7+\ysh) {\scriptsize Person2.name};
-	\node[data] (evs) at (4.2,-0.7+\ysh) {\scriptsize Event.startDate};
-	\node[data] (eve) at (6,-0.7+\ysh) {\scriptsize Event.endDate};
+	\node[data] (evs) at (4.2,-0.7+\ysh) {\scriptsize Event1.startDate};
+	\node[data] (eve) at (6,-0.7+\ysh) {\scriptsize Event1.endDate};
 	\node[data] (con) at (0.7,-0.7+\ysh) {\scriptsize Org2.name};
@@
 	{\small 
-	Place};
+	Place1};
 
@@
 
-\npr{reformulate for typed directed multigraphs and example based on Fig3}
+%\npr{reformulate for typed directed multigraphs and example based on Fig3}
 In our context, patterns are typed directed graphs.
 We mine these patterns from the set of semantic models in the training set $S_T$.
-This is known as Transactional Frequent Graph Pattern Mining, which generalizes 
+This is known as Transactional Frequent Graph Pattern Mining, which includes
 the subgraph isomorphism problem, known to be NP-complete.
-The frequency of a pattern is an anti-monotonous measure, meaning that bigger 
-patterns will have lower supports than their subgraphs. \ddg{Define support}
-We solve this pattern mining task with the tool DIMSpan \cite{petermann2017dimspan} which adapts gSpan~\cite{yan2002gspan} pruning techniques to the typed graphs and uses Apache Flink for scalability.
+The frequency of a pattern is the number of semantic models which contain at least one subgraph isomorphic to the pattern
+The \emph{support} of the pattern is calculated as its frequency relative to the number of semantic models.
+This is an anti-monotonous measure, meaning that bigger 
+patterns will have lower supports than their subgraphs.
+% \ddg{Define support}
+We solve the pattern mining task with the tool DIMSpan \cite{petermann2017dimspan} which adapts gSpan~\cite{yan2002gspan} pruning techniques to the typed graphs and uses Apache Flink for scalability.
 We obtain patterns of size up to 6 in under 4 minutes for the biggest instances 
 in our evaluation framework.
+Hence, this pattern mining procedure is a highly 
+scalable approach compared to the technique based on SPARQL queries 
+from~\cite{Taheriyan:Leveraging}.
 \npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe 
@@
 \begin{tikzpicture}
-	\node[class, rectangle, rounded corners] (CLASS) at (0,0) { \small{Class 
+	\node[class, rectangle, rounded corners] (CLASS) at (0,0) { \small{ 
 	Nodes of Alignment Graph}};
 
-	\node[data] (stn1) at (-3.9,-0.9) {\scriptsize S.n};
+	\node[data] (stn1) at (-3.9,-0.9) {\scriptsize S1.n};
 	\node[data] (cin1) at (-3.1,-0.9) {\scriptsize C1.n};
@@
 	\node[data] (pen2) at (2.3,-1+\ysh) {\scriptsize P2.n};
-	\node[data] (evs2) at (3.1,-1+\ysh) {\scriptsize E.s};
-	\node[data] (eve2) at (3.9,-1+\ysh) {\scriptsize E.e};
+	\node[data] (evs2) at (3.1,-1+\ysh) {\scriptsize E1.s};
+	\node[data] (eve2) at (3.9,-1+\ysh) {\scriptsize E1.e};
 
@@
 undirected edges). 
+\npr{This is not true: semantic models are directed. can we soften the statement here? direction of links can change semantics}
 
@@
 
-It is therefore natural to model this a STP with side constraints, since the 
+It is therefore natural to model this problem as a STP with side constraints, since the 
 two first requirements imply that $T^\star$ is a Steiner Tree of the 
@@
 \cite{Pham:semantic} or HTML tables \cite{Ritze:matching}.
-In current systems, these columns are removed in a process that requires 
-extra time and effort as this is typically done manually in the real world.
+In current systems, these columns are removed in a pre-processing step as a manual effort.
 
@@
 and build  a semantic model as usual. 
-Then, to maintain connectedness of the 
+To maintain connectedness of the 
 Steiner tree, the \emph{unknown} node and one of the other selected Class nodes 
@@
 Note that if all attributes find a 
-match, then both the \emph{unknown} and \emph{root} nodes won't be selected in 
+match, then both the \emph{unknown} and \emph{root} nodes will not be selected in 
 the Steiner tree and the normal behavior will take place.
-\ddg{Explain the weights of the edges introduced by the unknown nodes}
+The weights of the edges between these special nodes are
+assigned the same way as for the rest of the edges.
+%\ddg{Explain the weights of the edges introduced by the unknown nodes}
 
@@
 not based on the notion of similarity.
-\npr{Good enough explanation?}
+%\npr{Good enough explanation?}
 
@@
 		    coordinates {
-		    (1,0.517753313989873)(2,0.488688737671076)(3,0.51551313872799)(4,0.495118819099343)(5,0.527778910368045)(6,0.532176796157059)(7,0.566662366701066)(8,0.637110556563823)(9,0.685799234290614)(10,0.538089511412941)(11,0.621051710776405)(12,0.599367875333495)(13,0.670421793119162)(14,0.583598347357422)(15,0.623587223886899)(16,0.645277499838855)(17,0.653525664651826)(18,0.665572696108086)(19,0.670283086011174)(20,0.663804745401859)(21,0.633242908391853)(22,0.66099516031458)(23,0.644625119528521)(24,0.72069799334011)(25,0.737468671679198)(26,0.715572819263667)(27,0.727291592547725)(28,0.752558983666062)
+		    (1,0.514832366157273)(2,0.520674170412197)(3,0.521026469009226)(4,0.497426082405143)(5,0.564688628672475)(6,0.55713561774315)(7,0.535076529852905)(8,0.560010216333054)(9,0.584508074744603)(10,0.546065110600816)(11,0.572489269396419)(12,0.564125297742057)(13,0.569829859460611)(14,0.543552852090991)(15,0.549734788036156)(16,0.558412528664919)(17,0.560598355931883)(18,0.607717979536758)(19,0.599585378842078)(20,0.612366200965436)(21,0.593021913264951)(22,0.623428063505196)(23,0.584747451140003)(24,0.605908308460775)(25,0.62089087544623)(26,0.607245006682788)(27,0.616141552483661)(28,0.623256309823247)
 };
@@
 		    coordinates {
-		    (1,0.551714513556619)(2,0.682453503286837)(3,0.567702774084261)(4,0.646748619299324)(5,0.65492113250734)(6,0.701065228379203)(7,0.684439263401395)(8,0.700511175298951)(9,0.681034059961129)(10,0.685637253116215)(11,0.699316636125265)(12,0.697036509934383)(13,0.693463987436823)(14,0.704225209488367)(15,0.732978923190269)(16,0.724305489322319)(17,0.699459026247245)(18,0.716210056654951)(19,0.698987880687053)(20,0.733337516584389)(21,0.751908839952318)(22,0.75007040599401)(23,0.750592804644915)(24,0.814515445676703)(25,0.810987671748541)(26,0.817791638186375)(27,0.826003784931597)(28,0.809805364617137)
+		    (1,0.582318872699517)(2,0.628627876837901)(3,0.609932492636812)(4,0.610866990370165)(5,0.674948143747368)(6,0.679265687227716)(7,0.70619376828754)(8,0.715634190728361)(9,0.703653042970976)(10,0.714021677870418)(11,0.718515409501215)(12,0.72006314095146)(13,0.714534069979324)(14,0.739946209262199)(15,0.741872691279687)(16,0.759026528736177)(17,0.748648620477246)(18,0.765437399193282)(19,0.749182097087044)(20,0.764528564841459)(21,0.757553110476648)(22,0.753597067073318)(23,0.757298299109379)(24,0.778783553420146)(25,0.765628808466358)(26,0.785689475530164)(27,0.768145186235277)(28,0.783815747353212)
 };
@@
 		    coordinates {
-		    (1,0.598323207198336)(2,0.656420469232034)(3,0.551668227640311)(4,0.620327113896406)(5,0.623771074555817)(6,0.652894375155994)(7,0.625071981901494)(8,0.623287932111462)(9,0.601893257814311)(10,0.601192717220153)(11,0.602088073148115)(12,0.581718160067067)(13,0.570577347465439)(14,0.572274187082211)(15,0.581600752329829)(16,0.565774690293304)(17,0.5550594629542)(18,0.565097183518236)(19,0.524149694006153)(20,0.511449953555217)(21,0.576679655627024)(22,0.571388650336019)(23,0.546588180559473)(24,0.608169608169608)(25,0.608169608169608)(26,0.633066933066933)(27,0.634654234654234)(28,0.628305028305028)
+		    (1,0.58839328678273)(2,0.607758082933845)(3,0.58226798181609)(4,0.591999006493134)(5,0.636658963454311)(6,0.609378189548976)(7,0.65198352100422)(8,0.639237266085298)(9,0.646381524706678)(10,0.658451931832802)(11,0.651981340743635)(12,0.639000646239548)(13,0.638100886472842)(14,0.652718769812707)(15,0.65270159785683)(16,0.665279840041019)(17,0.663658936249597)(18,0.675430261986635)(19,0.662138443878962)(20,0.662006475337153)(21,0.664124779844034)(22,0.661879115723149)(23,0.670248656767086)(24,0.677264055645277)(25,0.676979334359473)(26,0.687880411346927)(27,0.67459653454876)(28,0.68627902145454)
 };
@@
 		    coordinates {
-		    (1,0.300191975130116)(2,0.387168789342702)(3,0.418780803201093)(4,0.414852632606256)(5,0.449767567691694)(6,0.454560596014134)(7,0.472473240503931)(8,0.552403403170667)(9,0.618322253509807)(10,0.45708434156857)(11,0.540246526073466)(12,0.523083348403042)(13,0.603209776078489)(14,0.509054454749254)(15,0.54874878365927)(16,0.577977828772285)(17,0.583053944903167)(18,0.591126557438254)(19,0.592414794781259)(20,0.591100946357877)(21,0.575601120513223)(22,0.587190134384184)(23,0.575949431206362)(24,0.655469912102772)(25,0.649409306042166)(26,0.64025693035835)(27,0.652378142479562)(28,0.666045239412379)
+		    (1,0.367995759495435)(2,0.43314958257729)(3,0.465102732953193)(4,0.446507314880989)(5,0.506469092210478)(6,0.506789578789452)(7,0.477080991784194)(8,0.503937397649502)(9,0.534229842849261)(10,0.492507267102593)(11,0.515796460946058)(12,0.509165531142068)(13,0.516097781643373)(14,0.488160651098756)(15,0.496282029692244)(16,0.504382820425249)(17,0.503923406733149)(18,0.552759367968562)(19,0.540550359776821)(20,0.554759177609889)(21,0.53688314428863)(22,0.561628603103704)(23,0.525601546354885)(24,0.548689620179471)(25,0.559372079917562)(26,0.54849327148799)(27,0.558777769863011)(28,0.561036686567106)
 };
@@
 		    coordinates {
-		    (1,0.517923133776792)(2,0.667141218952813)(3,0.56262382276875)(4,0.646790367442541)(5,0.651735815098987)(6,0.706388551614468)(7,0.698383379116542)(8,0.714984169630376)(9,0.700346244485205)(10,0.704664218197892)(11,0.717929077647748)(12,0.711690361988742)(13,0.707592621296799)(14,0.725417933239758)(15,0.760334088253952)(16,0.741766948274724)(17,0.726258869970838)(18,0.748428390280994)(19,0.723282293295816)(20,0.746991608671798)(21,0.769430045325921)(22,0.751719414109543)(23,0.756837646239269)(24,0.816669125330383)(25,0.816669125330383)(26,0.821841539123487)(27,0.824453869322024)(28,0.810608519269777)
+		    (1,0.568526176536315)(2,0.612789529917517)(3,0.603758658205161)(4,0.611122761022995)(5,0.679226888229885)(6,0.689545922126768)(7,0.718173517817693)(8,0.72049339757837)(9,0.712025690044822)(10,0.719376710211083)(11,0.719738340274138)(12,0.727571790593847)(13,0.718652567615389)(14,0.742375410864123)(15,0.744789115461273)(16,0.761896901012414)(17,0.753562034501087)(18,0.768934123583718)(19,0.753381510225111)(20,0.767814904456983)(21,0.758472395730288)(22,0.753685690354242)(23,0.754906882661518)(24,0.772285894201019)(25,0.771337684854641)(26,0.782427299035871)(27,0.762524256400432)(28,0.778430045086962)
 };
@@
 		    coordinates {
-		    (1,0.592810513524547)(2,0.704036744254136)(3,0.580300590445518)(4,0.665729761381935)(5,0.671789291034815)(6,0.721540066765983)(7,0.718258458411911)(8,0.728686409419572)(9,0.71549775963672)(10,0.719667189083217)(11,0.729479363111076)(12,0.713288181617252)(13,0.723866470903981)(14,0.739158277862456)(15,0.764121967041831)(16,0.755829992510182)(17,0.746486501253236)(18,0.758703555728573)(19,0.723655728717502)(20,0.729409784115667)(21,0.774654705722995)(22,0.768167419063295)(23,0.754561938768098)(24,0.828459715477971)(25,0.828459715477971)(26,0.838717192206036)(27,0.841329522404573)(28,0.833544778412933)
+		    (1,0.596084829534507)(2,0.640760186457491)(3,0.62082780704382)(4,0.636003942692136)(5,0.692664734541117)(6,0.701974230777832)(7,0.728319438123534)(8,0.750185705723487)(9,0.736888107321033)(10,0.742404159647386)(11,0.743250566844835)(12,0.732378757282814)(13,0.729581368486718)(14,0.7525692913614)(15,0.751549245497265)(16,0.767850111275969)(17,0.762600014025882)(18,0.778934826315818)(19,0.764342969952451)(20,0.767198788345341)(21,0.761867162993121)(22,0.765611676236013)(23,0.768814394670878)(24,0.779481328123055)(25,0.783142085550363)(26,0.789525770002408)(27,0.774378390471089)(28,0.790117094780008)
 };
@@
 However, constraint programming offers a convenient framework to incorporate integrity constraints specified either within relational or ontological schema as additional constraints to govern the search for the solution.
-This opens an interesting direction for further research to develop an automatic system.
+This opens an interesting direction for further research.
 
@@
 \serenepats{} produces, on average, better semantic models in terms of 
-recall, and it's precision can be enhanced by adding a scaling factor for 
+recall, and its precision can be enhanced by adding a scaling factor for 
 pattern costs.
@@
 \bibliography{main}
+
+\newpage
+
+Below are the description of features used by \serene{} semantic model.
+Note that features are extracted from the name and values of each attribute in the data source.
+Thus, all the data from a single column is reduced to some feature
+vector of the concatenation of values computed by the extractors below.
+
+We refer to a single value from the column as an entry.
+E.g.
+
+\begin{table}[!ht]\small
+  \centering
+  \caption{Example table.}
+  	\label{tab:semlab}
+  	\begin{tabular}{ccc} 
+  		\hline
+		Person & Age & Gender \\
+  		\hline
+	    John & 20 & M\\
+    	Jane & 30 & F\\
+  		\hline
+		\end{tabular} 
+%\vspace*{-3mm}
+\end{table}
+
+From the table above, John is an entry of the column Person.
+
+The following feature extractors produce a scalar value:
+\begin{enumerate}
+\item num-unique-vals      : A simple count of unique entries of a column
+\item prop-unique-vals     : The proportion of unique entries of a column. 
+\item prop-missing-vals    : The proportion of all missing/empty entries from all entries in a column.
+\item ratio-alpha-chars    : The average of the proportion of alphabetic characters from each entry.
+\item prop-numerical-chars : The average of the proportion of numeric characters from each entry.
+\item prop-whitespace-chars       : The average of the proportion of whitespace characters from each entry.
+\item prop-entries-with-at-sign   : The proportion of entries with an '@' sign.
+\item prop-entries-with-hyphen    : The proportion of entries with a '-'.
+\item prop-range-format           : The proportion of entries which follow some numerical range format: ([0-9]+)-([0-9]+).
+\item is-discrete                 : A binary indicator if the column entries are discrete.
+\item entropy-for-discrete-values : The entropy of the entries of a column.
+\item shannon-entropy             : Shannon's entropy for the vocabulary specified in the description of the feature 'char-dist-features'
+\end{enumerate}
+
+The following feature extractors produce a vector value.
+Some of these are computed together to reduce computation time.
+Others are values that are computed for all classes.
+
+\begin{enumerate}
+\item inferred-data-type      : Produces a vector which contains the inferred data type.  
+                          Only a single element is non-zero in the vector (i.e. 1-of-K format).  
+                          The set of inferred types are in {float,integer,long,boolean,date,time,datetime,string}.
+
+\item char-dist-features      : produces a vector for character distribution of column values;
+                        considered characters are printable characters:
+%                        0123456789abcdefghijklmnopqrstuvwxyz
+%                        ABCDEFGHIJKLMNOPQRSTUVWXYZ!"
+%                        #$%&\'()*+,-./:;<=>?@[\\]^_`{|}~ \t\n\r\x0b\x0c
+
+\item stats-of-text-length    : Computes the mean, median, mode, min, max of string lengths from a columns entries.
+
+\item stats-of-numerical-type : Computes the mean, median, mode, min, max of entries from a column of numerical type.
+
+\item prop-instances-per-class-in-knearestneighbours         : This finds the k columns from the training set with most similar names.
+                                                         It then produces a vector of class proportions from these k neighbours.
+                                                         Parameters:
+                                                             "num-neighbours": The number of neighbours to find (k).
+
+\item mean-character-cosine-similarity-from-class-examples   : For some test instance t, this computes the character distribution 
+                                                         from this instance's entries.  It then produces a vector of the average
+                                                         cosine similarity of t with training instances of each class.
+
+\item min-editdistance-from-class-examples                   : For some test instance t, this produces a vector of the minimum column name
+                                                         edit distance between t and all training instances of each class.
+                                                         Parameters:
+                                                              "cache-size": Size of cache for storing edit distances of words 
+                                                              "max-comparisons-per-class": Max number of training instances to compare
+                                                                                           against for each class.
+
+\item min-wordnet-jcn-distance-from-class-examples            : For some test instance t, this produces a vector of the minimum column name
+                                                         JCN WS4J distance between t and all training instances of each class.
+                                                         Parameters:
+                                                              "cache-size": Size of cache for storing wordnet distances of words 
+                                                              "max-comparisons-per-class": Max number of training instances to compare
+                                                                                           against for each class.
+
+\item min-wordnet-lin-distance-from-class-examples            : For some test instance t, this produces a vector of the minimum column name
+                                                         LIN WS4J distance between t and all training instances of each class.
+                                                         Parameters:
+                                                              "cache-size": Size of cache for storing wordnet distances of words 
+                                                              "max-comparisons-per-class": Max number of training instances to compare
+                                                                                           against for each class.
+
+\end{enumerate}
 

### 2017-08-30 stp/paper_aaai/main.tex
Made couple of sentences shorter, made tables for the features intead of enums

@@
 
-\usepackage{color}
+\usepackage{color,colortbl}
 \usepackage{xcolor}
+\definecolor{Gray}{gray}{0.96}
 \usepackage{amsmath,amsthm,stmaryrd}
@@
 \usepgfplotslibrary{colorbrewer}
+
+\usepackage{supertabular}
 
@@
 \usetikzlibrary{mindmap,backgrounds}
-\tikzstyle{class}=[draw,green,ellipse,align=center,fill=green!25,text=black]
-\tikzstyle{data}=[draw,rectangle,align=center,black!70]
+\tikzstyle{class}=[draw,green,ellipse,align=center,fill=green!25,text=black,inner sep=1]
+\tikzstyle{data}=[draw,rectangle,align=center,black!70,inner sep=2]
 \tikzstyle{att}=[rectangle,align=center,fill=brown!70!red]
@@
 In this paper we use Machine Learning techniques (ML) to learn mapping rules from previously mapped instances.
-To this end we formulate the Relational-To-Ontology Mapping Problem (\relonto{}) as a Minimum Cost Steiner Tree Problem (STP) with side constraints \cite{deuna2016steiner}.
+To this end we formulate the Relational-To-Ontology Mapping Problem (\relonto{}) as a Minimum Steiner Tree Problem (STP) with side constraints \cite{deuna2016steiner}.
 
@@
 Steiner Tree is a valid and coherent semantic model for the new source. 
-The contributions of this work are:
+Our contributions are:
 \begin{itemize}
@@
 (e.g, mean/max/min string length and numeric statistics), etc. 
-A full list can be found in appendix \ddg{Apendix!}
+A full list can be found in Appendix \ref{Ann:SemLab}.
 \npr{If I remove entropy descr, we are perfectly within page limit}
@@
 Note that, although the alignment graph is directed, the semantic models are 
-not necessarily rooted directed trees (e.g. Fig. \ref{FIG:sem}), therefore the 
+not necessarily rooted graphs (e.g. Fig. \ref{FIG:sem}), therefore the 
 direction of the edges is ignored for the STP model (and are all treated as 
 undirected edges).
-\npr{This is not true: semantic models are directed. can we soften the statement here? direction of links can change semantics}
 
@@
 strategy}.}
-Since only using a backtracking algorithm would have a prohibitive cost, CP 
-uses a combination of search and \emph{propagation}. The latter is achieved by  
+CP uses a combination of search and \emph{propagation}. The latter is achieved by  
 removing inconsistent values 
@@
 constraint over a set of variables. These are typically implemented with 
-specialized algorithms for these 
-constraints and perform substantially better than a decomposition approaches
+specialized algorithms that perform substantially better than decomposition approaches
 \cite{regin1994filtering,beldiceanu2012global}.
@@
 implemented for Steiner 
-Tree Problems \cite{deuna2016steiner}.
+Tree Problems \cite{deuna2016steiner}. The model can be found in Appendix \ref{Ann:MZ}.
 
@@
 \newpage
+\section*{Appendices}
+\renewcommand{\thesubsection}{\Alph{subsection}}
+
+\subsection{Features for Semantic Labeling\label{Ann:SemLab}}
 
@@
 vector of the concatenation of values computed by the extractors below.
-
-We refer to a single value from the column as an entry.
-E.g.
+We refer to a single value from the column as an entry. For example, in the table below, John is an entry of the column Person.
 
@@
 
-From the table above, John is an entry of the column Person.
-
+\begin{table}[!ht]
+	\centering
+	\caption{Feature extractors that produce a scalar value}
+	\begin{tabular}{p{3cm}p{4.5cm}}
+	Feature name & Description \\ \hline
+	num-unique-vals & A simple count of unique entries of a column\\
+	\rowcolor{Gray}
+	prop-unique-vals & The proportion of unique entries of a column. \\
+	\rowcolor{Gray}
+	prop-missing-vals & The proportion of all missing/empty entries from all entries in a column.\\
+	ratio-alpha-chars & The average of the proportion of alphabetic characters from each entry.\\
+	\rowcolor{Gray}
+	prop-numerical-chars & The average of the proportion of numeric characters from each entry.\\
+	prop-whitespace-chars    & The average of the proportion of whitespace characters from each entry.\\
+	\rowcolor{Gray}
+	prop-entries-with-at-sign& The proportion of entries with an '@' sign. \\
+	prop-entries-with-hyphen & The proportion of entries with a '-'. \\
+	\rowcolor{Gray}
+	prop-range-format        & The proportion of entries which follow some \\ numerical range format &  ([0-9]+)-([0-9]+) \\
+	\rowcolor{Gray}
+	is-discrete              & A binary indicator if the column entries are discrete. \\
+	entropy-for-discrete-values & The entropy of the entries of a column.\\
+	\rowcolor{Gray}	
+	shannon-entropy          & Shannon's entropy for the vocabulary specified in the description of the feature 'char-dist-features'\\
+	\end{tabular}
+\end{table}
+\ignore{
 The following feature extractors produce a scalar value:
@@
 \end{enumerate}
-
+}
+
+\begin{table}[!ht]
+	\centering
+	\caption{Feature extractors that produce a vector value. Some of these are computed together to reduce computation time.
+	Others are values that are computed for all classes.}
+
+	\begin{tabular}{p{2.5cm}p{5cm}}
+	Feature name & Description \\ \hline
+inferred-data-type      & Produces a vector which contains the inferred data type.  
+Only a single element is non-zero in the vector (i.e. 1-of-K format).  
+The set of inferred types are in float, integer, long, boolean, date, time, datetime, string. \\
+	\rowcolor{Gray}
+char-dist-features      & Produces a vector for character distribution of column values;
+considered characters are printable characters
+%                        0123456789abcdefghijklmnopqrstuvwxyz
+%                        ABCDEFGHIJKLMNOPQRSTUVWXYZ!"
+%                        #$%&\'()*+,-./:;<=>?@[\\]^_`{|}~ \t\n\r\x0b\x0c
+\\
+stats-of-text-length    & Computes the mean, median, mode, min, max of string lengths from a columns entries.\\
+	\rowcolor{Gray}
+stats-of-numerical-type & Computes the mean, median, mode, min, max of entries from a column of numerical type.\\
+
+prop-instances-per-class-in-knearestneighbours         & This finds the k columns from the training set with most similar names.
+It then produces a vector of class proportions from these k neighbours.
+Parameters:
+"num-neighbours": The number of neighbours to find (k).\\
+	\rowcolor{Gray}
+mean-character-cosine-similarity-from-class-examples   & For some test instance t, this computes the character distribution 
+from this instance's entries.  It then produces a vector of the average
+cosine similarity of t with training instances of each class.\\
+min-editdistance-from-class-examples                   & For some test instance t, this produces a vector of the minimum column name
+edit distance between t and all training instances of each class.
+Parameters:
+"cache-size": Size of cache for storing edit distances of words 
+"max-comparisons-per-class": Max number of training instances to compare
+against for each class.\\
+
+	\rowcolor{Gray}
+min-wordnet-jcn-distance-from-class-examples            & For some test instance t, this produces a vector of the minimum column name
+JCN WS4J distance between t and all training instances of each class.
+Parameters:
+"cache-size": Size of cache for storing wordnet distances of words 
+"max-comparisons-per-class": Max number of training instances to compare
+against for each class.\\
+
+min-wordnet-lin-distance-from-class-examples            & For some test instance t, this produces a vector of the minimum column name
+LIN WS4J distance between t and all training instances of each class.
+Parameters:
+"cache-size": Size of cache for storing wordnet distances of words 
+"max-comparisons-per-class": Max number of training instances to compare
+against for each class.\\
+
+\end{tabular}
+\end{table}
+
+\ignore{
 The following feature extractors produce a vector value.
@@
 \end{enumerate}
+}
+
+\subsection{\minizinc{} Model \label{Ann:MZ}}
 

### 2017-08-30 stp/paper_aaai/main.tex
Added minizinc model at the end, shortened text. added description of serch startegy

@@
 
-\usepackage{color,colortbl}
+\usepackage{colortbl}
+\usepackage{color}
 \usepackage{xcolor}
@@
 
-\usepackage{supertabular}
+\usepackage{listings}
+%%AR defines some stuff such as syntax highlighting for stochastic Minzinc listings
+\input{commondefs.tex}
 
@@
 
-\subsubsection{Example} Consider the situation where we have some simple relational database tables with columns $\langle$\textit{Surname, Workplace, Date, Location}$\rangle$, 
-$\langle$\textit{Company, Event, Begin, Until, Location}$\rangle$ and 
-$\langle$\textit{Name, D.O.B, Location}$\rangle$.
-We do not \textit{a priori} know whether ``Date'' in the first table is the 
-date of birth or the date a persons started working; or whether the 
+\subsubsection{Example} Consider the situation where we have some simple relational database tables with columns $\langle$\textit{Surname, Workplace, Date}$\rangle$, and 
+$\langle$\textit{Company, Event, Begin, Until, Location}$\rangle$.
+We do not \textit{a priori} know if ``Date'' in the first table is a 
+date of birth or the date a person started working; or whether the 
 ``Location'' on the second table refers to the location of the event, or the 
 address of the company. 
-If we are given an ontology like the one in Fig. \ref{FIG:onto}, we would like to automatically map the new data sources to classes of the 
+Given an ontology like the one in Fig. \ref{FIG:onto}, we would like to automatically map the new data sources to classes of the 
 ontology.\hfill$\square$
@@
 and \emph{datatype properties}, which relate individuals to literal values.
-An example of an ontology is given in Fig.~\ref{FIG:onto}. 
+Fig.~\ref{FIG:onto} gives an example of an ontology. 
 Here, an individual of the class ``Organisation'' can be related to an individual of the class ``Person'' via object properties ``ceo'' or ``worksFor'', and it can have a data property ``name''. 
@@
 The algorithm we use for the construction of the alignment graph 
-$\mathcal{G_O}$ was given by~\cite{taheriyan2016learning}.
-Briefly, the algorithm has three parts:
+$\mathcal{G_O}$ was given by~\citeasnoun{taheriyan2016learning}.
+Briefly, it has three parts:
 %\begin{enumerate}
@@
 %\item 
-$(iii)$ Expanding the graph using the domain ontology $\mathcal{O}$.
+$(iii)$ Expanding the graph using the domain ontology.
 %\end{enumerate}
@@
 The graph is weighted by a function $w_\mathcal{O} : \mathcal{E_O} \mapsto 
-\mathbb{R}$ in 
-such a way that edges which are present in
+\mathbb{R}$ such that edges which are present in
 the known semantic models have lower weights than those 
 which are inferred from the ontology.
-As we will see in the next section, this makes edges present in semantic models 
+In the next section we will see that this makes edges from semantic models 
 more attractive. 
-Details on the weighting function can be found in \cite{taheriyan2016learning}.
+\citeasnoun{taheriyan2016learning} provide details on the weighting function.
 %\ddg{How exactly are they weighted?}
@@
 
-A Constraint Optimization Problem (COP) is a tuple $P = (\boldsymbol{v},C,o)$ 
+A Constraint Optimization Problem (COP) is a tuple $P=(\boldsymbol{v},C,o)$ 
 where $\boldsymbol{v}$ is a 
@@
 Briefly, the way a CP solver works is by assigning a value to each variable of 
-$\boldsymbol{v}$ in turn. At each iteration it will check whether any 
+$\boldsymbol{v}$ in turn. 
+\ignore{At each iteration it will check whether any 
 constraint in $C$ is violated, in which case it will backtrack to change its 
@@
 choice of the value to be assigned to each variable is called the \emph{search 
-strategy}.}
-CP uses a combination of search and \emph{propagation}. The latter is achieved by  
-removing inconsistent values 
+strategy}.}}
+CP uses a combination of complete search and \emph{propagation}. The latter
+removes inconsistent values 
 from the domains of variables. That way, values that cannot appear in a 
@@
 complex 
-constraint over a set of variables. These are typically implemented with 
-specialized algorithms that perform substantially better than decomposition approaches
-\cite{regin1994filtering,beldiceanu2012global}.
+constraint over a set of variables. They are implemented with 
+specialized algorithms for performance.
 
@@
 without \emph{unknown} nodes (by dropping Eq. \ref{EQ:unk}).
+
+We choose a search strategy that will first try to match attributes using the cheapest edges in $\mathcal{M}_\mathcal{O}^{s^\star}$.
+Then, it will try to use the cheapest unfixed edge $e\in\mathcal{E_O}$ that completes a pattern $p$ such that $w_\mathcal{P}(p) > w_\mathcal{O}(e)$ or simply the cheapest edge if none complete a pattern.
+
 \section{Results \label{SEC:Res}}
@@
 \hspace*{-15pt}
-\begin{tikzpicture}[baseline,scale=0.47]
+\begin{tikzpicture}[baseline,scale=0.43]
 \begin{axis}[
@@
 \centering
-\begin{tikzpicture}[baseline,scale=0.47]
+\begin{tikzpicture}[baseline,scale=0.43]
 		\begin{axis}[
@@
   \caption{Example table.}
-  	\label{tab:semlab}
   	\begin{tabular}{ccc} 
@@
 
-\begin{table}[!ht]
+\begin{table}[h]
 	\centering
@@
 \end{table}
-\ignore{
-The following feature extractors produce a scalar value:
-\begin{enumerate}
-\item num-unique-vals      : A simple count of unique entries of a column
-\item prop-unique-vals     : The proportion of unique entries of a column. 
-\item prop-missing-vals    : The proportion of all missing/empty entries from all entries in a column.
-\item ratio-alpha-chars    : The average of the proportion of alphabetic characters from each entry.
-\item prop-numerical-chars : The average of the proportion of numeric characters from each entry.
-\item prop-whitespace-chars       : The average of the proportion of whitespace characters from each entry.
-\item prop-entries-with-at-sign   : The proportion of entries with an '@' sign.
-\item prop-entries-with-hyphen    : The proportion of entries with a '-'.
-\item prop-range-format           : The proportion of entries which follow some numerical range format: ([0-9]+)-([0-9]+).
-\item is-discrete                 : A binary indicator if the column entries are discrete.
-\item entropy-for-discrete-values : The entropy of the entries of a column.
-\item shannon-entropy             : Shannon's entropy for the vocabulary specified in the description of the feature 'char-dist-features'
-\end{enumerate}
-}
-
-\begin{table}[!ht]
+
+\begin{table}[t]
 	\centering
@@
 
-\ignore{
-The following feature extractors produce a vector value.
-Some of these are computed together to reduce computation time.
-Others are values that are computed for all classes.
-
-\begin{enumerate}
-\item inferred-data-type      : Produces a vector which contains the inferred data type.  
-                          Only a single element is non-zero in the vector (i.e. 1-of-K format).  
-                          The set of inferred types are in {float,integer,long,boolean,date,time,datetime,string}.
-
-\item char-dist-features      : produces a vector for character distribution of column values;
-                        considered characters are printable characters:
-%                        0123456789abcdefghijklmnopqrstuvwxyz
-%                        ABCDEFGHIJKLMNOPQRSTUVWXYZ!"
-%                        #$%&\'()*+,-./:;<=>?@[\\]^_`{|}~ \t\n\r\x0b\x0c
-
-\item stats-of-text-length    : Computes the mean, median, mode, min, max of string lengths from a columns entries.
-
-\item stats-of-numerical-type : Computes the mean, median, mode, min, max of entries from a column of numerical type.
-
-\item prop-instances-per-class-in-knearestneighbours         : This finds the k columns from the training set with most similar names.
-                                                         It then produces a vector of class proportions from these k neighbours.
-                                                         Parameters:
-                                                             "num-neighbours": The number of neighbours to find (k).
-
-\item mean-character-cosine-similarity-from-class-examples   : For some test instance t, this computes the character distribution 
-                                                         from this instance's entries.  It then produces a vector of the average
-                                                         cosine similarity of t with training instances of each class.
-
-\item min-editdistance-from-class-examples                   : For some test instance t, this produces a vector of the minimum column name
-                                                         edit distance between t and all training instances of each class.
-                                                         Parameters:
-                                                              "cache-size": Size of cache for storing edit distances of words 
-                                                              "max-comparisons-per-class": Max number of training instances to compare
-                                                                                           against for each class.
-
-\item min-wordnet-jcn-distance-from-class-examples            : For some test instance t, this produces a vector of the minimum column name
-                                                         JCN WS4J distance between t and all training instances of each class.
-                                                         Parameters:
-                                                              "cache-size": Size of cache for storing wordnet distances of words 
-                                                              "max-comparisons-per-class": Max number of training instances to compare
-                                                                                           against for each class.
-
-\item min-wordnet-lin-distance-from-class-examples            : For some test instance t, this produces a vector of the minimum column name
-                                                         LIN WS4J distance between t and all training instances of each class.
-                                                         Parameters:
-                                                              "cache-size": Size of cache for storing wordnet distances of words 
-                                                              "max-comparisons-per-class": Max number of training instances to compare
-                                                                                           against for each class.
-
-\end{enumerate}
-}
-
+\clearpage\newpage
 \subsection{\minizinc{} Model \label{Ann:MZ}}
+\renewcommand{\lstlistingname}{Model}
+\begin{minipage}{\textwidth}
+%\begin{figure}[!h]
+	\begin{lstlisting}[caption={\minizinc{} model (part 1 of 2)},captionpos=b]
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                          %%
+%% MiniZinc model to solve the Steiner Tree Problem arising %%
+%% in the Rel2Onto problem.                                 %%
+%%                                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+include "globals.mzn";
+
+%%%%%%% Steiner Tree Problem
+int: nbV;                               % Nb of nodes in alignment graph
+int: nbE;                               % Nb of edges in alignment graph
+set of int: nodes = 1..nbV;    
+set of int: edges = 1..nbE;
+set of int: cnodes;                     % Class nodes in alignment graph
+set of int: dnodes;                     % Data nodes in alignment graph
+set of int: anodes;                     % Attribute nodes in alignment graph (normally none)
+array [nodes] of var bool: vs;          % Is a node of the alignment graph in the solution?
+array [edges] of var bool: es;          % Is an edge of the alignment graph in the solution?
+array [nodes,edges] of bool: adjacent;  % adjacent[n,e] <=> node n is an endnode of edge e
+array [edges] of nodes: heads;          % endpoint 1 of each edge (The graph is undirected!!)
+array [edges] of nodes: tails;          % endpoint 2 of each edge
+array[1..2,edges] of int: endpairs = array2d(1..2,edges,tails++heads);
+array [edges] of int: ws;               % Weights of edges in alignment graph
+var 0..sum(ws): w;                      % Weight of the solution corresponding to the alignment part
+constraint steiner_tree(vs,es,adjacent,endpairs,w,ws);  % Steiner Tree constraint
+constraint forall (d in dnodes) (vs[d] <-> sum(e in edges where adjacent[d,e])(es[e]) == 1); %Only 1 edges per data node
+
+%%%%%%% Matching Problem
+int: nbA;                                           % Nb of attribute nodes
+set of int: atts = 1..nbA;                 
+array [atts] of set of int: attribute_domains;      % Data nodes to which each attribute can attach  
+constraint forall(att in anodes) (vs[att] == true); % Attribute nodes (normally none) are in the graph.
+array [atts] of var int: match;                     % Match between Attributes and Data nodes
+array[atts,int] of int: match_costs;                % Weight of match edges
+constraint forall (a in atts) (match[a] in (attribute_domains[a]));   % Must match someone in the domain
+constraint forall (a in atts) (vs[match[a]]);       % The data node matched must be in the subgraph of the alignment
+constraint alldifferent(match);                     % Exact match
+var 0..sum(a in atts)(sum(n in index_set_2of2(match_costs))(match_costs[a,n])): wm;  %Total cost from matching part :
+constraint wm = sum(a in atts) (match_costs[a,match[a]]);
+
+	\end{lstlisting}
+%	\caption{\minizinc{} model (1/2).}
+%\end{figure}
+\end{minipage}
+\clearpage
+\newpage
+\begin{minipage}{\textwidth}
+%\begin{figure*}[t]
+	\begin{lstlisting}[caption={\minizinc{} model (part 2 of 2)},captionpos=b]
+%%%%%%% Unknown nodes
+int: nb_unknown_nodes;                 % Number of unknown data nodes
+set of int: unknowns = 1..nb_unknown_nodes;
+array [int] of int: all_unk_nodes;     % List of all unknown nodes (first two elements are class nodes, by convention)
+int: node_root = all_unk_nodes[1];     % Root node if unknown class node is used.
+int: node_unk = all_unk_nodes[2];      % Unknown class node
+constraint if nb_unknown_nodes > 0 then
+    vs[node_unk] <-> vs[node_root]     % If class node "Unknown" is used, class node "Root" is used as well
+ /\ vs[node_root] <-> sum(e in edges where adjacent[node_root,e])(es[e]) in {1,2}
+else true %Ignore constraint
+endif;
+
+%%%%%%% Patterns
+int: nb_patterns;                     %Number of patterns
+set of int: PATTS = 1..nb_patterns;
+array[PATTS] of int: patterns_w;      %Support of patterns
+array[PATTS] of set of int: patterns; %The actual patterns
+array[PATTS] of var bool: c_p;        %Is pattern chosen
+constraint forall (p in PATTS) ((sum (e in patterns[p])   % All edges of a pattern are used <-> pattern is used
+							                  	(es[e]) == card(patterns[p])) <-> c_p[p]);
+var 0..sum(patterns_w): wp; % Total prize collected from patterns : 
+constraint if nb_patterns = 0 then wp = 0 else wp = sum(p in PATTS) (c_p[p] * patterns_w[p]) endif;
+
+%%%%%%% Final objective function 
+var int: obj = w + wm - wp; % Total cost of semantic model - prize collected from patterns
+
+%%%%%%% Search startegy
+array[atts,int] of int: match_costs_sorted;  % Match of attributes, sorted by cost.
+ann: cheap_matches = int_search([ match[a] == match_costs_sorted[a,i] |a in atts, i in index_set_2of2(match_costs_sorted)], input_order,indomain_max,complete);
+
+array[edges] of int: sorted_edges = arg_sort(ws);
+ann: cheap_edges = int_search([es[sorted_edges[nbE + 1 - e]] | e in edges],input_order,indomain_min,complete);
+
+ann: cheap_edges_fill_pattern; % Custom search strategy for patterns
+ann: custom(ann, array[int] of int, array[int] of var bool);
+array[int] of ann: cefp = 
+if nb_patterns == 0 then [] 
+else [custom(cheap_edges_fill_pattern,[nbE]++[nb_patterns]++ws++[ card(patterns[p]) | p in PATTS]++patterns_w++array1d([ e | p in PATTS, e in patterns[p]]),es)] endif;
+
+solve ::seq_search([cheap_matches]++cefp++[cheap_edges]) 
+minimize obj;
+
+	\end{lstlisting}
+	%\caption{\minizinc{} model (2/2).}
+%\end{figure*}
+\end{minipage}
 

### 2017-08-31 stp/alignment.py
Experiments with optimal solutions

@@ -511,12 +511,13 @@ def to_graphviz(graph, out_file=None, prog="dot"):
 ####################
 
 import time
-try:
-    import integration as integ
-except ImportError as e:
-    import sys
-    sys.path.insert(0, '.')
-    import integration as integ
+import stp.integration as integ
+# try:
+#     import integration as integ
+# except ImportError as e:
+#     import sys
+#     sys.path.insert(0, '.')
+#     import stp.integration as integ
 
 def create_octopus(server, ssd_range, sample, ontologies):
     octo_local = server.Octopus(
@@ -855,6 +856,7 @@ def do_chuffed(server, ch_octopus, ch_dataset, ch_column_names, ch_ssd, orig_ssd
         if len(solution) < 1:
             logging.error("Chuffed found no solutions for ssd {}".format(orig_ssd.id))
             raise Exception("Chuffed found no solutions!")
+        max_sol = len(solution) -1
 
         for idx, sol in enumerate(solution):
             # convert solution to SSD
@@ -863,11 +865,17 @@ def do_chuffed(server, ch_octopus, ch_dataset, ch_column_names, ch_ssd, orig_ssd
             cp_ssd = SSD().update(json_sol, server._datasets, server._ontologies)
             eval = cp_ssd.evaluate(ch_ssd, False, True)
 
+            # time returned by chuffed
             chuffed_time = json_sol["time"]
+            # match score calculated by chuffed
             match_score = json_sol["match_score"]
+            # cost of the calculated steiner tree
             cost = json_sol["cost"]
+            # value of the calculated objective function
             objective = json_sol["objective"]
             extended_time = json_sol["extended_time"]
+            # optimal soluiotn is the last found by chuffed
+            optimal_flag = json_sol["optimalFlag"] & idx == max_sol
 
             try:
                 comparison = server.ssds.compare(cp_ssd, ch_ssd, False, False)
@@ -891,14 +899,14 @@ def do_chuffed(server, ch_octopus, ch_dataset, ch_column_names, ch_ssd, orig_ssd
                      soft_assumptions, pattern_sign, accu, sol_accuracy,
                      match_score, cost, objective,
                      cor_match_score, cor_cost, pattern_time,
-                     integrat.graph.number_of_nodes(), integrat.graph.number_of_edges(), extended_time]]
+                     integrat.graph.number_of_nodes(), integrat.graph.number_of_edges(), extended_time, optimal_flag]]
     except Exception as e:
         print("CP solver failed to find solution: {}".format(e))
[…]

### 2017-08-31 stp/integration.py

@@ -17,7 +17,7 @@ try:
 except ImportError as e:
     import sys
     sys.path.insert(0, '.')
-    from minizinc import *
+    from stp.minizinc import *
 
 import subprocess
 import re
@@ -537,7 +537,7 @@ class IntegrationGraph(object):
             return ag.graph_attr[attr_name]
         return None
 
-    def _digraph_to_ssd(self, digraph, dot_file=None):
+    def _digraph_to_ssd(self, digraph, dot_file=None, optimal_flag=False):
         """
         Convert digraph string to ssd request
         :param digraph: string of a digraph
@@ -564,7 +564,8 @@ class IntegrationGraph(object):
             "time": t,
             "cost": cost,
             "match_score": match_score,
-            "objective": obj
+            "objective": obj,
+            "optimalFlag": optimal_flag
         }
 
         # mappings: [{"attribute": column_id, "node": data_node_id}]
@@ -638,6 +639,7 @@ class IntegrationGraph(object):
         output = output.decode("ascii")
         pat = re.compile("digraph \{.+?\}", re.DOTALL)
         logging.debug("Chuffed output: {}".format(output))
+        optimal_flag = not("Time limit exceeded" in output)
 
         try:
             # get graphviz digraph
@@ -647,7 +649,7 @@ class IntegrationGraph(object):
             # ssd_request = self._digraph_to_ssd(digraph, dot_file)
             # # to return json:
             # return json.dumps(ssd_request)
-            result = [json.dumps(self._digraph_to_ssd(digraph, dot_file)) for digraph in pat.findall(output)]
+            result = [json.dumps(self._digraph_to_ssd(digraph, dot_file, optimal_flag)) for digraph in pat.findall(output)]
 
             return result
 

### 2017-08-31 stp/soccer_experiments.py

@@ -56,7 +56,7 @@ log.addHandler(my_handler)
 # =======================
 sn = serene.Serene(
     host='127.0.0.1',
-    port=9090,
+    port=8080,
 )
 print(sn)
 
@@ -246,8 +246,167 @@ def do_experiment(octopus, orig_ds, orig_ssd, avail_labels, chosen_paths, chosen
 # =======================
 import time
 import yaml
+# chuffed_lookup_path = os.path.join(project_path, "stp", "minizinc")
+# result_csv = os.path.join(project_path, "stp", "resources", "results", "soccer_experiments_optimal.csv")
+# with open(result_csv, "w+") as f:
+#     csvf = csv.writer(f)
+#     csvf.writerow(["experiment", "octopus", "dataset", "name", "ssd",
+#                    "method", "solution", "status",
+#                    "jaccard", "precision", "recall",
+#                    "karma_jaccard", "karma_precision", "karma_recall",
+#                    "known_num", "time", "chuffed_path", "simplify", "chuffed_time",
+#                    "soft_assumptions", "pattern_significance", "sm_accuracy", "sol_accuracy",
+#                    "match_score", "cost", "objective", "cor_match_score", "cor_cost",
+#                    "pattern_time", "number_nodes", "number_links", "extended_time"])  # header
+#
+#     sample_range = list(range(len(new_ssds)))
+#     len_sample = len(sample_range)
+#     benchmark_results = [["experiment", "octopus", "dataset", "name", "ssd",
+#                           "method", "solution", "status",
+#                           "jaccard", "precision", "recall",
+#                           "karma_jaccard", "karma_precision", "karma_recall",
+#                           "train_flag", "time", "chuffed_path", "simplify", "chuffed_time",
+#                           "soft_assumptions", "pattern_significance", "sm_accuracy", "sol_accuracy",
+#                           "match_score", "cost", "objective", "cor_match_score", "cor_cost", "pattern_time",
+#                           "extended_time"]]
+#
+#     print("Starting benchmark")
+#
+#     for cur_id in sample_range:
+#         print("Currently selected ssd: ", cur_id)
+#         test_sample = [cur_id]
+#
+#         for num in range(1, len(sample_range)):
+#             train_sample = sample_range[:max(cur_id + num + 1 - len_sample, 0)] + sample_range[cur_id + 1: cur_id + 1 + num]
+#             print("     train sample size: ", num)
+#
+#             try:
[…]

### 2017-08-31 stp/stp_experiments_unknown.py

@@ -27,8 +27,8 @@ try:
 except ImportError as e:
     import sys
     sys.path.insert(0, '.')
-    import integration as integ
-    import alignment as al
+    import stp.integration as integ
+    import stp.alignment as al
 
 import logging
 from logging.handlers import RotatingFileHandler
@@ -245,8 +245,170 @@ def do_experiment(octopus, orig_ds, orig_ssd, avail_labels, chosen_paths, chosen
 # =======================
 import time
 import yaml
+# chuffed_lookup_path = os.path.join(project_path, "stp", "minizinc")
+# result_csv = os.path.join(project_path, "stp", "resources", "results", "museum_optimal.csv")
+# with open(result_csv, "w+") as f:
+#     csvf = csv.writer(f)
+#     csvf.writerow(["experiment", "octopus", "dataset", "name", "ssd",
+#                    "method", "solution", "status",
+#                    "jaccard", "precision", "recall",
+#                    "karma_jaccard", "karma_precision", "karma_recall",
+#                    "known_num", "time", "chuffed_path", "simplify", "chuffed_time",
+#                    "soft_assumptions", "pattern_significance", "sm_accuracy", "sol_accuracy",
+#                    "match_score", "cost", "objective", "cor_match_score", "cor_cost", "pattern_time",
+#                    "num_node", "num_edges", "extended_time"])  # header
+#
+#     sample_range = list(range(len(new_ssds)))
+#     len_sample = len(sample_range)
+#     benchmark_results = [["experiment", "octopus", "dataset", "name", "ssd",
+#                           "method", "solution", "status",
+#                           "jaccard", "precision", "recall",
+#                           "karma_jaccard", "karma_precision", "karma_recall",
+#                           "train_flag", "time", "chuffed_path", "simplify", "chuffed_time",
+#                           "soft_assumptions", "pattern_significance", "sm_accuracy", "sol_accuracy",
+#                           "match_score", "cost", "objective", "cor_match_score", "cor_cost", "pattern_time"]]
+#
+#     print("Starting benchmark")
+#
+#     for cur_id in sample_range:
+#         print("Currently selected ssd: ", cur_id)
+#         test_sample = [cur_id]
+#
+#         for num in range(1, len(sample_range)):
+#             train_sample = sample_range[:max(cur_id + num + 1 - len_sample, 0)] + sample_range[
+#                                                                                   cur_id + 1: cur_id + 1 + num]
+#             print("     train sample size: ", num)
+#
+#             try:
[…]

### 2017-08-31 stp/paper_aaai/commondefs.tex

\definecolor{lightgray}{rgb}{0.97, 0.97, 0.97}
%\definecolor{lightgray}{rgb}{0.83, 0.83, 0.83}
%\definecolor{orange}{HTML}{FF7F00}

% Syntax highlighting for stochastic Minizinc in listings
\lstdefinelanguage{minizinc}
{
morekeywords={
% minizinc keyworkds
ann, annotation, any, array, assert, bool, constraint, else, endif, enum, float, forall, function,
if, in, include, int, list, of, op, output, minimize, maximize, par, predicate, record, set,
solve, string, test, then, tuple, type, var, where,
% minizinc functions
abort, abs, acosh, array_intersect, array_union,
array1d, array2d, array3d, array4d, array5d, array6d, asin, assert, atan, bool2int, card,
ceil, combinator, concat, cos, cosh, dom, dom_array, dom_size, dominance,
fix, exp, floor, index_set, index_set_1of2,
index_set_2of2, index_set_1of3, index_set_2of3, index_set_3of3, int2float, is_fixed,
join, lb, lb_array, length, let, ln, log, log2, log10, min, max, pow, product, round, set2array,
show, show_int, show_float, sin, sinh, sqrt, sum, tan, tanh, trace, ub, and ub_array},
sensitive=false, % are the keywords case sensitive
morecomment=[l][\bfseries\color{orange}]{::},
morecomment=[l][\em\color{green}]{\%},
%morecomment=[s]{/*}{*/},
morestring=[b]",
}

% settings for listings
\lstset{ %
  backgroundcolor=\color{lightgray},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  basicstyle=\scriptsize\ttfamily,        % the size of the fonts that are used for the code
  belowskip=-.5em,
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{ForestGreen},    % comment style
%  deletekeywords={...},            % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=single,                    % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\bfseries\color{blue},       % keyword style
  language=minizinc,                % the language of the code
%  morekeywords={*,...},            % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{Gray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{red},     % string literal style
  tabsize=2,                       % sets default tabsize to 2 spaces
  title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
}

%\def\mzninline{\lstinline[basicstyle=\ttfamily,annotationstyle=\normalfont]}
\def\mzninline{\verb}

### 2017-09-02 stp/paper_aaai/main.tex
Small fix

@@
 \caption{Example of ontology
-(`\tikz{ \node[class] () at (0,0)  {};}' are Classes, `\tikz{ \path[hasaC,->] 
+(`\tikz{ \node[class, inner sep = 2] () at (0,0)  {};}' are Classes, `\tikz{ \path[hasaC,->] 
 (0,1) -- (3ex,1);}' means ``has an object property'', 
@@
 \end{tikzpicture}
-\caption{Examples of two semantic models (`\tikz{ \node[class] () at (0,0)  
+\caption{Examples of two semantic models (`\tikz{ \node[class, inner sep = 2] () at (0,0)  
 {};}' are class nodes, and `\tikz{ \node[data] () at (0,0)  {};}' are data 
@@
 \end{tikzpicture}
-\caption{Example of alignment graph (`\tikz{ \node[class] () at (0,0)  
-{};}' `\tikz{ \node[class,orange,fill=orange!30!white,text=black] () at 
+\caption{Example of alignment graph (`\tikz{ \node[class, inner sep = 2] () at (0,0)  
+{};}' `\tikz{ \node[class,orange,fill=orange!30!white,text=black, inner sep = 2] () at 
 (0,0)  
@@
 We choose a search strategy that will first try to match attributes using the cheapest edges in $\mathcal{M}_\mathcal{O}^{s^\star}$.
-Then, it will try to use the cheapest unfixed edge $e\in\mathcal{E_O}$ that completes a pattern $p$ such that $w_\mathcal{P}(p) > w_\mathcal{O}(e)$ or simply the cheapest edge if none complete a pattern.
+Then, it will try to use the cheapest unfixed edge $e\in\mathcal{E_O}$ that fills a pattern $p$ (i.e.
+$\forall e_p\in p, e_p \neq e, c_{e_p}$) such that $w_\mathcal{P}(p) > w_\mathcal{O}(e)$ or simply the cheapest edge if none fill a pattern.
 

### 2017-09-03 stp/paper_aaai/main.tex
Shrink paper, correct some statements

@@
 	seamlessly incorporates machine learning and constraint programming.
+	\npr{symbolic AI, ontological reasoning, transitive closure}
 	\item An efficient approach to handle attributes which cannot be matched to 
@@
 values in the column 
-(e.g, mean/max/min string length and numeric statistics), etc. 
+%(e.g, mean/max/min string length and numeric statistics)
+, etc. 
 A full list can be found in Appendix \ref{Ann:SemLab}.
@@
 %\ignore{
-One of the important features characterising information content of an attribute is Shannon's entropy of the attribute's concatenated rows.
-Shannon's entropy (or information entropy~\cite{Manning:Introduction}) of a string $X$ is defined as
+One of the important features characterising information content of an attribute is Shannon's entropy.
+% of the attribute's concatenated rows
+Shannon's entropy 
+%(or information entropy~\cite{Manning:Introduction})
+ of a string $X$ is defined as
 $H(X) = -\sum_{i}{p_i \log_{2}p_i},$ where $p_i$ is the probability of a character, whose index in character vocabulary is $i$, to appear in $X$, and the summation ranges over all
-characters in the vocabulary of all possible characters.
+characters in the vocabulary.
+%of all possible characters
 To evaluate $p_i$ in Shannon's entropy, we evaluate normalized character frequency distribution \emph{chardist} of an attribute, as character counts in concatenated rows of the attribute, normalized by the total length of the concatenated rows.
@@
 We mine these patterns from the set of semantic models in the training set $S_T$.
-This is known as Transactional Frequent Graph Pattern Mining, which includes
-the subgraph isomorphism problem, known to be NP-complete.
-The frequency of a pattern is the number of semantic models which contain at least one subgraph isomorphic to the pattern
-The \emph{support} of the pattern is calculated as its frequency relative to the number of semantic models.
+This is known as Transactional Frequent Graph Pattern Mining, which
+includes the subgraph isomorphism problem, known to be NP-complete.
+The frequency of a pattern is the number of semantic models 
+which contain
+at least one subgraph isomorphic to the pattern.
+The \emph{support} of the pattern is calculated as its 
+frequency relative to the number of semantic models.
 This is an anti-monotonous measure, meaning that bigger 
@@
 from~\cite{Taheriyan:Leveraging}.
-\npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe 
-cite my work on how databases perform for graph pattern matching. Should it be 
-better in related work?}
+%\npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe 
+%cite my work on how databases perform for graph pattern matching. Should it be 
+%better in related work?}
 
@@
 ln(\psi(a_i,l_j))$. %\ddg{CHECK!}
-
-An example of integration graph can be found in Fig. \ref{FIG:inte}.
+An example of an integration graph can be found in Fig. \ref{FIG:inte}.
 
@@
 
-Note that, although the alignment graph is directed, the semantic models are 
-not necessarily rooted graphs (e.g. Fig. \ref{FIG:sem}), therefore the 
-direction of the edges is ignored for the STP model (and are all treated as 
-undirected edges).
+Note that, although the alignment graph is directed, we disregard the
+direction of edges for the STP model.
+We disambiguate the direction and semantics of edges via their
+weights.
+We can further improve this step by using patterns.
+%\npr{this was not completely correct}
+%the semantic models are 
+%not necessarily rooted graphs (e.g. Fig. \ref{FIG:sem}), therefore the 
+%direction of the edges is ignored for the STP model (and are all treated as 
+%undirected edges).
 
@@
 	c_{(unknown,root)} \big) \label{EQ:unk}
+\vspace{-3mm}
 \end{flalign}
 
-Eq. \ref{EQ:obj} is the objective function: we are minimizing the cost 
-of $T^\star$ while collecting prizes for each pattern we use. Eq. \ref{EQ:stp} 
-enforces that the solution 
-$T^\star$ is indeed a tree defined by the $c_n$ and $c_e$ variables, subgraph 
-of the alignment graph 
-and of total weight $w_{STP}$. Equations \ref{EQ:deg1} and \ref{EQ:deg2} ensure 
+Eq.~\ref{EQ:obj} is the objective function: we are minimizing the cost 
+of $T^\star$ while collecting prizes for each pattern we use. 
+Eq.~\ref{EQ:stp} enforces that the solution 
+$T^\star$ is indeed a tree defined by the $c_n$ and $c_e$ variables,
+subgraph of the alignment graph 
+and of total weight $w_{STP}$. 
+Eq.~\ref{EQ:deg1} and \ref{EQ:deg2} ensure 
 that if a data node of the alignment graph is selected, then at most one edge 
 reaches it (from the side of the alignment graph) and otherwise it is 
-disconnected. \ignore{Eq. \ref{EQ:matchdom} ensures that the domain of each 
+disconnected. 
+\ignore{Eq. \ref{EQ:matchdom} ensures that the domain of each 
 variable in 
 the array $match$ corresponds to a subset of data nodes of the alignment graph 
-for which there is an edge connecting to the attribute at hand. Eq. 
-\ref{EQ:alld} ensure that each attribute is mapped to exactly one data node of 
-the alignment graph.} Equations \ref{EQ:matchdom} and \ref{EQ:alld} ensure that 
-there is exactly one data node matched to an attribute. Eq. \ref{EQ:map} 
-ensures that 
+for which there is an edge connecting to the attribute at hand. 
+Eq.~\ref{EQ:alld} ensure that each attribute is mapped to exactly one data node of 
+the alignment graph.}
+Eq.~\ref{EQ:matchdom} and \ref{EQ:alld} ensure that 
+there is exactly one data node matched to an attribute. 
+Eq.~\ref{EQ:map} ensures that 
 if a data node of the alignment graph has been mapped to some attribute, then 
-that data node must be in the solution tree, and vice-versa. Eq. 
-\ref{EQ:matchcost} computes the cost $w_{ADIFF}$ of the matches.
-Eq. \ref{EQ:patt} indicates that a pattern is used if and only if all its edges 
-are selected in the tree. Eq. \ref{EQ:pcost} computes the prizes collected by using patterns.
+that data node must be in the solution tree, and vice-versa. 
+Eq.~\ref{EQ:matchcost} computes the cost $w_{ADIFF}$ of the matches.
+Eq.~\ref{EQ:patt} indicates that a pattern is used if and only if all its edges are selected in the tree. 
+Eq.~\ref{EQ:pcost} computes the prizes collected by using patterns.
 Eq. \ref{EQ:unk} ensures that if the \emph{unknown} class node is used, then it 
 is connected to \emph{root}.
-Notice how there is no further requirement for unmatched attributes, as the 
+Notice there is no further requirement for unmatched attributes, as the 
 $unk_i$ data nodes behave like normal data nodes, and the connectedness 
@@
 % datasets for evaluation
-For the rest of the paper, we call our system \serene{} when it is not using 
-patterns in the CP model, and \serenepats{} when it uses them.
+For the rest of the paper, we call our system \serene{} if no patterns are used in the model, and \serenepats{} otherwise.
 
@@
 parts.
-It solve the problems sequentially, i.e., once it produces a set of candidate 
-mappings for attributes into the ontology, it fixes this set and move onto the 
-STP part.
+It solves the problems sequentially, i.e., once it produces a set of candidate 
+mappings for attributes into the ontology, it fixes this set and moves
+onto the STP part.
 Additionally, it does not consider unmatched attributes in the sources.
@@
 To illustrate that our semantic labeling model is better suited for the
-matching task, we compare it against the state-of-the-art model \emph{DSL}~\cite{Pham:semantic} which was shown to perform even better than SemanticTyper. 
-\npr{not sure whether I should explain how this model works}
+matching task, 
+we compare it against the state-of-the-art model \emph{DSL}~\cite{Pham:semantic} which was shown to perform 
+even better than SemanticTyper. 
+%\npr{not sure whether I should explain how this model works}
 We use \emph{mean reciprocal rank} (MRR) to evaluate semantic labeling models.
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!ht]\small
 \centering
@@
 
-\npr{Maybe some words on how optimal solution found by chuffed relates to the ground truth?}
+%\npr{Maybe some words on how optimal solution found by chuffed relates to the ground truth?}
 
@@
 patterns to boost the performance of their system.
-To perform semantic modeling in such scenario, \cite{Taheriyan:Leveraging} had to revise their algorithm by introducing additional heuristics.
+To this end, \cite{Taheriyan:Leveraging} had to revise their algorithm by introducing additional heuristics.
 However, in our case we only had to add pattern variables and to modify the 

### 2017-09-03 stp/stp_experiments_unknown.py

@@ -408,7 +408,7 @@ import yaml
 # =======================
 
 chuffed_lookup_path = os.path.join(project_path, "stp", "minizinc")
-result_csv = os.path.join(project_path, "stp", "resources", "results", "museum_optimal.csv")
+result_csv = os.path.join(project_path, "stp", "resources", "results", "museum_optimal3.csv")
 with open(result_csv, "w+") as f:
     csvf = csv.writer(f)
     csvf.writerow(["experiment", "octopus", "dataset", "name", "ssd",
@@ -431,10 +431,16 @@ with open(result_csv, "w+") as f:
                           "match_score", "cost", "objective", "cor_match_score", "cor_cost", "pattern_time"]]
 
     print("Starting benchmark")
+    done_list = ["s02", "s20", "s11", "s29", "s21", "s27", "s10", "s26", "s13", "s16", "s18", "s08", "s28", "s19",
+                 "s22", "s24"]
 
     for cur_id in sample_range:
         print("Currently selected ssd: ", cur_id)
         num = 28
+        ssd = new_ssds[cur_id]
+        if any(item in ssd.name for item in done_list):
+            continue
+
         train_sample = sample_range[:max(cur_id + num + 1 - len_sample, 0)] + sample_range[cur_id + 1: cur_id + 1 + num]
         print("     train sample size: ", num)
 
@@ -465,15 +471,15 @@ with open(result_csv, "w+") as f:
         chuffed_paths = [
             # (os.path.join(chuffed_lookup_path, "chuffed-rel2onto_20170718"),
             #  True, None, False, 1.0),
-            (os.path.join(chuffed_lookup_path, "chuffed-rel2onto_20170722"), True, None, True, 1.0),
+            # (os.path.join(chuffed_lookup_path, "chuffed-rel2onto_20170722"), True, None, True, 1.0),
             # (os.path.join(chuffed_lookup_path, "chuffed-rel2onto_20170728"),
             #  False, octo_patterns, False, 1.0),
             (os.path.join(chuffed_lookup_path, "chuffed-rel2onto_20170728"),
              False, octo_patterns, True, 1.0),
-            (os.path.join(chuffed_lookup_path, "chuffed-rel2onto_20170728"),
-             False, octo_patterns, True, 5.0),
-            (os.path.join(chuffed_lookup_path, "chuffed-rel2onto_20170728"),
-             False, octo_patterns, True, 10.0),
[…]

### 2017-09-03 stp/paper_aaai/main.tex
Squeezed the paper for page limit

@@
 \begin{abstract}
-The problem of integrating heterogeneous data sources in an ontology is of high 
+The problem of integrating heterogeneous data sources into an ontology is of high 
 relevance in the database field. Several techniques exist to approach this 
@@
 In this paper we use Machine Learning techniques (ML) to learn mapping rules from previously mapped instances.
-To this end we formulate the Relational-To-Ontology Mapping Problem (\relonto{}) as a Minimum Steiner Tree Problem (STP) with side constraints \cite{deuna2016steiner}.
-
-Firstly, we build an \emph{integration graph} which includes the 
-attributes from the new source as well as ontology classes and properties. 
+To this end we formulate the Relational-To-Ontology Mapping Problem (\relonto{}) as a Minimum cost Steiner Tree Problem (STP) with side constraints \cite{deuna2016steiner}.
+
+Firstly, we build a graph which includes attributes from the new
+source as well as ontology classes and properties.
+We call it the \emph{integration graph}.
+This graph uses information gathered from the previously mapped data sources, and is further extended with information derived from the ontology.
+%Firstly, we build a \emph{integration graph} which includes the 
+%attributes from the new source as well as ontology classes and properties.
 Secondly, we apply machine learning techniques to 
@@
 	seamlessly incorporates machine learning and constraint programming.
-	\npr{symbolic AI, ontological reasoning, transitive closure}
+%	\npr{symbolic AI, ontological reasoning, transitive closure}
 	\item An efficient approach to handle attributes which cannot be matched to 
@@
 \label{FIG:onto}
+\vspace{-3mm}
 \end{figure}
@@
 \label{FIG:sem}
+\vspace{-3mm}
 \end{figure}
@@
 A full list can be found in Appendix \ref{Ann:SemLab}.
-\npr{If I remove entropy descr, we are perfectly within page limit}
+%\npr{If I remove entropy descr, we are perfectly within page limit}
 %\ignore{
@@
 
-Note how the alignment graph contains data nodes that correspond to semantic 
-types. 
+Note how the alignment graph contains data nodes that correspond to semantic types. 
 For instance, it could contain two nodes $City.name$ and $State.name$ rather than just one node $name$ connected to two 
@@
 \label{FIG:ali}
+\vspace{-3mm}
 \end{figure}
@@
 $T \subseteq V_s \subseteq 
-V$ and $E_s \subseteq E$. In other words, $G_s$ spans all the nodes in $T$ and 
+V$ and $E_s \subseteq E$. 
+In other words, $G_s$ spans all the nodes in $T$ and 
 may include additional nodes from $V$, in particular to ensure the 
-connectedness of the constructed tree. The Steiner Tree Problem 
+connectedness of the constructed tree. 
+The Steiner Tree Problem 
 (STP) is stated as follows: given $G$ and a weight function $w_f : E 
@@
 We associate a weighting function  $w_\mathcal{I} : E \mapsto \mathbb{R}^+$ to 
-the integration graph. For an edge $e \in \mathcal{E_O}$, $w_\mathcal{I}(e) = 
-w_\mathcal{O}(e)$. For an edge $e 
+the integration graph. 
+For an edge $e \in \mathcal{E_O}$, $w_\mathcal{I}(e) = 
+w_\mathcal{O}(e)$. F
+or an edge $e 
 \in \mathcal{M}_\mathcal{O}^{s^\star}$ connecting attribute $a_i$ to the node 
@@
 \label{FIG:inte}
+\vspace{-3mm}
 \end{figure}
@@
 
-It is therefore natural to model this problem as a STP with side constraints, since the 
-two first requirements imply that $T^\star$ is a Steiner Tree of the 
-integration graph. By designing the weighting function $w_\mathcal{I}$ through 
+It is therefore natural to model this problem as a STP with side constraints.
+%, since the two first requirements imply that $T^\star$ is
+%a Steiner Tree of the integration graph. 
+By designing the weighting function $w_\mathcal{I}$ through 
 ML techniques, as shown in Section \ref{SEC:ML}, 
-our expectation is that the minimum weight Steiner Tree is a valid semantic 
-model for the new source.
+our expectation is that the minimum cost Steiner Tree is a valid and coherent semantic model for the new source.
 
@@
 
-As explained in Subsection \ref{SSEC:pattern-mining}, we also tried to use 
-frequently appearing patterns in order to incentivise the solution tree 
+As explained in Subsection \ref{SSEC:pattern-mining}, we also use 
+graph patterns in order to incentivise the solution tree 
 $T^\star$ to contain subgraphs of the alignment graph that have been frequently 
 seen in the training set.
-
 To do this, we use the support of each of the obtained patterns as a prize. If 
@@
 with 4 cores each.
-\npr{check characteristics, AWS machine is bigger}
+%\npr{check characteristics, AWS machine is bigger}
 In all our experiments we use a timeout threshold of 15s for \chuffed{}, which 
@@
 \end{minipage}%
-\caption{Performance over the museum and soccer datasets. Average size of 
-integration graph: 88 nodes and 1129 nodes.\label{fig:perf}}
+\caption{Performance for the museum and soccer domains. 
+Average size of integration graphs for the museum domain: 88 nodes and 1129 edges2.
+Average run time for the museum domain: \serene{} 0.5s, \karma{} 0.5s, \serenepats{} 1s. \label{fig:perf}}
+\vspace{-3mm}
 \end{figure}
@@
 We have also observed that \serenepats{} manages to find the ground truth on 
-many instances among its sequential solutions, but again it takes much more 
-time.
+many instances among its sequential solutions.
+This property of our approach can be used to configure various parameters for the model, e.g., scaling factors for pattern costs or match score.
 
@@
 domain.}\label{fig:loo}
+\vspace{-3mm}
 \end{figure}

### 2017-09-04 stp/paper_aaai/main.tex
Typo
Fixed colors and couple fo typos

@@
 %}
-We also compute a set of features based on similarity metrics inspired by state-of-the-art works~\cite{Pham:semantic} or~\cite{Ritze:matching}.
+We also compute a set of features based on similarity metrics inspired by state-of-the-art works by ~\citeasnoun{Pham:semantic} or~\citeasnoun{Ritze:matching}.
 Among others, we compute mean cosine similarity for character distributions of attribute values and string similarity metrics for attribute names.
@@
 \caption{Performance for the museum and soccer domains. 
-Average size of integration graphs for the museum domain: 88 nodes and 1129 edges2.
+Average size of integration graphs for the museum domain: 88 nodes and 1129 
+edges.
 Average run time for the museum domain: \serene{} 0.5s, \karma{} 0.5s, \serenepats{} 1s. \label{fig:perf}}
@@
 constraint steiner_tree(vs,es,adjacent,endpairs,w,ws);  % Steiner Tree constraint
-constraint forall (d in dnodes) (vs[d] <-> sum(e in edges where adjacent[d,e])(es[e]) == 1); %Only 1 edges per data node
+constraint forall (d in dnodes) 
+                   (vs[d] <-> sum(e in edges where adjacent[d,e])(es[e]) == 1);% Only 1 edges per data node
 
@@
 constraint alldifferent(match);                     % Exact match
-var 0..sum(a in atts)(sum(n in index_set_2of2(match_costs))(match_costs[a,n])): wm;  %Total cost from matching part :
+var 0..sum(a in atts)(sum(n in index_set_2of2(match_costs))(match_costs[a,n])): wm;  % Total cost from matching part :
 constraint wm = sum(a in atts) (match_costs[a,match[a]]);
@@
 %%%%%%% Patterns
-int: nb_patterns;                     %Number of patterns
+int: nb_patterns;                     % Number of patterns
 set of int: PATTS = 1..nb_patterns;
-array[PATTS] of int: patterns_w;      %Support of patterns
-array[PATTS] of set of int: patterns; %The actual patterns
-array[PATTS] of var bool: c_p;        %Is pattern chosen
+array[PATTS] of int: patterns_w;      % Support of patterns
+array[PATTS] of set of int: patterns; % The actual patterns
+array[PATTS] of var bool: c_p;        % Is pattern chosen
 constraint forall (p in PATTS) ((sum (e in patterns[p])   % All edges of a pattern are used <-> pattern is used

### 2017-09-06 stp/paper_aaai/main.tex
I had removed the copyright thing because I had read it could be removed for submission, but I cant find the place I read that again, so just in case I added it back and rediced a bit the figures (had to be reduced anyway, if it gets accpeted they dont want Overfull boxes in latex) so it still fits in 8 pages
Peter's changes

@@
 \centering
-\begin{tikzpicture}
+\begin{tikzpicture}[scale=0.95]
 \begin{scope}
@@
 
-	\node[data] (pen) at (2.5,-0.7) {\scriptsize Person1.name};
-	\node[data] (peb) at (4.3,-0.7) {\scriptsize Person1.birthDate};
-	\node[data] (cin) at (1,-0.7) {\scriptsize City1.name};
+	\node[data] (pen) at (2.3,-0.7) {\scriptsize Person1.name};
+	\node[data] (peb) at (4.2,-0.7) {\scriptsize Person1.birthDate};
+	\node[data] (cin) at (0.7,-0.7) {\scriptsize City1.name};
 	\node[data] (stn) at (-1,-0.7) {\scriptsize State1.name};
@@
 
-	\node[data] (pen) at (2.5,-0.7) {\scriptsize Person2.name};
-	\node[data] (evs) at (4.2,-0.7) {\scriptsize Event1.startDate};
+	\node[data] (pen) at (2.2,-0.7) {\scriptsize Person2.name};
+	\node[data] (evs) at (4,-0.7) {\scriptsize Event1.startDate};
 	\node[data] (eve) at (6,-0.7) {\scriptsize Event1.endDate};
-	\node[data] (con) at (1,-0.7) {\scriptsize Org2.name};
+	\node[data] (con) at (0.7,-0.7) {\scriptsize Org2.name};
 	\node[data] (pln) at (-1,-0.7) {\scriptsize City2.name};
@@
 of whitespaces and other special characters, statistics of 
-values in the column 
-%(e.g, mean/max/min string length and numeric statistics)
-, etc. 
+values in the column. 
 A full list can be found in Appendix \ref{Ann:SemLab}.
@@
 \centering
-\begin{tikzpicture}
+\begin{tikzpicture}[scale=0.9]
 
@@
 	\node[data] (pen) at (2.3,0.7) {\scriptsize Person1.name};
-	\node[data] (peb) at (4.2,0.7) {\scriptsize Person1.birthDate};
+	\node[data] (peb) at (4.3,0.7) {\scriptsize Person1.birthDate};
 	\node[data] (cin) at (0.7,0.7) {\scriptsize City1.name};
 	\node[data] (stn) at (-1,0.7) {\scriptsize State1.name};
-	\node[data] (con) at (6,0.7) {\scriptsize Org1.name};
+	\node[data] (con) at (6.2,0.7) {\scriptsize Org1.name};
 
@@
 	\node[data] (evs) at (4.2,-0.7+\ysh) {\scriptsize Event1.startDate};
-	\node[data] (eve) at (6,-0.7+\ysh) {\scriptsize Event1.endDate};
+	\node[data] (eve) at (6.3,-0.7+\ysh) {\scriptsize Event1.endDate};
 	\node[data] (con) at (0.7,-0.7+\ysh) {\scriptsize Org2.name};
@@
 $l_j$ induced by the semantic model, $w_\mathcal{I}(e) = - 
-ln(\psi(a_i,l_j))$. %\ddg{CHECK!}
+ln(\psi(a_i,l_j))$, making unlikely matches have a higher weight. %\ddg{CHECK!}
 An example of an integration graph can be found in Fig. \ref{FIG:inte}.
@@
 \centering
-\begin{tikzpicture}
+\begin{tikzpicture}[scale=0.9]
 	\node[class, rectangle, rounded corners] (CLASS) at (0,0) { \small{ 
@@
 (source) at 
-(-4.1,-2) 
+(-4.5,-2) 
 {$s^\star$:};
@@
 We repeat the procedure for other data sources in the domain and then average the results.
-Such procedure ensures that each source is at least once in the training as well as testing datasets.
+This procedure ensures that each source is at least once in the training as well as testing datasets.
 
@@
 \centering
-\begin{tikzpicture}[scale=0.4]
+\begin{tikzpicture}[scale=0.39]
 \pgfplotsset{
@@
 array [nodes,edges] of bool: adjacent;  % adjacent[n,e] <=> node n is an endnode of edge e
-array [edges] of nodes: heads;          % endpoint 1 of each edge (The graph is undirected!!)
+array [edges] of nodes: heads;          % endpoint 1 of each edge (the graph is undirected)
 array [edges] of nodes: tails;          % endpoint 2 of each edge
@@
 set of int: atts = 1..nbA;                 
-array [atts] of set of int: attribute_domains;      % Data nodes to which each attribute can attach  
+array [atts] of set of dnodes: attribute_domains;   % Data nodes to which each attribute can attach (usually all) 
 constraint forall(att in anodes) (vs[att] == true); % Attribute nodes (normally none) are in the graph.
-array [atts] of var int: match;                     % Match between Attributes and Data nodes
-array[atts,int] of int: match_costs;                % Weight of match edges
+array [atts] of var dnodes: match;                  % Match between Attributes and Data nodes
+array[atts,dnodes] of int: match_costs;             % Weight of match edges
 constraint forall (a in atts) (match[a] in (attribute_domains[a]));   % Must match someone in the domain
@@
 constraint alldifferent(match);                     % Exact match
-var 0..sum(a in atts)(sum(n in index_set_2of2(match_costs))(match_costs[a,n])): wm;  % Total cost from matching part :
+var 0..sum(a in atts)(sum(n in dnodes)(match_costs[a,n])): wm;  % Total cost from matching part :
 constraint wm = sum(a in atts) (match_costs[a,match[a]]);
@@
 %%%%%%% Search startegy
-array[atts,int] of int: match_costs_sorted;  % Match of attributes, sorted by cost.
-ann: cheap_matches = int_search([ match[a] == match_costs_sorted[a,i] |a in atts, i in index_set_2of2(match_costs_sorted)], input_order,indomain_max,complete);
+array[atts,dnodes] of int: match_costs_sorted;  % Match of attributes, sorted by cost.
+ann: cheap_matches = int_search([ match[a] == match_costs_sorted[a,i] |a in atts, i in dnodes], 
+                                input_order,indomain_max,complete);
 
@@
 else [custom(cheap_edges_fill_pattern,[nbE]++[nb_patterns]++ws++[ card(patterns[p]) | p in PATTS]++patterns_w++array1d([ e | p in PATTS, e in patterns[p]]),es)] endif;
+
+% The solver will use these strategies in order:
+% 1) First try using the cheapest matches matches, until a match is found
+% 2) If there are patterns, use a specific search called "cheap_edges_first".
+%    It will start adding edges in increasing order of cost, while trying to fill patterns that are "worth" filling.
+%    E.g. We already set es[x] = true for x in {e1,e2,e3}; if adding ws[e5] = 4 and ws[e7] = 6, but
+%    {e1,e2,e3,e7} form a pattern p of patterns_w[p] = 3, then ws[e7] - patterns_w[p] <  ws[e5], so e7 is selected first
+%    If there are no patterns, this strategy is ignored.
+% 3) Try to eliminate edges my decreasing cost: it will eliminate the more expensive edges first, until
+%    the strictly necesary cheap edges are added by the propagators. This is used only when there are no 
+%    patterns, otherwise (2) already selects the edges.
 

### 2017-09-06 stp/paper_aaai/main.tex
revision of the paper

@@
 
-Firstly, we build a graph which includes attributes from the new
+Firstly, we build a graph which includes attributes (i.e. columns) from the new
 source as well as ontology classes and properties.
-We call it the \emph{integration graph}.
-This graph uses information gathered from the previously mapped data sources, and is further extended with information derived from the ontology.
+We name it \emph{integration graph}.
+It uses information gathered from the previously mapped data sources, and is further extended with information derived from the ontology.
 %Firstly, we build a \emph{integration graph} which includes the 
@@
 Section \ref{SEC:problem} formally states the problem. 
-In Section \ref{SEC:ML} we present how we convert the information given into a 
+In Section \ref{SEC:ML} we present how we convert learnt data into a 
 useful data representation. 
@@
 	\path[hasaC,->] (ci) edge  []
-	node [midway, above, sloped] {state} (st) ;
+	node [midway, above, sloped] {isIn} (st) ;
 
@@
 
-In our work we consider that an ontology $\mathcal{O}$ includes basic elements 
-as classes which represent a set of concepts, literal values, individuals which 
-are members of classes and properties~\cite{Spanos:semweb}.
+In our work we consider that an ontology $\mathcal{O}$ includes basic elements such 
+as classes (which represent concepts), literal values, individuals (members of classes) and properties~\cite{Spanos:semweb}.
 Properties are classified into \emph{object properties}, which relate two 
@@
 Edges in the semantic model correspond to properties in the ontology, as 
-shown in Fig.~\ref{FIG:onto} and \ref{FIG:sem}.
+shown in Fig.~\ref{FIG:sem} (notice the same edges appear in Fig.~\ref{FIG:onto}).
 The semantic model may have several instances of the same ontology class, that is why class nodes are enumerated.
@@
 are connected to the nodes of $m$.
-The attribute mapping function addresses the first part of the problem (semantic labeling).
+The attribute mapping function addresses the first part of the problem (i.e. the semantic labeling).
 
@@
 is a data property of that class (including inherited properties). 
-For example, from the ontology in Fig. \ref{FIG:onto}, we would get types such 
-as 
+For example, from the ontology in Fig. \ref{FIG:onto}, we would for example get
 (City,name) and (State,name).
@@
 alignment graph by the semantic types.
-We denote them as $\mathcal{D_{G_O}}$ and call them the \emph{data nodes} of the alignment graph.
+We note them $\mathcal{D_{G_O}}$ and call them the \emph{data nodes} of the alignment graph.
+Class nodes are noted $\mathcal{C_{G_O}}$.
 
@@
 According to the ontology in Fig.~\ref{FIG:onto} there are multiple ways to connect these nodes.
-However, if we know that the ``Person'' works for the ``Organization'', then based on the known semantic models ``City'' is more likely to be the birth place of the ``Person'' rather than the location of the ``Organization''.
+However, if we know that the ``Person'' works for the ``Organization'', then based on the known semantic models (Fig.~\ref{FIG:sem}), ``City'' is more likely to be the birth place of the ``Person'' rather than the location of the ``Organization''.
 To increase the coherence of the generated semantic models, we would like to discover such patterns of connections.
@@
 weights of the edges in $E_s$ given by $w_f$. This was proven to be NP-hard 
-by Karp \cite{Karp1972}.
+by \citeasnoun{Karp1972}.
 
@@
 For an edge $e \in \mathcal{E_O}$, $w_\mathcal{I}(e) = 
-w_\mathcal{O}(e)$. F
-or an edge $e 
+w_\mathcal{O}(e)$. For an edge $e 
 \in \mathcal{M}_\mathcal{O}^{s^\star}$ connecting attribute $a_i$ to the node 
@@
 	\node[class, rectangle, rounded corners] (CLASS) at (0,0) { \small{ 
-	Nodes of Alignment Graph}};
+	Class nodes of Alignment Graph (i.e. $\mathcal{C_{G_O}}$)}};
 
@@
 	$(v)$ %\item 
-	$\forall n \in \mathcal{D_{G_O}} \cap V^\star, degree(a) = 2$.
+	$\forall n \in \mathcal{D_{G_O}} \cap V^\star, degree(n) = 2$,
+	$(vi)$ 
+	$V^\star \cap \mathcal{C_{G_O}} \neq \emptyset$.
 %\end{enumerate}
@@
 \cite{regin1994filtering}, we split the problem into two parts: the 
-$\mathit{steiner}$ global constraint will only deal with the part of the 
+$\mathit{steiner}$ global constraint \cite{deuna2016steiner} will only deal with the part of the 
 integration graph that corresponds to the alignment graph, and the 
@@
 Tab.~\ref{tab:semlab} provides evidence that our new semantic labeling model is better suited for the task when there are unmatched attributes in domains.
-DSL uses heuristic measures to capture the similarity of attributes within the same class.
-It is clear that we cannot directly speak about similarity for unmatched attributes, since they are rather dissimilar from known semantic types.
+DSL uses heuristic measures to capture the similarity of attributes within the same class, but 
+unmatched attributes are clearly dissimilar from known semantic types, thus similarity measures may be unsound in the presence of unmatched attributes.
 Our intuition as to why our approach performs better is that we have 
@@
 nodes and use an exact algorithm to solve the STP.
-\cite{taheriyan2016learning} treat the matching and STP parts of \relonto{} independently and use heuristic algorithms for both.
+\citeasnoun{taheriyan2016learning} treat the matching and STP parts of \relonto{} independently and use heuristic algorithms for both.
 We, on the other hand, use exact algorithms for both parts and address them within a unified CP model.
 
-In their follow up work, \cite{Taheriyan:Leveraging} suggest using graph 
+In their follow up work, \citeasnoun{Taheriyan:Leveraging} suggest using graph 
 patterns to boost the performance of their system.
-To this end, \cite{Taheriyan:Leveraging} had to revise their algorithm by introducing additional heuristics.
+To this end, they had to revise their algorithm by introducing additional heuristics.
 However, in our case we only had to add pattern variables and to modify the 
@@
 Furthermore, our approach is extremely flexible and easy to extend with 
-specific side constraints thanks to the use of CP rather than a specific 
+arbitrary side constraints thanks to the use of CP rather than a specific 
 heuristic algorithm.
@@
 % 1) First try using the cheapest matches matches, until a match is found
-% 2) If there are patterns, use a specific search called "cheap_edges_first".
+% 2) If there are patterns, use a specific search called "cheap_edges_fill_pattern". (Implemented in Chuffed only)
 %    It will start adding edges in increasing order of cost, while trying to fill patterns that are "worth" filling.
@@
 %    If there are no patterns, this strategy is ignored.
-% 3) Try to eliminate edges my decreasing cost: it will eliminate the more expensive edges first, until
+% 3) Try to eliminate edges by decreasing cost: it will eliminate the more expensive edges first, until
 %    the strictly necesary cheap edges are added by the propagators. This is used only when there are no 
@@
 minimize obj;
-
 	\end{lstlisting}

### 2017-09-07 stp/paper_aaai/main.tex
changed example a bit after some feedback, so it's clearer now

@@
 
-\subsubsection{Example} Consider the situation where we have some simple relational database tables with columns $\langle$\textit{Surname, Workplace, Date}$\rangle$, and 
-$\langle$\textit{Company, Event, Begin, Until, Location}$\rangle$.
-We do not \textit{a priori} know if ``Date'' in the first table is a 
-date of birth or the date a person started working; or whether the 
-``Location'' on the second table refers to the location of the event, or the 
-address of the company. 
-Given an ontology like the one in Fig. \ref{FIG:onto}, we would like to automatically map the new data sources to classes of the 
+\subsubsection{Example} Consider the situation where we have some simple relational database tables with columns $\langle$\textit{Surname, Event, Date}$\rangle$, and 
+$\langle$\textit{Company, Festival, Address}$\rangle$.
+We do not \textit{a priori} know if ``Date'' is a 
+date of birth of the person or the start date of the event (c.f. Fig. \ref{FIG:onto}); or whether 
+``Address'' refers to the name of the place where the festival is located, or the 
+email address of the company. 
+Given an ontology like the one in Fig. \ref{FIG:onto}, we would like to automatically map the new data sources to  the 
 ontology.\hfill$\square$

### 2017-09-07 stp/paper_aaai/main.tex
couple more changes (typos mainly)

@@
 is a data property of that class (including inherited properties). 
-For example, from the ontology in Fig. \ref{FIG:onto}, we would for example get
+For example, from the ontology in Fig. \ref{FIG:onto}, we would get
 (City,name) and (State,name).
@@
 content, for example, startDate versus endDate for the Event class.
-Thirdly, there may be considerable number of attributes which do not have any 
+Thirdly, there may be a considerable number of attributes which do not have any 
 corresponding property in the ontology, either by accident or deliberately.
@@
 the known semantic type with the corresponding feature vector.
-The feature vector, among others, includes characteristics
+The feature vector includes, among others, characteristics
 such as a number 
@@
 To do this, we use the support of each of the obtained patterns as a prize. If 
-the tree contains a pattern, then its weight is automatically reduced by a the 
+the tree contains a pattern, then its weight is automatically reduced by the 
 value of the support of that pattern. We will see in the next section how this 
@@
 actually a matching problem. Each attribute must match exactly to one node of 
-$\mathcal{D_{G_O}}$. Note that not all nodes in $\mathcal{D_{G_O}}$ must match 
+$\mathcal{D_{G_O}}$. Note that not all nodes in $\mathcal{D_{G_O}}$ need to match 
 to an attribute, as not all of them are part of $T^\star$.
@@
 variables 
-$c_p, \forall p \in \mathcal{P}$ that tells us whether a pattern $p$ appears in 
+$c_p, \forall p \in \mathcal{P}$ that tell us whether a pattern $p$ appears in 
 $T^\star$ or not.

### 2017-09-07 stp/paper_aaai/main.tex
a few sentences changed

@@
 
-The algorithm we use for the construction of the alignment graph 
+The algorithm we use to construct the alignment graph 
 $\mathcal{G_O}$ was given by~\citeasnoun{taheriyan2016learning}.
@@
 $(i)$ %\item 
-Adding the known semantic models
+adding the known semantic models,
 $(ii)$ %\item 
-Adding the semantic types learned for the target source
+adding the semantic types learned for the target source,
 %\item 
-$(iii)$ Expanding the graph using the domain ontology.
+$(iii)$ expanding the graph using the domain ontology.
 %\end{enumerate}
@@
 $|\mathcal{A}_{s^\star}|$ data 
-nodes to the integration graph each connected to exactly one node in 
+nodes to the integration graph, each connected to exactly one node in 
 $\mathcal{A}_{s^\star}$ and to the \emph{unknown} Class node.
@@
 To maintain connectedness of the 
-Steiner tree, the \emph{unknown} node and one of the other selected Class nodes 
+Steiner tree, the \emph{unknown} node and one of the other Class nodes in $T^\star$ 
 will 
@@
 \emph{unknown} class node.
-In such way we validate how well the systems can detect earlier unseen cases.
+This way we can validate how well the systems can detect earlier unseen cases.
 
@@
 We use \emph{mean reciprocal rank} (MRR) to evaluate semantic labeling models.
-This measure is useful to estimate how highly the true semantic label is ranked among top $k$ suggestions.
+This measure is useful to estimate how highly the true semantic label is ranked among the top $k$ suggestions.
 It is calculated the following way:
@@
 % karma vs serene vs serene-pats
-We evaluate our new system \serene{} and its modification \serenepats{}, which 
+We evaluate \serene{} and its modification \serenepats{}, which 
 uses graph patterns, against the state-of-the-art system \karma{}.
 All three systems have access to the same set of matches produced by our semantic labeling model.
-Fig.~\ref{fig:perf} show their performance on the museum and soccer domains.
+Fig.~\ref{fig:perf} shows their performance on the museum and soccer domains.
 We report average precision and recall for the systems with regard to variable 
@@
 For \serene{} and \serenepats{} we report the first solutions found by
-\chuffed{}. All three systems find solutions in less than a second in average.
+\chuffed{}. All three systems find solutions in less than a second on average.
 We use default parameters for \karma{} which were shown to yield the best 
@@
 across sequentially found solutions.
-\chuffed{} successively finds better solutions in terms of Eq. \ref{EQ:obj}, 
-however,
+\chuffed{} successively finds better solutions in terms of Eq. \ref{EQ:obj}.
+However,
 that does not translate directly into more precise semantic models.
@@
 for pattern costs.
-When trying scaling factors 5, 10 or 20 for patterns costs from the museum 
+When trying scaling factors 5, 10 or 20 for pattern costs from the museum 
 domain we can generate semantic models which 
@@
 
-Relational data sources are still one of the most popular ways to store enterprise or Web data, however, the issue with relational schema is the lack of a well-defined semantic description.
+Relational data sources are still one of the most popular ways to store enterprise or Web data. However, the issue with relational schema is the lack of a well-defined semantic description.
 A common ontology provides a way of representing the meaning of a relational 
@@
 Our approach, on the other hand, allows a model to be trained on any data and can infer complex semantic paths which might exist between attributes.
-However, it might be further bootstrapped by leveraging external knowledge bases.
+However, it could be further bootstrapped by leveraging external knowledge bases.
 This is especially beneficial at the start when the system does not have sufficient training data.
@@
 It is clear that we cannot directly speak about similarity for unmatched attributes, since they are rather dissimilar from known semantic types.
-That is why we have developed a new approach for semantic labeling which can efficiently handle the \emph{unknown} class.
-We demonstrate its efficiency by comparing against the state-of-the-art approach DSL~\cite{Pham:semantic}.
+Our approach differs from previous work in that we incorporate an efficient method to handle the \emph{unknown} class, compared to the state-of-the-art approach DSL~\cite{Pham:semantic}.
 

### 2017-09-08 stp/paper_aaai/main.tex
Small fixes to charts and appendices

@@
 \newcommand{\karma}{\textsc{Karma}}
-\newcommand{\serene}{\textsc{Serene}}
+\newcommand{\serene}{\textsc{•}sc{Serene}}
 \newcommand{\serenepats}{\textsc{SerenePats}}
@@
 		    xmin=1, xmax=28,
-		    ymin=0.2, ymax=0.9,
+		    ymin=0.3, ymax=0.9,
 		    xtick={1,5,10,15,20,25,28},
-		    ytick={0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
+		    ytick={0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
 		    legend pos=south east,
@@
 		    xmin=1, xmax=28,
-		    ymin=0.2, ymax=0.9,
+		    ymin=0.3, ymax=0.9,
 		    xtick={1,5,10,15,20,25,28},
-		    ytick={0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
+		    ytick={0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
 		    ymajorgrids=true,
@@
   axis y line*=left,
-  ymin=0.5, ymax=1,
+  ymin=0.6, ymax=1,
+  xmin=1, xmax=10,
   xlabel=Solution Number,
@@
   coordinates{
-    (0,0.776507549540743)(1,0.71093042754513)(2,0.822783653218436)(3,0.845760233918129)(4,0.879310344827586)(5,0.88695652173913)(6,0.885964912280702)(7,0.870689655172414)(8,0.878260869565217)(9,0.87719298245614)
+    (1,0.776507549540743)(2,0.71093042754513)(3,0.822783653218436)(4,0.845760233918129)(5,0.879310344827586)(6,0.88695652173913)(7,0.885964912280702)(8,0.870689655172414)(9,0.878260869565217)(10,0.87719298245614)
 
@@
   coordinates{
-    (0,0.773180507486795)(1,0.677202255831871)(2,0.805899400726987)(3,0.838122605363985)(4,0.879310344827586)(5,0.879310344827586)(6,0.870689655172414)(7,0.870689655172414)(8,0.870689655172414)(9,0.862068965517241)
+    (1,0.773180507486795)(2,0.677202255831871)(3,0.805899400726987)(4,0.838122605363985)(5,0.879310344827586)(6,0.879310344827586)(7,0.870689655172414)(8,0.870689655172414)(9,0.870689655172414)(10,0.862068965517241)
 }; \label{plot_two}
@@
   ymin=0, ymax=15,
+  xmin=1, xmax=10,
   legend pos=south east,
@@
   coordinates{
-    (0,0.894338290115883)(1,2.39426428574782)(2,6.89703391393025)(3,10.3563708686829)(4,9.87668780326843)(5,9.92719115257263)(6,10.4045292949677)(7,14.3818371582031)(8,14.4026180458069)(9,14.8023208427429)
+    (1,0.894338290115883)(2,2.39426428574782)(3,6.89703391393025)(4,10.3563708686829)(5,9.87668780326843)(6,9.92719115257263)(7,10.4045292949677)(8,14.3818371582031)(9,14.4026180458069)(10,14.8023208427429)
 }; \addlegendentry{time}
@@
 	\rowcolor{Gray}
-	prop-range-format        & The proportion of entries which follow some \\ numerical range format &  ([0-9]+)-([0-9]+) \\
+	prop-range-format numerical range format  & The proportion of entries which follow some ([0-9]+)-([0-9]+)\\
+
+	is-discrete              & A binary indicator if the column entries are discrete. \\
 	\rowcolor{Gray}
-	is-discrete              & A binary indicator if the column entries are discrete. \\
 	entropy-for-discrete-values & The entropy of the entries of a column.\\
-	\rowcolor{Gray}	
 	shannon-entropy          & Shannon's entropy for the vocabulary specified in the description of the feature 'char-dist-features'\\
@@
 Parameters:
-"cache-size": Size of cache for storing edit distances of words 
+"cache-size": Size of cache for storing edit distances of words; 
 "max-comparisons-per-class": Max number of training instances to compare
@@
 Parameters:
-"cache-size": Size of cache for storing wordnet distances of words 
+"cache-size": Size of cache for storing wordnet distances of words;
 "max-comparisons-per-class": Max number of training instances to compare
@@
 Parameters:
-"cache-size": Size of cache for storing wordnet distances of words 
+"cache-size": Size of cache for storing wordnet distances of words; 
 "max-comparisons-per-class": Max number of training instances to compare
@@
 % The solver will use these strategies in order:
-% 1) First try using the cheapest matches matches, until a match is found
+% 1) First try using the cheapest matches, until a match is found
 % 2) If there are patterns, use a specific search called "cheap_edges_fill_pattern". (Implemented in Chuffed only)

### 2017-09-08 stp/paper_aaai/main.tex
switched intro with related work, to see how it looks

@@
 \section{Introduction}
+\ignore{
 The problem of integrating heterogeneous data sources is a long standing issue 
@@
 Henceforth, we focus on a specific data integration problem: automatically mapping a new relational data source onto a user provided ontology.
+}
+Relational data sources are still one of the most popular ways to store enterprise or Web data. However, the issue with relational schema is the lack of a well-defined semantic description.
+A common ontology provides a way of representing the meaning of a relational schema and can facilitate the integration of heterogeneous data sources within a domain.
+Indicating semantic correspondences manually might be appropriate if only few data sources need to be integrated, however, it becomes tedious with the growing number of heterogeneous schemata.
+
+Automatically integrating heterogeneous data sources is a long standing issue in the database research field and is of high relevance in many real-world 
+domains (see for example \cite{Rahm:2001:SAA:767149.767154,Dhamankar:imap,Taheriyan2013}).
+
+A standard approach to tackle this problem is to design a common ontology and to construct source descriptions which specify mappings between the sources and the ontology \cite{doan2012principles}.
+In this paper, we tackle the data integration problem consisting in automatically mapping a new relational data source onto a user provided ontology.
+To do so, we develop a new tool that automatically builds a semantic model which describes a relational data source in terms of concepts and relationships defined by an ontology \cite{taheriyan2016learning}.
 
@@
 \section{Related Work \label{SEC:pw}}
-
+\ignore{
 Relational data sources are still one of the most popular ways to store enterprise or Web data. However, the issue with relational schema is the lack of a well-defined semantic description.
@@
 Indicating semantic correspondences manually might be appropriate if only few data sources need to be integrated, however, it becomes tedious with the growing number of heterogeneous schemata.
-Hence, automatic or semi-automatic approaches for relational-to-ontology schema mapping are being actively developed.
+Hence, automatic or semi-automatic approaches for relational-to-ontology schema mapping are being actively developed.}
 

### 2017-09-09 stp/paper_aaai/main.tex
fixed the typo with the serene name and a just couple more typos in the appendices so the tables don't look hyperlong, and typos in the mzn model

@@
 	\rowcolor{Gray}
-	prop-range-format numerical range format  & The proportion of entries which follow some ([0-9]+)-([0-9]+)\\
-
+	prop-range-format        & The proportion of entries which follow some numerical range format   ([0-9]+)-([0-9]+) \\
 	is-discrete              & A binary indicator if the column entries are discrete. \\
@@
 inferred-data-type      & Produces a vector which contains the inferred data type.  
-Only a single element is non-zero in the vector (i.e. 1-of-K format).  
-The set of inferred types are in float, integer, long, boolean, date, time, datetime, string. \\
+Only a single element is non-zero in the vector (1-of-K format).  
+The set of inferred types are in float, integer, long, bool, date, time, datetime, string. \\
 	\rowcolor{Gray}
@@
 
-prop-instances-per-class-in-knearestneighbours         & This finds the k columns from the training set with most similar names.
-It then produces a vector of class proportions from these k neighbours.
+prop-instances-per-class-in-knearestneighbours         & This finds the $k$ columns from the training set with most similar names.
+It then produces a vector of class proportions from these $k$ neighbours.
 Parameters:
-"num-neighbours": The number of neighbours to find (k).\\
+"num-neighbours": The number of neighbours to find ($k$).\\
 	\rowcolor{Gray}
-mean-character-cosine-similarity-from-class-examples   & For some test instance t, this computes the character distribution 
-from this instance's entries.  It then produces a vector of the average
-cosine similarity of t with training instances of each class.\\
-min-editdistance-from-class-examples                   & For some test instance t, this produces a vector of the minimum column name
-edit distance between t and all training instances of each class.
+mean-character-cosine-similarity-from-class-examples   & For some instance $t$, computes the character distribution 
+from this instance's entries, and produces a vector of the average
+cosine similarity of $t$ with training instances of each class.\\
+min-editdistance-from-class-examples                   & For some instance $t$, produces a vector of the minimum column name
+edit distance between $t$ and all training instances of each class.
 Parameters:
-"cache-size": Size of cache for storing edit distances of words; 
-"max-comparisons-per-class": Max number of training instances to compare
+``cache-size'': size of cache to store edit distances of words;
+``max-comparisons-per-class'' : max number of training instances to compare for each class.\\
+
+	\rowcolor{Gray}
+min-wordnet-jcn-distance-from-class-examples            & For some instance $t$, produces a vector of the minimum column name
+JCN WS4J distance between $t$ and all training instances of each class.
+Parameters:
+"cache-size": size of cache to store wordnet distances of words; 
+"max-comparisons-per-class": max number of training instances to compare
 against for each class.\\
 
-	\rowcolor{Gray}
-min-wordnet-jcn-distance-from-class-examples            & For some test instance t, this produces a vector of the minimum column name
-JCN WS4J distance between t and all training instances of each class.
+min-wordnet-lin-distance-from-class-examples            & For some instance $t$, produces a vector of the minimum column name
+LIN WS4J distance between $t$ and all training instances of each class.
 Parameters:
-"cache-size": Size of cache for storing wordnet distances of words;
-"max-comparisons-per-class": Max number of training instances to compare
-against for each class.\\
-
-min-wordnet-lin-distance-from-class-examples            & For some test instance t, this produces a vector of the minimum column name
-LIN WS4J distance between t and all training instances of each class.
-Parameters:
-"cache-size": Size of cache for storing wordnet distances of words; 
-"max-comparisons-per-class": Max number of training instances to compare
+"cache-size": size of cache to store wordnet distances of words; 
+"max-comparisons-per-class": max number of training instances to compare
 against for each class.\\
@@
 %%                                                          %%
-%% MiniZinc model to solve the Steiner Tree Problem arising %%
-%% in the Rel2Onto problem.                                 %%
+%% MiniZinc model to solve the Rel2Onto problem             %%
+%%  as a composition of Steiner Tree Problem                %%
+%%  and a matching problem                                  %%
 %%                                                          %%
@@
 set of int: dnodes;                     % Data nodes in alignment graph
-set of int: anodes;                     % Attribute nodes in alignment graph (normally none)
 array [nodes] of var bool: vs;          % Is a node of the alignment graph in the solution?
@@
 array [nodes,edges] of bool: adjacent;  % adjacent[n,e] <=> node n is an endnode of edge e
-array [edges] of nodes: heads;          % endpoint 1 of each edge (the graph is undirected)
-array [edges] of nodes: tails;          % endpoint 2 of each edge
-array[1..2,edges] of int: endpairs = array2d(1..2,edges,tails++heads);
+array [edges] of nodes: heads;          % Endpoint 1 of each edge (the graph is undirected)
+array [edges] of nodes: tails;          % Endpoint 2 of each edge
+array[1..2,edges] of int: endpairs = array2d(1..2,edges,tails++heads);  % Endpoints of each edge
 array [edges] of int: ws;               % Weights of edges in alignment graph
@@
 array [atts] of set of dnodes: attribute_domains;   % Data nodes to which each attribute can attach (usually all) 
-constraint forall(att in anodes) (vs[att] == true); % Attribute nodes (normally none) are in the graph.
 array [atts] of var dnodes: match;                  % Match between Attributes and Data nodes
@@
 array [int] of int: all_unk_nodes;     % List of all unknown nodes (first two elements are class nodes, by convention)
-int: node_root = all_unk_nodes[1];     % Root node if unknown class node is used.
-int: node_unk = all_unk_nodes[2];      % Unknown class node
+int: node_root = all_unk_nodes[1];     % "Root" class node
+int: node_unk = all_unk_nodes[2];      % "Unknown" class node
 constraint if nb_unknown_nodes > 0 then
@@
 array[PATTS] of set of int: patterns; % The actual patterns
-array[PATTS] of var bool: c_p;        % Is pattern chosen
+array[PATTS] of var bool: c_p;        % Is pattern chosen to be part of the solution?
 constraint forall (p in PATTS) ((sum (e in patterns[p])   % All edges of a pattern are used <-> pattern is used
@@
 %%%%%%% Final objective function 
-var int: obj = w + wm - wp;           % Total cost of semantic model - prize collected from patterns
+var int: obj = w + wm - wp;           % Total = (cost of semantic model) - (prize collected from patterns)
 
@@
 
-ann: cheap_edges_fill_pattern;        % Custom search strategy for patterns
+ann: cheap_edges_fill_pattern;        % Custom search strategy for patterns (implemented in Chuffed)
 ann: custom(ann, array[int] of int, array[int] of var bool);
 array[int] of ann: cefp = 
-if nb_patterns == 0 then [] 
+if nb_patterns == 0 then []           % This builds a list in a format understood by Chuffed, to work on the "es" vars 
 else [custom(cheap_edges_fill_pattern,[nbE]++[nb_patterns]++ws++[ card(patterns[p]) | p in PATTS]++patterns_w++array1d([ e | p in PATTS, e in patterns[p]]),es)] endif;
@@
 % The solver will use these strategies in order:
-% 1) First try using the cheapest matches, until a match is found
+% 1) Try using the cheapest matches, until a complete match is found (i.e. for all attributes)
 % 2) If there are patterns, use a specific search called "cheap_edges_fill_pattern". (Implemented in Chuffed only)

### 2017-09-09 stp/paper_aaai/main.tex
fixed the typo with the serene name and a just couple more typos in the appendices so the tables don't look hyperlong, and typos in the mzn model
Added submission number
Last fixes ever.

@@
 \newcommand{\karma}{\textsc{Karma}}
-\newcommand{\serene}{\textsc{•}sc{Serene}}
+\newcommand{\serene}{\textsc{Serene}}
 \newcommand{\serenepats}{\textsc{SerenePats}}
@@
 
-%  \pdfinfo{
-%/Title (2018 Formatting Instructions for Authors Using LaTeX)
-%/Author (AAAI Press Staff)}
+\pdfinfo{
+/Title (Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping)
+/Author (Submission 1204)
+/Keywords (Machine Lerning Application, Constraint Programming, Ontology, Relational, Steiner Tree)}
 \setcounter{secnumdepth}{2}  
@@
 \title{Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping }
-\author{}
+\author{Submission 1204}
 \maketitle
@@
 \in \mathcal{M}_\mathcal{O}^{s^\star}$ connecting attribute $a_i$ to the node 
-$l_j$ induced by the semantic model, $w_\mathcal{I}(e) = - 
+$l_j$ induced by the semantic types, $w_\mathcal{I}(e) = - 
 ln(\psi(a_i,l_j))$, making unlikely matches have a higher weight. %\ddg{CHECK!}
@@
 
-We have also observed that \serenepats{} manages to find the ground truth on 
+We have also observed that \serene{} and \serenepats{} manage to find the ground truth on 
 many instances among its sequential solutions.

### 2017-09-11 stp/paper_aaai/main.tex
2 words in intro

@@
 A standard approach to tackle this problem is to design a common ontology and to construct source descriptions which specify mappings between the sources and the ontology \cite{doan2012principles}.
-In this paper, we tackle the data integration problem consisting in automatically mapping a new relational data source onto a user provided ontology.
-To do so, we develop a new tool that automatically builds a semantic model which describes a relational data source in terms of concepts and relationships defined by an ontology \cite{taheriyan2016learning}.
+In this paper, we approach the data integration problem consisting in automatically mapping a new relational data source onto a user provided ontology.
+To do so, we develop a new system that automatically builds a semantic model which describes a relational data source in terms of concepts and relationships defined by an ontology \cite{taheriyan2016learning}.
 

### 2018-01-06 stp/paper_aaai/main.tex
update paper

@@
 whereas Section \ref{SEC:CP} presents our implementation in CP. 
-Section \ref{SEC:Res} shows our results. 
+Section \ref{SEC:Res} shows the results. 
 Section \ref{SEC:pw} compares with the previous work done to achieve this task.
@@
 \emph{class nodes} and \emph{data nodes}. 
-We denote them as $\mathcal{C}_m$ and $\mathcal{D}_m$ respectively.
+We denote them as $\mathcal{C}_m$ and $\mathcal{D}_m$, respectively.
 $ \mathcal{C}_m$ corresponds to classes in the ontology 
@@
 
-We define a \emph{source description} as a triple $\delta = (s, m, \phi)$ where $s$ is a source, $m$ is a semantic model, and $\phi$ is an attribute mapping.
+We define a \emph{source description} as a triple $\delta = (s, m, \phi)$, where $s$ is a source, $m$ is a semantic model, and $\phi$ is an attribute mapping.
 Our problem can hence be stated as follows. We have an ontology 
-$\mathcal{O}$ and a set of source descriptions $S_T = \{(s_1, m_1, \phi_1),..., 
+$\mathcal{O}$ and a set of source descriptions $\Delta_T = \{(s_1, m_1, \phi_1),..., 
 (s_l, m_l, \phi_l)\}$.
@@
 problem.
-The known source descriptions $S_T$ provide us the training sample.
+The known source descriptions $\Delta_T$ provide us the training sample.
 We compute a feature vector for each attribute in a data source and associate 
@@
 
-To provide an integrated view over the known source descriptions $S_T$, we 
+To provide an integrated view over the known source descriptions $\Delta_T$, we 
 need to align their semantic models as well as all considered semantic 
@@
 In our context, patterns are typed directed graphs.
-We mine these patterns from the set of semantic models in the training set $S_T$.
+We mine these patterns from the set of semantic models in the training set $\Delta_T$.
 This is known as Transactional Frequent Graph Pattern Mining, which
@@
 %Our goal is to take a set of graphs (the semantic models from the training set 
-%$S_T$) and find patterns that appear often across that set of graphs. 
+%$\Delta_T$) and find patterns that appear often across that set of graphs. 
 %This is 
@@
 to exactly one value, and all the constraints in $C$ are satisfied by the 
-valuation is a \emph{solution} to $P$. A solution $\theta$ is optimal if$\not 
-\exists \theta', \theta'(\boldsymbol{v}) < \theta(\boldsymbol{v})$.
+valuation is a \emph{solution} to $P$. A solution $\theta^*$ is optimal if$\not 
+\exists \theta, \theta(\boldsymbol{v}) < \theta^*(\boldsymbol{v})$.
 
@@
 \subsection{\relonto{} in Constraint Programming}
-In order to model this problem we used the \minizinc{} language 
+In order to model the \relonto{} problem we used the \minizinc{} language 
 \cite{minizinc}, and the 
@@
 Because attributes must be connected to exactly one node of the alignment 
-graph, and that node will be in $\mathcal{D_{G_O}} \cap V^\star$ 
+graph, and that node will be in $\mathcal{D_{G_O}} \cap V^\star$, 
 then the part of the problem between attribute nodes and the alignment graph is 
-actually a matching problem. Each attribute must match exactly to one node of 
+actually a matching problem. Each attribute must match exactly one node of 
 $\mathcal{D_{G_O}}$. Note that not all nodes in $\mathcal{D_{G_O}}$ need to match 
@@
 variables 
-$c_p, \forall p \in \mathcal{P}$ that tell us whether a pattern $p$ appears in 
+$c_p, \forall p \in \mathcal{P}$, that tell us whether a pattern $p$ appears in 
 $T^\star$ or not.
@@
 The performance of these systems is estimated in terms of \emph{precision} and \emph{recall}.
-Assuming $m^\star$ is the predicted semantic model and $m^\dag$ is the correct semantic model, then:
-$$\mathit{prec} = \frac{|\mathit{rel}(m^\star)\cap 
-\mathit{rel}(m^\dag)|}{|\mathit{rel}(m^\star)|}, 
-\mathit{recall} = \frac{|\mathit{rel}(m^\star)\cap 
+Assuming $m^{p}$ is the predicted semantic model and $m^\dag$ is the correct semantic model, then:
+$$\mathit{prec} = \frac{|\mathit{rel}(m^{p})\cap 
+\mathit{rel}(m^\dag)|}{|\mathit{rel}(m^{p})|}, 
+\mathit{recall} = \frac{|\mathit{rel}(m^{p})\cap 
 \mathit{rel}(m^\dag)|}{|\mathit{rel}(m^\dag)|}$$
@@
 a domain.
-Indicating semantic correspondences manually might be appropriate if only few data sources need to be integrated, however, it becomes tedious with the growing number of heterogeneous schemata.
+Indicating semantic correspondences manually might be appropriate if only few data sources need to be integrated; however, it becomes tedious with the growing number of heterogeneous schemata.
 Hence, automatic or semi-automatic approaches for relational-to-ontology schema mapping are being actively developed.}

### 2018-01-06 stp/paper_aaai/main.tex
changed to ijcai style

@@
 \documentclass[letterpaper]{article} %DO NOT CHANGE THIS
-\usepackage{aaai18}  %Required
+\usepackage{ijcai18}  %Required
 \usepackage{times}  %Required
@@
 \caption{Example of ontology
-(`\tikz{ \node[class, inner sep = 2] () at (0,0)  {};}' are Classes, `\tikz{ \path[hasaC,->] 
+(`\protect\tikz{ \protect\node[class, inner sep = 2] () at (0,0)  {};}' are Classes, `\protect\tikz{ \protect\path[hasaC,->] 
 (0,1) -- (3ex,1);}' means ``has an object property'', 
-`\tikz{ \path[hasaA,decoration={post length=0}] (0,0) edge[decorate] (3ex,0);}' 
+`\protect\tikz{ \protect\path[hasaA,decoration={post length=0}] (0,0) edge[decorate] (3ex,0);}' 
 means ``has a data property'' and 
-`\tikz{ \path[isa,->] (0,1) -- (3ex,1);}' means ``is a'' ). Example by
-\citeasnoun{Taheriyan2013}.
+`\protect\tikz{ \protect\path[isa,->] (0,1) -- (3ex,1);}' means ``is a'' ). Example by
+\protect\citeasnoun{Taheriyan2013}.
 }
@@
 \end{tikzpicture}
-\caption{Examples of two semantic models (`\tikz{ \node[class, inner sep = 2] () at (0,0)  
-{};}' are class nodes, and `\tikz{ \node[data] () at (0,0)  {};}' are data 
+\caption{Examples of two semantic models (`\protect\tikz{ \protect\node[class, inner sep = 2] () at (0,0)  
+{};}' are class nodes, and `\protect\tikz{ \protect\node[data] () at (0,0)  {};}' are data 
 nodes).}
@@
 \end{tikzpicture}
-\caption{Example of alignment graph (`\tikz{ \node[class, inner sep = 2] () at (0,0)  
-{};}' `\tikz{ \node[class,orange,fill=orange!30!white,text=black, inner sep = 2] () at 
+\caption{Example of alignment graph (`\protect\tikz{ \protect\node[class, inner sep = 2] () at (0,0)  
+{};}' `\protect\tikz{ \protect\node[class,orange,fill=orange!30!white,text=black, inner sep = 2] () at 
 (0,0)  
-{};}' are class nodes, and `\tikz{ \node[data] () at (0,0)  {};}' are data 
+{};}' are class nodes, and `\protect\tikz{ \protect\node[data] () at (0,0)  {};}' are data 
 nodes). We omit weights for clarity.}
@@
 \end{tikzpicture}
-\caption{Example of integration graph. (`\tikz{ \node[att] () at (0,0)  
+\caption{Example of integration graph. (`\protect\tikz{ \protect\node[att] () at (0,0)  
 {};}' are attribute nodes). We omit weights and only show the most likely 
@@
 }
-\bibliographystyle{aaai}
+\bibliographystyle{named}
 \bibliography{main}

### 2018-01-06 stp/paper_aaai/main.tex
update paper

@@
 means ``has a data property'' and 
-`\protect\tikz{ \protect\path[isa,->] (0,1) -- (3ex,1);}' means ``is a'' ). Example by
+`\protect\tikz{ \protect\path[isa,->] (0,1) -- (3ex,1);}' means ``subClassOf'' ). Example by
 \protect\citeasnoun{Taheriyan2013}.

### 2018-01-24 stp/paper_aaai/main.tex
Adding citations, extending soa, improving experimental results section

@@
 \definecolor{Gray}{gray}{0.96}
+\usepackage{algorithm}
 \usepackage{amsmath,amsthm,stmaryrd}
 \usepackage{algpseudocode}
-\usepackage{algorithm}
 \algrenewcommand\algorithmiccomment[2][\footnotesize]{{#1\hfill\(\triangleright\)
@@
 \pgfplotsset{width=10cm,compat=1.9}
-\usepgfplotslibrary{colorbrewer}
+%\usepgfplotslibrary{colorbrewer}
 
@@
 
-\subsubsection{Example} Consider the situation where we have some simple relational database tables with columns $\langle$\textit{Surname, Event, Date}$\rangle$, and 
+%\subsubsection{Example} 
+Consider the situation where we have some simple relational database tables with columns $\langle$\textit{Surname, Event, Date}$\rangle$, and 
 $\langle$\textit{Company, Festival, Address}$\rangle$.
@@
 
-In this paper we use Machine Learning techniques (ML) to learn mapping rules from previously mapped instances.
+In this paper we use Machine Learning (ML) techniques and Constraint Programming (CP) to learn mapping rules from previously mapped instances.
 To this end we formulate the Relational-To-Ontology Mapping Problem (\relonto{}) as a Minimum cost Steiner Tree Problem (STP) with side constraints \cite{deuna2016steiner}.
@@
 assign costs to its edges. 
-Lastly, we use Constraint Programming (CP) to 
+Lastly, we use CP to 
 find a minimum cost Steiner Tree in the graph.
@@
 	\item A novel modeling framework for the \relonto{} problem which 
-	seamlessly incorporates machine learning and constraint programming.
+	seamlessly incorporates techniques from the areas of machine learning, knowledge representation and constraint programming.
 %	\npr{symbolic AI, ontological reasoning, transitive closure}
@@
 	the ontology, through a new semantic labeling model and a new STP 
-	model with additional nodes.
+	model with additional nodes in the integration graph.
 	\item A flexible and extensible approach to the problem, which is easy to 
-	reuse and adapt to specific situations.
+	reuse and adapt to specific situations. This is achieved since CP allows introduction of additional constraints with no changes to the solver. 
 \end{itemize}
@@
 The semantic model may have several instances of the same ontology class, that is why class nodes are enumerated.
+Semantic models can be formalized using a standard mapping language such as R2RML~\cite{r2rml}.
 
@@
 
-\subsection{Using Patterns}
-
+\textbf{Patterns}.
 As explained in Subsection \ref{SSEC:pattern-mining}, we also use 
@@
 
-\subsection{Unmatched Attributes}
+\textbf{Unmatched Attributes}.
 It is common that the data sources to be integrated will have columns that 
@@
 $MRR = \frac{1}{n}\sum_{i=1}^{n}{\frac{1}{rank_i}},$
-where $rank_i$ is the rank of the correct semantic label for the attribute $a_i$ among the top $k$ predictions.
+where $rank_i$ is the rank of the correct semantic label for the attribute $a_i$ among the top $k$ predictions and $n$ is the number of attributes in the data source.
 
@@
 We repeat the procedure for other data sources in the domain and then average the results.
-This procedure ensures that each source is at least once in the training as well as testing datasets.
+This procedure ensures that each source is at least once in the training and testing datasets.
 
@@
 recall.
-If we consider results separately per each instance and not on average, there 
-are few instances where \karma{} generates more precise models, however, our 
-new approaches produce much better models in terms of recall in all considered 
-instances. 
+The t-tests conducted for the obtained results confirm statistical significance of our improvements at the level $p<0.01$
+%If we consider results separately per each instance and not on average, there 
+%are few instances where \karma{} generates more precise models, however, our 
+%new approaches produce much better models in terms of recall in all considered 
+%instances. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 across sequentially found solutions.
-\chuffed{} successively finds better solutions in terms of Eq. \ref{EQ:obj}.
+\chuffed{}, which is the solver of \serene{}, successively finds better solutions in terms of Eq. \ref{EQ:obj}.
 However,
@@
 with the first solution found, and plateaus after the third solution.
+Furthermore, we have explored how the systems perform if we manually filter out the unmatched attributes.
+In such scenario \serene{} also yields better solutions than \karma{}, and in many situations \serene{} can prove optimality of the found solutions.
+This observation provides further evidence towards the validity of our new modeling framework.
 
@@
 The main advantage of these systems is the ability to run in a fully automatic setting.
-Our approach is complementary to the approaches from this group and at its current stage is semi-automatic.
-However, constraint programming offers a convenient framework to incorporate integrity constraints specified either within relational or ontological schema as additional constraints to govern the search for the solution.
+Our approach is complementary to these approaches and at its current stage is semi-automatic.
+However, CP offers a convenient framework to incorporate integrity constraints specified either within relational or ontological schema as additional constraints to govern the search for the solution.
 This opens an interesting direction for further research.
@@
 ideas for the construction of the alignment graph.
-The only difference is that we introduce the \emph{unknown} and \emph{root} class nodes and as many \emph{unknown} data nodes as there are attributes in the modeled data source.
+The difference at this step is that we introduce the \emph{unknown} and \emph{root} class nodes and as many \emph{unknown} data nodes as there are attributes in the modeled data source.
 These nodes serve to capture the unmatched attributes from the source.
@@
 We, on the other hand, use exact algorithms for both parts and address them within a unified CP model.
-
 In their follow up work, \citeasnoun{Taheriyan:Leveraging} suggest using graph 
@@
 limited in its size.}
+
+Another relevant problem within the Semantic Web community is ontology matching, or alignment~\cite{shvaiko2013}.
+This problem is similar to schema matching since it finds semantically related entities across different ontologies.
+Yet, it is different from \relonto{} since data sources in our case are not bound to any ontology.
+We think that our approach might be further extended to incorporate ontology matching techniques.
 

### 2018-01-25 stp/paper_aaai/main.tex
back to 7 pages + ref

@@
 
-\textbf{Patterns}.
+\textbf{Patterns:}
 As explained in Subsection \ref{SSEC:pattern-mining}, we also use 
@@
 
-\textbf{Unmatched Attributes}.
+\textbf{Unmatched Attributes:}
 It is common that the data sources to be integrated will have columns that 
@@
 The model is presented below.
-
+\vspace*{-0.5em}
 \begin{flalign}
@@
 \begin{table}[ht]\small
+	\vspace*{-0.8em}
   \centering
-  \caption{Description of data sources.}\label{tab:data}
+  \caption{Description of data sources.\vspace*{-0.8em}}\label{tab:data}
 		\begin{tabular}{ccccc}
@@
   \centering
-  \caption{Average performance of semantic labeling models for leave one out strategy.}
+  \vspace*{-0.8em}
+  \caption{Average performance of semantic labeling models for leave one out strategy.  \vspace*{-0.8em}}
   	\label{tab:semlab}

### 2018-01-29 stp/paper_aaai/main.tex
start shortenning it

@@
 \usepackage{amssymb}
+\usepackage{nicefrac}
 \usepackage{textcomp}
@@
 
+\newcommand{\forijcai}[1]{}
+
 \newcommand{\citeasnoun}[1]{\citeauthor{#1}~\shortcite{#1}}
@@
 /Title (Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping)
-/Author (Submission 1204)
+/Author (Submission 1228)
 /Keywords (Machine Lerning Application, Constraint Programming, Ontology, Relational, Steiner Tree)}
@@
 \title{Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping }
-\author{Submission 1204}
+\author{Submission 1228}
 \maketitle
@@
 we can achieve better precision, recall and speed compared to state-of-the-art 
-approaches. We provide a comprehensive set of experiments supporting our 
+approaches. We provide a comprehensive set of experiments backing our 
 findings.
@@
 Our contributions are:
-\begin{itemize}
-	\item A novel modeling framework for the \relonto{} problem which 
-	seamlessly incorporates techniques from the areas of machine learning, knowledge representation and constraint programming.
+%\begin{itemize}
+	%\item 
+	A novel modeling framework for the \relonto{} problem that use ML, KRR and CP techniques,
 %	\npr{symbolic AI, ontological reasoning, transitive closure}
-	\item An efficient approach to handle attributes which cannot be matched to 
-	the ontology, through a new semantic labeling model and a new STP 
-	model with additional nodes in the integration graph.
-	\item A flexible and extensible approach to the problem, which is easy to 
-	reuse and adapt to specific situations. This is achieved since CP allows introduction of additional constraints with no changes to the solver. 
-\end{itemize}
-
+	%\item
+	an efficient approach to handle attributes which cannot be matched to 
+	the ontology, \forijcai{arg1, through a new semantic labeling model and a new STP 
+	model with additional nodes in the integration graph.}
+	%\item 
+	a flexible and extensible approach to the problem, which is easy to 
+	reuse and adapt to specific situations through the use of CP.\forijcai{ allows introduction of additional constraints with no changes to the solver.} 
+%\end{itemize}
+
+\forijcai{
 Section \ref{SEC:problem} formally states the problem. 
@@
 Section \ref{SEC:pw} compares with the previous work done to achieve this task. 
+}
 
@@
 \centering
+\scalebox{0.8}{
 \begin{tikzpicture}
@@
 \end{tikzpicture}
+}
 \caption{Example of ontology
@@
 \begin{figure}[ht]
-\centering
+\centering\scalebox{0.8}{
 \begin{tikzpicture}[scale=0.95]
@@
 \end{tikzpicture}
+}
 \caption{Examples of two semantic models (`\protect\tikz{ \protect\node[class, inner sep = 2] () at (0,0)  
@@
 is a data property of that class (including inherited properties). 
-For example, from the ontology in Fig. \ref{FIG:onto}, we would get
+For example, in Fig. \ref{FIG:onto}, we would get
 (City,name) and (State,name).
@@
 \mathcal{L_O}$.
-Typically semantic labeling techniques encounter several problems.
-Firstly, there can be naming conflicts~\cite{Pinkel:rodi}, including those 
-cases where users represent the same data in different ways.
-Secondly, semantically different attributes might have syntactically similar 
-content, for example, startDate versus endDate for the Event class.
-Thirdly, there may be a considerable number of attributes which do not have any 
-corresponding property in the ontology, either by accident or deliberately.
+Typically semantic labeling techniques encounter several problems such as:
+naming conflicts~\cite{Pinkel:rodi}, multiple data representations, and semantically different attributes might have syntactically similar 
+content.%, for example, startDate versus endDate for the Event class.
+Also, there may be a considerable number of attributes which have no 
+corresponding property in the ontology (accidentaly or deliberately).
 %\ddg{CHECK!}
@@
 values in the column. 
-A full list can be found in Appendix \ref{Ann:SemLab}.
+\forijcai{A full list can be found in Appendix \ref{Ann:SemLab}.}
 %\npr{If I remove entropy descr, we are perfectly within page limit}
@@
 To provide an integrated view over the known source descriptions $\Delta_T$, we 
-need to align their semantic models as well as all considered semantic 
+align their semantic models as well as all considered semantic 
 types. 
@@
 The links correspond 
-to properties in  $\mathcal{O}$ and are weighted \cite{taheriyan2016learning}.
-
-The algorithm we use to construct the alignment graph 
+to properties in  $\mathcal{O}$ and are weighted.
+The full algorithm we use to construct the alignment graph 
 $\mathcal{G_O}$ was given by~\citeasnoun{taheriyan2016learning}.
-Briefly, it has three parts:
+\forijcai{Briefly, it has three parts:
 %\begin{enumerate}
@@
 %\end{enumerate}
+}
 
@@
 which are inferred from the ontology.
-In the next section we will see that this makes edges from semantic models 
-more attractive. 
+\forijcai{In the next section we will see that this makes edges from semantic models 
+more attractive. }
 \citeasnoun{taheriyan2016learning} provide details on the weighting function.
 %\ddg{How exactly are they weighted?}
-
 An example alignment graph is illustrated in Fig.~\ref{FIG:ali}. 
 %Bigger examples can be found in \cite{Taheriyan2013}. 
-Black links correspond to the links which are supported by the known semantic models. 
-Blue and orange links are inferred from the ontology $\mathcal{O}$ (the orange 
+Black links are links supported by the known semantic models. 
+Blue links are inferred from the ontology.\forijcai{(the orange 
 ones correspond to the ones added to connect Classes of the ontology that never 
-appeared in the semantic models).
+appeared in the semantic models).}
 % and can be assigned the 
@@
 \begin{figure}[ht]
-\centering
+\centering \scalebox{0.8}{
 \begin{tikzpicture}[scale=0.9]
@@
 
-	\node[class,orange,fill=orange!30!white,text=black] (PL) at (3,\ysh/2)  
+	\node[class,text=black] (PL) at (3,\ysh/2)  
 	{\small 
@@
 
-	\path[draw,hasaC,->,orange!30!white] (pe1) edge[bend left=10] (PL);
-	\path[draw,hasaC,->,orange!30!white] (pe1) edge[bend left=-10] (PL);
-
-	\path[draw,hasaC,->,orange!30!white] (pe2) edge[bend left=10] (PL);
-	\path[draw,hasaC,->,orange!30!white] (pe2) edge[bend left=-10] (PL);
-
-	\path[draw,hasaC,->,orange!30!white] (co1) edge[bend left=0] (PL);
-	\path[draw,hasaC,->,orange!30!white] (co2) edge[out=45,in=225] (PL);
-
-	\path[draw,hasaC,->,orange!30!white] (ev2) edge[out=90,in=0] (PL);
-
-	\path[draw,isa,->,orange!30!white] (ci1) edge[out=-25,in=130] (PL);
-	\path[draw,isa,->,orange!30!white] (pl2) edge[out=50,in=180] (PL);
-	\path[draw,isa,->,orange!30!white] (st1) edge[out=-45,in=160] (PL);
-
-\end{tikzpicture}
+	\path[draw,hasaC,->,blue!70] (pe1) edge[bend left=10] (PL);
+	\path[draw,hasaC,->,blue!70] (pe1) edge[bend left=-10] (PL);
+
+	\path[draw,hasaC,->,blue!70] (pe2) edge[bend left=10] (PL);
+	\path[draw,hasaC,->,blue!70] (pe2) edge[bend left=-10] (PL);
+
+	\path[draw,hasaC,->,blue!70] (co1) edge[bend left=0] (PL);
+	\path[draw,hasaC,->,blue!70] (co2) edge[out=45,in=225] (PL);
+
+	\path[draw,hasaC,->,blue!70] (ev2) edge[out=90,in=0] (PL);
+
+	\path[draw,isa,->,blue!70] (ci1) edge[out=-25,in=130] (PL);
+	\path[draw,isa,->,blue!70] (pl2) edge[out=50,in=180] (PL);
+	\path[draw,isa,->,blue!70] (st1) edge[out=-45,in=160] (PL);
+
+\end{tikzpicture}}
 \caption{Example of alignment graph (`\protect\tikz{ \protect\node[class, inner sep = 2] () at (0,0)  
-{};}' `\protect\tikz{ \protect\node[class,orange,fill=orange!30!white,text=black, inner sep = 2] () at 
+{};}' \forijcai{`\protect\tikz{ \protect\node[class,orange,fill=orange!30!white,text=black, inner sep = 2] () at 
 (0,0)  
-{};}' are class nodes, and `\protect\tikz{ \protect\node[data] () at (0,0)  {};}' are data 
+{};}'} are class nodes, and `\protect\tikz{ \protect\node[data] () at (0,0)  {};}' are data 
 nodes). We omit weights for clarity.}
@@
 Certain patterns of connections can be prevalent in the domain.
+\forijcai{
 For example, in Fig.~\ref{FIG:sem} both semantic models have class nodes ``City'', ``Organization'' and ``Person''.
 According to the ontology in Fig.~\ref{FIG:onto} there are multiple ways to connect these nodes.
-However, if we know that the ``Person'' works for the ``Organization'', then based on the known semantic models (Fig.~\ref{FIG:sem}), ``City'' is more likely to be the birth place of the ``Person'' rather than the location of the ``Organization''.
+}
+If we know that the ``Person'' works for the ``Organization'', then based on the known semantic models (Fig.~\ref{FIG:sem}), ``City'' is more likely to be the birth place of the ``Person'' rather than the location of the ``Organization''.
 To increase the coherence of the generated semantic models, we would like to discover such patterns of connections.
-
 %As an extension to the problem, we consider using pattern mining techniques in order to identify patterns in the training set of semantic model that repeat themselves often. 
@@
 %\npr{reformulate for typed directed multigraphs and example based on Fig3}
-In our context, patterns are typed directed graphs.
+
+%In our context, patterns are typed directed graphs.
 We mine these patterns from the set of semantic models in the training set $\Delta_T$.
-This is known as Transactional Frequent Graph Pattern Mining, which
-includes the subgraph isomorphism problem, known to be NP-complete.
+This is known as Transactional Frequent Graph Pattern Mining\forijcai{, which
+includes the subgraph isomorphism problem, known to be NP-complete}.
 The frequency of a pattern is the number of semantic models 
@@
 % \ddg{Define support}
-We solve the pattern mining task with the tool DIMSpan \cite{petermann2017dimspan} which adapts gSpan~\cite{yan2002gspan} pruning techniques to the typed graphs and uses Apache Flink for scalability.
+We solve the pattern mining task with the tool DIMSpan \cite{petermann2017dimspan} which adapts gSpan~\cite{yan2002gspan} pruning techniques to the typed graphs.\forijcai{and uses Apache Flink for scalability.}
 We obtain patterns of size up to 6 in under 4 minutes for the biggest instances 
@@
 	\path[draw] (a4) -- (con2);
-\end{tikzpicture}
+\end{tikzpicture} }
 \caption{Example of integration graph. (`\protect\tikz{ \protect\node[att] () at (0,0)  
@@
 direction of edges for the STP model.
-We disambiguate the direction and semantics of edges via their
+We disambiguate the direction \forijcai{and semantics} of edges via their
 weights.
-We can further improve this step by using patterns.
+\forijcai{We can further improve this step by using patterns.}
 %\npr{this was not completely correct}
@@
 \textbf{Patterns:}
-As explained in Subsection \ref{SSEC:pattern-mining}, we also use 
-graph patterns in order to incentivise the solution tree 
+As explained in Sec. \ref{SSEC:pattern-mining}, we use 
+graph patterns to incentivise the solution tree 
 $T^\star$ to contain subgraphs of the alignment graph that have been frequently 
 seen in the training set.
-To do this, we use the support of each of the obtained patterns as a prize. If 
+To do this, we use the support of each obtained patterns as a prize. If 
 the tree contains a pattern, then its weight is automatically reduced by the 
-value of the support of that pattern. We will see in the next section how this 
-information is integrated in the model.
+value of the support of that pattern. Sec. \ref{SEC:rel2ontocp} shows how this is integrated in the model.
 
@@
 \section{Modeling in Constraint Programming \label{SEC:CP}}
-\subsection{Definitions}
+%\subsection{Definitions}
 
@@
 
-Constraint Programming (CP) allows the user to model a COP and give it 
+CP allows the user to model a COP and give it 
 to a solver that will find solutions while optimizing 
@@
 
-Briefly, the way a CP solver works is by assigning a value to each variable of 
+Briefly, a CP solver assigns values to each variable of 
 $\boldsymbol{v}$ in turn. 
@@
 
-\subsection{\relonto{} in Constraint Programming}
-In order to model the \relonto{} problem we used the \minizinc{} language 
+\subsection{\relonto{} in Constraint Programming\label{SEC:rel2ontocp}}
+We used the \minizinc{} language 
 \cite{minizinc}, and the 
-\chuffed{} solver \cite{chu2011improving} because it has a global constraint 
+\chuffed{} solver. \cite{chu2011improving}\forijcai{ because it has a global constraint 
 implemented for Steiner 
-Tree Problems \cite{deuna2016steiner}. The model can be found in Appendix \ref{Ann:MZ}.
+Tree Problems \cite{deuna2016steiner}. The model can be found in Appendix \ref{Ann:MZ}}
 
@@
 
-Because there are global constraints in CP specialized in matching 
+Since there are global constraints in CP specialized in matching 
 \cite{regin1994filtering}, we split the problem into two parts: the 
@@
 	& w_{\mathit{ADIFF}} = \sum_{(a,d) \in \mathcal{M}_\mathcal{O}^{s^\star}} 
-	w_\mathcal{I}(~(a,d)~) * \llbracket match[a] = d\rrbracket 
+	w_\mathcal{I}((a,d)) * \llbracket match[a] = d\rrbracket 
 	\label{EQ:matchcost}  &&\\
@@
 	\mathit{true} \big) \Leftrightarrow c_p \label{EQ:patt}&&\\
-	& w_{PAT} = \sum_{p\in\mathcal{P}} w_\mathcal{P}(p)* c_p 
+	& w_{PAT} = \textstyle\sum_{p\in\mathcal{P}} w_\mathcal{P}(p)* c_p 
 	\label{EQ:pcost} &&\\
@@
 
+\forijcai{
 Note how this CP model is easy to adapt to more classic settings where no 
@@
 $\forall e_p\in p, e_p \neq e, c_{e_p}$) such that $w_\mathcal{P}(p) > w_\mathcal{O}(e)$ or simply the cheapest edge if none fill a pattern.
+}
 
@@
 
-\subsection{Experimental Setup}
+%\subsection{Experimental Setup}
 
@@
 
-We run experiments on two domains: museum and soccer (see Fig.~\ref{tab:data} for statistics).
+We run experiments on two domains: museum (29 sources, 20 labels, 443 attributes and 159 \emph{unknown}s) and soccer (12 sources, 18 labels, 138 attributes and 45 \emph{unknown}s).% (see Fig.~\ref{tab:data} for statistics).
+
+\forijcai{
 The museum dataset~\cite{taheriyan2016learning} contains 29 sources which are mapped to the EDM domain ontology.
@@
 \end{table}
+}
 
@@
 Assuming $m^{p}$ is the predicted semantic model and $m^\dag$ is the correct semantic model, then:
-$$\mathit{prec} = \frac{|\mathit{rel}(m^{p})\cap 
+$\mathit{prec} = \nicefrac{|\mathit{rel}(m^{p})\cap 
 \mathit{rel}(m^\dag)|}{|\mathit{rel}(m^{p})|}, 
-\mathit{recall} = \frac{|\mathit{rel}(m^{p})\cap 
-\mathit{rel}(m^\dag)|}{|\mathit{rel}(m^\dag)|}$$
+\mathit{recall} = \nicefrac{|\mathit{rel}(m^{p})\cap 
+\mathit{rel}(m^\dag)|}{|\mathit{rel}(m^\dag)|}$
 where $rel(m)$ is the set of triples $(u,e,v)$ with $e$ being an edge from the vertex $u$ to the vertex $v$ in the semantic model $m$.
@@
 matching task, 
-we compare it against the state-of-the-art model \emph{DSL}~\cite{Pham:semantic} which was shown to perform 
-even better than SemanticTyper. 
+we compare it against the state-of-the-art model \emph{DSL}~\cite{Pham:semantic}.\forijcai{which was shown to perform 
+even better than SemanticTyper.} 
 %\npr{not sure whether I should explain how this model works}
@@
 This measure is useful to estimate how highly the true semantic label is ranked among the top $k$ suggestions.
-It is calculated the following way:
-$MRR = \frac{1}{n}\sum_{i=1}^{n}{\frac{1}{rank_i}},$
-where $rank_i$ is the rank of the correct semantic label for the attribute $a_i$ among the top $k$ predictions and $n$ is the number of attributes in the data source.
+It is defined as:
+$MRR = \frac{1}{n}\sum_{i=1}^{n}{\frac{1}{r_i}},$
+where $r_i$ is the rank of the correct semantic label for the attribute $a_i$ among the top $k$ predictions and $n$ is the number of attributes in the data source.
 
 % evaluation strategy
-We perform an evaluation strategy outlined by~\cite{taheriyan2016learning}.
+We perform an evaluation strategy outlined by~\citeasnoun{taheriyan2016learning}.
 Let $M_j$ be the set of $j$ known semantic models.
@@
 where $t$ is the total number of data sources in the domain and each experiment has a different number of known semantic models $M_1, M_2, \ldots, M_{t-1}$.
-The case with $M_{t-1}$ known semantic models corresponds to leave-one-out validation strategy. 
+\forijcai{The case with $M_{t-1}$ known semantic models corresponds to leave-one-out validation strategy.} 
 For example, in the soccer domain for the source $s_1$ we run experiments 11 times using $M_1=\{m_2\}, M_2=\{m_2, m_3\}, \ldots, M_{11}=\{m_2, m_3, \ldots, m_{12}\}$
@@
 % architecture
-We have run all our experiments on a Dell server with 252 GB of memory, 2 CPUs 
-with 4 cores each.
+We have run all our experiments on a Dell server with 252 GB of RAM, 2 CPUs (4 cores).
 %\npr{check characteristics, AWS machine is bigger}
-In all our experiments we use a timeout threshold of 15s for \chuffed{}, which 
-runs on a single core (thus easy to deploy on any user's machine).
+We use a timeout threshold of 15s for \chuffed{}, which 
+runs on a single core.
 
@@
   \vspace*{-0.8em}
-  \caption{Average performance of semantic labeling models for leave one out strategy.  \vspace*{-0.8em}}
+  \caption{Average performance of semantic labeling models% for leave one out strategy.
+  	  \vspace*{-0.8em}}
   	\label{tab:semlab}
+  	\scalebox{0.8}{
   	\begin{tabular}{c|cc|cc} 
@@
 		\end{tabular} 
+		}
 %\vspace*{-3mm}
@@
 
-\begin{figure}[!htb]
+\begin{figure}[!b]
 \begin{minipage}[b]{.5\linewidth}
@@
 \hspace*{-15pt}
-\begin{tikzpicture}[baseline,scale=0.43]
+\begin{tikzpicture}[baseline,scale=0.35]
 \begin{axis}[
@@
 \centering
-\begin{tikzpicture}[baseline,scale=0.43]
+\begin{tikzpicture}[baseline,scale=0.35]
 		\begin{axis}[
@@
 \begin{minipage}[b]{0.5\linewidth}
+
 \centering
-\begin{tikzpicture}[baseline,scale=0.43]
+\begin{tikzpicture}[baseline,scale=0.35]
 		\begin{axis}[
@@
 \end{minipage}%
+\vspace*{-3mm}
 \caption{Performance for the museum and soccer domains. 
@@
 % karma vs serene vs serene-pats
-We evaluate \serene{} and its modification \serenepats{}, which 
-uses graph patterns, against the state-of-the-art system \karma{}.
+We evaluate \serene{} and \serenepats{} against the state-of-the-art system \karma{}.
 All three systems have access to the same set of matches produced by our semantic labeling model.
@@
 across sequentially found solutions.
-\chuffed{}, which is the solver of \serene{}, successively finds better solutions in terms of Eq. \ref{EQ:obj}.
+\chuffed{}, the solver of \serene{}, successively finds better solutions in terms of Eq. \ref{EQ:obj}.
 However,
@@
 with the first solution found, and plateaus after the third solution.
-Furthermore, we have explored how the systems perform if we manually filter out the unmatched attributes.
-In such scenario \serene{} also yields better solutions than \karma{}, and in many situations \serene{} can prove optimality of the found solutions.
-This observation provides further evidence towards the validity of our new modeling framework.
+Also, we have explored how the systems perform if we manually filter out the unmatched attributes.
+In such scenario \serene{} also yields better solutions than \karma{}, and can often prove optimality of the found solutions.
+This observation provides further evidence towards the validity of our new framework.
 
@@
 
-\begin{figure}[!ht]\small
+\begin{figure}[t]\small
 \centering
-\begin{tikzpicture}[scale=0.39]
+\begin{tikzpicture}[scale=0.35]
 \pgfplotsset{
@@
 \end{tikzpicture}
-\caption{Performance of \serene{} for leave-one-out strategy on the museum 
+\caption{Performance of \serene{} on the museum 
 domain.}\label{fig:loo}
@@
 
-The majority of approaches to solve the \relonto{} mapping problem are based on 
+Most approaches to solve the \relonto{} problem are based on 
 heuristic rules and alignment of constraints specified within relational 
@@
 Crudely speaking, these tools first apply a default direct mapping specified by the W3C.
-Further, the default ontology is enriched by using explicit and implicit schema constraints.
+Then, the default ontology is enriched by using explicit and implicit schema constraints.
 Finally, ontology alignment techniques are applied to match the default ontology to the target ontology.
 The main advantage of these systems is the ability to run in a fully automatic setting.
-Our approach is complementary to these approaches and at its current stage is semi-automatic.
+Our approach is complementary to them and at its current stage is semi-automatic.
 However, CP offers a convenient framework to incorporate integrity constraints specified either within relational or ontological schema as additional constraints to govern the search for the solution.
-This opens an interesting direction for further research.
+\forijcai{This opens an interesting direction for further research.}
 
@@
 the Web.
-To overcome this issue, we can apply ML techniques.
-\citeasnoun{Limaye:Annotating} design a system to annotate web tables with 
+To overcome this issue,
+\citeasnoun{Limaye:Annotating} design a ML system to annotate web tables with 
 entities for cell values, semantic labels for attributes and relationships for 
@@
 However, it could be further bootstrapped by leveraging external knowledge bases.
-This is especially beneficial at the start when the system does not have sufficient training data.
+This is especially beneficial when the system does not have sufficient training data.
 
@@
 \section{Conclusion}
-In this paper we have introduced a new approach, \serene{} (and its extension 
-that uses frequent graph patterns, \serenepats{}) to solve the problem of 
+In this paper we have introduced a new approach\forijcai{, \serene{} (and its extension 
+that uses frequent graph patterns, \serenepats{})} to solve the problem of 
 relational-to-ontology schema mapping.

### 2018-01-30 stp/paper_aaai/main.tex
shortened to 6 pages

@@
 Relational data sources are still one of the most popular ways to store enterprise or Web data. However, the issue with relational schema is the lack of a well-defined semantic description.
-A common ontology provides a way of representing the meaning of a relational schema and can facilitate the integration of heterogeneous data sources within a domain.
+A common ontology provides a way of representing the meaning of a relational schema and can facilitate the integration of heterogeneous data sources\forijcai{ within a domain}.
 Indicating semantic correspondences manually might be appropriate if only few data sources need to be integrated, however, it becomes tedious with the growing number of heterogeneous schemata.
@@
 email address of the company. 
-Given an ontology like the one in Fig. \ref{FIG:onto}, we would like to automatically map the new data sources to  the 
-ontology.\hfill$\square$
+Given an ontology like in Fig. \ref{FIG:onto}, we would like to automatically map new data sources to  the 
+ontology.\forijcai{\hfill$\square$}
 
@@
 We name it \emph{integration graph}.
-It uses information gathered from the previously mapped data sources, and is further extended with information derived from the ontology.
+It uses information gathered from previously mapped data sources, and is further extended with information derived from the ontology.
 %Firstly, we build a \emph{integration graph} which includes the 
 %attributes from the new source as well as ontology classes and properties.
-Secondly, we apply machine learning techniques to 
+Secondly, we apply ML techniques to 
 assign costs to its edges. 
@@
 	%\item 
-	A novel modeling framework for the \relonto{} problem that use ML, KRR and CP techniques,
+	a novel modeling framework for the \relonto{} problem that uses ML, KRR and CP techniques;
 %	\npr{symbolic AI, ontological reasoning, transitive closure}
@@
 	an efficient approach to handle attributes which cannot be matched to 
-	the ontology, \forijcai{arg1, through a new semantic labeling model and a new STP 
+	the ontology; \forijcai{through a new semantic labeling model and a new STP 
 	model with additional nodes in the integration graph.}
 	%\item 
-	a flexible and extensible approach to the problem, which is easy to 
+	a flexible and extensible approach to the problem, easy to 
 	reuse and adapt to specific situations through the use of CP.\forijcai{ allows introduction of additional constraints with no changes to the solver.} 
@@
 \section{Problem Statement \label{SEC:problem}}
-
-\begin{figure}[ht]
-\centering
-\scalebox{0.8}{
-\begin{tikzpicture}
-	\node[class] (pe) at (0,0)  {Person};
-	\node[class] (co) at (0,-2) {Organisation};
-	\node[class] (ev) at (3,0.2) {Event};
-	\node[class] (pl) at (5,-1) {Place};
-	\node[class] (ci) at (3,-2.5) {City};
-	\node[class] (st) at (5,-2.5) {State};
-
-	\path[hasaC,->] (pe) edge [bend left= -30] 
-	node [midway, above, sloped] {worksFor} (co) ;
-	\path[hasaC,->] (co) edge [bend left= -30] 
-	node [midway, above, sloped] {ceo} (pe) ;
-
-	\path[hasaC,->] (co) edge [] 
-	node [near start, above, sloped] {location} (pl) ;
-
-	\path[hasaC,->] (pe) edge [bend left = -20] 
-	node [midway, above, sloped] {bornIn} (pl) ;
-	\path[hasaC,->] (pe) edge [bend left = 0] 
-	node [midway, above, sloped] {livesIn} (pl) ;
-
-	\path[hasaC,->] (ev) edge [bend left = -20] 
-	node [midway, above, sloped] {organizer} (pe) ;
-	\path[hasaC,->] (ev) edge [bend left = 0] 
-	node [midway, above, sloped] {location} (pl) ;
-
-	\path[hasaC,->] (pl) edge [out=20,in=0,looseness=8] 
-	node [midway, above, sloped] {nearby} (pl) ;
-	\path[hasaC,->] (pl) edge [out=45,in=65,looseness=8] 
-	node [midway, above, sloped] {partOf} (pl) ;
-
-	\path[hasaC,->] (ci) edge  []
-	node [midway, above, sloped] {isIn} (st) ;
-
-	\path[isa,->] (ci) -- node [] {} (pl) ;
-	\path[isa,->] (st) -- node [] {} (pl) ;
-
-	\path[draw,hasaA,->] (pe) edge [decorate,out=140,in=0] 
-	node [midway, above, sloped] {name} (-0.9,0.5);
-	\path[draw,hasaA,->] (pe) edge [decorate,out=100,in=0] 
-	node [midway, above, sloped] {birthDate} (-0.9,1);
-
-	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
-	node [midway, below, sloped] {name} (-1,-3);
-	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
-	node [midway, above, sloped] {phone} (0,-3.2);
-	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
-	node [midway, above, sloped] {email} (1.4,-3);
-
-	\path[draw,hasaA,->] (ev) edge [decorate,out=70,in=200] 
-	node [midway, above, sloped] {startDate} (3.8,1);
-	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
-	node [midway, above, sloped] {endDate} (4.5,0.8);
-	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
-	node [midway, above, sloped] {title} (5,0.2);
-
-	\path[draw,hasaA,->] (pl) edge [decorate,bend left = 0] 
-	node [midway, above, sloped] {name} (6.5,-1.8);
-	\path[draw,hasaA,->] (pl) edge [decorate,bend left = 0] 
-	node [midway, above, sloped] {postalCode} (6,-3);
-
-\end{tikzpicture}
-}
-\caption{Example of ontology
-(`\protect\tikz{ \protect\node[class, inner sep = 2] () at (0,0)  {};}' are Classes, `\protect\tikz{ \protect\path[hasaC,->] 
-(0,1) -- (3ex,1);}' means ``has an object property'', 
-`\protect\tikz{ \protect\path[hasaA,decoration={post length=0}] (0,0) edge[decorate] (3ex,0);}' 
-means ``has a data property'' and 
-`\protect\tikz{ \protect\path[isa,->] (0,1) -- (3ex,1);}' means ``subClassOf'' ). Example by
-\protect\citeasnoun{Taheriyan2013}.
-}
-\label{FIG:onto}
-\vspace{-3mm}
-\end{figure}
 
@@
 
+\begin{figure}[!t]
+	\centering
+	\scalebox{0.8}{
+		\begin{tikzpicture}
+		\begin{scope}
+		\node[class] (pe) at (0,0)  {Person};
+		\node[class] (co) at (0,-2) {Organisation};
+		\node[class] (ev) at (3,0.2) {Event};
+		\node[class] (pl) at (5,-1) {Place};
+		\node[class] (ci) at (3,-2.5) {City};
+		\node[class] (st) at (5,-2.5) {State};
+
+		\path[hasaC,->] (pe) edge [bend left= -30] 
+		node [midway, above, sloped] {worksFor} (co) ;
+		\path[hasaC,->] (co) edge [bend left= -30] 
+		node [midway, above, sloped] {ceo} (pe) ;
+
+		\path[hasaC,->] (co) edge [] 
+		node [near start, above, sloped] {location} (pl) ;
+
+		\path[hasaC,->] (pe) edge [bend left = -20] 
+		node [midway, above, sloped] {bornIn} (pl) ;
+		\path[hasaC,->] (pe) edge [bend left = 0] 
+		node [midway, above, sloped] {livesIn} (pl) ;
+
+		\path[hasaC,->] (ev) edge [bend left = -20] 
+		node [midway, above, sloped] {organizer} (pe) ;
+		\path[hasaC,->] (ev) edge [bend left = 0] 
+		node [midway, above, sloped] {location} (pl) ;
+
+		\path[hasaC,->] (pl) edge [out=20,in=0,looseness=8] 
+		node [midway, above, sloped] {nearby} (pl) ;
+		\path[hasaC,->] (pl) edge [out=45,in=65,looseness=8] 
+		node [midway, above, sloped] {partOf} (pl) ;
+
+		\path[hasaC,->] (ci) edge  []
+		node [midway, above, sloped] {isIn} (st) ;
+
+		\path[isa,->] (ci) -- node [] {} (pl) ;
+		\path[isa,->] (st) -- node [] {} (pl) ;
+
+		\path[draw,hasaA,->] (pe) edge [decorate,out=140,in=0] 
+		node [midway, above, sloped] {name} (-0.9,0.5);
+		\path[draw,hasaA,->] (pe) edge [decorate,out=100,in=0] 
+		node [midway, above, sloped] {birthDate} (-0.9,1);
+
+		\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
+		node [midway, below, sloped] {name} (-1,-3);
+		\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
+		node [midway, above, sloped] {phone} (0,-3.2);
+		\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
+		node [midway, above, sloped] {email} (1.4,-3);
+
+		\path[draw,hasaA,->] (ev) edge [decorate,out=70,in=200] 
+		node [midway, above, sloped] {startDate} (3.8,1);
+		\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
+		node [midway, above, sloped] {endDate} (4.5,0.8);
+		\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
+		node [midway, above, sloped] {title} (5,0.2);
+
+		\path[draw,hasaA,->] (pl) edge [decorate,bend left = 0] 
+		node [midway, above, sloped] {name} (6.5,-1.8);
+		\path[draw,hasaA,->] (pl) edge [decorate,bend left = 0] 
+		node [midway, above, sloped] {postalCode} (6,-3);
+
+		\end{scope}
+		\begin{scope}[xshift=7cm]
+		\path[hasaC,->] (0,0)  to
+		(0.5,0) ;
+		\node[text=black,text width=2cm] (legend1) at (1.7,0)  
+		{\small 
+			``has an object property''};
+
+		\path[hasaA,->] (0,-1.2)  to
+		(0.5,-1.2) ;
+		\node[text=black,text width=2cm] (legend1) at (1.7,-1.2)  
+		{\small 
+			``has a data property''};
+
+		\path[isa,->] (0,-1.9)  to
+		(0.5,-1.9) ;
+		\node[text=black,text width=2cm] (legend1) at (1.7,-1.9)  
+		{\small 
+			``subClassOf''};
+
+		\end{scope}
+		\end{tikzpicture}
+	}
+	\caption{Example of ontology \forijcai{
+			(`\protect\tikz{ \protect\node[class, inner sep = 2] () at (0,0)  {};}' are Classes, `\protect\tikz{ \protect\path[hasaC,->] 
+				(0,1) -- (3ex,1);}' means ``has an object property'', 
+			`\protect\tikz{ \protect\path[hasaA,decoration={post length=0}] (0,0) edge[decorate] (3ex,0);}' 
+			means ``has a data property'' and 
+			`\protect\tikz{ \protect\path[isa,->] (0,1) -- (3ex,1);}' means ``subClassOf'' ). Example }by
+		\protect\citeasnoun{Taheriyan2013}.
+	}
+	\label{FIG:onto}
+	\vspace{-3mm}
+\end{figure}
+
 A \emph{semantic model} $m$ is a directed graph with two types of nodes: 
@@
 The semantic model may have several instances of the same ontology class, that is why class nodes are enumerated.
-Semantic models can be formalized using a standard mapping language such as R2RML~\cite{r2rml}.
+\forijcai{Semantic models can be formalized using a standard mapping language such as R2RML~\cite{r2rml}.}
 
@@
 is a data property of that class (including inherited properties). 
-For example, in Fig. \ref{FIG:onto}, we would get
+E.g., in Fig. \ref{FIG:onto}, we would get
 (City,name) and (State,name).
@@
 naming conflicts~\cite{Pinkel:rodi}, multiple data representations, and semantically different attributes might have syntactically similar 
-content.%, for example, startDate versus endDate for the Event class.
+content. %, for example, startDate versus endDate for the Event class.
 Also, there may be a considerable number of attributes which have no 
@@
 To evaluate $p_i$ in Shannon's entropy, we evaluate normalized character frequency distribution \emph{chardist} of an attribute, as character counts in concatenated rows of the attribute, normalized by the total length of the concatenated rows.
-The vocabulary of all characters consists of 100 printable characters (including $\backslash$n).
+The alphabet\forijcai{vocabulary of all characters} consists of 100 printable characters\forijcai{ (including $\backslash$n)}.
 Finally, we add the 100-dimensional vector of $p_i$ to the attribute feature vector.
@@
 To provide an integrated view over the known source descriptions $\Delta_T$, we 
-align their semantic models as well as all considered semantic 
+align their semantic models as well as all semantic 
 types. 
-This is achieved by constructing an \emph{alignment graph}.
+This is done by building an \emph{alignment graph}.
 
@@
 %Bigger examples can be found in \cite{Taheriyan2013}. 
-Black links are links supported by the known semantic models. 
-Blue links are inferred from the ontology.\forijcai{(the orange 
+\forijcai{Black links are links supported by the known semantic models. 
+Blue links are inferred from the ontology.(the orange 
 ones correspond to the ones added to connect Classes of the ontology that never 
@@
 \begin{tikzpicture}[scale=0.9]
+\begin{scope}[xshift=-10]
 
@@
 
+\end{scope}
+\begin{scope}[xshift=7cm]
+	\path[hasaC,->] (0,0)  to
+	 (0.5,0) ;
+	 \node[text=black,text width=2cm] (legend1) at (1.7,0)  
+	 {\small 
+	 	Link supported by known semantic models};
+
+	 	\path[isa,->,blue!70] (0,-1.2)  to
+	 	(0.5,-1.2) ;
+	 		 	\path[hasaC,->,blue!70] (0,-1.5)  to
+	 		 	(0.5,-1.5) ;
+	 	\node[text=black,text width=2cm] (legend1) at (1.7,-1.3)  
+	 	{\small 
+	 		Links inferred from ontology};
+\end{scope}
 \end{tikzpicture}}
@@
 (V, E)$ and a subset of its nodes $T \subseteq V$, a 
-Steiner Tree $G_s = (V_s, E_s )$ is a tree (connected acyclic graph) such that 
+Steiner Tree $G_s = (V_s, E_s )$ is a tree \forijcai{(connected acyclic graph) }such that 
 $T \subseteq V_s \subseteq 
 V$ and $E_s \subseteq E$. 
-In other words, $G_s$ spans all the nodes in $T$ and 
-may include additional nodes from $V$, in particular to ensure the 
+That is\forijcai{In other words}, $G_s$ spans all the nodes in $T$ and 
+may include additional nodes from $V$\forijcai{, in particular} to ensure the 
 connectedness of the constructed tree. 
@@
 \mapsto \mathbb{R}$, find the Steiner Tree that minimizes the sum of the 
-weights of the edges in $E_s$ given by $w_f$. This was proven to be NP-hard 
+weights of the edges in $E_s$\forijcai{ given by $w_f$}. This was proven to be NP-hard 
 by \citeasnoun{Karp1972}.
@@
 \begin{tikzpicture}[scale=0.9]
+\begin{scope}
 	\node[class, rectangle, rounded corners] (CLASS) at (0,0) { \small{ 
@@
 	\path[draw] (a4) -- (con2);
+	\end{scope}
+	\begin{scope}[xshift=5cm]
+\node[att] () at (0,0)  
+{};  
+\node[text=black,text width=1.5cm] (legend1) at (1.3,0)  
+{\small 
+	Attribute nodes};
+
+	\end{scope}
 \end{tikzpicture} }
-\caption{Example of integration graph. (`\protect\tikz{ \protect\node[att] () at (0,0)  
-{};}' are attribute nodes). We omit weights and only show the most likely 
-matches for clarity. Data node
-are the same as in Fig \ref{FIG:ali}.}
+\caption{Example of integration graph. We omit weights and only show the most likely 
+matches for clarity.\forijcai{ Data node
+are the same as in Fig. \ref{FIG:ali}.}}
 \label{FIG:inte}
@@
 the tree contains a pattern, then its weight is automatically reduced by the 
-value of the support of that pattern. Sec. \ref{SEC:rel2ontocp} shows how this is integrated in the model.
+value of the support of that pattern. \forijcai{Sec. \ref{SEC:rel2ontocp} shows how this is integrated in the model.}
 
@@
 node \emph{unknown}. 
-The rest of the attributes can then be matched normally 
+The other attributes can be matched normally 
 and build a semantic model as usual. 
-To maintain connectedness of the 
-Steiner tree, the \emph{unknown} node and one of the other Class nodes in $T^\star$ 
+To maintain connectedness of $T^\star$, the \emph{unknown} node and one of the other Class nodes in $T^\star$ 
 will 
@@
 Note that if all attributes find a 
-match, then both the \emph{unknown} and \emph{root} nodes will not be selected in 
-the Steiner tree and the normal behavior will take place.
+match, then neither \emph{unknown} or \emph{root} will be selected and the normal behavior will take place.
 The weights of the edges between these special nodes are
@@
 \exists \theta, \theta(\boldsymbol{v}) < \theta^*(\boldsymbol{v})$.
-
 CP allows the user to model a COP and give it 
-to a solver that will find solutions while optimizing 
-the objective function (and prove optimality).
+to a ``black-box'' solver to find solutions while optimizing 
+the objective function\forijcai{ (and prove optimality)}.
 
@@
 \cite{minizinc}, and the 
-\chuffed{} solver. \cite{chu2011improving}\forijcai{ because it has a global constraint 
+\chuffed{} solver \cite{chu2011improving}. \forijcai{ because it has a global constraint 
 implemented for Steiner 
@@
 
-Because attributes must be connected to exactly one node of the alignment 
+Since attributes must be connected to exactly one node of the alignment 
 graph, and that node will be in $\mathcal{D_{G_O}} \cap V^\star$, 
 then the part of the problem between attribute nodes and the alignment graph is 
-actually a matching problem. Each attribute must match exactly one node of 
+\forijcai{actually} a matching problem. Each attribute must match exactly one node of 
 $\mathcal{D_{G_O}}$. Note that not all nodes in $\mathcal{D_{G_O}}$ need to match 
-to an attribute, as not all of them are part of $T^\star$.
-
-Since there are global constraints in CP specialized in matching 
+to an attribute, as they are not all part of $T^\star$.
+
+Because there are global constraints in CP specialized in matching 
 \cite{regin1994filtering}, we split the problem into two parts: the 
@@
 
-We use the following variables to represent the tree $T^\star$: Boolean 
+We use Boolean 
 variables $c_n,\forall n \in 
 \mathcal{V_O}$, $c_e, \forall e \in	\mathcal{E_O}$ and an array of variables 
-$match$ indexed by the set of attributes of $s^\star$. The combination of these 
-sets of variables define the value of $T^\star$: $c_n = \mathit{true}$ means 
+$match$ indexed by the set of attributes of $s^\star$ to represent the tree $T^\star$: $c_n = \mathit{true}$ means 
 that $n \in V^\star$, $c_e = \mathit{true}$ means that $e \in E^\star$ and 
@@
 
-Eq.~\ref{EQ:obj} is the objective function: we are minimizing the cost 
+Eq.~\ref{EQ:obj} is the objective function: we minimize the cost 
 of $T^\star$ while collecting prizes for each pattern we use. 
-Eq.~\ref{EQ:stp} enforces that the solution 
-$T^\star$ is indeed a tree defined by the $c_n$ and $c_e$ variables,
-subgraph of the alignment graph 
+Eq.~\ref{EQ:stp} enforces the solution 
+$T^\star$ to be a tree defined by the $c_n$ and $c_e$ variables,
+subgraph of $\mathcal{G_O}$%the alignment graph 
 and of total weight $w_{STP}$. 
-Eq.~\ref{EQ:deg1} and \ref{EQ:deg2} ensure 
-that if a data node of the alignment graph is selected, then at most one edge 
-reaches it (from the side of the alignment graph) and otherwise it is 
+Eqs.~\ref{EQ:deg1} and \ref{EQ:deg2} ensure 
+that if a data node of $\mathcal{G_O}$ is selected, then at most one edge 
+reaches it (from the side of $\mathcal{G_O}$) and otherwise it is 
 disconnected. 
@@
 variable in 
-the array $match$ corresponds to a subset of data nodes of the alignment graph 
+the array $match$ corresponds to a subset of data nodes of $\mathcal{G_O}$ 
 for which there is an edge connecting to the attribute at hand. 
 Eq.~\ref{EQ:alld} ensure that each attribute is mapped to exactly one data node of 
-the alignment graph.}
-Eq.~\ref{EQ:matchdom} and \ref{EQ:alld} ensure that 
+$\mathcal{G_O}$.}
+Eqs.~\ref{EQ:matchdom} and \ref{EQ:alld} ensure that 
 there is exactly one data node matched to an attribute. 
 Eq.~\ref{EQ:map} ensures that 
-if a data node of the alignment graph has been mapped to some attribute, then 
+if a data node of $\mathcal{G_O}$ has been mapped to some attribute, then 
 that data node must be in the solution tree, and vice-versa. 
@@
 Notice there is no further requirement for unmatched attributes, as the 
-$unk_i$ data nodes behave like normal data nodes, and the connectedness 
+$unk_i$ nodes behave like normal data nodes, and the connectedness 
 requirement will make sure that \emph{root} is connected to the rest of the 
@@
 % datasets for evaluation
-For the rest of the paper, we call our system \serene{} if no patterns are used in the model, and \serenepats{} otherwise.
-
-We run experiments on two domains: museum (29 sources, 20 labels, 443 attributes and 159 \emph{unknown}s) and soccer (12 sources, 18 labels, 138 attributes and 45 \emph{unknown}s).% (see Fig.~\ref{tab:data} for statistics).
+From now on, we call our system \serene{} if no patterns are used in the model, and \serenepats{} otherwise.
+We run experiments on two domains: museum (29 sources, 20 labels, 443 semantic attributes and 159 \emph{unknown} attributes) and soccer (12 sources, 18 labels, 138 attributes and 45 \emph{unknown}s).% (see Fig.~\ref{tab:data} for statistics).
 
@@
 % semantic labeling models
-To illustrate that our semantic labeling model is better suited for the
-matching task, 
-we compare it against the state-of-the-art model \emph{DSL}~\cite{Pham:semantic}.\forijcai{which was shown to perform 
-even better than SemanticTyper.} 
+\forijcai{To illustrate that our semantic labeling model is better suited for the
+matching task, }
+We compare our semantic labeling model against the state-of-the-art model \emph{DSL}~\cite{Pham:semantic}, which was shown to perform 
+even better than SemanticTyper.
 %\npr{not sure whether I should explain how this model works}
@@
 \forijcai{The case with $M_{t-1}$ known semantic models corresponds to leave-one-out validation strategy.} 
-For example, in the soccer domain for the source $s_1$ we run experiments 11 times using $M_1=\{m_2\}, M_2=\{m_2, m_3\}, \ldots, M_{11}=\{m_2, m_3, \ldots, m_{12}\}$
-We repeat the procedure for other data sources in the domain and then average the results.
-This procedure ensures that each source is at least once in the training and testing datasets.
+For example, in the soccer domain, for source $s_1$ we run experiments 11 times using $M_1=\{m_2\}, M_2=\{m_2, m_3\}, \ldots, M_{11}=\{m_2, m_3, \ldots, m_{12}\}$.
+We repeat the procedure for all sources in the domain and then average the results.
+This \forijcai{procedure} ensures that each source is at least once in the training and testing datasets.
 
@@
 \begin{figure}[!b]
+	\vspace*{-3mm}
 \begin{minipage}[b]{.5\linewidth}
@@
 % karma vs serene vs serene-pats
-We evaluate \serene{} and \serenepats{} against the state-of-the-art system \karma{}.
+We then evaluate \serene{} and \serenepats{} against the state-of-the-art system \karma{}.
 All three systems have access to the same set of matches produced by our semantic labeling model.
@@
 We use default parameters for \karma{} which were shown to yield the best 
-results~\cite{taheriyan2016learning}.
+results\forijcai{~\cite{taheriyan2016learning}}.
 As we can see, \serene{} produces on average the best semantic models in terms 
@@
 recall.
-The t-tests conducted for the obtained results confirm statistical significance of our improvements at the level $p<0.01$
+The t-tests run for the obtained results confirm statistical significance of our improvements at the level $p<0.01$
 %If we consider results separately per each instance and not on average, there 
@@
 Also, we have explored how the systems perform if we manually filter out the unmatched attributes.
-In such scenario \serene{} also yields better solutions than \karma{}, and can often prove optimality of the found solutions.
-This observation provides further evidence towards the validity of our new framework.
+In such scenarios, \serene{} also yields better solutions than \karma{}, and can often prove optimality of the found solutions.
+This observation provides further evidence of the validity of our new framework.
 
@@
 \centering
-\begin{tikzpicture}[scale=0.35]
+\begin{tikzpicture}[scale=0.3]
 \pgfplotsset{
@@
 \end{tikzpicture}
+\vspace*{-3mm}
 \caption{Performance of \serene{} on the museum 
@@
 schemata and ontologies.
-A very comprehensive overview and comparison of existing mapping generation 
-tools based on this approach is given by~\citeasnoun{Pinkel:rodi}
-and~\citeasnoun{Spanos:semweb}.
+\citeasnoun{Pinkel:rodi} and~\citeasnoun{Spanos:semweb} give
+a very comprehensive overview and comparison of existing mapping generation 
+tools based on this approach.
 As examples, there are BootOX~\cite{Jimenez:Bootox}, MIRROR~\cite{Luciano:Mirror} and  ontop~\cite{Fagin:Clio}.
-Crudely speaking, these tools first apply a default direct mapping specified by the W3C.
+Briefly, these tools first apply a default direct mapping specified by the W3C.
 Then, the default ontology is enriched by using explicit and implicit schema constraints.
 Finally, ontology alignment techniques are applied to match the default ontology to the target ontology.
-The main advantage of these systems is the ability to run in a fully automatic setting.
+The main advantage of these systems is that they are fully automatic\forijcai{ the ability to run in a fully automatic setting}.
 Our approach is complementary to them and at its current stage is semi-automatic.
-However, CP offers a convenient framework to incorporate integrity constraints specified either within relational or ontological schema as additional constraints to govern the search for the solution.
+However, CP offers a convenient framework to incorporate integrity constraints specified \forijcai{either} within relational or ontological schema as additional constraints to govern the search for the solution.
 \forijcai{This opens an interesting direction for further research.}
@@
 As in our approach, they decompose the process of mapping into two main stages: semantic labeling and finding relationships between matched semantic labels.
-\citeasnoun{Limaye:Annotating} enrich their data sources by using YAGO.
+\citeasnoun{Limaye:Annotating} enrich their data sources by using YAGO \cite{suchanek2007yago}.
 \citeasnoun{Mulwad:Semantic} extend this approach by leveraging information 
@@
 However, they disregard the attributes which are not matched to the ontology 
-(the so-called \emph{unknown} set of attributes) which are especially abundant 
+(the \forijcai{so-called} \emph{unknown} set of attributes) which are especially abundant 
 on the Web~\cite{Ritze:matching,Pham:semantic}.
-It is clear that we cannot directly speak about similarity for unmatched attributes, since they are rather dissimilar from known semantic types.
+Clearly we cannot speak about similarity for these attributes, since they are rather dissimilar from known semantic types.
 Our approach differs from previous work in that we incorporate an efficient method to handle the \emph{unknown} class, compared to the state-of-the-art approach DSL~\cite{Pham:semantic}.
@@
 \section{Conclusion}
-In this paper we have introduced a new approach\forijcai{, \serene{} (and its extension 
+We have introduced a new approach\forijcai{, \serene{} (and its extension 
 that uses frequent graph patterns, \serenepats{})} to solve the problem of 
 relational-to-ontology schema mapping.
-Our experiments demonstrate that 
+Our experiments show that 
 \serene{} generates on average more consistent semantic models in terms of 
@@
 pattern costs.
-
-Furthermore, our approach is extremely flexible and easy to extend with 
-arbitrary side constraints thanks to the use of CP rather than a specific 
+Furthermore, our approach is highly flexible and easy to extend with 
+arbitrary side constraints thanks to the use of CP instead of a specific 
 heuristic algorithm.

### 2018-01-30 stp/paper_aaai/main.tex
Minor tweaks

@@
 \citeasnoun{Pinkel:rodi} and~\citeasnoun{Spanos:semweb} give
-a very comprehensive overview and comparison of existing mapping generation 
+a comprehensive overview and comparison of existing mapping generation 
 tools based on this approach.
@@
 As in our approach, they decompose the process of mapping into two main stages: semantic labeling and finding relationships between matched semantic labels.
-\citeasnoun{Limaye:Annotating} enrich their data sources by using YAGO \cite{suchanek2007yago}.
+\citeasnoun{Limaye:Annotating} enrich their data sources by using YAGO Knowledge Base (KB)\cite{suchanek2007yago}.
 \citeasnoun{Mulwad:Semantic} extend this approach by leveraging information 
-from Wikitology Knowledge Base (KB).
+from Wikitology KB.
 \citeasnoun{Venetis:Recovering} develop a scalable approach to recover the 

### 2018-01-30 stp/paper_aaai/main.tex
Acronym KR in introduction

@@
 
-Firstly, we build a graph which includes attributes (i.e. columns) from the new
+Firstly, we build a graph which includes attributes
+% (i.e. columns) 
+from the new
 source as well as ontology classes and properties.
@@
 	%\item 
-	a novel modeling framework for the \relonto{} problem that uses ML, KRR and CP techniques;
+	a novel modeling framework for the \relonto{} problem that uses knowledge representation, ML and CP techniques;
 %	\npr{symbolic AI, ontological reasoning, transitive closure}

### 2018-01-30 stp/paper_aaai/main.tex
link to supplementary

--- 2018-01-30 stp/paper_aaai/main.tex
@@
 of whitespaces and other special characters, statistics of 
-values in the column. 
+values in the column\footnote{Full list of features: https://git.io/vN92f (anonymously hosted)}. 
 \forijcai{A full list can be found in Appendix \ref{Ann:SemLab}.}
@@
 \begin{figure}[ht]
+	\vspace*{-3mm}
 \centering \scalebox{0.8}{

### 2018-04-17 stp/paper_aaai/main.tex
Updated abstract

@@
 \begin{abstract}
-The problem of integrating heterogeneous data sources into an ontology is of high 
-relevance in the database field. Several techniques exist to approach this 
-problem. Nonetheless, side constraints on the data integration cannot be easily 
-integrated with these tools and thus the results may be inconsistent. We 
-present a new approach that combines Machine Learning and 
-Constraint Programming techniques, by modeling the data integration problem as 
-a Steiner Tree Problem in a weighted graph. We show that through this approach 
-we can achieve better precision, recall and speed compared to state-of-the-art 
-approaches. We provide a comprehensive set of experiments backing our 
-findings.
+%% REWRITTEN:
+
+The problem of integrating heterogeneous data sources into an ontology is highly relevant in the database field.
+Several techniques exist to approach the problem, but side constraints on the data cannot be easily implemented and thus the results may be inconsistent.
+In this paper we improve previous work by \citeasnoun{taheriyan2016learning} using Machine Learning (ML) to take into account inconsistencies in the data (unmatchable attributes) and encode the problem as a Steiner Tree, for which we use work by \citeasnoun{deuna2016steiner} in Constraint Programming (CP).
+Combining ML and CP achieves state-of-the-art precision, recall and speed, and provides a more flexible framework for variations of the problem.
+
+%% OLD:
+%The problem of integrating heterogeneous data sources into an ontology is of high 
+%relevance in the database field. Several techniques exist to approach this 
+%problem. Nonetheless, side constraints on the data integration cannot be easily 
+%integrated with these tools and thus the results may be inconsistent. We 
+%present a new approach that combines Machine Learning and 
+%Constraint Programming techniques, by modeling the data integration problem as 
+%a Steiner Tree Problem in a weighted graph. We show that through this approach 
+%we can achieve better precision, recall and speed compared to state-of-the-art 
+%approaches. We provide a comprehensive set of experiments backing our 
+%findings.
 \end{abstract}

### 2018-04-24 stp/paper_aaai/main.tex
authors

@@
 /Title (Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping)
-/Author (Submission 1228)
+/Author (Submission)
 /Keywords (Machine Lerning Application, Constraint Programming, Ontology, Relational, Steiner Tree)}
@@
 \title{Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping }
-\author{Submission 1228}
+\author{Diego De U\~na$^1$ , Natalia Ruemelle$^2$, Graeme Gange$^1$, Peter Schachte$^1$ \and Peter J. Stuckey$^{1,2}$\\
+$^1$Department of Computing and Information Systems --- The University of Melbourne\\
+$^2$Data61, CSIRO\\
+diegod1@student.unimelb.edu.au, Natalia Email, \{gkgange,schachte,pstuckey\}@unimelb.edu.au
+}
+
 \maketitle

### 2018-04-24 stp/paper_aaai/main.tex
metadata

@@
 /Title (Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping)
-/Author (Submission)
+/Author (Diego De Una , Natalia Ruemelle, Graeme Gange, Peter Schachte and Peter J. Stuckey)
 /Keywords (Machine Lerning Application, Constraint Programming, Ontology, Relational, Steiner Tree)}

### 2018-04-25 stp/paper_aaai/main.tex
updated info Natalia

--- 2018-04-17 stp/paper_aaai/main.tex
@@
 /Title (Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping)
-/Author (Submission 1228)
+/Author (Diego De Una , Natalia Rummele, Graeme Gange, Peter Schachte and Peter J. Stuckey)
 /Keywords (Machine Lerning Application, Constraint Programming, Ontology, Relational, Steiner Tree)}
@@
 \title{Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping }
-\author{Submission 1228}
+\author{Diego De U\~na$^1$ , Natalia R\"ummele$^2$, Graeme Gange$^1$, Peter Schachte$^1$ \and Peter J. Stuckey$^{1,3}$\\
+$^1$Department of Computing and Information Systems --- The University of Melbourne\\
+$^2$Siemens, Germany ~~~~~
+$^3$Data61, CSIRO, Melbourne, Australia\\
+d.deunagomez@student.unimelb.edu.au, nataliia.ruemmele@siemens.com\\ \{gkgange,schachte,pstuckey\}@unimelb.edu.au
+}
+
 \maketitle
@@
 Also, there may be a considerable number of attributes which have no 
-corresponding property in the ontology (accidentaly or deliberately).
+corresponding property in the ontology (accidentally or deliberately).
 %\ddg{CHECK!}

### 2018-04-25 stp/paper_aaai/main.tex
gottena  bit of space left

@@
 Several techniques exist to approach the problem, but side constraints on the data cannot be easily implemented and thus the results may be inconsistent.
-In this paper we improve previous work by \citeasnoun{taheriyan2016learning} using Machine Learning (ML) to take into account inconsistencies in the data (unmatchable attributes) and encode the problem as a Steiner Tree, for which we use work by \citeasnoun{deuna2016steiner} in Constraint Programming (CP).
+In this paper we improve previous work by \citeasnoun{taheriyan2016learning} using Machine Learning (ML) to take into account inconsistencies in the data (unmatchable attributes) and encode the problem as a variation of the Steiner Tree, for which we use work by \citeasnoun{deuna2016steiner} in Constraint Programming (CP).
 Combining ML and CP achieves state-of-the-art precision, recall and speed, and provides a more flexible framework for variations of the problem.
@@
 
-Following the traditional data integration framework~\cite{doan2012principles}, we decompose the problem into two parts: schema matching and schema mapping.
-Schema matching, which we refer to as \emph{semantic labeling}, finds 
+Following the traditional data integration framework~\cite{doan2012principles}, we decompose the problem into two parts.
+%: schema matching and schema mapping.
+First, \emph{semantic labeling} finds 
 correspondences between attributes from data sources and data nodes of the 
 target ontology.
-In the schema mapping part we want to generate the semantic models of data sources by identifying the connecting paths for the matched data nodes.
+Second, in the \emph{schema mapping} part we want to generate the semantic models of data sources by identifying the connecting paths for the matched data nodes.
 
 An \emph{attribute mapping} function $\phi : \mathcal{A}_s \mapsto 
-\mathcal{D}_m$ is a function which maps the attributes of the source $s$ into the nodes of the semantic model $m$. 
-It can be a partial mapping, meaning that only some of the attributes
-are connected to the nodes of $m$.
-The attribute mapping function addresses the first part of the problem (i.e. the semantic labeling).
+\mathcal{D}_m$ maps the attributes of the source $s$ into the nodes of the semantic model $m$. 
+It can be a partial mapping, (i.e. only some of the attributes
+are connected to the nodes of $m$).
+This function addresses the first part of the problem (i.e. the semantic labeling).
 
@@
 of whitespaces and other special characters, statistics of 
-values in the column\footnote{Full list of features: https://git.io/vN92f (anonymously hosted)}. 
+values in the column. 
 \forijcai{A full list can be found in Appendix \ref{Ann:SemLab}.}
@@
 
-To evaluate our new system \serene{}, we show that its semantic labeling model 
+To evaluate our new system \serene{}\footnote{All code and full list of features available at \url{http://github.com/NICTA/serene-benchmark}}, we show that its semantic labeling model 
 produces more accurate matches for attributes and that the CP formulation leads 

### 2018-04-25 stp/paper_aaai/main.tex
gotten a  bit of space left
Correct bib file and add new results

@@
 \title{Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping }
-\author{Diego De U\~na$^1$ , Natalia R\"ummele$^2$, Graeme Gange$^1$, Peter Schachte$^1$ \and Peter J. Stuckey$^{1,3}$\\
+\author{Diego De U\~na$^1$ , Nataliia R\"ummele$^2$, Graeme Gange$^1$, Peter Schachte$^1$ \and Peter J. Stuckey$^{1,3}$\\
 $^1$Department of Computing and Information Systems --- The University of Melbourne\\
@@
 %: schema matching and schema mapping.
-First, \emph{semantic labeling} finds 
+First, \emph{semantic labeling} \cite{ruemmele2018evaluating} finds 
 correspondences between attributes from data sources and data nodes of the 
@@
 		\end{tabular} 
+		\vspace*{-3em}
 \end{table}
@@
 		}
-%\vspace*{-3mm}
+\vspace*{-3mm}
 \end{table}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[!ht]\small
+  \centering 
+  \vspace*{-0.8em}
+  \caption{Performance with unknowns manually removed% for leave one out strategy.
+  	  \vspace*{-0.8em}}
+  	\label{tab:nounkn}
+  	\scalebox{0.8}{
+  	\begin{tabular}{c|cc|cc} 
+  		\hline
+  		\multirow{2}{*}{Model} & \multicolumn{2}{c|}{Precision} & 
+  		\multicolumn{2}{c}{Recall}\\
+  		 & museum & soccer & museum & soccer\\
+  		\hline
+  		\karma{} &  0.72 & 0.87 & 0.54 & 0.61 \\
+ 		\serene{} & 0.82 & 0.86 & 0.62 & 0.75 \\
+		\serenepats{} & 0.6 & 0.86 & 0.64 & 0.75 \\  		
+  		\hline
+		\end{tabular} 
+		}
+\vspace*{-3mm}
+\end{table}
 
@@
 that does not translate directly into more precise semantic models.
-On average, we have observed that \serene{} yields very good results already 
+On average, \serene{} yields very good results already 
 with the first solution found, and plateaus after the third solution.
-Also, we have explored how the systems perform if we manually filter out the unmatched attributes.
-In such scenarios, \serene{} also yields better solutions than \karma{}, and can often prove optimality of the found solutions.
+In Tab.~\ref{tab:nounkn} we show how the systems perform if we manually remove the unmatched attributes.
+In such scenarios, \serene{} also yields better solutions than \karma{}, especially in terms of recall, and can often prove optimality of the found solutions.
 This observation provides further evidence of the validity of our new framework.
@@
 		\end{tabular} 
-%\vspace*{-3mm}
+\vspace*{-3mm}
 \end{table}
@@
 	\end{tabular}
+	\vspace*{-3mm}
 \end{table}

### 2018-04-25 stp/paper_aaai/main.tex
Fit in 10 pages, taken all reviewers comments int

@@
 /Title (Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping)
-/Author (Diego De Una , Natalia Rummele, Graeme Gange, Peter Schachte and Peter J. Stuckey)
+/Author (Diego De Una , Nataliia Ruemmele, Graeme Gange, Peter Schachte and Peter J. Stuckey)
 /Keywords (Machine Lerning Application, Constraint Programming, Ontology, Relational, Steiner Tree)}
@@
 Automatically integrating heterogeneous data sources is a long standing issue in the database research field and is of high relevance in many real-world 
-domains (see for example \cite{Rahm:2001:SAA:767149.767154,Dhamankar:imap,Taheriyan2013}).
+domains \cite{Rahm:2001:SAA:767149.767154,Dhamankar:imap,Taheriyan2013}.
 
@@
 In this paper we use Machine Learning (ML) techniques and Constraint Programming (CP) to learn mapping rules from previously mapped instances.
-To this end we formulate the Relational-To-Ontology Mapping Problem (\relonto{}) as a Minimum cost Steiner Tree Problem (STP) with side constraints \cite{deuna2016steiner}.
+To this end we formulate the Relational-To-Ontology Mapping Problem (\relonto{}) as a Steiner Tree Problem (STP) with side constraints.
 
@@
 %attributes from the new source as well as ontology classes and properties.
-Secondly, we apply ML techniques to 
-assign costs to its edges. 
-Lastly, we use CP to 
-find a minimum cost Steiner Tree in the graph.
+Secondly, we apply ML techniques to assign costs to its edges, by borrowing ideas from previous work by \citeasnoun{taheriyan2016learning}. 
+Lastly, we use CP to find a minimum cost Steiner Tree in the graph by building a novel CP model and using solving techniques developed by \citeasnoun{deuna2016steiner}.
 The goal is to assign the costs on the edges in such a way that the resulting 
@@
 \begin{figure}[ht]
-	\vspace*{-3mm}
+	\vspace*{-1mm}
 \centering \scalebox{0.8}{
@@
 
-\begin{figure}[ht]
-	\vspace*{-3mm}
+\begin{figure}[t]
+	%\vspace*{-3mm}
 \centering \scalebox{0.8}{
@@
 	\begin{scope}[xshift=5cm]
-\node[att] () at (0,0)  
+\node[att] () at (0,-1)  
 {};  
-\node[text=black,text width=1.5cm] (legend1) at (1.3,0)  
+\node[text=black,text width=1.5cm] (legend1) at (1.3,-1)  
 {\small 
@@
 \label{FIG:inte}
-\vspace{-3mm}
+\vspace{-5mm}
 \end{figure}
@@
 and build a semantic model as usual. 
-To maintain connectedness of $T^\star$, the \emph{unknown} node and one of the other Class nodes in $T^\star$ 
-will 
-both be connected to the \emph{root} node. 
+To maintain connectivity of $T^\star$, the \emph{unknown} node and any  of the other Class nodes in $T^\star$ will both be connected to the \emph{root} node (in the optimal solution only one will be connected to the root).
 Note that if all attributes find a 
@@
 
-We use Boolean 
-variables $c_n,\forall n \in 
-\mathcal{V_O}$, $c_e, \forall e \in	\mathcal{E_O}$ and an array of variables 
-$match$ indexed by the set of attributes of $s^\star$ to represent the tree $T^\star$: $c_n = \mathit{true}$ means 
-that $n \in V^\star$, $c_e = \mathit{true}$ means that $e \in E^\star$ and 
+We use Boolean variables $c_x$ for any node $x \in 
+\mathcal{V_O}$, $c_y$ for any edge $y \in \mathcal{E_O}$ and an array of variables $match$ indexed by the set of attributes of $s^\star$ to represent the tree $T^\star$.
+The semantics of the variables are: $c_x = \mathit{true} \Leftrightarrow x \in V^\star$, $c_y = \mathit{true} \Leftrightarrow y \in E^\star$ and
 $match[a] = d$ (for $a \in \mathcal{A}_{s^\star}$ and $d \in 
@@
 The model is presented below.
-\vspace*{-0.5em}
+\vspace*{-0.3em}
 \begin{flalign}
@@
 $T^\star$ to be a tree defined by the $c_n$ and $c_e$ variables,
-subgraph of $\mathcal{G_O}$%the alignment graph 
+subgraph of $\mathcal{G_O}$ %the alignment graph 
 and of total weight $w_{STP}$. 
@@
 that data node must be in the solution tree, and vice-versa. 
-Eq.~\ref{EQ:matchcost} computes the cost $w_{ADIFF}$ of the matches.
+Eq.~\ref{EQ:matchcost} computes the cost $w_{ADIFF}$ of the selected match edges in $\mathcal{M}^{s^\star}_\mathcal{O}$.
 Eq.~\ref{EQ:patt} indicates that a pattern is used if and only if all its edges are selected in the tree. 
@@
 Eq. \ref{EQ:unk} ensures that if the \emph{unknown} class node is used, then it 
-is connected to \emph{root}.
+is connected to \emph{root} through the edge $(\mathit{unknown},\mathit{root})$.
 Notice there is no further requirement for unmatched attributes, as the 
-$unk_i$ nodes behave like normal data nodes, and the connectedness 
-requirement will make sure that \emph{root} is connected to the rest of the 
+$unk_i$ nodes behave like normal data nodes, and the connectivity 
+requirement ensures that \emph{root} is connected to the rest of the 
 tree (i.e. the semantic model).
@@
 
-To evaluate our new system \serene{}\footnote{All code and full list of features available at \url{http://github.com/NICTA/serene-benchmark}}, we show that its semantic labeling model 
+To evaluate our new system \serene{}\footnote{ \url{http://github.com/NICTA/serene-benchmark}}, we show that its semantic labeling model 
 produces more accurate matches for attributes and that the CP formulation leads 
@@
   \centering 
-  \vspace*{-0.8em}
+  %\vspace*{-0.9em}
   \caption{Average performance of semantic labeling models% for leave one out strategy.
@@
 };
+\legend{\karma{},\serene{},\serenepats{}}
 
@@
 \end{tikzpicture}
+\vspace*{-1mm}
 \subcaption{Precision (museum)}\label{fig:museumprec}
@@
 		    ymajorgrids=true,
-		    grid style=dashed,
-		    		    style = {font=\huge},
-		    legend style={at={(0.5,1.1)},anchor=south, legend columns=-1}
+		    grid style=dashed, legend pos=south east,
+		    		    style = {font=\huge}
+		    %legend style={at={(0.5,1.1)},anchor=south, legend columns=-1}
 		]
@@
 };
-		 %\legend{karma,serene,serene-pats}
-
+\legend{\karma{},\serene{},\serenepats{}}
 		\end{axis}
 	\end{tikzpicture}
+	\vspace*{-1mm}
 \subcaption{Recall (museum)}\label{fig:museumrec}
@@
 		    ymajorgrids=true,
-		    grid style=dashed,
+		    grid style=dashed, legend pos=south east,
 		    		    		    style = {font=\huge},
@@
 		    };
-		%\legend{karma,serene,serene-pats}
+		    \legend{\karma{},\serene{},\serenepats{}}
 
@@
 \end{tikzpicture}
+\vspace*{-1mm}
 \subcaption{Precision (soccer)}\label{fig:soccerprec}
@@
 	\end{tikzpicture}
+	\vspace*{-1mm}
 \subcaption{Recall (soccer)}\label{fig:soccerrec}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In Tab.~\ref{tab:nounkn} we show how the systems perform if we manually remove the unmatched attributes.
+In such scenarios, \serene{} also yields better solutions than \karma{}, especially in terms of recall, and can often prove optimality of the found solutions.
+This observation provides further evidence of the validity of our new framework.  
 \begin{table}[!ht]\small
   \centering 
-  \vspace*{-0.8em}
+  \vspace*{-0.6em}
   \caption{Performance with unknowns manually removed% for leave one out strategy.
@@
 		}
-\vspace*{-3mm}
+\vspace*{-2mm}
 \end{table}
@@
 with the first solution found, and plateaus after the third solution.
-In Tab.~\ref{tab:nounkn} we show how the systems perform if we manually remove the unmatched attributes.
-In such scenarios, \serene{} also yields better solutions than \karma{}, especially in terms of recall, and can often prove optimality of the found solutions.
-This observation provides further evidence of the validity of our new framework.
 
@@
 domain.}\label{fig:loo}
-\vspace{-3mm}
+\vspace{-5mm}
 \end{figure}

### 2018-04-26 stp/paper/commondefs.tex
Rename folder, fix some bib items, correct code link, update readme

--- 2017-08-31 stp/paper_aaai/commondefs.tex
@@
-\definecolor{lightgray}{rgb}{0.97, 0.97, 0.97}
+\definecolor{lightgray}{rgb}{0.98, 0.98, 0.98}
 %\definecolor{lightgray}{rgb}{0.83, 0.83, 0.83}
@@
 % minizinc keyworkds
-ann, annotation, any, array, assert, bool, constraint, else, endif, enum, float, forall, function,
+any, array, assert, bool, constraint, else, endif, enum, float, forall, 
+function,
 if, in, include, int, list, of, op, output, minimize, maximize, par, predicate, record, set,
-solve, string, test, then, tuple, type, var, where,
+solve, string, test, then, tuple, type, where,
 % minizinc functions
@@
 sensitive=false, % are the keywords case sensitive
-morecomment=[l][\bfseries\color{orange}]{::},
-morecomment=[l][\em\color{green}]{\%},
+morecomment=[l][\bfseries\color{cyan!90!black}]{::},
+morecomment=[l][\em\color{green!50!black}]{\%},
 %morecomment=[s]{/*}{*/},
@@
   tabsize=2,                       % sets default tabsize to 2 spaces
-  title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
+  title=\lstname,                   % show the filename of files included with 
+  %\lstinputlisting; also try caption instead of title
+  % keyword highlighting
+      classoffset=1, % starting new class
+      morekeywords={var},
+      otherkeywords={var},
+      keywordstyle=\itshape\bfseries\color{red!80!black},
+      classoffset=0,
+      classoffset=2, % starting new class
+      morekeywords={ann},
+      otherkeywords={ann},
+      keywordstyle=\bfseries\color{cyan!80!black},
+      classoffset=0
 }

### 2018-04-26 stp/paper/main.tex
Rename folder, fix some bib items, correct code link, update readme

--- 2018-04-25 stp/paper_aaai/main.tex
@@
 
-To evaluate our new system \serene{}\footnote{ \url{http://github.com/NICTA/serene-benchmark}}, we show that its semantic labeling model 
+To evaluate our new system \serene{}\footnote{ \url{http://github.com/NICTA/serene-python-client/tree/stp/stp}}, we show that its semantic labeling model 
 produces more accurate matches for attributes and that the CP formulation leads 

### 2018-04-26 stp/paper/main.tex
Fixed results
extra room simply by changint eh url format

--- 2018-04-25 stp/paper_aaai/main.tex
@@
 
-To evaluate our new system \serene{}\footnote{ \url{http://github.com/NICTA/serene-benchmark}}, we show that its semantic labeling model 
+To evaluate our new system \serene{}\footnote{ http://github.com/NICTA/serene-python-client/tree/stp/stp}, we show that its semantic labeling model 
 produces more accurate matches for attributes and that the CP formulation leads 
@@
   		\hline
-  		\karma{} &  0.72 & 0.87 & 0.54 & 0.61 \\
- 		\serene{} & 0.82 & 0.86 & 0.62 & 0.75 \\
+  		\karma{} &  0.72 & 0.81 & 0.54 & 0.64 \\
+ 		\serene{} & 0.82 & 0.85 & 0.62 & 0.75 \\
 		\serenepats{} & 0.6 & 0.86 & 0.64 & 0.75 \\  		

### 2018-04-29 stp/paper/main.tex
Fixed results

--- 2018-04-26 stp/paper/main.tex
@@
 
-In Tab.~\ref{tab:nounkn} we show how the systems perform if we manually remove the unmatched attributes.
+In Tab.~\ref{tab:nounkn} we show how the systems perform if we manually remove the unmatched attributes for the leave-one-out setting.
 In such scenarios, \serene{} also yields better solutions than \karma{}, especially in terms of recall, and can often prove optimality of the found solutions.
-This observation provides further evidence of the validity of our new framework.  
+%This observation provides further evidence of the validity of our new framework.
+The first solutions found by \serenepats{} tend to be bigger than those of \serene{}: hence the precision suffers, but the recall is better.
+We have further observed that given enough time \serenepats{} finds much better solutions both in precision and recall.
+
 \begin{table}[!ht]\small

### 2018-04-29 stp/paper/main.tex

@@
 
-To evaluate our new system \serene{}\footnote{ \url{http://github.com/NICTA/serene-python-client/tree/stp/stp}}, we show that its semantic labeling model 
+To evaluate our new system \serene{}\footnote{ http://github.com/NICTA/serene-python-client/tree/stp/stp}, we show that its semantic labeling model 
 produces more accurate matches for attributes and that the CP formulation leads 

### 2018-04-29 stp/paper/main.tex
Added one more citation

--- 2018-04-29 stp/paper/main.tex
@@
 incorporated features which are derived directly from attribute values and are 
-not based on the notion of similarity.
+not based on the notion of similarity~\cite{ruemmele2018evaluating}.
 %\npr{Good enough explanation?}

### 2018-04-29 stp/paper/main.tex
last change

@@
 In such scenarios, \serene{} also yields better solutions than \karma{}, especially in terms of recall, and can often prove optimality of the found solutions.
-%This observation provides further evidence of the validity of our new framework.
-The first solutions found by \serenepats{} tend to be bigger than those of \serene{}: hence the precision suffers, but the recall is better.
-We have further observed that given enough time \serenepats{} finds much better solutions both in precision and recall.
+The first solutions found by \serenepats{} tend to be bigger than those of \serene{}, hence the precision suffers but the recall is better.
+We have also observed that given enough time \serenepats{} finds much better solutions both in precision and recall.
+These observations provide further evidence of the validity of our framework.
 
